\documentclass[a4paper,10pt]{book}
\parindent=0pt
\usepackage{fullpage}
\frenchspacing
\usepackage{parskip}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{nameref}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage[setpagesize=false,colorlinks=true,linkcolor=red,urlcolor=blue,pdftitle={The Stubborn Skill-Grinder In A Time Loop},pdfauthor={AUTHOR}]{hyperref}
\author{AUTHOR}
\title{The Stubborn Skill-Grinder In A Time Loop}
\begin{document}
\selectlanguage{english}
\maketitle
\section*{Chapter 1 - A Warrior\u0027s Death And A Looper\u0027s Beginning}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 1 - A Warrior\u0027s Death And A Looper\u0027s Beginning}%
\par
A keening wail ringing in the night sky awoke him.\par
Orodan was a light sleeper in general, but the shrill shriek of a harpy, even if distant was enough to wake most people.\par
The bloody birds were a public menace. Living in one of the poorest neighborhoods on the outskirts of the capital didn’t help of course. No archers or battlemages around to shoot the damn things down. Sometimes he found himself wishing the griffin riders did a fly-over and cleaned up one day.\par
Worst of all, the stupid things hunted in flocks, and their flight path to and from their hunting grounds was above his district of Ogdenborough. Taken in tandem with the fact that they hunted at night?\par
No wonder property values in Ogdenborough were so abysmal.\par
Orodan still held onto his long term dream of eventually becoming a Sword Adept, and when that day came he’d march into their dens and kill every single harpy around the capital. Nobody would be bothered then.\par
The moon still hung in the sky and the sun had yet to show its face, and as such Orodan muttered a curse for his lost sleep and decided to freshen up and eat. A stale loaf of bread and two pieces of jerky later, he decided to begin his self-imposed habit of cleaning the house and picked up a dirty rag.\par
He always stubbornly cleaned every inch before he had to report to the barracks.\par
His derelict bedside table was wiped down, the bed was made, the rugs were taken outside and thoroughly beaten to rid them of dust and debris and even the rocky footpath leading to his hovel was broomed to sweep all loose rocks to the side.\par
He then wet a separate rag at the nearby well and thoroughly scrubbed the floors as the finishing touch before he felt satisfied that the job was done.\par
\textbf{[Cleaning 23 → Cleaning 24]}\par
Well that was long overdue. Two weeks since his last increase.\par
The other militia cracked jokes at him for being a Cleaning Initiate, but at this rate he’d cross the threshold of 30 and earn the title of Cleaning Apprentice before the year was up.\par
He had no plans on joining a noble’s house staff, but unlike most of his fellows in the town militia he was an orphan and was a ward of the Lady Sashwari House for the Wayward till he was 14 and deemed old enough to fend for himself and hold an independent job.\par
His current hovel in Ogdenborough was the only affordable option he and his caretakers at the orphanage could fit into the budget once he came of age. It was also the only place that would accept him on the budget he had given his lengthy record of fighting and delinquency as a child.\par
He sighed and mentally called forth his Status Screen.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Sword Apprentice}\par
\textbf{Skills: Sword Mastery 34 (Apprentice), Cleaning 24 (Initiate), Shield Mastery 23 (Initiate), Physical Fitness 21 (Initiate), Unarmed Combat Mastery 19 (Initiate), Laboring 17 (Initiate), Club Mastery 15 (Initiate), Sprinting 14 (Initiate), Combat Mastery 11 (Initiate), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate)]}\par
Orodan would say it was halfway decent, and given his upbringing it could almost be seen as good.\par
In fact, he’d outworked and gotten ahead of every other child from the orphanage. A Sword Mastery of 34 by the time he was 17 was decent enough to barely meet the qualifications for a bottom of the barrel martial academy if he had the means. That and his determination to work hard enough to reach 20 in Physical Fitness meant that the Volarbury County Militia was willing to take him as a recruit once he did well in their entrance examination last year.\par
Serving with them, he hoped to reach at least the Adept-level in Sword Mastery over the course of his life.\par
Fighting was all he was good at, but, he could always fall back on his Laboring skill if nothing in his life worked out well. But Orodan’s ambitions were not that low. And he enjoyed fighting too much to do anything else for overly long.\par
He mentally waved his Status away and decided to continue his routine.\par
\par
After an hour of running laps in a loop through the neighbourhood leading back to his home he noticed the beginnings of the sun start to rise so he concluded his training and came to a stop in front of the construction site at 4 Ale Road.\par
Old Man Hannegan was sitting aloft the driver’s seat of his mule drawn cart, the cargo was of course stacks upon stacks of lumber. Albeit of different coloration and wood species than the delivery of yesterday Orodan noticed.\par
“Morning Mr. Hannegan… I notice the wood’s looking different today?” Orodan asked as he began unloading the thick stacks of lumber, four at a time, onto the empty pallets on the ground. Volunteering to assist the man every morning was also part of his self-imposed training.\par
“Mornin’ kid, the supplier and I had a minor argument is all. Don’t you worry, the house’ll get built all the same.”\par
Getting built and getting built properly were two different things, Orodan thought. But he kept his thoughts on the noticeably cheaper lumber to himself if the old man didn’t want to talk.\par
Local businesses and construction projects in Ogdenborough often faced difficulties like this. It wasn’t one of the poorest places in the republic without reason.\par
“I see…” Orodan replied as he continued placing the lumber down onto the pallets with a decent amount of exertion.\par
Two stacks of thick lumber per arm for a total of four. That was his current optimal exertion point, which was a great improvement from when his Physical Fitness was at 18 a year ago when he first started helping Old Man Hannegan and could only move two stacks at a time.\par
At 21 Physical Fitness he attempted it and could successfully lift the full cart, with all the wood inside above his head momentarily with maximal effort, albeit he’d have to drop it momentarily after.\par
Perhaps reaching even 40 over the course of his life was not impossible.\par
With a grunt of exertion he finished unloading the last of the lumber onto the pallets and made some further small talk with the old delivery driver.\par
Before he knew it the morning officially started as the unique sound of the county dawn bell chiming went out across all of Ogdenborough.\par
There was one bell tower for all of Volarbury County and Orodan always wondered what qualifications the mages in charge of magically amplifying the sound to reach the entire county had to possess. The noise was neither louder in Trumbetton where the tower was situated nor was it any quieter a few hour’s horse ride away in Ogdenborough at the farthest reachest of the county.\par
He cut his own musings short as he began to make way back to his hovel to freshen himself after his exertions. His shift at the barracks started an hour after the bell and he already saw one of the night shift patrols winding down and making their way back towards the local barracks at the edge of Ogdenborough.\par
\par
“Botterson?”\par
“Sergeant!”\par
“Bistrid?”\par
“Corporal…” came a resentful voice.\par
“Come again Bistrid?” he asked in a low and threatening tone.\par
“Sergeant!” she corrected herself.\par
“Wainwright?”\par
“Sergeant!” Orodan responded back with vigor.\par
“Edrosic?”\par
“Sergeant!”\par
And so on roll-call went until Sergeant Woodgard reached the end of Orodan’s platoon of fifty and twenty-five more extra detail troops that had been ordered over from their days off just for the occasion. The recently promoted man carried himself a bit more severely than usual and it was apparent today. Orodan thought it was understandable given the upcoming public event today and how much more work it would entail, plenty of opportunity for him to look bad in his new position.\par
“Alright… it’s Liberation Day today and you all know what that means,” the Sergeant stated while sweeping his gaze across the room. “No pre-shift training and drills today. We’re expecting drunks, looters, fights and maybe even a body or two. So I want double patrols, we have extra hands on deck and I want a show of presence and force out in the main roads and the main squares, particularly Eversong Plaza and the tavern. I’m sure every orphan, urchin and no-good scumbag will be gathering to pick easy targets today. Additionally, there’s been rumours that the Council in the Capital will be making an announcement at noon, so we need to maintain order.”\par
Orodan heard what the Sergeant was saying but disagreed. He was an orphan, and he knew growing up that Eversong Plaza was the territory of House Argon and their people.\par
A noble house with criminal connections was far deadlier than any street gang could ever hope to be. No orphan or urchin would dare cause trouble around that area if they wanted to stay in one piece. Well, no orphan or urchin that wasn’t Orodan. He had quite the reckless delinquent character growing up. The local barracks of the County Militia in Ogdenborough, while not under the purview of House Argon, knew better than to pry into the affairs of noble houses.\par
Even Orodan himself, as brash and headstrong of a youth as he was growing up still knew to not push things too far whenever he challenged their guards to a fight. He knew they were humouring him and could easily kill a young boy if they so desired.\par
That the man was asking them to patrol the area meant that House Argon allowed, and perhaps even asked for their presence in the area. For what? Such things were above the paygrade of a mere private such as Orodan of course.\par
“The mounted unit from the Trumbetton barracks will also be present and running patrols in the area. For everyone’s sakes, do not get in their way or bother them, if you see them take over a situation use your amulets to call it out so we remain operationally aware. And if they require support, assist them. They might even have a griffin rider or two doing fly-overs.”\par
Not all Volarbury County Militia barracks were equal. The Trumbetton barracks where Sergeant Woodgard’s predecessor was transferred to for example, was the center of the county and consequently the militia barracks there was the headquarters and had all manner of specialized units such as investigations, the Elite response unit, a mounted unit and others. Other barracks also had specialized units; alas, the barracks in Ogdenborough was one of two in the county that had nothing besides regular militia.\par
For the mounted unit from Trumbetton to be coming in and doing patrols meant that again, the going-ons behind the scenes were above Orodan’s paygrade.\par
“Now for the assignments, Botterson, I want you and your troop doing patrols of the road leading in from Exerston County, leave carriage and caravan searches to the mounted unit, just do patrols. Sahar, your troop’s on relief duties, reinforce and relieve as needed. Bistrid… you’re doing Eversong Plaza, your troop’s to stay posted there at all times, keep the riff-raff in line and support House Argon in whatever they might need. Vargorias…”\par
Orodan tuned out the rest of Sergeant Woodgard’s orders as he focused on the fact that Corporal Bistrid’s troop, which included him, would be posted at the plaza itself. The militia rarely ever saw the plaza outside of special occasions as it was otherwise primarily the domain of House Argon.\par
Although it stabbed at Orodan’s principles, the militia and by extension himself were essentially ordered to ignore House Argon’s activities, no matter how shady they might be. And it looked like today was going to be more of the same.\par
\par
Eversong Plaza had Mount Castarian looming above it. In fact, Ogdenborough itself was a town that was landlocked against the mountain, probably a part of what made the town so poor and limited any expansion opportunities.\par
That the town existed at all in such a location was likely due to House Argon running Eversong Plaza and the Castarian’s Boot, that tavern that was built into the side of the mountain and always had strange traffic coming in and out. It was a popular theory among the locals of Ogdenborough that the tavern was where House Argon ran a smuggling operation via tunnels they mined through the mountain, or where they catered to wealthy clientele with forbidden desires.\par
Of course, nobody could or would dare to pry, especially if a noble house was involved. Plenty of strange and powerful individuals could be seen entering and exiting the tavern from time to time, and the numbers going in and coming out often didn’t match up. It went without saying that entering the tavern was via invitation only, and no local had ever set foot inside.\par
Of course, a town and economy sprung up around the tavern to service its various needs even if none of the locals, including the County Militia, were ever allowed in.\par
Orodan stood on the perimeter of the plaza alongside his assigned partner Parthus Edrosic, with them monitoring foot traffic into the plaza. Most inbound foot traffic made its way to the various stalls set up within Eversong Plaza. While the Tavern was off-limits to the public, the stalls outside in the plaza were not.\par
“Hey Orodan… you think those Argon goons would care if I took something from one of the stalls?” A question which made Orodan give his partner an unimpressed and severe look.\par
“If you value your limbs you won’t even think about it. All of their guards are near the Adept level in a martial skill.” Orodan replied, speaking from experience and many beatings received as a younger boy and warning Edrosic who was newer to the County Militia than him and was consequently working the Plaza for the first time in his career. Plus, given how quickly he saw the rare thieving attempt get caught during his orphan rat days, he was almost certain they had people with perception type skills keeping watch too.\par
Although Orodan was seventeen years old and younger than the twenty year old Edrosic, the man didn’t have the same rough upbringing and street sense the orphan Orodan did as he was the son of a carpenter and a seamstress and simply joined the County Militia to have a stable paying job and maybe eventually move to a nicer town after putting in some time and work.\par
Furthermore, the differences in their work ethic and talent were apparent. Orodan was probably the second strongest militia member in the local barracks after Sergeant Woodgard. Which wasn’t saying much given they were all cannon fodder militia members with not an Adept among them. But it was still a fact worth mentioning that Orodan could give Edrosic a beating if it came to it.\par
“Alright, alright! I don’t know the plaza and the shadier side of town like you do.” Edrosic amended.\par
“Well if you’re going to think about stealing, at least have the power to outrun the enforcers,” Orodan fired back.\par
“We can’t all be battle-junkie masochists like you Orodan, you’re a certified weirdo, you’ll fit right in at Trumbetton when you get transferred one day.”\par
Orodan felt annoyed at the description of his character, but couldn’t exactly deny it. He was a conflict-seeking person, even when younger. The meaner kids at the orphanage certainly learned it the hard way within a week of him being registered.\par
Orodan simply grunted and decided to focus on surveilling foot traffic.\par
Time passed and soon it was high noon, and as forewarned the regal trumpets of the Spire of Karilsgard, the tallest tower of the Capital, magically resounded everywhere to herald an announcement. And soon, a melodious voice, one that felt soothing and uplifting despite being projected from a far distance away in the capital, began speaking.\par
\textbf{“To the brave and hard-working citizens of the glorious Republic of Aden, I High-Burgher Sarvaan Ilsuan Arslan, leader of your elected council speak to you today in celebration and commemoration of the one hundred and twentieth anniversary of our liberation from the Novarrian Empire.”}\par
At the magically projected announcement, everyone in the plaza began cheering and hollering, even Orodan himself felt a fire stir in his heart and despite his duties demanding he keep the crowd in check, found himself wanting to join them in their revelry. However he tried his best to stay focused and instead got back to keeping watch and noticed a group of ten hooded and masked individuals approaching the plaza.\par
\textbf{“On this auspicious day I wish to thank you, the citizens of our Republic, for your hard work, courage and sacrifices that have made our way of life and freedom from the tyrannical Novarrians possible.”}\par
Orodan tapped Edrosic, who was far too enraptured by the announcement, on the shoulder as he approached the suspicious group.\par
“Hold there, I’ll have to ask what business brings you this way. You wear no House Argon insignia nor are you entering through their guest entrance.” Orodan asked, and he had an uncomfortable feeling in his gut as he asked and decided to rest his hand on the hilt of the sword at his hip.The story has been stolen; if detected on Amazon, report the violation.\par
“Ah apologies, we have business with House Argon, I’d strongly recommend you get out of the way militia man.” The man, the seeming leader of the group of ten hooded individuals, replied.\par
Although his words came across as rather brash and arrogant, this was a world where power determined one’s actions. Orodan found himself wondering if this individual and group weren’t secretly at the Adept level to be talking like this. Times like this he wished he had access to the Observe skill that all nobles and their guards knew, which allowed one to view another's title and name.\par
Orodan looked around to see none of the rest of his troop present, although he felt some hope at seeing a group of five members of the mounted unit rushing their way, including the Argon enforcers.\par
Furthermore he saw griffin riders flying their way. But as they got closer he realized they weren’t the standard brown feathered with harnesses that the mounted unit rode, but instead silvered with plate armor covering them.\par
And then a bright glow emanated from the lead griffin rider, and something large and bright flew towards the plaza.\par
\textbf{“Unfortunately, freedom never comes freely. And sometimes maintaining freedom involves rooting out the poison from within. So I use this auspicious day to call upon my fellow citizens of our Republic of Aden, to mobilize, to gather together, for freedom comes at a price and sometimes it involves facing enemies both within and without.”}\par
As soon as the announcement’s final words finished, the weapons of every member of the suspiciously hooded and masked group were drawn.\par
And carnage began.\par
The first thing Orodan saw was an Argon enforcer’s head go flying across his vision, an Adept… killed like a chicken. And the second thing Orodan saw was the bright projectile fired by the griffin rider reach the tavern and collide with a shimmering magic shield he didn’t know existed, and the world turned orange and lit up in flame.\par
Years of instinct saved him as he used every ounce of his Physical Fitness to furiously leap a dozen metres out of the way in one jump and immediately dive for cover behind a stall.\par
The shockwave from the blast helped him gain even more distance than he could himself, and he hit the ground dozens of metres away, the wind knocked out of him by the explosive shockwave.\par
“County Militia! We’re under attack! Face the attackers!” Ordered a massive higher ranking House Argon enforcer who Orodan had not seen before, but who was now clashing against the leader of the attackers in what was clearly a battle at the Elite Realm due to the shockwaves shattering the nearby ground with their regular attacks and pushing Orodan back to the point where he was struggling to hold onto solid ground.\par
“Hmmph! Tricking the local bumpkin militia into being your cannon fodder are you, traitor?” the leader of the attackers asked as his spear moved about in frightening speeds with enchanting motions while clashing against the war hammer of the Argon Elite. “Hear me, House Argon are traitors to the Republic, stay out of this fight or suffer death!”\par
Hearing that, Orodan had no problem with complying. The fight was clearly above him and although he was a fighter who wouldn’t back down, he also knew when he was beyond outmatched.\par
“Hmmph! Northmen! Come out and do some work! Delay them as long as possible!” The Argon Elite roared, and on command the still intact tavern doors opened and dozens of fur-clad warriors stormed out of the building wielding an assortment of weapons, shouting savage war cries and heading right towards Orodan and Edrosic.\par
Guzuharan barbarians! Sworn enemies of the Republic!\par
Orodan himself was found as a crying infant amongst the blood and bodies of a Guzuhar raid upon a caravan traveling the coast. Both his parents had been killed that day and the trajectory of his life had been changed forever.\par
Orodan’s blood boiled for a fight, and on principle he refused to back down in the face of the Northmen scum.\par
Orodan immediately drew his sword and shield for the first time and took a stance beside the unknown attackers. He didn’t understand the first thing about this conflict, but hearing the brief bits that he did and given the fact that House Argon was siding with filthy barbarians made the decision for him. The masked figures were loyalists to the Republic.\par
Orodan was merely at the Apprentice level of his swordsmanship, but his training, his desire to seek challenges and improve, his upbringing scrounging for scraps as an orphan, and his blood which boiled hot for a fight against the scum responsible for his misfortune all came together and sang to him and he stood beside these loyalists and prepared to receive the charge of these barbarous raiders from across the sea.\par
Above him the mages mounted atop the silvered griffins were casting luminous and deadly looking spells at the tavern’s barrier. And behind him, Parthus Edrosic and the rest of the Volarbury County Militia including the vaunted mounted unit… had all turned tail and fled.\par
A dozen raiders on the front rank were killed on the spot by the loyalists who were all at least Adept level. But some survived, and Orodan himself received one of them in the form of a charging overhead blow from an Apprentice-level Northman. The axe which bit into the top of his shield then attempted to pull it away from him.\par
Of course, the beginner habit of hiding behind the shield was one of the first things drilled out of new militia, and Orodan grew up fighting and sharpening his combat instincts even before he joined them.\par
Orodan twisted his shield at an angle which exposed the savage’s arm, and with a swift burst of strength, sent a cut right towards his arm.\par
The arm came flying off, and a follow-up stroke had the Guzuharan gurgling blood as his throat was sliced through. He had killed another street rat during his formative years; over a piece of stale jerky too. But killing a man in head-to-head battle was different.\par
It felt rewarding.\par
Five more barbarians rushed to charge at Orodan, seeking revenge for the death of their comrade, and he realized that death approached; but before they could reach him they were slain by the incredible movements of one of the Adept-level loyalists who wielded a sword and shield like Orodan himself did, but with a fervor and skill Orodan could only strive for.\par
“Kid! You’ll die by daring to fight here alongside us! I respect your guts and warrior spirit, but leave now!” One of the Adept level loyalists shouted at Orodan from behind his shield, but before he could continue admonishing him, the air trembled, a shockwave blew Orodan backwards and a massive great axe split the man and his shield in two.\par
His saviour, an Adept, killed in a single blow. Just who could do such a thing?\par
The killer of Orodan’s protector was the single largest man Orodan had ever seen, he was bigger than even the largest orcs Orodan had heard of, and was approaching the size of an ogre.\par
“Bah… you send the whelps out and they all die like cockroaches. Not a single shred of talent among the new group of unblooded. What are the youth coming to these days… Guzuhar blood can’t be allowed to be this weak.” The ogre barbarian derisively spoke. As he did a furious loyalist wielding a rapier charged him with murder in her every movement.\par
“I’ll make sure you die for that!” a murderous female voice screamed as she launched a blitz of attacks Orodan couldn’t even keep up with. Unfortunately, the ogre-barbarian wasn’t strained at all.\par
And in more bad news, behind the now dead line of initial barbarians came another group of three savages, and Orodan raised his shield and sword as the first one screamed like a madman, raised his axe in the air and threw himself at him.\par
A diagonal side-step followed by a shield bash threw the savage off balance allowing Orodan’s subsequent stab to put a stop to him.\par
The other two reached him at the same time however.\par
Fighting two opponents on the same level as himself at the same time was a lopsided affair to begin with. But so what if it was two-on-one? Orodan’s heart roared for blood and battle and he would show these Northmen what real ferocity was.\par
He took one of the two aback with how crazed his zeal for battle was. Orodan roared, swung, hacked, kicked, punched and bashed. And while he gave as good as he got, unfortunately the regular rank and file of the militia like himself were provided no armor.\par
A deep cut to his own thigh was exchanged for a mad thrust which ran the hesitant Northman through, and the sword he received through his own shoulder was reciprocated by a frenzied overhead chop that cut through the barbarian’s helmet and split the foe’s skull in half.\par
He took lethal wounds, but dealt out fatal wounds of his own. And at the end, while he would eventually die… the two Apprentice level Guzahar savages he fought lay dead at his feet first. His bloodlust and battle spirit having proven too much for them.\par
\textbf{[Sword Mastery 34 → Sword Mastery 35]}\par
\textbf{[Shield Mastery 23 → Shield Mastery 24]}\par
\textbf{[Unarmed Combat Mastery 19 → Unarmed Combat Mastery 20]}\par
\textbf{[Combat Mastery 11 → Combat Mastery 14]}\par
\textbf{[Agathor, God of War, smiles upon you]}\par
\textbf{[Received Blessing → Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
He was too preoccupied with battle-lust and his own impending end to care overmuch for the messages.\par
And as he drew his final breaths he used the last of his body’s strength to rush at the unprotected back of the ogre-barbarian.\par
He struck with his all… and the blade bounced off the monster’s hide.\par
The massive man turned around to find what had tickled his back and was surprised.\par
“Three to fuckin’ one… and they still couldn’t kill one damn Adenian? Now this is what a warrior should fight like!” the Ogre-man exclaimed while casually slapping away the rapier-Adept he was playing around with, sending her flying through a nearby house dozens of metres away. “A shame that you’re in front of me and on the wrong side, you’d make a good warrior.”\par
And the last thing Orodan saw was his vision flipping upside down over and over.\par
\textbf{[Title Gained: One Who Has Experienced Death]}\par
\par
A keening wail ringing in the night sky awoke him\par
What?\par
“What the ever loving f-”\par
\textbf{[Quest System Activated]}\par
\textbf{[Quest Bestowed → Battle of Ogdenborough - Defeat the Novarrians and their allies as they attempt to activate and commandeer the ancient war machine beneathe Mount Castarian]}\par
Orodan believed he was dreaming. Genuinely.\par
Quests. Not what the word meant in common language, but actual Quests as granted by the world. Many people throughout history claimed to have received Quests, but only a select few could truly say they had received a Quest and completed it. The last known Quest bearer being the founder of the Republic a hundred and twenty years ago.\par
And now he… Orodan Wainwright, a meager militiaman in Volarbury County, was receiving a Quest from the world?\par
But most importantly… what had just happened?\par
The last thing Orodan remembered was losing all feeling and his vision tumbling almost as though he was sent flying through the air. He was almost certain he had died in battle. Even if that hulking Guzuhar didn’t kill him, the many lethal injuries he took during the fighting certainly would have.\par
And yet, here he was back in his bed within the hovel at 13 Briar Court in Ogdenborough.\par
It made no sense. He needed answers and he needed them now. If he truly went back in time, did this mean the Gods had sent him back? Perhaps this was tied to the Quest he received?\par
He mentally summoned his Status before him.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Sword Apprentice}\par
\textbf{Available Titles: One Who Has Experienced Death}\par
\textbf{Skills: Sword Mastery 35 (Apprentice), Shield Mastery 24 (Initiate), Cleaning 24 (Initiate), Physical Fitness 21 (Initiate), Unarmed Combat Mastery 20 (Initiate), Laboring 17 (Initiate), Club Mastery 15 (Initiate), Combat Mastery 14 (Initiate), Sprinting 14 (Initiate), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate)}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
As he looked it over Orodan was certain everything that had transpired prior was very real. For one, his newly available title, which he would not be displaying, was the first bit of evidence. For another, many of his skills were higher than they were, and especially Combat Mastery was at a whopping 14 instead of at 11 like it was previously.\par
Did fighting in life and death battles increase skill gains that much?\par
And most importantly… a Blessing!\par
Maybe one in a thousand people received a Blessing in their lifetimes, and although most Blessings were minor, they still guaranteed those who got them a good life.\par
Orodan’s life wasn’t bad. True, he had a rough upbringing, but his hard work had gotten him somewhere in life. Even though he was a private in the Militia, Sergeant Woodgard and his predecessor before him had both taken him aside and told him that a transfer to Trumbetton was coming up for him in the near future due to his talent and work ethic, with a spot on the mounted unit being a real possibility once he started approaching the Adept level.\par
But for him to now have a Blessing as well? He immediately set about his usual routine with a furious pace as he wanted to get it done with as fast as possible so he could visit the nearest Temple in the town of Scarmorrow.\par
Breakfast was practically inhaled, the house was cleaned with such speed and effort that Orodan found himself almost breathing fast at how hard he pushed himself, and the run and subsequent assisting of Old Man Hannegan was blazed through with little to no time for small talk.\par
If Old Man Hannegan was surprised or curious about Orodan’s sudden urgency, he didn’t mention it.\par
With enough time to spare, Orodan practically sprinted the whole way for the Temple in Scarmorrow and arrived before the ringing of the county’s dawn bell.\par
Temples to the Gods were commonplace throughout the continent of Inuan; and while there were minor variations in the pantheons across geographical and national lines, most humans on Inuan held faith in and communed with the Prime Five.\par
At this time the Temple wasn’t too busy. The dawn bell had yet to ring and the early worshipers had yet to come in, thus it was only a few priests and priestesses cleaning the Temple and performing their early duties that were on-scene when Orodan barged through the doors demanding to speak to a priest of Agathor.\par
“Calm down my son… what has you seeking the faithful of the God of War so early in the morning?”\par
“Priestess, I’ve received a Blessing!” Orodan blurted out as he came to a stop, breathing heavily as he put all 21 levels of his Physical Fitness to work in running as fast as he could.\par
The Priestess seemed taken aback for a small moment, but recovered and smiled.\par
“Excellent, come my child, allow us to verify this and add you to the registry. I take it that mighty Agathor has blessed you? Are you with the militia perhaps? Do they know yet?” she calmly asked.\par
“Yes, I’ve received the Blessing of Agathor, I’m with the Volarbury County Militia and I haven’t informed them as of yet.”\par
“That’s fine, we can handle all of that. If you had to attend to your duties today you need not worry about it, they will be informed,” the priestess spoke as she led Orodan into a smaller chamber within the Temple where a priest covered in armor was praying in front of a statue of a divine figure posed with a hammer in his right hand, a greatsword in his left, and two spears strapped across his back. The statue of Agathor looked as warlike as stories of the God himself.\par
Without turning around to face them the priest spoke.\par
“I sense it, the feeling of a fellow Blessed of Agathor,” the man said and finally turned around. He was grizzled and had a scar across his face, befitting a priest of the God of War. “I am Solamus Einshield, battle-priest of Agathor. You, warrior, what is your name?”\par
“Orodan… Orodan Wainwright. I was blessed by Agathor yesterday,” Orodan replied, deciding to take things one step at a time.\par
“Oh? And what were you doing around the time you were blessed?” Solamus asked him, suddenly all too interested in Orodan.\par
“You won’t believe this, but I came back in time after dying. Today, around noon in Ogdenborough around the time of the Council announcement from the Capital there’s going to be a huge battle. Guzuhar barbarians attack the Eversong Plaza and House Argon is in on it. A brave few Republic loyalists come by to try and stop whatever they’re doing… but I fell before I could see any more.”\par
Orodan’s explanation was earnest and straightforward. The idea of dancing around the issue and keeping knowledge to himself wasn’t in his nature. If a problem existed, his solution was to batter his head against it until either it broke or he did.\par
To Solamus’s credit the battle-priest didn’t scoff or laugh at Orodan. But he did suddenly became very silent and gave him an almost piercing gaze.\par
A full twenty seconds passed before Orodan himself spoke up.\par
“As unbelievable as this sounds… I also received a Quest-”\par
“That’s enough. I believe you,” Solamus suddenly interrupted, and then he moved to close the door to the inner chamber they were in. “Aelis, what is spoken here cannot leave this room. The same goes for you as well Orodan.”\par
The battle-priest’s tone was severe and brooked no dissent. If his hand suddenly resting on the hilt of his sword was any indication, he was also willing to come to blows over the matter.\par
“You just, believe me?” Orodan asked, almost in disbelief himself.\par
“Certain Blessed faithful can commune with their Gods… for Agathor to speak directly to me after so many years…” Solamus trailed off. “But that isn’t the issue, you… who are you? Agathor tells me he does not recall having ever given you his Blessing, and he has spoken to the other Gods and nothing adds up.”\par
Gods were above the realm of mortals. They had perfect memory and could process an unfathomable number of things at once. Simply put, there was no way Agathor would have forgotten or not paid attention to the fact that he had Blessed a mortal.\par
Furthermore… this carried the uncomfortable implication that even the Gods seemed not to be aware of the fact that Orodan had been sent back in time. Which to Orodan was inconceivable.\par
Gods were supposed to be outside of the flow of time and were unaffected by time magic. Agathor also presumably conversed with the God of Time, so for even him to be unaware…\par
Just who was responsible for Orodan’s second chance?\par
“I don’t know, I am and always have been Orodan, a member of the County Militia. And yesterday… or I should say, today, I died while fighting against Northmen barbarians in Ogdenborough’s Eversong Plaza.”\par
Solamus took another moment to look at him closely, but then broke eye contact and sighed.\par
“As insane as this all sounds, I believe you. Lord Agathor has spoken to me and your tale has enough evidence for me to consider it. Eversong Plaza and that tavern have always been a closely guarded secret of House Argon, you’d best take this report back to your superiors, it might even need to get back to the Capital Guard. I’m just a battle-priest, I know some old friends but none of them are anywhere relevant to help in a matter like this.” Solamus spoke and then ushered him out with a word to the priestess Aelis to see Orodan out the door.\par
Orodan made it twenty steps outside the temple when something hit him from behind and he was knocked right off his feet and sent sprawling to the ground. Whatever hit him, hit very hard.\par
He tried getting to his feet but found that he couldn’t move his arms at all. They lacked any strength. And looking down at his own chest he saw the tip of a great arrow sticking out.\par
He then realized he was choking on his own blood.\par
Orodan’s mind kicked into overdrive and he desperately attempted to regain control of his body and crawl away to safety. He couldn’t die like this! He was given a second chance!\par
He gritted his teeth and scrounged up every bit of spite, grit and determination within him and furiously dragged his critically wounded body to cover in the alleyway between two nearby houses. He had a Physical Fitness of 21 and his body could thus survive somewhat more blood loss and trauma than anyone untrained in the skill… but a gaping hole caused by a great arrow would still kill him. The wound was looking to be fatal.\par
He held the great arrow in place and with every iota of willpower and focus his adrenaline-fuelled mind could muster, he concentrated till his face was red and tried to control his breathing and attempted to mentally slow the rate of bleeding.\par
His vision started to slowly darken, but he felt like he earned himself maybe another minute.\par
\textbf{[New Skill → Bleeding Control 1]}\par
He ignored the message and the screams of nearby witnesses and instead tried very hard to now staunch his own bleeding. Perhaps if he survived long enough a priest from inside the Temple could help?\par
That hope was dashed as a dark figure wearing a full face mask and hood stepped into the alleyway, a great bow slung across their shoulders.\par
As the figure drew a dagger the length of his forearm, Orodan desperately lashed out with as strong a kick he could muster and caught the figure in the knee.\par
The assassin’s knee slightly buckled, but they suffered no visible injury from the kick. They were likely at the Adept level then.\par
Orodan refused to die quietly as he lunged out and grabbed his killer’s dagger with both hands, even when the enchanted blade sliced into his palm like hot butter and nearly broke his focus with the searing pain it inflicted.\par
As the killer began easily pushing the dagger towards his head Orodan tried everything he could think of. He kicked, scratched, and exerted so much force he broke his own fingers in desperation. He spat out a glob of his own blood that was simply blocked by the killer’s face mask.\par
Finally, as the blade reached his head he struggled and twisted enough that the dagger entered his left eye instead of his forehead. The pain was utterly all-consuming but Orodan still fought like a rabid dog to hold onto consciousness.\par
\textbf{[New Skill → Pain Resistance 1]}\par
As the darkness began to take over his vision he reached out and did the last thing he could, he reached out and grabbed his killer’s belt, specifically the strange green flask on their hip.\par
And he crushed it in his hand.\par
\textbf{[New Skill (Uncommon) → Dying Struggle 1]}\par
His vision faded to darkness but as he passed he could hear sizzling and frantic screams of pain even as he lost all feeling in his own body.\par
So much for a second chance.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
\par
A keening wail ringing in the night sky awoke him.\par
He… he was back?\par
\textbf{[Quest Bestowed → Battle of Ogdenborough - Defeat the Novarrians and their allies as they attempt to activate and commandeer the ancient war machine beneathe Mount Castarian]}\par
Was this a third chance?\par
He was so brazenly murdered in broad daylight once he let slip about the upcoming attack. And by an Adept level archer too. How was he supposed to deal with all this?\par
But who was Orodan?\par
He clenched his fist. Orodan was someone who saw things through to the end. Someone who would doggedly clean every single inch of floor in his dilapidated hovel. Someone who would train every single day and struggle despite being an orphan without a background. Someone who would stand his ground out of spite and receive a charge from Guzuhar barbarians when all his peers fled. Someone who would lash out like a rabid dog even when he was dying and make his killer feel his revenge with his dying struggles.\par
Maybe there was a limit to the number of times he would be allowed to come back, maybe there wasn’t.\par
But while a more reasonable person might have decided to plan and scheme and strategize, what did Orodan intend to do?\par
As the harpies keening wails died off in the distance he could only say one thing.\par
“I’m going to keep going to the Temple and struggling against that fucking archer until I succeed!”\par
If there was a wall in front of him, he would ram his head into it until either it broke or he did.\par
For him there was no easy way out, no attempting to find a hidden solution, no cheap tricks or enlisting of allies. He would only ever accept doing things the hard way.\par
Orodan was a stubborn skill-grinder who didn’t quit.\par
And he was in a time loop.\par


\section*{Chapter 2 - Using Death As A Whetstone}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 2 - Using Death As A Whetstone}%
\par
Orodan wouldn’t be caught unaware this time. Yes, he was up against an archer a whole tier above him, but he wasn’t the type to care one bit about that.\par
He exited the Temple with his sword and shield drawn and just barely saw the great arrow coming in time to put his shield in the way and brace for impact with all the strength he had.\par
The difference between Apprentice and Adept was not only a numerical one, but a qualitative one as well. As one progressed further along the road of mastery each skill level at higher levels became dramatically more impactful.\par
The difference between Sword Mastery 9 and 10 for example wasn’t anywhere near the difference between Sword Mastery 35 and 36. Each level of the skill was qualitatively more powerful as the numbers got higher. To that end, the payout in raising a group of a hundred conscripts to level 10 Spear Mastery was considered pathetic versus raising a talented warrior from level 35 to level 36 of Spear Mastery.\par
And the qualitative difference between Orodan’s 24 Shield Mastery and his assassin’s 50+ Archery Mastery made itself known painfully as the great arrow pierced right through his shield and it was only a last minute angling to the side that allowed him to merely lose the use of his left arm as the great arrow cleanly dismembered it.\par
\textbf{[Shield Mastery 24 → Shield Mastery 25]}\par
Gains could be made even in failure.\par
Orodan’s new Pain Resistance skill was paying off, as even level 1 of it allowed him to mostly take the edge off a frankly debilitating amount of pain. He cursed and dashed into the same alleyway in-between two houses and had his sword at the ready in his right hand.\par
As expected, the assassin dropped down into the alleyway from above and this time drew double daggers which they were dual wielding.\par
Orodan put up a decent enough struggle, but the difference between an Apprentice and an Adept was a harsh reality, and he received a dozen stab wounds within the span of a second that he couldn’t even react to in time.\par
He could maybe deliver and react to four, maybe five or six blows blows a second if he truly tried. A dozen a second was almost double his speed and he stood no chance in a trade of blows, yet.\par
As he fell to a knee while holding his throat and gurgling on his own blood from the stab wound in his throat, Orodan once again mustered as much rage and bitter, spiteful willpower as he could and attempted to lash out and fight as hard as he could.\par
\textbf{[Sword Mastery 35 → Sword Mastery 36]}\par
\textbf{[Dying Struggle 1 → Dying Struggle 2]}\par
\textbf{[Bleeding Control 1 → Bleeding Control 2]}\par
\textbf{[Pain Resistance 1 → Pain Resistance 2]}\par
Two dozen more stab wounds later as he was about to have his vision darken and the loop reset he got an interesting message.\par
\textbf{[New Skill (Rare) → Unyielding Vitality 1]}\par
With the acquisition of the skill he felt as though whatever vitality his body held, whatever blood flowed through his veins, he felt as though it extended further. He could now push his existing vitality further based purely off of what he had.\par
The coup de grace stab to his head sent him to the darkness where he saw the Quest failure message.\par
A keening wail ringing in the night sky awoke him and Orodan clenched his fist and decided he would die as many times as necessary in order to defeat this opponent.\par
That damned archer would be the whetstone that Orodan would sharpen himself against.\par
\par
For the sake of saving time and getting to the fight as soon as possible, Orodan’s loops now consisted of blitzing through his routine as quickly as possible, Sprinting to the Temple and proclaiming loudly that he was a prophet who had a vision of the battle of Ogdenborough and promptly leaving.\par
Somebody in the Temple was an informant for House Argon and in the know, but he just couldn’t narrow it down to who it was. Even if he spent no time inside the Temple at all after making his proclamation he’d always be met by the assassin right outside the Temple.\par
The next five attempts went similarly, although he did make gains in his skills across the board. Any attempts to target the flask of acid on his enemy’s belt like he somehow managed the first time, were a no-go. Partly because the assassin wasn’t nearly so careless when Orodan was armed and ready to trade blows in melee combat, and partly because Orodan was a warrior who refused to take the easy way out, even if it was against a superior opponent.\par
He was stubborn.\par
The tenth loop onwards was when the assassin started taking him seriously and went all out right from the get-go. Maybe it was the fact that Orodan’s Sword Mastery had reached level 40 and his Shield Mastery had hit 30, but the assassin no longer toyed with him and instead fought to immediately kill him. This was also the point where Orodan felt that he was starting to remember and learn his opponent’s fighting style and moves, that and his increasing skills signified a benchmark where he was able to start barely trading blows with the man for brief moments at a time without dying. Even if he was on the losing end of these exchanges.\par
Unfortunately, the sudden display of competence did not make the assassin happy. Given the man’s choice of sending a great arrow at him to start with every time, it was no surprise that the daggers he fought with were not his specialty. So this led to the man suddenly leaping backwards and deciding to pepper Orodan from range as befitting his specialty.\par
Furthermore, running into the alleyway for cover wasn’t as viable an option when the assassin was serious.\par
Great bows were powerful weapons of war, and a great arrow fired from one was more than capable of piercing through multiple houses when fired by an Adept-level archer.\par
It was however great practice for Unyielding Vitality, Pain Resistance and Bleeding Control as the archer treated him like a porcupine and stuck him full of arrows from a distance.\par
The fifteenth attempt had an interesting message for him.\par
\textbf{[New Skill (Uncommon) → Perfect Parry 1]}\par
It was the result of somehow managing to perfectly deflect one of the assassin’s great arrows in such a way that even though it carved a streak of damage across his shield, it didn’t outright pierce it for the first time and instead the projectile was deflected and its trajectory veered off to the side.\par
His shield wasn’t capable of standing up to a great arrow from an Adept level archer who could pierce multiple buildings in a single shot. The materials were far too shoddy for that. But this was another hallmark moment from where on Orodan began to occasionally Perfect Parry the great arrows.\par
A few attempts were ended early as he mistimed the skill, but he started getting a better handle on it as the attempts went on. Plus, this was the first active combat skill Orodan had learned. Passive skills were the backbone of a warrior, but what separated the average from the great, even within the same tier, was active combat skills.\par
This alone right now, could see him transferred to Trumbetton as active combat skills denoted great potential. And an Uncommon rarity skill too!\par
He gained another skill on the thirtieth loop when he decided to sheathe all his weapons and tried purely dodging the great arrows right from the start of the fight.\par
\textbf{[New Skill (Uncommon) → Evasiveness 1]}\par
He ate a few great arrows to the face in training this skill too.\par
Finally on the forty-third attempt, he managed to get an interesting reaction out of his killer.\par
For this attempt Orodan had already displayed his improbably good melee combat skill and caused his training partner to leap away and begin the ranged peppering phase of the fight.\par
Unfortunately for the man Orodan’s ability to Perfect Parry his great arrows alongside his Evasiveness skill meant that for the first time not a single one of the thirty great arrows the man fired managed to touch Orodan.\par
A part of what lead to this great result was Orodan genuinely knowing the man’s projectile speed and firing patterns inside out by this point. It wouldn’t be so easily replicated with anyone else. But Orodan still felt proud of himself for the accomplishment of evading every one of an Adept-level archer’s shots while being at the Apprentice level himself.\par
The prickly archer didn’t feel the same way however and because his feelings were undoubtedly hurt he decided to be a spoilsport and throw the flask of acid he had on his hip for the first time.\par
Orodan evaded the flask, but not the explosion when it touched the ground.\par
\textbf{[Pain Resistance 18 → Pain Resistance 20]}\par
As his flesh melted and he practically began to disintegrate, Orodan reflected that it was a new and entirely unpleasant sort of pain which he wasn’t capable of properly feeling the first time around.\par
\par
It was now the fourty-forth attempt and Orodan was determined to teach this man a lesson.\par
As he set foot outside the Temple he almost automatically stepped to the side, making sure to move an extra inch to account for the fucker’s ability to influence the arrow’s path while it was mid-flight.\par
He used Perfect Parry on the following arrow with minimal damage to his shield and then quickly ducked into the alleyway between the two nearby houses.\par
The assassin dropped to the ground in front of him shortly after and drew his two daggers.\par
A furious melee ensued in which Orodan managed to actually trade blows evenly for the first time against the man and almost felt as though he could push him back if the exchange went on. The assassin’s dual daggers met with Orodan’s sword and shield in a blitz of blows that caused powerful winds to erupt outwards from the collisions.\par
The speed difference between him and his opponent was no longer as great as before. While the assassin could launch a dozen strikes a second, Orodan could now launch ten a second himself. And the remaining gap was bridged by his use of a shield and the Perfect Parry skill at opportune moments to seriously throw the man off-balance.\par
His longer sword afforded him a reach and power advantage, and soon Perfect Parries followed by shield bashes began to wear his opponent down and at a critical moment Orodan lashed out with a fist which connected crisply on the man’s jaw.\par
His Physical Fitness was now at 31 due to the constant battles and physical exertion. How and why it carried over across time, Orodan did not know, but he was appreciative of it.\par
His punch backed by 31 Physical Fitness and 28 Unarmed Combat Mastery, despite the gap in numbers between them, still sent the man stumbling backwards due to the clean hit, and soon enough the assassin decided to back off and decide he was going to play by what he was good at.\par
Great arrows began to fly towards Orodan, however each one was calmly and methodically deflected via Perfect Parry or simply evaded. Soon enough, out of frustration the assassin decided to throw the acid flask at Orodan.\par
And in return Orodan decided to throw his shield right at it.\par
\textbf{[New Skill (Uncommon) → Shield Throw 1]}\par
As soon as he threw the shield he didn’t bother waiting to see the result, he dove away to cover. A loud shattering and hissing noise occurred and a deadly looking green smoke lazily drifted down to the ground where it settled into a goopy liquid and chewed through more than a foot of the dirt road before it lost efficacy. His shield was utterly disintegrated of course.\par
“Now get back here and let’s finish this fight!” Orodan proclaimed.\par
The man was taken aback and remained silent for a moment before speaking.\par
“Are you really that same rat Orodan Wainwright who would ask for beatings every day in the plaza?” A grizzled voice asked, and it confirmed that this archer was definitely one of House Argon’s enforcers.\par
“One and the same! Now get down here and face me like a warrior! Let me show you that you messed with the wrong kid back then!” Orodan declared, but to his utter surprise the assassin simply clenched his fist and shook his head.\par
“I don’t know how the hell you got so strong… but you won’t live long you damned street rat, nobody in this stupid town will.” The man proclaimed and then… leapt away.Stolen content warning: this tale belongs on Royal Road. Report any occurrences elsewhere.\par
Orodan took a second to do a double take at the absurdity of how the situation ended, and then attempted to give chase.\par
A fruitless endeavour as the assassin had Adept level abilities and while Orodan might have fought him to a standstill and prevented his assassination attempt, chasing him down while having inferior levels in skills was another thing.\par
“Damn it! I’ll get you the next time!” Orodan roared and swung a fist at a nearby stall, breaking it in half. His Physical Fitness had come a decent way since the beginning of his attempts at beating that fucking archer.\par
He mentally called his Status screen forth.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Sword Apprentice}\par
\textbf{Available Titles: One Who Has Experienced Death, Shield Apprentice, Combat Apprentice, Physical Apprentice}\par
\textbf{Skills: Sword Mastery 46 (Apprentice), Shield Mastery 37 (Apprentice), Combat Mastery 32 (Apprentice), Physical Fitness 31 (Apprentice), Unarmed Combat Mastery 28 (Initiate), Cleaning 27 (Initiate), Perfect Parry 21 (Initiate - Uncommon), Pain Resistance 20 (Initiate), Evasiveness 18 (Initiate - Uncommon), Laboring 18 (Initiate), Bleeding Control 17 (Initiate) Sprinting 16 (Initiate), Club Mastery 15 (Initiate), Dying Struggle 14 (Initiate - Uncommon), Unyielding Vitality 11 (Initiate - Rare), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate), Shield Throw 1 (Initiate - Uncommon)}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
Let it not be said that Orodan’s stone-headed approach to brute forcing an issue didn’t have results. Three new uncommon skills and a rare skill; alongside many skill increases which made him an apprentice in Shield Mastery, Combat Mastery and Physical Fitness.\par
It just took dying nearly fifty times.\par
Orodan took a moment to reflect on the fact that his life had just changed immeasurably. Previously he was a hard worker with slightly above average talent, but now with the ability to time loop and all these skills he essentially changed his lot in life within the course of a few days worth of work and training.\par
Unless one had a Blessing, a Bloodline or was a supreme talent, advancing from a fresh Apprentice at 20 to nearing the Adept-level threshold of 50 at the mid-40s was something that took at least a year of dedicated training for the decently talented; and many years for the average person. And Orodan had just crossed that gulf within a few days of training via the circumstances that let him loop.\par
Nobody else could match this insane rate of learning, and if people knew how fast he could grow in skill… they might be willing to kill him or worse. Life and death battles were widely agreed upon as the single best way to raise skill levels, however it was incredibly risky, and the rate of skill gain was commensurate with the danger to one’s self in these battles.\par
Coddled rich youths attempting to kill slimes and goblins with someone overseeing their safety experienced growth rates slightly higher than regular training. Whereas soldiers who survived hellish battles and situations often came back with incredible gains which changed their lots in life. Such was the world they lived in.\par
But who could dare to consistently train the way Orodan did? For Orodan, dying meant nothing as he’d just reset back to being awoken by harpies in the deep night. So for him, having almost fifty life and death battles within the course of a single day and dying in forty-three of those battles held no consequences.\par
In fact, right at this moment based on his talent and age alone, Orodan could leave the Volarbury County Militia behind and apply to the Capital Guard or an academy. While not at the level of a prodigy, he would certainly qualify as being called a very good talent if he were to undergo the examination right now.\par
But was that even what he wanted? To merely be a great talent in a martial academy?\par
Orodan’s ambitions extended higher than simply attending an academy. Maybe one day once he had resolved the issues of this day he was stuck in he’d think about sitting down and attending classes in a structured environment. But an academy lacked the edge of death and real experiences that were allowing him to advance so quickly now.\par
He changed his active title to Combat Apprentice and for the first time in forty-four loops, moved on from the damned Temple.\par
\par
Orodan managed to make it to his local barracks in Ogdenborough with time to spare before roll call. Physical Fitness was a skill that naturally lagged behind by ten to twenty points for almost everyone but the most insane of people. And even Orodan who was considered a very hard worker with a great Physical Fitness level wasn’t exempt from this.\par
But having 31 Physical Fitness now made running between towns dramatically easier for him. The additional two levels he gained in Sprinting during his battles against that Argon archer-assassin now made what was a half-hour’s travel, into a sprint he finished in less than ten minutes.\par
He went straight for Sergeant Woodgard’s office and knocked on the door.\par
“Come in!” a man barked from inside.\par
Orodan walked in and saw the man swamped with paperwork and looking rather stressed.\par
“Sergeant, I’d like to report a crime sir.” Orodan said and stood at attention.\par
“What the fuck, Wainwright! It’s Liberation Day today, it’s a half-hour before shift starts and you want to put more on my plate?!” The man barked, but not with any real venom. He then sighed and continued. “Well? Out with it.”\par
“On the way back from the Temple in Scarmorrow this morning I was attacked by an enforcer of House Argon who tried to kill me. I managed to fight him to a standstill and get away, but I overheard something about a plot of theirs to smuggle Guzuharan raiders into Volarbury County via the tavern at Eversong Plaza.” Orodan finished, and he noticed the Sergeant’s face getting redder by the second.\par
“So that was you?! Wainwright, why the flying fuck are you fighting the men of a noble house in another town?! Do you understand how much work you’ve created for me?! I’ve been hearing reports about that fight for the last half hour!” The man roared with spittle flying from his mouth. He then calmed himself for a moment and spoke more calmly. “But… eyewitness reports are conflicting as the County Militia got there well after the fact. Some reports say it was an Adept-level fight, some are saying it was at least high level Apprentices fighting. So… care to explain why you’re coming to me claiming to have fought off someone that’s on the cusp of reaching Adept-level at least?”\par
“Sir, if you pull out the Observer orb I can show you,” Orodan calmly explained, and to his credit Sergeant Woodgard stopped his usual angry tirade and simply pulled the orb out, seemingly interested in what he was about to see.\par
Observer orbs were commonplace across the continent. It was the artificers’ solution to making the common Observe spell that diviners and nobles used available for widespread use. It was a technological innovation widespread across the Continent and beyond. As long as the individual voluntarily placed their hand on the orb, the reading would show up on a mana-powered display.\par
Orodan placed his hand on the orb and after a moment the readings began to display. Titles and skills were what was displayed. Available titles were not shown only the ones someone chose to display, and neither were Blessings, although any competent diviner, or a priest of the relevant divinity could detect Blessings if in close proximity to someone.\par
“Alright… now let’s see here…” Sergeant Woodgard muttered and began to look through the display. And then he promptly froze.\par
He remained silent and his face made a range of different expressions before he finally spoke.\par
“Combat Apprentice?” He quietly asked in the most subdued voice I’d ever heard from the man. “Apprentice level in Shield Mastery and Physical Fitness too? Three Uncommon skills and a Rare skill? Two of which are active combat skills…”\par
“Yes sir,” Orodan happily replied, although he wouldn’t deny he was feeling at least a bit smug and enjoying Sergeant Woodgard’s reaction and complete change of demeanour.\par
“This is…” He stopped for a moment to gather himself. “Your last examination at the Observer orb was over a year ago when you first signed up with the County Militia… and your skills, while promising, weren’t anywhere near this at that time.” Sergeant Woodgard slowly spoke, almost taking care not to talk out of turn.\par
Truthfully, to Orodan while this was initially amusing, it was now slightly awkward.\par
Sergeant Woodgard was essentially now treating him as though he was a superior that couldn’t be spoken down to.\par
Which… in a sense wasn’t an an unwise attitude. Orodan used to be the second strongest member of the barracks, but now he currently was the most powerful person by a ridiculous gap. He could legitimately fight against an Adept level combatant and hold his own given all his skills, and the active combat skills he had.\par
In fact, only the nearest mounted unit might have individuals that could beat him one on one at this time, and not the rank and file among them but the mounted unit captains who were Adepts would be needed.\par
But most important was his Combat Mastery skill sitting at 32, which gave him a massive advantage over most people at the same level. Combat Mastery was an amplifier type skill which determined someone’s combat instincts and how good they were at fighting in general. It was an amplifier on almost everything a warrior had available to them in combat. And most people at the Apprentice level were lucky to have it exceed 10. Even Orodan originally having it at 11 was considered quite excellent in the context of the Militia and indicative of his rough upbringing.\par
The world was bigger than just the County Militia however.\par
But 32? Level 32 Combat Mastery alongside everything else shown on the display? Sergeant Woodgard did not want to offend such an individual. And he certainly believed Orodan now about his earlier claim about fighting a near-Adept level member of House Argon. And if he knew the truth, that he’d fought a full-on Adept level individual, he’d tread even more carefully.\par
“Well then… allow me to congratulate you. I’ll immediately put in for your transfer to Trumbetton, they’ll likely want to sponsor you for entry into the County Academy given your talent for your age. You can take the rest of the day off… fully paid of course.” Sergeant Woodgard said, with a very deferential tone of voice.\par
“Thank you sir, but I’d like to remain on-shift and assist with today, particularly with the matter involving House Argon I just spoke of,” Orodan replied.\par
Sergeant Woodgard nervously bit his lip and seemed as though he wanted to pull his little remaining hair out.\par
As much as the Republic of Aden claimed to be a… republic; the Volarbury County Militia was primarily funded by and under the authority of House Firesword whose base of power was in Trumbetton. And the leadership of every barracks in the County knew that Burgher Ignatius Firesword, the head of the noble house, was a talent seeker who expected the County Militia to deliver all talented youth to Trumbetton where they would be assessed and sent to academies or placed under apprenticeships as suitable.\par
It was a decent system which lead to a good life for these youth, where if they displayed exceptional talent in the martial arts they would be sponsored to enter a martial academy and serve the Volarbury County Militia in the Elite response unit, or serve House Firesword directly depending on the needs of the House.\par
And Orodan’s talent would be considered great even within an academy, so the Sergeant was truly nervous about allowing Orodan to risk himself doing even simple patrol work given that Observer orb records were sent to the Militia Headquarters in Trumbetton and Woodgard would be under heavy scrutiny for not immediately delivering such a talented youth to Trumbetton for a better future and superior tutelage.\par
“Look… this is genuinely above my paygrade at this point. If I don’t immediately take you off the roster and put in for you to go to Trumbetton, I’ll be in big trouble. Please be reasonable… surely you’re aware of how talented you are for your age, can you not see how badly I’ll be investigated if I don’t send you to headquarters for further examination?”\par
This was without a doubt, the most awkward situation Orodan had been in. Sergeant Woodgard, the man whose face went red with spittle every time he roared orders at militia… was actually speaking softly and actually pleading with Orodan to understand his position.\par
Orodan sighed. He truly didn’t want to put the Sergeant in a miserable spot, so he quietly agreed to the transfer. Plus, although his warrior spirit protested avoiding the fight… him being near Eversong Plaza in this loop was tantamount to committing suicide. House Argon undoubtedly knew that their enforcer had failed to kill him and they knew who he was.\par
Frankly, it was truly lucky that he even survived the run back to Ogdenborough from Scarmorrow without any other enforcers trying to go after him.\par
Showing his face in Eversong Plaza this loop would just end in him being killed on the spot as there were way too many enemies present and House Argon already showed that they had no issues acting publicly and trying to brazenly have him murdered right outside a Temple.\par
\par
Orodan was in the back of a rather nice-looking horse drawn carriage, with members of the mounted unit flanking him on multiple sides as they rode for Trumbetton.\par
The escort was sent in by the Trumbetton headquarters of the Volarbury County Militia who diverted an additional troop of ten riders specifically for his escort. Apparently once they received the transmission of his Observer orb readings they immediately insisted on it.\par
The ride was smooth, and the members of the mounted unit were oddly respectful with an accompanying captain who was an Adept-level spearman introducing himself as Keharion Taj and saying he looked forward to working with Orodan in the future.\par
Talent really did make the world go round.\par
Orodan wondered for a second why the County Militia would waste such resources on simply transporting a private like himself and then recalled that in this world, training even one talented youth to the level of an Elite was worth more than training a hundred Adepts. And given Orodan’s current skill levels and the Blessing he hadn’t even disclosed yet… becoming an Elite was definitely in the cards across his lifetime. And this was without factoring in his ability to go back in time.\par
Noon went by and the announcement came and went, with the battle of Ogdenborough undoubtedly being underway.\par
Orodan had done his best to inform the mounted unit of his ‘prophetic vision’, and they passed the message onto the headquarters of the Militia at Trumbetton. And the reaction was… nil?\par
Nothing changed in the response of the Militia, their patrols weren’t stepped up, and there was no impact whatsoever. Which Orodan found highly suspect. There was undoubtedly foul play involved. Either House Argon or maybe even House Firesword in Trumbetton was in on it?\par
It was an hour since the announcement and surely the battle had been won by now?\par
Suddenly, Orodan felt a tremor, and the horses did too as they bucked and were terrified.\par
And in the distance, many hours away, Mount Castarian… moved.\par
And the peak of the mountain which Orodan thought was massive enough, shifted as something emerged and wore the peak atop its head like a mere cap.\par
Multiple metallic arms pulled themselves free and Orodan watched on in amazement and wonder as whatever this machine was, it was almost divine in nature.\par
It had a humanoid face, and finally stood tall appearing like a humanoid metal golem, except, as tall as a small town’s length as its head went past the cloud layer.\par
It was utterly gigantic at a scale Orodan had never seen before.\par
It had a brilliant red jewel on its forehead, and it began to glow very ominously.\par
And then it flashed red.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
\par
A keening wail ringing in the sky awoke him.\par
\textbf{[Quest Bestowed → Battle of Ogdenborough - Defeat the Novarrians and their allies as they attempt to activate and commandeer the ancient war machine beneathe Mount Castarian]}\par
He brushed past the quest messages that showed themselves and simply thought to himself…\par
“…so that’s the ancient war machine the Quest talks about.”\par
It was an unpleasant fact to learn that the Republic would always lose and the war machine was fated to awaken without any intervention.\par
Seems there was no escaping the day until this Quest was resolved. Yet, Orodan had absolutely no idea how to go about fighting such a thing which was bigger than Mount Castarian to the point that its head broke through the cloud layer.\par
Orodan doubted even a group of the Republic’s rumoured Master-level combatants could bring that thing down. He was starting to understand why a Quest had been bestowed upon him in relation to this machine’s awakening. In the history of the continent the times Quests were issued to certain remarkable individuals was when the very sanctity of the world was somehow threatened, or a great disaster would befall the people.\par
It was just hard to think of himself, the Apprentice-level warrior as being of the same cloth as one of those great and remarkable individuals who the world bestowed Quests upon in history. But then again, he had seemingly infinite tries to get it right. Orodan heard of nobody else with such a strange ability.\par
Orodan was a bull-headed individual with a propensity towards violence and straightforward solutions, and it seemed as though this situation truly was tailor-made for someone like him. The stories the matrons would read to him had scheming and smart individuals who would undoubtedly try to plan, gather allies and maximize their odds of success via diplomacy in such situations.\par
Orodan unfortunately was not one of those individuals. His pride wouldn’t allow it and he genuinely believed that the only way out of this situation was brute force and personal power.\par
And on the note of his personal power and advancement; he had already advanced to the level where he could fight off a low level Adept and survive against them, the archer-assassin outside the Temple in Scarmorrow was starting to provide diminishing returns near the end.\par
So it was time to find new foes to sharpen himself against. And Orodan knew just the nearby town to spend the next many loops doing so in.\par


\section*{Chapter 3 - Warehouse Massacre}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 3 - Warehouse Massacre}%
\par
Desertion was technically illegal, but Orodan didn’t care given that in approximately eight hours the entirety of Volarbury County would likely be devoid of life thanks to an ancient war machine from a bygone era.\par
Who even knew where that thing came from? All Orodan could be certain of was that the Novarrian Empire couldn’t have built it.\par
As for Orodan, he was enjoying his self-granted day off of work in this loop in the nearby town of Loviaston, an hour’s Sprint away, where he was sitting at a table in a coffee shop.\par
Across the street from said coffee shop was a warehouse with the banner of a flower and shield flying atop it. The banner of noble House Argon, traitors to the Republic and future perpetrators of mass slaughter.\par
He had been sitting at the table for about thirty minutes now and was reaching the limit on information that could be gleaned by just sitting at a coffee table and observing.\par
He knew about this place as being one of the warehouses that House Argon used to send goods to and from the tavern in Eversong Plaza. As fascinating as it would be if there was some secret weapon or stashes of illegal substances there, the warehouse was used for delivering food to the tavern, and the shipments were in open crates and handled by local carriage drivers who had plenty of opportunity to snoop if they really wanted.\par
The warehouse, from what Orodan knew, was more of a staging point for House Argon’s enforcers to go out and do their dirty work, and a location where going to and from wouldn’t easily have their personal details leaked. The warehouse was strictly manned by guards and enforcers of House Argon, and Orodan heard rumours of at least two Adept-level guards within from the gossip of the townfolk.\par
If he spent any longer at the table and kept asking around word might get back to the warehouse that someone was sniffing around, so he decided to do what he was best at. Take action.\par
The security on this warehouse, at 82 Caltrop Road, wasn’t anywhere near the constant eyes that were watching the tavern at Eversong Plaza in Ogdenborough. So Orodan was able to get within twenty feet of the main double doors to the warehouse before a burly Argon guard put his hand out and gestured for him to stop.\par
Orodan’s fist smashed into the axe-wielding guard’s nose, a satisfying crunch reverberated through the air and a shield bash to the head followed by a sword swing decapitated the man all within a single second.\par
The pedestrian traffic nearby suddenly fell very silent.\par
And as the first woman screamed at the sight of the gruesome murder Orodan rushed the second guard who was a second too late to react at the shocking sight of the violence. Orodan’s sword stabbed through his head and sent him to the afterlife as well.\par
\textbf{[New Skill → Surprise Attack 1]}\par
Two near-Adept guards put down in less than three seconds, admittedly with the element of surprise on his side. But still, these were fighters on the same tier as himself. Orodan had grown strong.\par
He felt they weren’t at the Adept-level, but near it. And compared to Orodan who could now fight Adepts to a standstill, they weren’t too much of a threat.\par
He kicked the double doors in with as much force as he could muster, sending them flying inwards and revealing the inside of the warehouse where five angry looking guards had their weapons drawn.\par
Orodan roared and feinted a charge at the nearest one, a halberd user who raised his weapon to defend, only for Orodan to redirect and lash out with a furious swing at the second nearest one, a swordswoman who was caught off-guard and received a deep cut to her leg.\par
The element of surprise wore off and the fury and exchange of steel-on-steel melee combat was joined. Even though it was five-on-one all the guards on the first floor weren’t Adept-level yet.\par
Perfect Parries and Evasiveness to create openings lead to the swordswoman and a mace wielding guard being cut down in the next ten seconds. Active combat skills really were a game-changer, the Blessing that allowed Orodan to learn warrior skills faster truly was a boon for allowing him to so easily pick such things up.\par
The remaining three all ganged up on him at the same time, and while he could launch ten attacks a second, each of them were capable of at least six a second themselves, and taken together it meant that Orodan took some blows while dealing them in return. Although he did try his absolute best to mitigate the damage as best as consciously possible by focusing on receiving blows at the most optimal angles, maneuvering his body to receive a blow in the least critical area, and whatnot.\par
His left arm had a deep cut which made moving it slightly more difficult, and his ribs were likely cracked from a hammer, but the message he received was worth it.\par
\textbf{[New Skill → Damage Mitigation 1]}\par
Within the next ten seconds two of the remaining three were dead, but as Orodan attempted to deliver a killing blow to the last one whose morale was on its last legs, a sudden greatsword intercepted his attack and all of a sudden he was on the backfoot trading blows and being forced back as a tough-looking old man pressured him. And unlike the archer-assassin in Scarmorrow, this man was an Adept-level fighter who specialized in melee combat.\par
Orodan had no surefire way of knowing whether someone was an Adept, but it was a sense of decently reliable feel. He didn’t know the basic Observe spell that was taught to all nobles and students of any academy, so for him, going by feel was how he identified someone’s approximate skill levels in combat.\par
By this point anyone capable of pressuring and pushing Orodan back in melee combat had to be at least Adept-level, as anyone beneath that just wasn’t up to par.\par
The difference between fighting the Temple archer at Scarmorrow and fighting this man was quite stark. Unlike the archer whose strikes lacked conviction, this man’s attacks with his greatsword were full of lethal commitment and crisp focus.\par
This old man was undoubtedly a far stronger Adept-level fighter than the archer was. The situation got worse as Orodan realized that his Perfect Parry skill wasn’t nearly as effective at creating openings and unbalancing the other man. This greatsword-Adept was a master of melee combat and what worked on an archer with commitment issues in close quarters wouldn’t work on him.\par
Still, that Orodan could keep pace with and trade blows against this vastly more dangerous melee combatant even if it was in brief moments and exchanges that he was the loser in… it spoke well of his own growing skill levels.\par
Orodan wasn’t ashamed to admit that he had to start vaulting over crates, climbing up equipment and even hopped across support beams and swung himself up to the second floor of the warehouse in order to gain space and not remain in a melee exchange for too long at a time lest he get overwhelmed.\par
\textbf{[New Skill → Parkour 1]}\par
\textbf{[Shield Mastery 37 → Shield Mastery 38]}\par
At some point Orodan’s shield completely shattered under the powerful blows of his opponent’s greatsword and he was forced to go sword to sword against an opponent with a reach and power advantage.\par
Not ideal. And even his sword wouldn’t last much longer given the dangerous creaking noises the metal was making as it absorbed the mighty blows of the old man’s greatsword, which was far faster than it had any right to be.\par
The remaining guard who the old man had rescued from Orodan had fled already, whether to get help or not would soon be seen.\par
The man paused for a split moment to speak for the first time. “Murderer, you fight suspiciously well for one who’s not yet an Adept. I am Balus Mogram, enforcer of House Argon, and you’ve killed our people for no good reason. Why? Give me your name so I know who my blade slays.”\par
He was far more forthcoming than the archer, but understandably so given that he wasn’t an assassin and Orodan had provoked his ire.\par
“Orodan Wainwright… and I bring justice upon the traitors of House Argon and any who serve them!” he replied, and as Balus’s face took on a grim visage in response, Orodan too prepared to end this loop with one final exchange of blows as he could see the rumored second Adept-level fighter, a spear-wielding woman, had arrived at the ground floor of the warehouse below them. Must not have been initially present then.\par
Orodan breathed in slowly and tried to focus and center his nerves as best he could. Now, in the middle of life and death combat with his survival instincts and adrenaline at peak capacity, was the best time to attempt the learning of the new skill he was attempting.\par
He got into a power stance, gripped his sword with both hands and raised it overhead in the most powerful load-up position he could manage. And as Balus Mogram’s greatsword came in overhead in a frighteningly strong and fast swing of his own, Orodan uncoiled and exploded with every muscle in his body at full strength, to the point that he felt he might’ve even dislocated his shoulder. The sole objective being to meet the oncoming greatsword with as much pure power as physically possible.\par
The two blades met in the middle, and against all common sense, deadlocked for a fraction of a second as the momentum of the larger and heavier greatsword was incredulously stopped.\par
\textbf{[New Skill (Uncommon) → Power Strike 1]}\par
\textbf{[Sword Mastery 46 → Sword Mastery 47]}\par
\textbf{[Combat Mastery 32 → Combat Mastery 33]}\par
\textbf{[Physical Fitness 31 → Physical Fitness 32]}\par
And then Orodan’s sword broke under the strain.\par
As the greatsword continued onwards to reap his life, its wielder’s eyes were shocked. Balus had felt the power behind the last ditch strike that stopped his greatsword. He almost felt pity and lament at having to put down a youth who could learn an active combat skill in the middle of battle.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
A keening wail ringing in the night sky awoke him.\par
Orodan ignored the Quest bestowal message that always came up and instead pulled up his Status with a mental command.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Combat Apprentice}\par
\textbf{Available Titles: One Who Has Experienced Death, Shield Apprentice, Sword Apprentice, Physical Apprentice}\par
\textbf{Skills: Sword Mastery 47 (Apprentice), Shield Mastery 38 (Apprentice), Combat Mastery 33 (Apprentice), Physical Fitness 32 (Apprentice), Unarmed Combat Mastery 28 (Initiate), Cleaning 27 (Initiate), Perfect Parry 21 (Initiate - Uncommon), Pain Resistance 20 (Initiate), Evasiveness 18 (Initiate - Uncommon), Laboring 18 (Initiate), Bleeding Control 17 (Initiate) Sprinting 16 (Initiate), Club Mastery 15 (Initiate), Dying Struggle 14 (Initiate - Uncommon), Unyielding Vitality 11 (Initiate - Rare), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate), Shield Throw 1 (Initiate - Uncommon), Surprise Attack 1 (Initiate), Parkour 1 (Initiate), Power Strike 1 (Initiate - Uncommon), Damage Mitigation 1 (Initiate)}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
With that loop he added one more Uncommon rarity skill to his repertoire.\par
Taking advantage of the ability to risk his life and engage in genuine and lethal battles against stronger opponents gave him a rate of growth that was unparalleled.\par
Most people would be lucky to have an Uncommon skill or two across their lifetimes. And yet here was Orodan, with five Uncommon skills and a rare one at the age of 17 thanks to his ability to go back in time.\par
Putting that aside, Orodan couldn’t stop thinking about Balus’s final attack and his own Power Strike that met it. Should he plan the target prioritization better for the next loop? Should he try to pick them off one by one?\par
Who was Orodan kidding? He was a bull and knew only one solution.\par
To stubbornly grind away until his Power Strike could blow right through Balus Mogram’s greatsword strike.\par
\par
The grind was slow, yet Orodan kept at it all the same.\par
After his daily routine, where he now took to simply lifting Old Man Hannegan’s entire cart and pouring the lumber out onto the pallets, Orodan now immediately sprinted to the town of Loviaston in every single loop and skipped the coffee shop entirely.\par
82 Caltrop Road was his new destination of choice, and the second he arrived he always began by immediately rushing up to the first guard and hitting him with a Power Strike, something which levelled both Surprise Attack and Power Strike.\par
And throughout the frequent loops of battling at the warehouse he also did his best to grind his other skills, old and new as much as possible.\par
During the first twenty-seven loops of this routine Orodan managed to scout out the place and discover that there were in fact seven near-Adept guards and two Adept-level warriors; Balus Mogram and Estilia Valenur.\par
Being an Adept was a pre-requisite to being considered an enforcer of House Argon, so it came as no surprise that both Balus and Estilia were considered as such, doing the dirty work of the most noble House Argon in Loviaston and the nearby towns when needed.\par
Between the two of them Orodan discovered that Balus was unsurprisingly the stronger one, he was older and was at a later stage of being an Adept, but his potential wasn’t very good. Estilia however was considered a decent talent with her being a spear-Adept by the age of 34.\par
Orodan continued slowly and stubbornly making headway against the House Argon troops at 82 Caltrop Road. He refused to take the easy way and resort to trickery, memorizing patterns or knowing their moves. It was further complicated by the fact that Power Strike was an active combat skill that was very strenuous. Orodan could maybe manage fifteen or so Power Strikes before exhaustion set in. Thankfully higher skill levels lowered the strain of using the skill.\par
Additionally, every single loop Orodan focused not on fighting Balus normally, but instead insisted on slamming his own sword against the old man’s greatsword using Power Strike in a foolhardy endeavour to level the skill and his Physical Fitness too.If you discover this tale on Amazon, be aware that it has been unlawfully taken from Royal Road. Please report it.\par
And inch by inch, Orodan was gaining ground in his stubborn goal as his Physical Fitness and Power Strike continually improved.\par
By the thirty-fourth loop his Sword Mastery was at 49 and Surprise Attack was at 23, which was good enough to be the tipping point where he could rush through and kill all seven near-Adept guards before Balus Mogram was alerted and joined the fray.\par
Killing all seven guards caused Balus Mogram to fight very very seriously right from the beginning of their duels. Furthermore, it caused the unintended side-effect of Estilia not showing up at all unless one guard was left alive to go fetch her from wherever she was.\par
So from then on Orodan toned down the efficiency of his butchery and always left one regular guard alive to go fetch Estilia. It wouldn’t do to not have every single Argon bastard in the warehouse for when the loop came that he won.\par
It took till the fifty-sixth loop for Orodan to finally make headway in his mad endeavor.\par
Balus Mogram’s greatsword flew down at Orodan’s neck at furious speeds, but Orodan’s own Power Strike flew upwards towards the blow.\par
A horrible clash of metal on metal occurred…\par
…and Balus’s greatsword flew out of his hands.\par
\textbf{[Power Strike 33 → Power Strike 34]}\par
\textbf{[Physical Fitness 42 → Physical Fitness 43]}\par
\textbf{[Sword Mastery 48 → Sword Mastery 49]}\par
“Finally!” exclaimed Orodan as he rushed forward and took advantage of Balus’s shock at his heavier weapon strike being powered through by a sword wielded by a near-Adept. “Thank you for your tutelage Balus Mogram… I’ll remember you.”\par
The last words were said genuinely, the sheer improvement he received in fighting against a melee specialist Adept of Balus’s caliber were unfathomable. A Power Strike followed and Balus’s head hit the warehouse floor shortly after.\par
\textbf{[Title Gained: Adept Slayer]}\par
He could have honestly slain Balus a few loops ago if he didn’t insist on testing his power against the old man’s greatsword, but this way was the superior option.\par
Orodan had done it. He had killed an Adept and was on the cusp of achieving Adept level in Sword Mastery himself.\par
The realization hit his mind that he killed an Adept for the first time in his life, while at a lower tier too. It wasn’t an impossible feat, but it was one reserved for the likes of the greats. Orodan now felt his confidence in himself increase; the feeling that he might not live up to the task of completing the Quest bestowed upon him grew smaller as he realized that he was shaping up to become someone who the history books would talk about if he kept on this trajectory.\par
Adepts specializing in a combat skill were respected and influential people in society. Guard captains, veteran soldiers, bodyguards, adventurers, enforcers. To be an Adept was to be on a social level beyond the average masses which consisted mainly of Initiates and Apprentices.\par
To put it into perspective, the entirety of the Volarbury County Militia in the local Ogdenborough barracks, had no Adept-level individuals whatsoever. Reaching Adept meant a guaranteed captain rank in the mounted unit, or becoming a staff sergeant in the militia, or becoming a candidate for training and eventual induction into the Elite response unit.\par
Now Orodan could say he had killed such a caliber of person with his own two hands, in fair battle. He could now choose to make that bastard archer pay too if he wanted. But most importantly, he could start making a noticeable contribution in the Battle of Ogdenborough if he were to head there.\par
He turned to look at the other enemy Adept, Estilia Valenur, a look of fear upon her face… who turned and fled like a scurrying rat.\par
What was it with these Argon enforcers fleeing at the first sight of trouble?\par
He immediately gave furious chase and with his new Physical Fitness of 43 he was definitely comparable to an Adept in terms of physical ability. He easily caught up and ran her down, sending her sprawling to the ground with a powerful Shield Throw which took her leg out, allowing him to rush up and finish the job with a swift decapitation.\par
In truth, if she struggled and fought back properly she could have made him work for it a little bit, but it would have been a moot point as she was weaker than Balus who Orodan had already overpowered and slain.\par
As Orodan mentally compared the enforcers of House Argon he also decided to bring up his status.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Combat Apprentice}\par
\textbf{Available Titles: One Who Has Experienced Death, Shield Apprentice, Sword Apprentice, Physical Apprentice, Unarmed Combat Apprentice, Adept Slayer}\par
\textbf{Skills: Sword Mastery 49 (Apprentice), Shield Mastery 46 (Apprentice), Physical Fitness 43 (Apprentice), Combat Mastery 41 (Apprentice), Power Strike 34 (Apprentice - Uncommon), Unarmed Combat Mastery 30 (Apprentice), Cleaning 29 (Initiate), Perfect Parry 26 (Initiate - Uncommon), Surprise Attack 23 (Initiate), Pain Resistance 22 (Initiate), Evasiveness 21 (Initiate - Uncommon), Damage Mitigation 21 (Initiate) Sprinting 21 (Initiate), Laboring 20 (Initiate), Bleeding Control 19 (Initiate), Dying Struggle 17 (Initiate - Uncommon), Club Mastery 15 (Initiate), Unyielding Vitality 14 (Initiate - Rare), Shield Throw 12 (Initiate - Uncommon), Parkour 11 (Initiate), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate), }\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
His status was… monstrous, to say the least.\par
Physical Fitness and Combat Mastery were known as amplifier skills. Overarching skills that made everything related to their purview more effective. They were also hard to level unless one trained diligently at high intensity, or went through life and death battles.\par
But who else could do both and attempt focused training in the middle of battle like Orodan?\par
Either Physical Fitness or Combat Mastery being in the 40s for an Apprentice was unthinkable, but for an Apprentice to have both in the 40s? Orodan’s battle power was now higher than his title would indicate.\par
He decided to live a little and thus switched his active title to Adept Slayer.\par
Orodan then decided to spend the rest of the loop seeking out more House Argon soldiers and went about hunting them across the town of Loviaston, causing a decent amount of mayhem and the town alarm bells to start going off after the first five minutes.\par
Militia troops responded but fearfully stayed right out of his way at the display of him slaughtering near-Adept level Argon guards like cattle. The Militia’s elite response unit would eventually respond, but that would take longer than he was planning on staying in the loop. That he was killing only the troops of House Argon and not targeting civilians also helped them maintain their non-interference.\par
Trouble unfortunately found him and he was reminded that he wasn’t invincible and brought back down to earth. After killing a few dozen more House Argon guards his loop was brought to an end by a late-stage Adept, a middle-aged man wearing a tabard bearing the House Argon sigil, who was on the cusp of achieving the Elite level in the spear.\par
Except, this man also had an Uncommon rarity active combat skill of his own.\par
Orodan almost couldn’t see the Lunge the man did from across a full street length to impale Orodan on his spear.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
A keening wail ringing in the night sky awoke him.\par
The Quest bestowal message was routinely brushed off as he got to his feet and began planning for the loops moving forward while furiously cleaning his home as always.\par
On one hand, he could start another crusade of loops against this new opponent whose spear caused his demise. It would undoubtedly lead to great gains, and perhaps even more new skills, something Orodan was beginning to collect a rather large number of.\par
But, on the other hand it wasn’t Orodan’s way to half-ass something and do it sloppily. He already felt as though he was expanding widely to acquire a lot of skills, but that he was starting to run the risk of lacking depth and quality in what he did have.\par
So what that he could kill one of House Argon’s stronger Adepts?\par
Orodan wasn’t satisfied with just the result, he needed to delve deeper and solidify some of his weaker skills and sharpen existing ones before he could move on. He was as stubborn as a mule, a man who would shut his mouth and chip away at a skill for months on end 'till he got a single level increase.\par
Thankfully, his current circumstances made his rate of skill gain something nations would go to war for.\par
So Orodan decided, he was going to return to the warehouse and solidify his understanding of some of his skills. Sure, he could kill Balus Mogram, one-on-one, but could he take him and all seven guards in the warehouse at the same time?\par
A feral grin emerged on Orodan’s face as he knew his next goal.\par
\par
“Balus Mogram come down and show your face! I demand a duel! For every second you waste I’ll continue to beat these useless guards black and blue!”\par
Orodan parried the swing of a hammer and delivered a pommel strike to the man’s gut which made him spit blood. The remaining six guards all began furiously attacking him at once.\par
It was insanity.\par
Orodan could easily kill a regular guard. His abilities were far beyond theirs.\par
But even with him being able to deliver thirty attacks a second now, the combined pressure from seven near-Adepts, each capable of launching at least six blows a second themselves… was nothing to scoff at.\par
Particularly with them all attacking him at once while he returned theirs and stood in one place while refusing to evade, only blocking and parrying with the sword was allowed. No skills such as Power Strike or Perfect Parry either.\par
This was Orodan’s new goal. To stand in one place as all seven warehouse guards furiously attacked him. He did not allow himself to move from his spot whatsoever. No matter how many wounds he took, no matter how many loops were cut short as he attempted the absolutely stupid feat of being able to stand and trade blows, purely with his sword, against seven near-Adepts at once… and come out on top.\par
Initially, he would always die when Balus Mogram himself joined the fray as the combination was far too much.\par
As he was on the cusp of achieving it, it came as no surprise that it took only the fifth loop of his self-imposed madness to receive a message he had been waiting for.\par
\textbf{[Sword Mastery 49 → Sword Mastery 50]}\par
\textbf{[Title Gained: Sword Adept]}\par
\textbf{[Additional Title Slot Gained]}\par
The messages would have been celebratory for anyone else. Even for Orodan himself whose life goal before his current circumstances was to become an Adept, it would be cause for joy at any other time.\par
But right now he had a goal, and it wasn’t to merely become an Adept.\par
The thirty-seventh loop passed and he was able to stand and trade evenly against the seven guards at the same time, however Balus’s arrival still led to him losing the exchange.\par
He could definitely kill all seven and Balus at once… if he allowed himself to move from the one spot and let up on his self-imposed restrictions. But he did not.\par
The eightieth loop passed and Orodan could finally evenly hold and trade blows indefinitely against all seven guards and Balus at the same time while standing in one spot and refusing to move, evade or use any other active combat skills.\par
He began the eighty-first loop by tracking Estilia down in a pottery shop a block away and throwing her through the double doors of the warehouse so she too could join in. Of course, the addition of a second Adept, to the training exercise caused him to begin dying frequently again.\par
His Sword Mastery and Physical Fitness weren’t levelling as fast. Each level got exponentially harder as one advanced, and because Orodan could kill these opponents easily if he wanted the simulated danger he was in didn’t count nearly as much as actual combat against stronger foes.\par
But bit by bit, he was still making progress.\par
And finally, after two hundred and three loops, Orodan got what he wanted.\par
His sword lashed out and caught both Balus’s and Estilia’s incoming blows, while a second motion of his sword, all within the same move, intercepted and diverted the weaker blows of the seven guards.\par
This was the tipping point.\par
His first return blow beheaded both Balus and Estilia at once, and his second and third strikes killed the remaining seven guards in an instant.\par
\textbf{[Sword Mastery 52 → Sword Mastery 53]}\par
\textbf{[New Skill (Exquisite) → Impregnable Bladewall 1]}\par
Two hundred and three damn loops, which meant dying two hundred and two times.\par
Orodan wouldn’t lie and say it was pleasant but by now his Pain Resistance of 26 truly did make most pain, even the pain of death, seem trivial. It was an unnaturally high number that would raise questions, but who else could train Pain Resistance by repeatedly dying like he could?\par
Of course, his Damage Mitigation of 29, Bleeding Control of 23 and his Unyielding Vitality of 20 meant that death took an uncomfortably long time to arrive, even when his limbs were lopped off, he was stabbed multiple times and had most vital organs destroyed.\par
Frankly, his enemies were more terrified of his ludicrous vitality and refusal to die quickly than they were of his unnaturally good swordplay.\par
And he himself still wasn’t used to maintaining consciousness for a full minute after being decapitated.\par
But despite suffering through some uncomfortably drawn out deaths, Orodan had accomplished his goal. He had acquired the skill he had felt the inklings of right from the beginning when he had fought against the two Northmen in his very first life.\par
None of his other skills had made gains because he hadn’t bothered using any of them during this crazy training regimen.\par
But now… he had an Exquisite rarity skill. This was almost unfathomable for Orodan who grew up an orphan and a street rat.\par
Exquisite rarity skills weren’t spoken of openly by those who had them, usually in hushed whispers and there were many rumors surrounding who had them. But it was usually very high ranking members of the military, powerful noble houses and other exceptional individuals who were likely to hold Exquisite skills.\par
And now Orodan had one.\par
Frankly, if someone decided to use an Observer orb on him he stood a very high chance of being reported and promptly ‘asked’ to go along with some very powerful individuals to wherever they chose.\par
The last rumour he heard of someone with an Exquisite skill a few years ago was a girl in the neighboring Tooksten County, and the Capital Guard came by within an hour of her using the Observer orb at her local crafting guild office. Her family suddenly skyrocketed in wealth and often went to go visit her in the capital and they spoke of how she was doing important work and had a very lucrative position in the High Forges of Karilsgard.\par
So Orodan had to tread at least slightly carefully if he didn’t want to be nabbed away to the Capital. Furthermore, his was an active combat skill of Exquisite rarity.\par
The likelihood of him missing out on the ability to influence the Battle of Ogdenborough due to being kidnapped by the Capital Guard and trained into being a military asset of the Republic was incredibly high if anyone caught wind.\par
And while that sounded like a dream career to Orodan, in the short term he didn’t want to go anywhere until he dealt with this damn Quest looming over his head.\par
And so he continued, eager to test himself against that very strong, spear-wielding Adept who put a stop to his rampage in Loviaston last time.\par
\par
Even at level 1 of Impregnable Bladewall, the difference was like night and day. An Exquisite skill was… powerful.\par
The tabard wearing spear-Adept confronted him like last time for daring to rampage and slaughter the troops of House Argon, but this time Orodan successfully used Impregnable Bladewall and fended off the dangerous Lunge and engaged the man in a heated melee exchange of steel on steel that tore apart the surrounding street with the shockwaves.\par
He was an Adept-level combatant now. And while regular Adepts couldn’t cause collateral damage with just their regular attacks, an exceptional Adept when combined with active combat skills absolutely could. And Orodan had an Exquisite rarity active combat skill. It went without saying that he could now cause a certain level of environmental destruction if he wasn’t holding back.\par
Impregnable Bladewall was his defense, and Power Strike was his offense. Furthermore, once he got into close-quarters combat Orodan kept pressuring the man and preventing him from gaining sufficient distance to use his active combat skill again.\par
He weaved both his offense and defense together beautifully and fought the man very evenly until the spear-Adept finally had enough and leapt away with an ugly look on his face.\par
“Who the fuck are you? A dog of the Republic who’s done playing the charade? If so why aren’t you at Eversong Plaza?” the man asked, and Orodan was surprised he was as forthcoming with the information. Then again, the attack was in a few hours and Orodan had already acted openly.\par
“Less talking, come here and fight me already!” Orodan replied as he gave chase.\par
Unfortunately, all good things must come to an end. The man was nearing the Elite level in his abilities and was thus able to outrun Orodan with a sizeable gap.\par
Furthermore, the alarm bells for Loviaston had been rung a while ago when Orodan started his massacre and enough time had passed.\par
So he finally got to see what the Volarbury County Militia’s Elite response unit looked like for the first time.\par
And by see he meant experience a city block levelling attack which likely splattered him into fine red paste.\par
He didn’t even see the attack which killed him, only the sight of an armored woman in Militia colors atop a brown griffin in the sky.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
A keening wail ringing in the night sky awoke him.\par
The Quest messages were brushed away, and Orodan got to his feet with a smile on his face.\par
“I actually forced an Elite-level member of the County Militia to come deal with me personally.”\par
He smiled and mentally called forth his status.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Combat Apprentice}\par
\textbf{Title 2: Empty}\par
\textbf{Available Titles: One Who Has Experienced Death, Sword Adept, Shield Apprentice, Physical Apprentice, Unarmed Combat Apprentice, Combat Apprentice, Cleaning Apprentice}\par
\textbf{Skills: Sword Mastery 53 (Adept), Shield Mastery 46 (Apprentice), Physical Fitness 43 (Apprentice), Combat Mastery 41 (Apprentice), Power Strike 34 (Apprentice - Uncommon), Cleaning 31 (Apprentice), Unarmed Combat Mastery 30 (Apprentice), Damage Mitigation 29 (Initiate) Perfect Parry 26 (Initiate - Uncommon), Surprise Attack 23 (Initiate), Pain Resistance 26 (Initiate), Sprinting 23 (Initiate), Laboring 22 (Initiate), Evasiveness 21 (Initiate - Uncommon), Unyielding Vitality 20 (Initiate - Rare), Bleeding Control 23 (Initiate), Dying Struggle 19 (Initiate - Uncommon), Club Mastery 15 (Initiate), Shield Throw 12 (Initiate - Uncommon), Parkour 11 (Initiate), Maintenance 8 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate), Impregnable Bladewall 3 (Initiate - Exquisite)}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor]}\par
He made the decision to change his title to Combat Apprentice and leave his newly gained second title slot empty. Titles and the number of slots one had were a symbol of social status. When one crossed 50 and achieved Adept level in a skill for the first time, they received a second slot. A third was received for crossing the Elite threshold at 70 for the first time, and so forth.\par
Of course, if a slot was left empty then to anyone using Observe it would only show the singular active Title, which had to have a Title assigned.\par
Orodan made this decision because the enforcers of House Argon at Eversong Plaza knew him growing up, and most importantly, they used Observe on every passing person they saw. So the discrepancy between Observing him the last time before the loops began, to now where he was suddenly an Adept? It would alarm them, and for the purposes of what he wanted to do, he didn’t need them being alerted instantly based off his Observe readings.\par
But still, Orodan’s smile grew wider at how far he had come.\par
Now it was time to put his stone head to work at grinding against the Quest once more.\par


\section*{Chapter 4 - Chipping Away At Mount Castarian I}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 4 - Chipping Away At Mount Castarian I}%
\par
There was a popular folk tale about a poor miner who while wandering the mountains found a motherlode of precious star-metal. Unfortunately, his Mining skill was too low to ever harvest it.\par
Determined to raise his skill to the point that he could, he started mining the very mountains themselves. One after another, he chipped away day in and day out at the foot of the massive mountains that made up the range.\par
And as entire mountains started to fall due to his growing talents, he one day turned around and realized that he had found many more lodes of precious metals over the course of his journey.\par
Orodan felt as though he was the man in that story.\par
He knew there was no way he could beat the challenges before him at Eversong Plaza at this point in time. He could fight evenly against a single powerful Adept with an active combat skill, but Eversong Plaza had dozens of them. They also had Elite level fighters, and who knew what else was inside. It would be futile death after futile death.\par
In fact, he could now if he so chose decide to immediately flee to the Capital, display his prodigious talent and be accepted into the Capital Guard for mentorship and being groomed into a military asset of the Republic.\par
He didn’t think the war machine’s reach was capable of going all the way to the Capital, so fleeing the day he had relived hundreds of times was a real possibility for him now.\par
But would Orodan be Orodan if he did that?\par
His heart, his blood, it called to him to batter through even the biggest mountain in his immediate path with nothing more than his head. Either the mountain would break, or his head would.\par
But Orodan had the advantage of having his head returned to how it was every time it shattered.\par
His usual daily routine was entirely forgone for once, something that left him feeling slightly dissatisfied, but something that was necessary.\par
A person might think someone in his situation would coordinate with the loyalists coming to attack at Eversong.\par
Orodan would say that person didn’t know him very well.\par
His sword split the first woman in front of him, an Adept enforcer, in half. A combination of Surprise Attack and Power Strike reaping her life in an instant. Most people didn’t have defensive skills or the ability to train them like Orodan did. So singular, powerful blows could slay the average Adept in one strike.\par
What he learned the hard way however, was that this wasn’t the warehouse in Loviaston. And the level of vigilance and combat power concentrated here was an altogether different thing.\par
Before he could begin massacring the non-Adept guards, Two enforcers, one wielding a spear and one a great axe, immediately engaged him with active combat skills of their own, and it took everything Orodan had to defend against them, even with Impregnable Bladewall.\par
Mages at lower levels were usually sequestered away in magic academies if talented, or doing non-combat magical trades and jobs.\par
But a powerful lightning bolt sailing towards his face after two seconds of the melee marked Orodan’s first ever battle against one of the mana-focused.\par
Four seconds passed, and despite his valiant efforts Orodan began taking some serious wounds.\par
The great axe buried itself hard in his ribs and the spear impaled his shoulder, all the while the lightning ran throughout his entire body and virtually locked it up, preventing him from using much of his body at all. Even with all his defensive and vitality skills were working overtime to keep him in the fight, he was approaching death.\par
He was strong enough to resist and not instantly die against the onslaught, but was still overwhelmed. This was probably some of the most intense combat he had ever experienced.\par
\textbf{[Combat Mastery 41 → Combat Mastery 42]}\par
\textbf{[Impregnable Bladewall 3 → Impregnable Bladewall 5]}\par
Six seconds passed as the moon’s pale light illuminated the plaza and five more Adept enforcers rushed out of the tavern’s doors. Orodan also saw a javelin speeding towards his head through the air alongside a second mage about to cast a powerful fire spell.\par
And as the combined assortment of elemental destruction and weaponry reached him, he knew his loop was over.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
A keening wail ringing in the night sky awoke him.\par
Orodan sat up in bed, brushed away the Quest messages and immediately got to his feet and Sprinted for Eversong Plaza again.\par
This was his new bout of insanity.\par
To charge and attempt a rampage at Eversong Plaza in the middle of the night right after beginning the loop. No coordinating with the loyalist attackers at noon. No enlisting allies.\par
He could only kill one Adept in a surprise attack, and that too the one farthest out from the Tavern, before a level of calamitous response fell upon him.\par
With his first try he only had six to eight seconds of life. His vitality and defensive skills not doing enough at their current levels to delay death against the total bodily destruction that came with being hit with multiple Adept level mage spells.\par
All in all, the entire loop, from waking up and Sprinting to the Plaza in a minute, till his death… probably took less than two minutes.\par
But, he would eventually improve.\par
\par
Each loop was less than two minutes long.\par
And Orodan began attempting and experimenting training in skills which nobody in their right mind would try training the way he was.\par
Shield Mastery and Combat Mastery had both risen to Adept level, which would be incredible for one at his age outside of a time loop context, but progress was very slow after someone reached level 50 in a skill, at least without fighting against stronger opponents.\par
A lot of his skills had increased across the board, and pretty much all of his defensive and vitality skills had crossed the Apprentice threshold at 30. Something which lead to the interesting problem of death taking even longer each time, so he spent the remaining minutes of life being electrocuted, burnt and hacked apart focusing on developing a resistance skill.\par
What were resistance skills?\par
They were powerful, very highly valued, but just not deemed safe or practical to train. Some argued that developing a resistance skill essentially involved torturing one’s self. Others clamored that it involved understanding something about the nature of the attack one was resisting.\par
Most resistance skills were the product of Bloodlines or ritual enhancement to alter one’s self innately.\par
But what madman could sit there and forcibly endure lightning bolts till he died? And how many times would this process have to repeat until one received one of the vaunted resistance skills?\par
The answer for Orodan was three-hundred and forty-nine loops.\par
\textbf{[New Skill (Exquisite) → Lightning Resistance 1]}\par
Orodan experimented with multiple kinds of techniques to obtain the first level of the skill.\par
At first he thought simply letting himself be drowned in lightning countless times would do the trick. But he quickly thought focused experimenting would be superior.\par
So he tried flexing his muscles in different patterns when lightning hit, instinctually trying to give mental commands with his full willpower to the lightning coursing through his veins even though it wasn’t his mana, and he wasn’t a mage with access to his mana pool.\par
He also tried getting a better feel for moving while under the effects of fatal levels of lightning coursing through his body.\par
In the end, it ended up being a combination of the two methods, training the techniques for moving while paralyzed by lightning, and mentally trying to guide the lightning itself, that yielded results.\par
He had yet to get a Fire Resistance skill, but he figured some focused training in unveiling its secrets would help with that.\par
\par
The three-hundred and fiftieth loop onward his Lightning Resistance skill immediately began to show how powerful it was. While it didn’t let him ignore the element altogether, even at level 1 it let him mostly move normally even while being assaulted by furious torrents of lightning from a now flummoxed House Argon lightning mage-Adept.\par
Outside of the loops, level 1 of Lightning Resistance wasn’t enough to prevent severe injuries requiring extensive recovery afterwards. But within the context of this fight where he could retry infinitely? He might as well have been immune to the mage’s lightning given it had no stopping power against him.\par
Seeing his face twist and grimace in confusion as his lightning was massively reduced in effectiveness was incredibly satisfying for Orodan. The man must have been an arrogant asshole about his lightning.\par
Furthermore, the incredibly intense melee against two Adepts, each with their own active combat skills of Power Strike and Multi-Attack had levelled Impregnable Bladewall to 17, and the difference it made at level 17 instead of its previous level 5… was massive.\par
Active combat skills were a multiplier, but even then the Power Strikes and Multi-Attacks of the two Adepts combined, weren’t capable of getting past his Exquisite rarity skill. It was an Exquisite skill for a reason, and alongside Lightning Resistance he could now survive the first six seconds of the engagement in relatively good condition.\par
That was when he ran into his new wall head-first however. The second mage… was an Elite-level fire specialist.\par
And now he knew why the loops almost instantly ended once the man’s concentrated fire beam reached him.\par
\textbf{[Quest Failed → Battle of Ogdenborough - You have died]}\par
A keening wail ringing in the night sky awoke him and Orodan nearly slapped the Quest messages out of the way and rushed for the Plaza once more.\par
His new objective, to find a way to develop Fire Resistance.\par
\par
Burning to death was supposed to be painful.\par
But Orodan wasn’t sure if it was his ludicrously high Pain Resistance or the fact that the Elite fire mage’s flames killed him almost instantly; but he barely felt much before he woke up to the sounds of the harpies again.\par
It was frustratingly difficult to train something you had such little exposure time to.\par
Unlike the lightning mage who was an Adept and whose spell power wasn’t enough to kill him immediately; this Elite’s fire spells left him with almost no time to analyze what was happening to his own body and appropriately test out counter measures and experiment with trying to grasp the first level of Fire Resistance.\par
He began trying every single experiment and theory he could think of to counteract the temperature and increase his own body’s resistance to fire.\par
Loops three hundred and fifty to four hundred were spent trying to mentally command the fire once it hit him and before it killed him.\par
Loops four hundred to four hundred and fifty were spent trying to forcibly cool his body via powerful breathing and mental commands while trying to command the fire in tandem.\par
It took all the way till the seven-hundredth loop for him to gain a second of life due to his Unyielding Vitality hitting level 44 due to the sheer number of times he died and his dogged concentration on gaining even an extra split second of life.\par
And Orodan treasured this extra second as though it was the finest of treasures.\par
He began even attempting to somehow harness the hostile lightning coursing through him into defending against the near instant-death fire beam. But it was for naught on that front.\par
Finally, by loop eight-hundred and ninety-eight Orodan’s Unyielding Vitality had progressed to 50 and hit Adept, and for a Rare skill to be at Adept level was unfathomably powerful and it allowed him a full three seconds of life as he now began living long enough to experience the feeling of being charred to a complete crisp as his flesh disintegrated to the bone and the bone turned to ash.This tale has been unlawfully lifted from Royal Road; report any instances of this story if found elsewhere.\par
While he kept experimenting and grinding, occasionally he’d get slightly bored of the routine and spice it up by talking to his enemies mid-battle.\par
“Hey, lightning fucker? What’s your name? You must be an embarrassment to your family with those piddly little bolts?” Orodan asked before the man even cast his first spell this loop.\par
“What the hell did you just say?! I Sagatos Astrapium won’t brook such insults!”\par
And so a furious torrent of deep blue energy came Orodan’s way.\par
Which was summarily ignored as Orodan only pronounced one word during his melee against the two Adepts.\par
“Weak!”\par
In a surprising turn, the man actually didn’t cast a single further lightning spell that loop! The ugly look of shame and red face he had at Orodan’s insult alongside the shock at his lightning being ineffective actually sidelined him entirely.\par
Of course, the fire beam came along and ended his loop all the same.\par
“Hey, who taught you to use that axe? Your movements are inefficient, you should be striking with more conviction, your Power Strike skill must be low huh?” Orodan insulted the man on the next loop while turning away his active combat skill. “What’s your name?”\par
“I’m the third strongest great axe Adept of House Argon! Say the name Buximus Valadiyadris around town and everyone will know! Who the hell are you?!” the great axe-Adept angrily replied as he attacked with greater fervor.\par
Which was still easily defended against by Orodan, as by now Impregnable Bladewall had reached 24 and the issue wasn’t defeating the Adepts in melee, but surviving the Elite fire mage who cast his beam of death from atop the balcony.\par
Filling his seconds of life each loop with some dialogue was one of the things that helped spice up Orodan’s training. For even for one as stubborn and dogged as he, doing the exact same thing over and over could get repetitive.\par
“I heard this Adept archer with a great bow in Scarmorrow talk about how he’d turn you into a pincushion the other day, who was that?”\par
“Erestur? That weak fucker doesn’t even have an active combat skill! They sent him there as a demotion for being so weak! I’d shove my axe up-”\par
The fire beam hit him before Buximus could finish talking and he then focused too much on training against it to ponder more.\par
But once he woke back up in his bed he made a mental note of the name. So that’s who the cunt archer was? Orodan resolved to spend at least one loop bullying him as recompense when he decided to take some time off far down the line.\par
“Hey fire mage! Why the fuck are your flames so hot?!” Orodan asked on his next loop.\par
He received no reply besides a cold and indifferent look as the Elite fire mage killed him with the fire beam all the same.\par
“Hey, you hit pretty good with that axe of yours, who’s that uppity Elite fire mage on the balcony?” Orodan asked on the next one as he Perfect Parried Buximus’s strike.\par
“Don’t concern yourself with Lord Aeglos! For daring to interrupt his star-watching you’ll die here for your transgressions!”\par
The fire beam sent his way by Lord Aeglos ended his loop as usual, albeit with a delay of several seconds that surprised even the usually stoic man.\par
Orodan’s brute force method was paying off and he was starting to get somewhere. He felt something there in the beam of fire that killed him, something beyond just the fiery temperature and subsequent death.\par
Elites, particularly those who were Elite-level in a combat skill were some of the most powerful people in society, so for Orodan’s killer to be a member of the nobility was hardly shocking. Virtually all Elites held some kind of powerful position in society.\par
\par
It was now the nine-hundred and eighty-ninth loop.\par
By now Orodan was slowly coming to understand that the flames from Lord Aeglos and the lightning from Sagatos Astrapium both had something in common. He didn’t understand what it was, but he felt it, he experienced it, and he’d died from it nearly a thousand times.\par
He didn’t need an academic understanding to realize that there was a common energy source in both attacks, albeit molded differently depending on the nature and talents of the caster.\par
And as Lord Aeglos’s fire beam hit him, he felt it as usual, brought all his experiences and insights into what he’d been feeling for the hundreds of loops together.\par
And for the first time in nearly one thousand loops, resisted it.\par
\textbf{[New Skill (Legendary) → Mana Resistance 1]}\par
The difference was utterly astonishing. The fire beam from an Elite-fire mage a whole tier above him just… washed over him. As though it was a flashy cantrip cast by a wandering illusionist with no real substance.\par
Was this… a Legendary rarity skill? The stuff of legends and fairy tales that nobody could confirm as real?\par
Even Orodan who was suicidally daring and foolhardy, found himself quieting down in the midst of the battle. The seconds stretched on as Lord Aeglos’s face warped in confusion, then in a genuine hint of shock, and even the five reinforcing Adepts who normally rushed out of the tavern and formed a perimeter as the fire beam would usually melt him to death, had disquieted looks upon their faces at the sight.\par
It was still hot, scaldingly so.\par
But compared to the previous beam that would turn him to ash within seconds, this was akin to being dipped in a vat of boiling water. And only at level 1 of the skill.\par
“Who… who are you?” The spell ceased, the plaza went quiet and a voice he hadn’t heard speak before till this loop rang out as Lord Aeglos spoke. “I sense no barrier protecting you, Observe tells me you’re still an Adept, which we both know is blatant title obscurity… but still… even Masters cannot simply shrug off my fire beam.”\par
Orodan looked around to see nobody was attacking him any longer.\par
And that didn’t sit well with him.\par
“Who am I? That’s none of your fucking business. All I’m here for is to slay every single member of House Argon in Eversong Plaza and tear apart that hunk of scrap metal hiding under the mountain!”\par
With those words Lord Aeglos’s face hardened and the battle resumed.\par
Five more mages joined Aeglos and the weakling Sagatos, but even the combined magical torrent from them which tore apart the very earth, scorched the grounds of the entire plaza and sent Orodan flying into the nearby streets… still didn’t kill him.\par
Sagatos and the other five mages that joined in were Adept-level. And now Orodan could genuinely say he had the ability to outright ignore most magic at the Adept level, for they neither made him feel anything, nor did they cause any damage to his body.\par
Lightning harmlessly coursed through as though it was a natural part of him. Wind blades simply bent and broke on his flesh as though they were gentle breezes, and ice refused to stick and form on his skin whatsoever. He resisted the very mana that made up the hostile spells coming his way.\par
Finally, Lord Aeglos started letting loose some very powerful spells, probably his active skills. These mighty spells destroyed multiple buildings with the collateral damage from each one, and although the heat of the flames was quite hot and scalded him, what started becoming dangerous was the debris and hard impacts on the ground Orodan suffered as he was shot around like a ball.\par
Magic was now something he was virtually immune to, particularly as he continued to train this new Legendary skill which was at 4 due to the sheer barrage.\par
His unfortunately high vitality and defense skills allowed him to survive a long time even amidst this barrage however, and he gained a new skill.\par
\textbf{[New Skill → Impact Resistance 1]}\par
But this wasn’t an ideal situation for Orodan, as he was now being bounced around like a child’s plaything, and his impossible survivability still kept him alive.\par
Mana Resistance and Impact Resistance continued to level, and even Physical Fitness gained a level due to the sheer exertion of keeping his footing, bracing to stand strong against the explosions and impacts, and constantly moving about.\par
His weapons and clothes had all been utterly disintegrated by this point. And if not for the awe-inspiring power of a Legendary rarity skill keeping him alive, he should’ve been killed a hundred-thousand times over by this level of damage.\par
This was what made mages incredibly dangerous. In a one-on-one duel a martial combatant held the advantage in terms of speed, durability and combat mastery. But as a group? Mages were capable of terrifying artillery style bombardments which could utterly suppress groups of warriors. And Orodan was but one man facing a mage an entire tier higher who was assisted by six other Adept mages.\par
The Adept warriors had long since stepped back as they’d be minced by the bombardment.\par
But alas, the damage coming his way was mostly magical, and magic was composed of mana.\par
So, slowly but surely. Without dying, his Impact Resistance and Mana Resistance gained levels. And finally, after nearly a full two minutes of an insane barrage which destroyed much of the town, Orodan was able to stand tall even in the face of it.\par
And he took a step forward. And another. And soon the distance between him and Lord Aeglos grew shorter.\par
Until finally he was face to face with the man, and the Adept mages near the Elite also began holding their spellfire lest they hit their Lord himself.\par
\textbf{[Agathor, God of War, smiles upon you]}\par
\textbf{[Received Blessing → Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark]}\par
He was nearing death from the sheer amount of total damage that he had accrued from impacts, shrapnel from explosions and whatnot. But he still had strength left despite undoubtedly looking like a mangled ghoul.\par
So he reached out with both hands, for the face of the arrogant fire mage.\par
But suddenly he felt a fist enter his chest and go out the other side.\par
“Little Eggy…” a haunting voice crooned. “Is this what you caused a mess for? From the sounds of it I thought the Republic gave up their farce and attacked earlier than scheduled.”\par
The voice didn’t belong to the skeletal monk in front of him with its hand embedded in his chest which appeared faster than his eyes could track.\par
It belonged to the woman behind the skeleton.\par
A pale, gaunt face which looked as though she belonged in a coffin rather than standing before him and speaking. Her hair was pure white, her skin perfectly unblemished in a creepy way that would have anyone’s instincts screaming that it was unnatural and abhorrent. And her eyes were glowing a subtle shade of a sickly green color. The classic appearance of a necromancer.\par
The nearby Adepts all fell to their knees in respect and supplication.\par
“M-master… I apologize for my failure… this man, he-”\par
“Hmm! I see it! He should be screaming in pain and torn apart as his bones decay and necrotic spikes erupt throughout his body…” the woman spoke in an eerie tone as though she was examining a dissected rat. “…but it’s as though only the physical attack of my pet had any effect on him. The mana… it can’t find any purchase on him whatsoever.”\par
Orodan strained and struggled, letting loose his fists against the reanimated skeleton, but it was at least Elite level and his Unarmed Combat Mastery wasn’t even Adept.\par
Dozens of furious punches and he began to only slightly damage it. Plus, his vision began to darken as whatever source of vitality his body was running on genuinely began to run dry after all the ludicrous damage he took.\par
“And he’s somehow still alive despite all this damage. Incredible… is it a Bloodline? A Blessing? There’s no way you’re an Adept only of course. Hiding your titles are we? Are you some secret weapon cultivated by the Republic?” her questions came frantically. “Oh! How I’d love to capture and experiment on you… but alas, we’re on a strict schedule today and I can’t afford one of my nicer pets being blemished by your brutish fists. Kill him.”\par
And suddenly another skeletal hand gripped around his face, and the glowing green flames inside the hollow eye sockets of his bony killer peered into his own.\par
The skeletal hand squeezed, and his vision went dark.\par
\par
A keening wail ringing in the night sky awoke him, and Orodan was thankful his survivability had not yet grown enough to allow him to survive his head being crushed like a grape.\par
He brushed away the Quest messages routinely but sat for a moment.\par
Another Blessing by Agathor?\par
The first time he was Blessed was when he fought and killed a few Guzuharan raiders in his first life, followed by rushing that monstrous Ogre barbarian in a hopeless attack. Was it the valor and bravery he displayed that earned Agathor’s approval?\par
Then, this time he earned his second Blessing from the same God when he stood tall in the face of an impossible barrage of magic. And Agathor was a God who was known for looking down on ‘cowardly’ individuals, which a lot of mages tended to be due to their risk-aversion.\par
It was a misconception that Agathor disliked mages in general, for if that was the case he’d dislike archers, peltasts and ranged martial fighters as well.\par
But Lord Aeglos, despite his stoic mask, seemed to be a bit of a coward from the measure Orodan got of him near the end. The type that crumbled if they didn’t have superior power or if they had to fight an equally strong opponent.\par
What really concerned Orodan however was Lord Aeglos’s ‘master’.\par
He was almost certain the woman was a Master-level necromancer. An Elite would never refer to anyone as their master otherwise.\par
Orodan didn’t know whether she intervened in order to mop up the mess or to prevent even the slightest bit of risk towards her disciple who she seemed to dote on in a creepy manner. Either way, she would be a very real obstacle in his path.\par
Furthermore, by this point given his new Legendary rarity skill, his enemies were starting to often overestimate his rank. With both Lord Aeglos and his master assuming his title as a Combat Adept was a lie.\par
He mentally called forth his Status.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Combat Adept}\par
\textbf{Title 2: Empty}\par
\textbf{Available Titles: One Who Has Experienced Death, Sword Adept, Shield Adept, Physical Apprentice, Unarmed Combat Apprentice, Combat Adept, Cleaning Apprentice}\par
\textbf{Skills: Sword Mastery 58 (Adept), Shield Mastery 55 (Adept), Combat Mastery 53 (Adept), Unyielding Vitality 52 (Adept - Rare), Physical Fitness 47 (Apprentice), Damage Mitigation 39 (Apprentice), Power Strike 37 (Apprentice - Uncommon), Pain Resistance 37 (Apprentice), Perfect Parry 37 (Apprentice - Uncommon), Dying Struggle 34 (Apprentice - Uncommon), Bleeding Control 34 (Apprentice), Unarmed Combat Mastery 32 (Apprentice), Cleaning 31 (Apprentice), Surprise Attack 27 (Initiate), Sprinting 25 (Initiate), Impregnable Bladewall 24 (Initiate - Exquisite), Evasiveness 24 (Initiate - Uncommon), Laboring 22 (Initiate), Impact Resistance 19 (Initiate), Club Mastery 15 (Initiate), Lightning Resistance 12 (Initiate - Exquisite), Shield Throw 12 (Initiate - Uncommon), Parkour 11 (Initiate), Maintenance 8 (Initiate), Mana Resistance 7 (Legendary - Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Intimidation 6 (Initiate), Deception 4 (Initiate),}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor] [Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark]}\par
There were two massive gains from this series of loops.\par
The first being his new Legendary rarity resistance skill. Something that would likely have him chased to the ends of the earth for abduction and indoctrination into a nation’s military force if anyone found out.\par
The second being his second Blessing from Agathor. Which could cause a similar upheaval and outright kidnapping if he approached things the wrong way. Furthermore he’d really have to avoid Temples from now on as any battle-priests or high-levelled faithful of Agathor would be able to detect that he had two Blessings if they met him face-to-face. Which would be a problem because the only kinds of people with more than one Blessing were Favored.\par
Favored were people who had the eyes of the Gods themselves upon them at all times. Their actions being watched and guided. And depending on what God was watching them, they were destined for great things and nations would furiously scramble to entice them to their side as they were a source of great karma and good fortune.\par
The most well-known Favored was Lady Lakshiya, the High Oracle of the Cathedral of the Gods in the Capital. Her advice and counsel was favored and sought by not only the Council in the Capital, but also by the leaders of other nations who would visit simply to meet with her and hear her portents.\par
Which meant that being Favored, was a rather big deal. It would certainly lend credence to his claims of having received a Quest if he ever decided to open up about that.\par
Orodan wasn’t quite sure what Agathor’s thought process was when deciding to give him another Blessing. After all, even when he revealed that he had his first one, the battle-priest in Scarmorrow had seemed confused as Agathor himself did not know when he blessed Orodan. While the Church liked to spout a lot of dogma about the Gods being all-knowing and omniscient, Orodan suspected that the other, more academic theory proposed by certain ‘heretical madmen’ was true.\par
That the Gods couldn’t glimpse too much into the affairs of the mortal realm unless it was through their priests. And the only things they could do in terms of interference were bestowing Blessings or possessing Avatars.\par
Orodan shook his head and got to his feet.\par
His break had lasted long enough.\par
With his new Legendary skill and Blessing, it was time to return to the fray and smash his head against the mountain that was Lord Aeglos and the Master-level necromancer who he called his master.\par
However many thousands of loops it took, Orodan was stubborn. He would persevere, and he would grind.\par


\section*{Chapter 5 - Chipping Away At Mount Castarian II}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 5 - Chipping Away At Mount Castarian II}%
\par
Since surviving the fire beam wasn’t an issue anymore, there was now new ground to gain in this fight.\par
The nine-hundred and nintieth loop began with Orodan’s customary Surprise Attack and Power Strike on the very first hapless Adept he had slaughtered nearly a thousand times by now in a practiced routine.\par
The woman was split right in half and Orodan immediately managed to slaughter three non-Adept guards before the Buximus and the weaker spear-Adept engaged him in melee with Sagatos flinging lightning from overhead on a lower balcony.\par
Prior to this, Orodan had been holding his offensive prowess back even as the loops progressed onwards, his priority having been developing a skill to resist the formerly lethal fire beam cast by Lord Aeglos.\par
But now he wanted to gain new ground from this loop onward, his priority being running headfirst against the new wall that was Lord Aeglos and the Master-necromancer protecting him.\par
Which meant that Impregnable Bladewall held off the assault, but he actually decided to reciprocate for the first time in a long time.\par
A Perfect Parry imbalanced Buximus, its skill level combined with his Physical Fitness now being high enough to make even near-Elite melee specialists stagger as their guard was exposed. And a Power Strike carved through the accompanying weaker spear-Adept’s armor and bisected him.\par
His new Blessing was strong. Evasion was no longer possible for his enemies.\par
A second Power Strike took the head off of Buximus himself, and Orodan leapt onto the balcony while completely ignoring the lightning bolts of Sagatos as he got right up in the mage’s face.\par
Sagatos looked terrified at the sudden turn of events.\par
Frankly, without melee fighters tying Orodan down, a mage of the same level, barring skills which allowed them to fight faster, was at a severe disadvantage. And Sagatos was a coward and a weakling.\par
And Orodan’s second Blessing made it so he couldn’t even flee. It was frankly perfect for hunting down spineless mages.\par
“Back away fro-”\par
Sagatos’s head was separated from his neck and Orodan moved on to engage the five reinforcing Adepts.\par
It was difficult, and even though Impregnable Bladewall had improved tremendously, he still took a blow here and there against the five-on-one onslaught. But his survivability now was unfathomable to these people, and so he happily accepted damage trades which he knew he’d survive in order to return unavoidably lethal Power Strikes of his own which quickly reaped the lives of three out of the five Adepts before a much earlier than expected fire beam hit him in the back.\par
Four seconds.\par
If he fought defensively and appeared to not be making ground against the initial engagement, Lord Aeglos wouldn’t start acting until the eighth second. A timeline which was now halved as Orodan’s frankly terrifying blitz and massacre had likely caused the Elite to get serious right from the get-go.\par
In the next two seconds the remaining two melee Adepts died and Lord Aeglos stood in his usual spot atop the highest balcony of the tavern with a look of genuine concern on his face as his fire beam was essentially walked through.\par
Even its impact force was almost ignored.\par
Which lead to a reaction Orodan should have expected, but an outcome that made him grumble all the same.\par
“Sound the alarm! We’re under attack! Master please help us!” the man cried out with a magically infused voice.\par
Lord Aeglos, was a certified gutless coward. And he would honor Agathor by putting the rat down.\par
The good news was that it seemed the Master-necromancer was at least some distance away, as she didn’t arrive until at least two minutes of bombardment in the last loop. And it was a similar situation this time around as well.\par
The bad news was that a torrent of Adept-level reinforcements began crawling out of the tavern at a steady rate. Worse, while Orodan could survive the Elite fire mage’s spells, his weapons could not.\par
His sword turned to molten slag in his hands and slipped through his fingers. His shield disintegrated, and his clothes were burnt clean off, leaving him in the nude. Not that he was shy of such things.\par
So he reached Lord Aeglos with no more than his Unarmed Combat Mastery to rely upon.\par
Which proved… to be surprisingly enough?\par
It shouldn’t have surprised Orodan. But Elites specialized in different things.\par
The gulf between him and the Elite-level skeleton that slaughtered him last loop was tremendous in melee combat.\par
But once Aeglos’s main advantage of magic was nullified? The man had little to no ability in anything martial. Frankly, Orodan wouldn’t put his Physical Fitness at even the level of an Apprentice.\par
A swift unarmed Power Strike which the man couldn’t flee or evade crushed Lord Aeglos’s skull.\par
\textbf{[New Title: Elite Slayer]}\par
The acquisition of the title was but a small distraction which he quickly brushed off as a crowd of dozens of Adepts mobbed him.\par
Impregnable Bladewall still worked with just his fists, however the effectiveness was multiplied by his far lower Unarmed Combat Mastery instead. And if Impregnable Bladewall, even with a sword and shield, still allowed blows through in a five-on-one against Adepts; then it was utterly overwhelmed against the mob of nearly fifty Adepts attacking him from all sides.\par
And when Orodan thought he might be able to survive through attrition and playing the long game via his incredible survivability, he was reminded that two minutes had passed.\par
And the now dead Lord Aeglos’s Master-level master had arrived.\par
And she was not happy.\par
“You killed my favourite little disciple!” she howled, a chilling madness reverberating throughout the entire Plaza.\par
And when she realized that the colossal beams of pure necrotic energy which levelled massive swathes of Ogdenborough weren’t outright killing him but only causing him small black spots of decay to appear on his otherwise functioning body. She sent a new pet out.\par
It was big, at least a head taller than the Ogre-barbarian who’d killed him in his first life. Some kind of eight-armed rotting undead abomination with horns protruding from its head.\par
It moved faster than anything he had ever seen before.\par
Suffice to say, if the Elite-level skeleton killed him without any struggle in melee, then this thing was far beyond him.\par
Orodan was torn to shreds and his remains were scattered all over Ogdenborough. The sheer rage and ferocity of that thing was inhuman. Whatever creature it was in life, it became even more fearsome in death.\par
A keening wail ringing in the night sky awoke him, and for once Orodan took a moment after brushing the Quest message away to remain in bed and simply… exhale.\par
The traits of being vicious, bloodthirsty and ferocious were ones Orodan was often described with.\par
But whatever that thing he fought was… it possessed a beyond human level of rage and sadism in its butchery. Orodan had a lot of work to do, even in regards to his own warrior spirit and mentality before he could properly fight such a nightmarish creature toe to toe like a warrior.\par
The reminder of his own weakness in the larger scale of things was offset by his hint of pride at the fact that he had killed an Elite.\par
Elites were essentially the most powerful people in society, and for him to have killed one at a lower tier himself? Even if Lord Aeglos was a mage and he had a Legendary skill which completely nullified the man’s specialty; it was nothing but a legendary feat itself.\par
So Orodan resolved that he wouldn’t give up, no matter how daunting the foes before him were. He would simply keep hitting his head against the impassable wall.\par
\par
Mana Resistance and Impact Resistance continued to increase in level as he was knocked about by the Master-necromancer’s incredibly destructive beams of pure necrotic energy, and when that failed, that abomination was sent against him.\par
The power of necromancers didn’t necessarily lie in their personal combat prowess, but mainly in their undead minions. Necromancers sharpened their overall power by finding, killing and bringing into their collection, more and more powerful creatures, and perhaps even enhancing them.\par
So Orodan held a small bit of hope that if he managed to eventually somehow defeat this Master-level necromancer’s minion. As impossible as it seemed, he had a shot of defeating the necromancer herself.\par
And so it began.\par
Orodan was torn apart, oftentimes sadistically, in almost every single way imaginable.\par
The long, drawn out deaths as his limbs were ripped off, he was chewed alive and more, were probably the most painful things he had ever experienced. Furthermore it was objectively degrading and made him feel weak and powerless.\par
Being killed by sentient beings felt as though it was a death in honorable battle. But this freak of nature tearing him apart and toying with him as though he was mere prey was something else entirely.\par
But he still refused to give up, for this was the personality of Orodan. Who knew? Perhaps it was a Bloodline of his, to be able to mentally persist for so long against pure impossibility.\par
His Pain Resistance skyrocketed and he began gaining new skills over the course of fighting this freakish creature. And he turned his usual focus on fighting and experimenting.\par
Although calling it fighting was overstating it when he was basically torn apart over the course of a minute. With it only lasting so long because a part of the creature’s retained personality in undeath was excruciatingly sadistic.\par
The message greeted him on the fifty-third loop of this self-imposed torture.\par
\textbf{[New Skill (Rare) → Slashing Resistance 1]}\par
And that death and the subsequent loops onward became even more horrifyingly painful. For as the skill levelled alongside his constantly increasing suite of defensive skills, each death took ever so slightly longer and gave the fucking thing even more opportunity to butcher him.\par
\textbf{[New Skill (Rare) → Piercing Resistance 1]}\par
Was the message he got on his one-hundred and ninth loop.\par
He must have fought and died for what felt like ages. His entire waking existence was filled with nothing but fighting, death and pain. But, incredibly slowly but surely he started to gain ground.\par
Dying Struggle levelled up to 56, which gave him some freakishly increased abilities of his own in every single area as he was close to death. That alongside his own growing rage and indignation at being torn apart lead to another skill at loop four-hundred and ninety.\par
\textbf{[New Skill (Rare) → Death Rage 1]}\par
It wasn’t an ability that required him to be dying, but it was one that would eventually lead him to death if he kept using it for a while. Of course, for Orodan when was death ever an issue?\par
It was an empowering type skill to essentially siphon his very vitality and lifeforce into increasing his physical prowess. And he had a lot of vitality to spare given his Physical Fitness, and every ounce of it counted for far more thanks to Unyielding Vitality. So even though it was a Rare skill, it felt more like an Exquisite skill in terms of power.\par
He actually managed to leave visible damage on the beast for once and was actually able to see some of its slower moves.\par
The loops following that his newfound Death Rage allowed him to butcher all of the dozens of Adepts that rushed him after the death of Lord Aeglos. Which moving forward left him in the awkward position of having to wait for the arrival of the Master-necromancer and her beast.\par
It incensed her even further to see every responding Adept dead before she arrived.\par
At the six-hundred and second loop his experimentation in attempting to mentally focus on his body and essentially toughen himself all around through intense concentration even in the middle of taking damage paid off, and he was rewarded with another skill.\par
\textbf{[New Skill (Exquisite) → Iron Body 1]}\par
Deaths now took excruciatingly long, but he also survived the initial fight till the arrival of the necromancer with much more life left in him. This finally allowed for a unique situation where he was strong enough to deal some very minor but visible damage to the abomination, and also tough enough to survive it for ten seconds without losing his limbs and becoming unable to effectively deal damage.\par
The monster became consumed by an even greater rage whenever it realized Orodan was going toe to toe against it and actually reciprocating some damage, even if the trade was overwhelmingly lopsided.\par
He continued fighting and dying past a thousand loops. Even though he still kept count, the number became meaningless. Only the slow but steady trickle of his skill levels rising was what mattered to Orodan.\par
Around loop number one-thousand four-hundred and forty-three his Death Rage had reached 45 and his Iron Body had reached 38, and Physical Fitness hit 51. This in combination with his now high levelled defensive and vitality skills lead to a crack in the impassable barrier he faced.This tale has been unlawfully lifted from Royal Road. If you spot it on Amazon, please report it.\par
Orodan was now strong enough to start grappling one or two of the abomination’s limbs in an attempt to minimize the damage he received and put it at an awkward angle incapable of hitting him properly.\par
It was still drastically physically superior to him, but it was larger than him. His entire body was perhaps the size of one of its arms.\par
But if he put his full body strength into it, he could grapple and tie up one or two of these arms.\par
\textbf{[New Skill → Wrestling 1]}\par
The Abomination roared in horrifying rage and psychotic frenzy as it attempted to throw Orodan off, all while continuing to pummel, claw, rip and tear at him with its other free arms. But Orodan too was also pummeling its arms that he was holding onto and keeping tied up, and soon, his new toughness and increased strength paid dividends and he won a damage trade-off for the first time.\par
Won a damage trade-off against its arms at least.\par
The eight-armed necrotic monstrosity roared as two of its arms were ripped off and Orodan fell to the ground with them.\par
He was definitely far more beat up overall than it was. But he had made genuine progress.\par
What’s more, the necromancer was not amused.\par
“Raaargh! What are you?! A zombie?! Kill him now!” she shrieked.\par
And soon enough Orodan was sent back to being awoken by the harpies.\par
\par
Attempt one-thousand six-hundred and eighty-seven brought with it a tipping point where his wrestling became good enough that he could effectively tie up four of its arms and pummel it with impunity.\par
Now, it was just a matter of time and vitality for him to wear it down and kill it. And he was going to eventually start winning the damage trade.\par
Too bad that the necromancer was a spoilsport and promptly sent in the Elite-skeleton that had crushed his head a long while ago; alongside five Adept-level undead wolves. Together they decided to gang up on him and assist the abomination.\par
He was mobbed and killed. But not without the realization that he could now, with some decent exertion, destroy the Elite-skeleton which killed him the first time.\par
Attempt two-thousand three-hundred and forty-three was the loop where he grappled the abomination into submission, managed to destroy the interfering skeleton and undead wolves, and was about to win.\par
When the necromancer decided to glow a sickly green and connect an energy tether to the abomination, which started healing and growing stronger, albeit at the rapid expense of its own integrity and condition.\par
Finally, the results came on loop three-thousand and seventy-three.\par
\par
Orodan had disliked Eversong Plaza and House Argon before the time loops, but now he positively hated them.\par
Every little stone tile, every stupid stall, he hated it all.\par
He had shattered each and every tile in his struggles against the abomination. He had disintegrated each and every stall as he was knocked around and thrown like a ragdoll.\par
One day when the loops were over, he would completely raze this shithole into a crater.\par
But for now, House Argon’s destruction would suffice.\par
A single motion of his wrist, and his sword slaughtered the first Adept who he had slain thousands of times.\par
He shot like a cannonball along the plaza perimeter and killed each and every single non-Adept guard of House Argon. They were butchered like chickens before they had the chance to even realize what killed them.\par
A second passed, and Buximus and the spear-Adept rushed him but were slain in a single blow each as Orodan activated Death Rage. At level 53 the empowerment skill completely overwhelmed Adepts as though they were children before a grown man in rage.\par
Sagatos and the following five Adepts that rushed out were slain by the time two seconds had passed.\par
Lord Aeglos the cowardly pyromancer was met by a Shield Throw which decapitated him before he could cast a fire beam and Orodan himself then proceeded to roar.\par
It was a deep, guttural thing which came from within and carried far farther than it naturally should. It held the rage and sheer bloodlust that had built up within him over the thousands of times he had died and the thousands of lives he had reaped.\par
\textbf{[New Skill (Rare) → War Cry 1]}\par
“Aeglos the weakling is dead and every worm of Argon outside the tavern lies dead! Come out and avenge your Lord, and send for his necromancer master and her pets!”\par
Nearly fifty Adepts stormed out of the tavern doors to see a single man standing before them, surrounded by corpses. Blood seeped out of his eyes, nose and mouth as the effects of the Death Rage were quite detrimental to his health.\par
Of course, they didn’t know just how deep Orodan’s vitality ran.\par
They charged, and they were butchered. Pieces flew everywhere and blood and organs coated hundreds of stone tiles red.\par
In the course of fighting it, Orodan came to respect the sheer rage, brutality and bloodlust of the abomination as being traits worthy of a true warrior. While he didn’t intend to go around letting these traits control him. He felt that when needed, they were truly warrior-like traits that should be harnessed in battle.\par
And so Orodan had fought his enemy thousands of times and took after it. And he perfected the lesson he began learning as an orphaned street rat; that when the time for violence came, it was best to be the most violent person in the room.\par
He waited two minutes before the arrival of the necromancer, and while he could have gone into the tavern, he did not. He refused to enter until he bested the obstacle in his path, it was a matter of principle. He would not be Orodan if he didn’t bull-headedly break a wall in his path with his own head.\par
“You killed my favorite little disciple!” the woman howled, but before she could get to casting a necrotic spell, Orodan interrupted her.\par
“Don’t waste my time. Your pathetic magic won’t work against me, send out the eight-armed warrior that serves you, it’s the only thing that can challenge me,” he spoke calmly, in contrast to the Death Rage running through him that was ravaging his veins.\par
Of course, she didn’t comply right away. But changed her mind after seeing how Orodan simply stood there with a nonplussed expression on his face as she launched her most powerful beams of pure necrotic wrath at him.\par
Her expression seemed far graver this loop.\par
The abomination came out, and Orodan wasted no time.\par
Both combatants were at a perfectly matched level of aggression and rage, and Orodan could now keep up with it.\par
He met its furious charge in the middle. And while he was still inferior to its raw strength, he could match its speed.\par
And he could definitely match it in terms of technique and ferocity.\par
Its claws found greatly reduced purchase in his flesh, and its attempts to grab and tear him apart were thrown off with pure Death Rage enhanced physicality as the gap in strength was no longer as massive.\par
He began bullying it with a combination of swordplay, shieldwork and unarmed strikes, and this time the necromancer immediately sent out her ancillary minions, which she decided to immediately empower with a necrotic tether at the cost of their lives. Something she had never done before.\par
She was taking Orodan very seriously this loop.\par
The abomination alongside its new allies met Orodan in a brutal and frenzied barrage of blows. Seven-on-one and yet Orodan still held strong, even if he was on the losing end of the exchange. Ten seconds passed before the undead wolves were crushed.\par
And before the skeletal warrior could meet the same fate despite its necrotic empowerment, the necromancer’s eyes glowed green and she began empowering the abomination as well.\par
It was a titanic and furious clash.\par
The skeleton, an Elite-level undead minion. One that had slain Orodan with casual ease thousands of loops ago.\par
This skeleton was now a non-factor and was pulverized within two seconds by the death zone of violent and savage fighting between Orodan and the abomination.\par
When empowered the abomination’s skin would begin cracking and its eyes and wounds would start glowing green. Furthermore, its advantage in physical strength grew greatly and it even gained a small speed advantage over Orodan.\par
But Orodan was by now used to fighting uphill battles against foes who were his superior. This did not deter him in the slightest.\par
Every single skill he had was pushed to its limits and weaved together in a desperate and vicious fight that only got more dangerous as his vitality dipped lower.\par
The empowered abomination held the advantage and was slowly gaining ground on Orodan, but was made to pay dearly for it.\par
And finally, Orodan was pressed to the point where the increased skill level of Dying Struggle allowed for him to activate it earlier. And the battle changed.\par
The increased skill level of Dying Struggle now made him nearly twice as powerful, and he used the advantage to his benefit by slamming the empowered monstrosity on its head with the strength advantage he now held, and slowly beginning to grapple its arms while pummeling and savaging it with repeated blows that never relented.\par
The monster was an undead, but deep in its instincts it still retained the ability to recognize when a creature was more aggressive and lethally violent than it, and even as an undead it instinctually quivered and weakened under the Death Rage fueled mauling by Orodan.\par
One by one, each of its eight arms came off, and finally Orodan stood on top of its back, pinning it onto the ground beneath him.\par
It must have looked comical, the man-sized Orodan on top of and overpowering the massively larger undead.\par
But nothing about this vicious struggle was funny, and Orodan barely wrapped both arms around the creature’s thick neck… and pulled.\par
It roared for the last time as green necrotic energy leaked out in increasing quantities, and finally, its head tore free from its shoulders. A move it had performed on Orodan himself countless times.\par
Finally.\par
He looked up, its head in both his hands, towards its master.\par
Her ugly gaunt face was filled with shock, and a true expression of fear.\par
“You’re… you’re a monster… that was a Demonic Berserker I empowered… no mortal should be able to match it blow for blow… not at your level.”\par
“And you’re a weakling and a coward, using your minions to fight for you,” Orodan insulted. “And now that they’re dead… you’re next!”\par
She tried to flee, to escape, and at last when true death came for her, to evade. But Orodan’s second Blessing would let her do none of that.\par
The inklings of begging might have started to form on her face, as unused to such a thing as she might have been, being a Master-level mage.\par
But Orodan didn’t give her the time to think about it as her now torn off head was grasped in his hand.\par
\textbf{[New Title: Master Slayer]}\par
She was as physically weak and slow as the other mages he had fought in this damned plaza.\par
Finally, he allowed Death Rage to deactivate. He was left with only a tenth of his total life force. But even that was substantial enough to still allow him to explore. Furthermore, at the high level the skill was at, Unyielding Vitality now started allowing him to slowly recover his life force if he rested a bit. He’d be back to at least half of his overall vitality over the course of thirty or so minutes.\par
And so for the first time in maybe close to ten-thousand loops. He stepped through the double doors of the Castarian’s Boot tavern.\par
\par
There were no defensive measures waiting for him inside. And the interior was… like any luxurious tavern he had heard about.\par
Orodan supposed it was a poor experience for his first time being inside a wealthy tavern, but he wasn’t overly impressed by the whimpering non-Adept guards and servants inside. He left the servants be.\par
He kept interrogating guards and killing them upon refusal to answer until one was forthcoming to his question of where the war machine was. An act which levelled his Intimidation to 7.\par
The trembling non-Adept said that they weren’t informed of its exact location, but did inform Orodan of the entrance to the tunnel system which lead under the mountain.\par
He entered and was shocked.\par
He was a street rat and an orphan who’d been inside Ogdenborough his whole life.\par
The sight of tunnels which were hundreds of feet tall and wide was genuinely wondrous for him. Was this what adventurers saw in the distant dungeons they delved? Perhaps it wouldn’t be the worst career option.\par
The idyllic nature of the exploration was interrupted however as after a few minutes of Sprinting through the tunnels he was ambushed by two Elite-level House Argon guards.\par
He dispatched both of them with some work, but proceeded more cautiously moving forward.\par
After another ten minutes of delving deeper and following the beginnings of some strange metallic pipes he saw, he finally came to see a rather large metallic console of sorts, guarded by a group of Adept-level armored warriors.\par
They wore Novarrian colors. Imperial military.\par
Their captain, an Elite halberdier approached Orodan.\par
“Damn, so Master Fausta truly did fall out there… you Adenians have control of the Republic side of the range I take it?” the man with an ornate hat asked. “Well then, why have you come here alone? As a messenger? To ask us to surrender? I didn’t realize you Republic dogs would give up this game and just attack early on the day of.”\par
“You’re mistaken, I’m no messenger and I haven’t come here to ask you to surrender. I butchered every single member of House Argon at the tavern and I’m looking for a way to stop this damn war machine they’re trying to awaken.”\par
Whatever the Novarrian captain was expecting to hear, that was not it.\par
Next to him his soldiers murmured in shock.\par
“You… what sort of negotiating tactic is this? Is that meant to be a threat? Have all the Imperial loyalists on the Republic side of the mountain been executed? Do you Republic dogs have no respect for the standards of war?!” the captain exclaimed. “There are hundreds of troops deeper down the caverns, just so you’re aware. It won’t be a bloodless victory for you!”\par
Orodan quirked an eyebrow.\par
This man was a little too forthcoming, friendly and willing to talk for someone that should be an enemy of the Republic.\par
“Why are you talking to me so freely? Who are you?” Orodan asked.\par
“Captain Tibiratus Vicena, of the third penal battalion… as you can tell. Those of us down here are the rejects of the Empire. Sent to guard this spot till that thing’s activated, and we’ll die as a result when it does,” the man replied. “So… I wouldn’t be opposed to facilitating the honorable surrender of my unit. We’ll be killed by our own forces if we try to leave through the other side of the mountain.”\par
It made sense. Orodan doubted the people chosen to guard the tunnels inside the mountain would have a high survival rate when the metallic giant awakened.\par
“These tunnels connect to the Novarrian side of the mountains?”\par
“Of course! Why do you think that tavern on the Republic side exists, and where do you think we all came from?” Tibiratus replied.\par
“Well… I have no idea what’s going on… what’s this farce everyone’s talking about? Why hasn’t the Republic raided this place already, and why the hell do Northmen show up?” Orodan asked bluntly, tired of the prancing about.\par
“You… you really don’t know?” the captain asked. “So… what’s actually happened out there at the tavern? Where’s Master Fausta? Who are you really?”\par
“I’ve already told you. I killed everyone up there besides the non-combatants, and if this Master Fausta of yours is the necromancer with an eight-armed Demonic Berserker as a minion, then I killed her and her pets too. Now hurry up and tell me what’s going on before I decide you’re next.”\par
Tibiratus Vicena visibly gulped, and for the first time he seemed to take Orodan very seriously and realize the gravity of the situation he was in.\par
Nobody would arrive down here alone and simply claim to have killed a Master if there wasn’t truth to it. And Tibiratus wasn’t going to ask the man about his titles, which were obviously a disguise if he was able to kill a Master.\par
“I apologize sir… to put it bluntly, both the Republic and the Empire have been coveting the machine for decades now. But it wasn’t until recently that the means to activate it were found. However, it was Republic scholars who found the second half of the key, while the Empire already had the first. So the both of them agreed to ‘work together’ to activate it,” Tibiratus replied in a most respectful tone as he diligently explained. “Also, the machine can only be activated at a certain time of year, which funnily enough starts from today in the afternoon. I believe the charade both sides are playing is pretending to get along until the time for activating the machine arrives. Both Republic and Imperial researcher and guard teams are down in the main control chamber. It’s an open secret among both sides that a bloodbath will start in that room when the time comes...”\par
Orodan finally had a general understanding of the situation. The war machine was something both sides were supposed to work on activating, but of course both the Republic and the Empire planned on mutually backstabbing one another. And it made sense for the losing side to send a massive response around that time in the hopes of taking back control of the machine.\par
Given the desperate attack he saw at the tavern… he believed the Republic’s team down in the control chamber were on the losing side. Furthermore, he recalled one of the Republic soldiers denouncing House Argon as traitors.\par
So then…\par
“Say… how are your relations with House Argon?” Orodan asked.\par
“House Argon? They’re a noble house of the Republic sir, we don’t have much dealings with them.”\par
Orodan couldn’t confirm anything, but he now suspected that House Argon’s betrayal might have been what lead to the Imperials gaining control of the machine and the desperate attack at noon, which was quite near the time for the machine to activate.\par
From what he recalled of his first life, House Argon and the Guzuharans seemed to be fighting a rather defensive battle and trying to delay and buy as much time as possible.\par
“Alright, that’s enough. My head hurts thinking about this. Politics were never my strong suit during training in the militia… tell me where the main control chamber is.” Orodan replied. “Also, the way up to the Republic side is entirely clear. I’ve killed everyone. Get out.”\par
They didn’t have to be told twice, and once Tibiratus finished explaining to Orodan where the control chamber was they scampered off quickly.\par
The directions were thankfully straightforward and the tunnel paths themselves naturally lead there.\par
And as Orodan continued delving deeper down the tunnels the question of what exactly guards were posted throughout the tunnels for was answered. It was an answer in the form of a weird skittering centipede, as large as a horse and much longer.\par
Thankfully they were monsters that could be slain by Adept-level guards, so they posed no threat to him whatsoever. But it did mean that unless they wanted the tunnels crawling with these things, they needed guards around the junctions.\par
And guards Orodan did find.\par
Every minute or so of Sprinting lead him into groups of a dozen or so Adepts wearing Novarrian colors. The initial groups were penal battalion soldiers and decided to simply give him a wide berth and flee out the way he came once he informed them of the situation on the surface.\par
But as he got deeper the strength of the guards increased, and they refused to back down without a fight.\par
He killed four separate groups of a dozen high-level Adepts on his journey, and finally, he arrived in the largest subterranean chamber he had seen thus far. At one end of the chamber was the entrance, which split off in two directions. One where he came from, and one a direction Orodan could only assume was towards the Novarrian entrance to the tunnels. Both paths lead to this massive chamber however.\par
On the other end of the chamber was a large metallic gate which looked firmly shut. In front of it stood the strongest group Orodan had yet encountered.\par
A group of ten Elite Novarrian soldiers, their leader, a near-Master level warrior in heavy armor with a sword and shield. And it didn’t look as though the man was interested in any sort of dialogue.\par
He activated Death Rage and prepared for a fight.\par


\section*{Chapter 6 - No Escape In Sight}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 6 - No Escape In Sight}%
\par
Orodan’s vitality had recovered to roughly three-quarters, which was good enough in his opinion.\par
But this was not an easy fight.\par
Undead minions were naturally weaker than their living counterparts, and the Elite-level skeleton he could crush in the Plaza by now wasn’t indicative of the battle-strength of a living Elite soldier.\par
He was still confident in beating a few, even by himself.\par
But ten Elites at once? And they were trained in working together?\par
Orodan found himself incredibly pressured, and took serious blows from the pressure despite every single defensive skill synergizing with Impregnable Bladewall. Furthermore, unlike the abomination these troops had active combat skills which could get past his Iron Body and Resistance skills.\par
But by this point… simply inflicting shallow wounds on him wasn’t enough.\par
True, they were skilled and the old Orodan would have been killed many times over. But Orodan now was a different beast altogether.\par
Two of the soldiers were skilled in some sort of movement or evasion type skill. They were the first to die as they landed their attacks on him, but found their ability to evade his blows… failing.\par
He could take their hits, but they couldn’t take his.\par
Furthermore, the raw ferocity of Death Rage genuinely pressured the rest of them and gave him a psychological edge.\par
After ten seconds of furious fighting they started to realize he wasn’t going to die to the myriad of blows they were delivering, and so they switched gears and started forgoing defense to instead go all-out in offense.\par
They died very quickly after that, albeit not without causing some genuine damage to Orodan before they did.\par
Damage, which still wasn’t anywhere near the abomination fielded by the necromancer.\par
Down to a quarter of his vitality now, the scene was a grim one. The bodies of the slain Elites lay scattered across the rocky floor of the chamber, and the gates loomed ahead of him.\par
Orodan approached the metal gates and pushed them open. They likely weighed as much as a building, but his strength had grown and with some effort he pushed them till an opening formed.\par
And he stepped inside.\par
\par
The sight inside wasn’t what he was expecting to see.\par
There were corpses everywhere. Some wearing Novarrian colors, many more bearing Republic insignia.\par
A battle had taken place here, and the Imperials came out on top, if just barely. The sheer destruction which scarred the stone floor was good evidence that Master-level combatants were involved. Frankly, it was a surprise that the tunnels hadn’t collapsed.\par
There were three people present inside the chamber.\par
One, the ogre-barbarian Guzuharan he was slain by in his first life. The second, a wiry man with a sword and shield strapped across his back, bearing Imperial colors. And the third… Baron Viglas Argon himself, the head of House Argon.\par
The Novarrian’s hand lay on a glowing red orb, the same color as the jewel he recalled seeing on the head of the machine many loops ago. A look of concentration upon the man’s face.\par
The ogre-man stepped forward and drew his great axe.\par
“So this is the warrior responsible for forcing us to act early? That was some fight you had against that corpse-lover’s pet demon! I approve!” the ogre-man bellowed with a chuckle. “I’m Ovuru World-Drinker! Warchief of the Leviathan tribe! Tell me your name before we fight warrior!”\par
“This street rat is Orodan Wainwright, don’t waste any more time. Kill him now Northman,” spoke the Baron with a cold tone. “I’d act myself but for the risk of collapsing the tunnels… and his particular abilities seem to render magic ineffective.”\par
Ovuru’s grin subsided at the imperious order coming from the Baron.\par
“Feh… you Republic worms are no fun. Warriors should exchange names before engaging in honest battle, he’s a worthy opponent. You mages wouldn’t understand,” Ovuru derisively replied. “I don’t understand how you aren’t chomping at the bit to kill him yourself. His shield took off your little princeling’s head did it not?”\par
“I can always sire another son, now do as you were brought here for!” the Baron barked, and one might wonder why the hell such a powerful warrior like Ovuru was tolerating the barking from a mage such as the Baron. Particularly when they were within melee range of one another and Ovuru held a supreme advantage in such a position.\par
The answer was a deadly glare towards Ovuru from the Novarrian man handling the orb. The sword and shield wielding Novarrian did not care to move, but even then the ogre-man seemed almost… scared of him.\par
Ovuru chambered his great axe into prime position, and he moved.\par
Orodan wasn’t ashamed to admit he felt genuine fear for the first time in thousands of loops.\par
His sword and shield were both instantly cut straight through and his arm was almost dismembered if not for a narrowly timed evasion.\par
Undead minions were weaker than their living counterparts. And if he thought fighting a Master-level necromantic minion was near his limits… then this ogre-man’s abilities were on a completely different level.\par
He received a pommel strike which crushed all his ribs, and a punch that almost certainly shattered his skull and neck. If not for his skills granting him unnatural durability and survivability that allowed him to function for a time without certain organs, he would certainly not be able to move right now.\par
A sonic boom occurred as he was sent flying into the stone wall of the chamber, and the impact finally brought his life force beneath a certain threshold.\par
Dying Struggle activated, and alongside the existing Death Rage the two times boost allowed him to begin a desperate struggle for survival instead of the outright bullying that was occurring in his first battle against a Master-level melee specialist.\par
He had thought himself strong after beating that undead Demonic Berserker… but he was wrong.\par
The world was a big place, and Orodan was a small fish in the ocean.\par
“I felt the Blessing from the get-go… but you have a second one? You’re a Favored like myself then?!” Ovuru exclaimed as he shot towards Orodan, trying to splatter him into the wall he was already cratered into.\par
Orodan barely avoided the certain death and began narrowly holding onto life by the slimmest of margins, even with maximal effort. Every exchange was a losing one, and he would just only manage to survive by an inch each time.\par
But what Orodan did manage to do even in his desperate struggle, was force the fighting towards the orb, and consequently towards the other two in the room. Something which Ovuru did not take kindly to, but was too late to stop now.\par
“Why won’t you die you cockroach!” Baron Viglas yelled.\par
In desperation to keep Orodan away from the orb, the Baron blasted him from behind with an incredibly powerful fire beam which carried a level of power and heat well beyond Lord Aeglos, hoping the impact force would at least send Orodan away.\par
Which, unfortunately for him, still had no effect. Orodan was used to taking magical impacts and standing his ground. And the Baron’s beam helped lessen the immediate pressure on him by forcing Ovuru to back away for a moment as he lacked the Legendary Mana Resistance that Orodan had.\par
And a moment was all that Orodan needed.\par
He could have lashed out and killed Baron Viglas Argon, but Orodan’s target was a different one.\par
He rushed, with as much speed as his empowered body could muster, and headed straight for the orb.\par
The Novarrian was strong. But he was a little too strong, which was to his detriment as his free hand not on the orb shot through Orodan’s chest and out the other side instead of batting him away.\par
The man maintained eye contact with Orodan, and his own eyes widened in shock as both of Orodan’s hands came to rest on the orb.\par
“What the fuck do you think you’re doing you pest!” the Baron screamed. “What even are you?!”\par
Truthfully, Orodan didn’t know what he was doing in the slightest, but even as the Novarrian’s eyes trembled with rage, he could not speak for so great was the concentration the man was exerting.\par
From the moment Orodan’s hands touched the orb, he felt the very same energy that the mages of the Plaza had hit him with fruitlessly. Mana… a near bottomless well of it, powering the machine.\par
And as Ovuru bore down upon him from behind, death coming for him, Orodan did the only thing he could.\par
“I am Orodan Wainwright… and I… am a warrior!”\par
He felt the mana… and he pulled.\par
“No! don’t d-”\par
The Novarrian’s first words were cut off as the world turned a glowing red in his eyes.\par
The whole room, the inhabitants of it, the very stone, it all turned red.\par
The Novarrian was undoubtedly powerful, he had to be in order to make a Master-level warrior like Ovuru fear him. But the man just… melted and disintegrated.\par
As did the Baron and Ovuru.\par
The red-colored energy in the air was so utterly thick and rich that it was turning liquid and Orodan was essentially drowning in it.\par
It was mana.\par
And it was a colossal amount, an almost… divine quantity of mana.\par
Orodan should have been vaporized millions of times over. In fact, the entirety of Volarbury County should have been vaporized. Yet Orodan tried his absolute hardest to pull the mana into himself.\par
Which was disastrous, as Orodan’s body slowly flaked to pieces, his Legendary Mana Resistance being nowhere near enough to disregard this much mana.\par
But his vitality allowed him to persist.\par
And even as he began dying, the persistence allowed him to increase his skill levels.\par
\textbf{[Mana Resistance 19 → Mana Resistance 23]}\par
Came the first message.\par
As time passed Orodan’s body disintegrated further, although the rate began to slow, and more messages came along.\par
\textbf{[Mana Resistance 23 → Mana Resistance 30]}\par
Until finally, the last set of messages came along.\par
\textbf{[Mana Resistance 30 → Mana Resistance 39]}\par
The very mountain exploded upwards, and Orodan could see the beginnings of the sun peeking through the night sky and illuminating the world.\par
The many miles of rock above were sent high into the air in the colossal explosion of mana from the main control chamber, and enough of the rock had cleared away that Orodan could also see the somewhat mangled but still functional metallic frame of the machine itself now.Unauthorized use: this story is on Amazon without permission from the author. Report any sightings.\par
It was inert of course, given the mana pool he had now pulled on and stolen.\par
And as the last of the mana drained from the orb and flowed into him, Orodan received a message.\par
\textbf{[New Skill (Legendary) → Mana Black Hole 4]}\par
It was interesting. His body was essentially torn apart. His now incredibly high Legendary skill was strong, it let him adapt and grow with a County shattering amount of mana… but it still wasn’t enough to prevent his death this loop.\par
He felt strangely full, as though he had an unlimited reservoir of energy within him however.\par
If he hadn’t pulled it all into him, who knew how much utter destruction the orb’s out of control mana pool would have wrought?\par
As he lay dying and the entire mountain for miles above which had exploded upwards now came flying down he received one last message.\par
\textbf{[Quest Completed → Battle of Ogdenborough - Guzuharan leader killed, Novarrian leader killed, House Argon leader killed, ancient war machine disabled]}\par
\textbf{[Reward Granted → Permanent +1 Action Increase]}\par
What even was an Action Increase? Orodan didn’t know.\par
And honestly, he might not even wake up after this.\par
As the rocks descended towards him at speed, Orodan couldn’t help but have a smile on his face.\par
The battles he had gone through to get to this point were worth it in and of themselves.\par
\par
A keening wail ringing in the night sky awoke him.\par
He was… awake and returned?\par
\textbf{[Quest Bestowed → Battle of Ogdenborough - Defeat the Novarrians and their allies as they attempt to activate and commandeer the ancient war machine beneath Mount Castarian]}\par
Orodan’s eyes widened at the message.\par
This was wrong.\par
He had succeeded!\par
Why was he back?!\par
An angry downwards fist from him shattered his bed and threw out the walls of home, causing the entire hovel to collapse.\par
“What the flying fuck?! I succeeded! I won! I completed your damn Quest! Why won’t you leave me be!?”\par
His furious roars into the night sky along with his entire hovel collapsing necessitated the militia being called.\par
Of course the night-shift squad that came by as response looked at him incredibly fearfully and kept a distance.\par
A destroyed building, even if it was a hovel, implied at least the Adept level.\par
“And what the fuck are you looking at?!” he roared at the responding Sergeant who stood there and cowered.\par
Eventually, thirty minutes later a mounted unit came by and their captain, an Adept, attempted to arrest him for causing a disturbance.\par
Which lead to the captain being sent flying through a building the moment he put a hand on Orodan.\par
He simply stood there in fury, the area was cleared of any non-combatants and soon the flapping of griffin wings signified the arrival of the Militia’s Elite response unit.\par
“Orodan Wainwright! I don’t know how you got so strong! Surrender yourself and come with us! You’ll be treated amicably given your newfound strength!” the captain of the Elites riding atop a brown feathered griffin called out.\par
It seemed even he was wary of offending someone who had shown the strength to throw an Adept through a building, at such a young age too.\par
But Orodan could only reply one way currently, for so great was his rage.\par
“Fuck off!”\par
He roared, backed by a War Cry which caused the griffins to panic and go out of control and attempt to fly away.\par
“So be it! Don’t blame me for the beating you’re about to get! Perhaps you’ll learn some manners and we can work together in the future after some time to cool down in the holding room!” the Elite captain said, and then the Elites rushed him.\par
The Militia Elites were… lacking.\par
The ten Novarrian Elites Orodan had defeated under the mountain were the cream of the crop, chosen to guard the main control chamber of the ancient war machine. Those Elites had active combat skills of decent rarity.\par
But these amateurs? They couldn’t even break past his Iron Body.\par
The Elite captain’s face turned to one of disbelief, and then fear. He and his subordinates stopped their blitz of attacks once they realized it was having no effect on Orodan.\par
“As I said… fuck off!”\par
And with that proclamation, the Elite captain was sent flying into the air with a punch.\par
The Elite response unit simply flew off and maintained a perimeter after that.\par
\par
It was fifteen minutes after that individuals he’d never seen before started to appear.\par
A man in luxurious clothes and a flowing cape bearing the symbol of a flaming sword. And behind him, members of the Capital Guard.\par
“Hail friend! I hear you’ve been causing a ruckus in my County! I’m Burgher Ignatius Firesword, why don’t we talk peacefully? I don’t plan on approaching you roughly like some of the overzealous but well-intentioned men of the Militia,” the man calmly greeted with a friendly attitude. Orodan almost found himself swayed, undoubtedly the work of a social skill.\par
“Burgher Ignatius… I must refuse. I am in no condition to speak to anyone right now,” Orodan replied out of respect for the man’s own cordiality.\par
“Hmm… well you leave me in quite the pickle. I don’t want to escalate the matter, you’re clearly a very talented young man, who from what the reports tell me, was rather average before this. Have you awoken a Bloodline or been Blessed?” the Burgher asked. “Regardless, I still can’t stand idly and have a neighborhood in one of the towns of my County terrorized, even if you’ve been merciful and haven’t killed anyone.”\par
“I have no intention of harming anyone who doesn’t bother me. I just… require time to myself right now.”\par
“Hmm… unfortunately, your very presence is now a threat given what you’ve done. It necessitates the reality that I must regrettably bother you. Please, I implore you to come with us and we can get you whatever it is you need,” the burgher spoke.\par
Truly, the difference in treatment and regard was almost nauseating. When he was but an Apprentice in his first life, he’d have been given a beating and thrown into the holding cells. But now when he’d displayed battle power beyond an average Elite? Even Burgher Ignatius Firesword who wasn’t a Master-level combatant himself, was forced to tread diplomatically.\par
“I’m afraid not. I respect your manners in approaching me Burgher, but I must respectfully decline. Send whoever you need to at me.”\par
And with that the man had a sad smile on his face. He seemed like a good-natured noble and was appreciative of the fact that Orodan had given him face and not insulted him during the conversation.\par
Ten seconds later the Capital Guardsmen captains approached.\par
Being an Adept was the basic requirement for being the lowest rank of the Capital Guard. With corporals being average Elites and Captains being near-Masters with high rarity combat skills.\par
Additionally, many members of the Capital Guards often served in military operations part time. It wouldn’t do to waste such high-level warriors as simple guards.\par
So when the five captains came at him, the entire neighborhood went silent, when after a furious exchange of steel on steel he threw even them backwards.\par
The senior most among the captains must have realized it was a losing fight, for he activated the amulet around his neck and sent out a message to someone.\par
“Young master… I don’t know if you’re a reincarnator or have some absurd Blessing, but we apologize for offending you, I hope you understand we had to act as is our duty… our Master will be coming by shortly to speak with you himself.”\par
The man’s words were unusually respectful, and Orodan could understand why.\par
For a 17 year old to suddenly best five captains of the Capital Guard at once… was unprecedented unless one was a reincarnator, and those were closely tracked and known of.\par
\par
It took five minutes for the man to arrive.\par
He wore glittering silver armor and rode a lustrous gold feathered griffin. His very aura screamed power, and Orodan knew that this man was a step above Ovuru and was likely on the same level as the Imperial manning the orb.\par
Sarvaan Ilsuan Arslan, the High-Burgher of the Republic of Aden, the leader of the council of Karilsgard had arrived.\par
And his presence brooked no quarter.\par
His regal griffin touched down onto the scarred ground of Briar Court in Ogdenborough, which by now had become a savage debris-laden landscape due to the fighting, even with Orodan trying to hold back.\par
A hammer was slung across his shoulders, its massive head the size of Orodan’s torso. He suspected it could bring down a mountain.\par
The High-Burgher slid off the back of his majestic mount and his feet touched down.\par
He stood about fifty paces from Orodan, and started with two words.\par
“I see.”\par
And then silence stretched on as the man’s eyes began glowing gold, although Orodan didn’t get the feeling it was harmful or offensive magic.\par
A minute of silence ensued. A silence Orodan was neither in the mood nor willing to break. The rage still ran hot through his veins.\par
After this minute another gold-feathered griffin touched down, bearing a dark-skinned woman in a flowing white robe. She too touched down and moved to stand beside the High-Burgher.\par
And the man finally spoke once more.\par
“Do you see it as well Lakshiya? I wished to confirm it with you… but I’m almost certain he is Favored,” spoke Sarvaan. “I sense not the usual presence of a single Blessing, but two Blessings of Agathor from him. The only other person I’ve ever felt that from was High-King Vokrim.”\par
Lady Lakshiya, the High Oracle of the Cathedral of the Gods in Karilsgard. She was a woman who kings would travel to speak with. And her abilities in divining the future were almost god-like from the stories he’d heard.\par
“Yes… I sense it. His destiny is…” she spoke. And then she stopped, and her face twisted. “Impossible… impossible!”\par
The High-Burgher raised an eyebrow at her outburst and waited for further clarification. Even Orodan himself who hadn’t said anything all this time, came out of his stupor at the question of just what Lady Lakshiya found so impossible about him?\par
“His threads of fate… they do not have any connection to the world… it’s as though they are a coiling ouroboros, devouring itself over and over… growing larger and larger with each cycle,” she spoke with widened eyes. “You… what are you?”\par
And for the first time in a while Orodan spoke.\par
“I don’t know what I am, but I seem to be stuck in a time loop. I relive this day over and over, every time I die I wake up in bed deep into the night,” Orodan explained as his audience’s eyes carried utter disbelief. “I’ve done this thousands of times now, and I thought completing the Quest I received to stop the Imperial invasion and activation of the machine beneath the mountain would set me free in my last try… but instead I wake back up once more and the Quest is simply bestowed upon me again. There is no escape for me.”\par
High-Burgher Sarvaan and Lady Lakshiya stared at him for two full seconds before deciding to speak.\par
“That’s not possible… I am communing with my lady Ilyatana, Goddess of Fate as we speak, she says neither she nor any of the other Gods are aware of this. No time magic can affect the gods, a time loop even on the scale of a world would only affect the mortal plane. The Gods are beyond the flows of time!” she exclaimed, almost convincing herself as much as she was trying to Orodan. “Your story sounds contrived, and yet your threads of fate are-”\par
She was cut off mid-sentence and suddenly stopped speaking. She stopped speaking to Orodan and began speaking to herself.\par
“But my lady… for this…” she muttered, and the High-Burgher began to take some distance from her.\par
“…it is as you command… in your name…”\par
What was going on? Orodan didn’t know.\par
But what he did know was that a massive beam of light descended down upon Lady Lakshiya a second after.\par
Orodan had to shield his eyes from the sheer luminosity and intensity of the light. Even the rays of the sun itself were not so brilliantly blinding.\par
And as the light settled down, Lady Lakshiya’s eyes were glowing, her skin was cracking, and light seeped through these cracks. Whatever the magic was, it wasn’t exactly good for her body.\par
Even the High-Burgher Sarvaan Ilsuan Arslan, took a knee in respect.\par
\textbf{“So this is the mortal that has caused such upheaval and confusion. Orodan Wainwright.”}\par
The voice spoke, as though testing out the name like a curious syllable. It spoke through the body of Lady Lakshiya, but he knew it was not her speaking. It was something beyond him, a level he could never hope to reach, power beyond this world.\par
This… this was an Avatar. A God descending to the mortal plane with but a small fraction of their power to possess one of their Favoured.\par
He was speaking to Ilyatana, the Goddess of Light and Fate herself.\par
\textbf{“I apologize in advance for having to empower and use one of the skills of your body Lakshiya… the strain will undoubtedly leave it unusable for a month.”}\par
And the Avatar’s eyes glowed a deep shade of gold, and she looked.\par
And Orodan felt completely naked before the gaze of a Goddess, as though his very soul was being peered into.\par
\textbf{“Two Legendary skills, two Blessings, a Reward… fascinating. Agathor genuinely does not recall Blessing you… your tale might not be incorrect child. And one of your active titles… One Who Has Experienced Death… incredible. Malzim does not recall you dying and returning to life, he would certainly know and have Blessed you by now as well.”}\par
The normal Observe skill could not see skill levels and available titles. Only an Observer orb could see skill levels and this was with consent. But of course a Goddess could disregard the limitations of such a thing.\par
“I’ve lived this day thousands of times without end, why would I lie about such a thing? Does my Status not show some proof?” he asked.\par
\textbf{“Indeed it does… we have decided we shall assist you, even if we might not remember it in the times to come. I peer into your mind as we speak… and the memories of what you’ve done, what you’ve endured… Agathor has never looked so proud.”}\par
At the thought that his mind was being read Orodan felt distinctly uncomfortable, but any protest would be pointless. An Avatar, even though they were capable of exerting only a fraction of the power of a God at the expense of the life of the host, was still an existence beyond any mortal. If Ilyatana wished to read his mind, he could only sit there and accept it.\par
\textbf{“Malzim says he does not remember you dying and returning, but from what your memories show… you return through time immediately upon death. I will train and mold you personally, so that you might survive these trials and discover an answer for the Gods as to who could be responsible for this. First, I will begin by implanting a gift unto you… a memory packet which will meld with your soul and allow you to synergize with my will easier and better enable you to work towards the task before you.”}\par
That did not sound good. That wasn’t good at all.\par
Orodan would rather not have any sort of foreign mind altering magic implanted in his soul which allowed him to serve the Goddess of Fate easier.\par
He desperately wished he had a swift way of killing himself, and thus immediately activated Death Rage.\par
Which the Avatar of Ilyatana swiftly caught on to, and strange bindings composed of pure light began restraining him and healing him simultaneously. He cursed and lamented for once that his damned vitality was so high.\par
\textbf{“Do not try to refuse this gift my child, this way you will escape the curse that plagues you and all of us Gods will be in your debt. You are already one to batter at a challenge till it crumbles, so why reject something that assists in this?”}\par
Orodan struggled, he furiously tried to will Death Rage to burn his life faster than it ever had before. It even levelled up twice and granted him a further power boost at the faster burning of life force.\par
Sadly, no amount of self harm was enough to overcome the healing from Ilyatana’s Avatar.\par
And as the strange rainbow colored orb approached him, Orodan could only pray to anyone out there that his personality and memories were not altered.\par
And someone answered.\par
\textbf{[Malzim, God of Death, smiles upon you]}\par
\textbf{[Received Blessing → Death’s Call - Whenever you will it, Death takes you]}\par
Without any further thought, Orodan immediately called upon his new Blessing.\par
\par
A keening wail ringing in the night sky awoke him.\par
He customarily brushed away the Quest messages, and immediately got to his feet.\par
“To Malzim, God of Death, Decay and the Afterlife… thank you. I, Orodan Wainwright, will forever owe you a favor which will eternally persist, this I swear!”\par
To Orodan, the Blessing he received was tantamount to a new life being bestowed upon him.\par
The God of Death had saved him from quite possibly the worst of fates, which was becoming the thrall of a Goddess.\par
Ilyatana… was dangerous.\par
But he would pay this near horrific end back in time.\par
Despite making it out of that horrid situation in one piece Orodan sighed at the thought that he was back at square one with no escape in sight.\par
And he needed a break from fighting.\par
So for the first time in thousands of loops. He resumed his daily routine, but this time… he decided to spend the day somewhere he normally never would.\par
The entire cart of lumber neatly landed on the pallets in one swoop.\par
“Mister Hannegan… you have any room on your crew for another hand?”\par


\section*{Chapter 7 - A Different Sort Of Grinding}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 7 - A Different Sort Of Grinding}%
\par
“No, you can’t just slam a load-bearing beam down into the ground with that kind of strength! Gentler! Get the alignment right, work with me, not independently!”\par
And Orodan found himself struggling in a way he hadn’t in a while.\par
\textbf{[New Skill → Construction 1]}\par
Was a message he had received a while ago, but it didn’t seem to help quite as much as he thought it would, even as it slowly levelled up to 3 over the course of a few hours of work. Unlike being able to brute force his fighting skills and go by feel, Construction required more focus, more theory-work being followed right from the get-go and getting the very techniques and principles of what he was doing, correct, before he could achieve a successful result.\par
Frankly, Orodan’s Physical Fitness of 55 now likely made him the physically strongest person in all of Ogdenborough. Aside from the Masters underneath the mountain of course.\par
But it made him vastly overqualified to work at a poor construction site crewed by people merely using non-magical skills to construct a building. Only one of them had a skill at the Apprentice-level and that was the architect, a young and ragged looking woman who looked as though she detested her life choices.\par
Frankly, Old Man Hannegan wasn’t aware of quite how high Orodan’s Physical Fitness was even as he yelled at him. To non-combatants, anyone above the Apprentice-level in combat skills and Physical Fitness were all in a different world. So for Orodan to juggle entire wooden support beams in each hand without a care in the world must have seemed a little out of place given that the man knew him, but he didn’t suspect anything too far out of the ordinary simply because he had no knowledge of what was the standard for each level.\par
Of course, if Orodan decided to destroy a house with a single punch like he did last loop, now that would be a different story.\par
Most importantly however, Construction required Orodan to work with other people. He had to execute the architect’s instructions as she envisioned, he had to work alongside the other workers and Mister Hannegan the foreman in bringing the plan together, and so on.\par
If not for his Physical Fitness which made him appear as a god to the average person, Orodan doubted they’d be as patient with teaching him. But, being able to casually throw support beams from one end of the site to the other made him a valuable commodity that increased their work power by hundreds of times.\par
Orodan fixed the wooden beam into the foundation properly this time and received a grunt of approval from Mister Hannegan.\par
“Took you long enough! Now then, we’ll need some more material prepared ourselves to save on costs, so get to sawing Orodan. Put those muscles to use!”\par
He followed the old man’s instructions and got to work attempting to saw planks out of the logs. Something which was trivially easy to do physically, but was a nightmare to do technically.\par
Sawing construction wood out of the stack of felled trees the site had on hand was… difficult. Frankly, the job was best left to people with the Lumberjacking or Woodworking skill. He got all the directions from Old Man Hannegan, but committing them to practice was harder than it seemed.\par
For starters the tree needed to be split into different lengths of log depending on what length and size of construction wood was needed. Carving a wooden support beam obviously took the most wood and consequently used almost the entire tree at times.\par
And then came the de-barking process where the bark had to be stripped. And finally came the act of uniformly sawing a board to perfect specifications. Or as perfect as he could get it anyways.\par
\textbf{[New Skill → Woodworking 1]}\par
The message came along after his fifth log being stripped of bark.\par
Frankly, the old man looked at Orodan as though he was staring at a golden goose. The physical part of preparing the log, which was supposed to be the hardest part for the average craftsperson whose Physical Fitness typically never exceeded 10, was as easy as breathing for Orodan.\par
Chopping and preparing a log into a support beam was something that would normally take a few laborers working in concert with someone with the Woodworking skill, and it would take at least fifteen to thirty minutes per log.\par
But Orodan who could shave the bark right off a log within seconds and split it into pieces within even less time? The difficult part of the process for others was but a breeze for him.\par
Furthermore, sawing a board uniformly was quite difficult, and poorer construction crews like theirs would take what they could get as physical strength was often a limiting factor when attempting to saw well measured boards without the aid of magic or a decent craftsperson.\par
But Orodan could simply make the saw glide through the wood like hot butter. His arm never struggled against the wood, it simply flew right through.\par
Orodan instead faced the opposite problem of butchering the wood and not going with the grain correctly many times as he simply brutalized his way into sawing a plank or a beam.\par
But even if the quality wasn’t high, this was still an absolutely titanic level of production for these poor laborers, none of whom had a skill at the Apprentice level.\par
These laborers wouldn’t be toiling at one of the poorest worksites in Ogdenborough if they had in-demand skill levels. And to them, producing multiple beams and boards within a handful of minutes was rather unbelievable.\par
“Well damn… Gods be praised… you could get an apprenticeship at a carpenter’s shop with muscles like that. You’d be making a lumber yard a great amount of profit with that sort of turn around of material,” Mister Hannegan remarked with genuine awe in his voice.\par
“Sure, but none of my beams and planks are of any good quality… does shoddy workmanship like this even… sell?” Orodan asked. Truthfully, he could make thousands of times more gold with his combat skills, but this day, this loop… was a break while he found himself and thought about his next steps.\par
“You overestimate how fine quality the wood needs to be lad. Most construction projects use standard non-magical wood, and not all the construction wood a lumber yard sells is used for building houses. Patching up existing buildings, repairing fortifications, setting up temporary camps, there’s a big market for even shoddy wood. And at your rate of work… any lumber yard would be making a fantastic profit,” the old man explained. “If I’m being honest, I’d scoop up a budding talent like you simply as an investment. Who knows how much better you’d become in the future. Damn, you fighters really are a different breed with your Physical Fitness… shame you’re in the militia.”\par
“And what if I was interested in an apprenticeship and working with you further?” Orodan asked leadingly.\par
“Then I’d tell you to stop yanking my chain and get lost kid!” Old Man Hannegan exclaimed. “The others might not realize, but I’ve been around for a while… your Physical Fitness is at least 30 isn’t it? I’d be taken aside and given a serious beating on a good day if I dared think about coercing a talent like you into wasting his time with Woodworking… the Burgher would make sure I pay for daring to set eyes on such a young talent in his County.”\par
Well, that answered why an offer for future work wasn’t exactly forthcoming in this loop.\par
Orodan sighed and shook his head. “Fine, fine… can you at least direct me to where I can learn to improve my Woodworking skill? Can’t I test for the Crafting Guild?”\par
“Any test would involve a mandatory examination at the Observer orb, and good luck wasting your time as a craftsman when you’re as strong as you are at your age… what’s gotten into you Orodan?” Old Man Hannegan suddenly asked with a bit of seriousness. “You show up at least a dozen times stronger than you were yesterday, blow off your shift at work and decide to just… work with me? I mean, my door’s always open for you kid, but ever since I’ve known you as that one mean and stupid kid with a death wish who picked fights with the enforcers of House Argon, you’ve always wanted to become a warrior.”\par
“It’s not that I don’t want to become a warrior…” Orodan quietly replied. “I am a warrior. I’ll always be a warrior… but I need some time to think about what to do, I need some time to hone my mind in other ways. Will you help me old man?”\par
For his part, Old Man Hannegan had a frown on his face at being called an old man, but which turned to a sigh and a shake of his head soon after.\par
“Lad… I won’t say that I’m unwilling to teach you, but this can’t be considered any sort of official apprenticeship or employment,” Mister Hannegan said with the inklings of acceptance on his face. “You won’t be paid, and if anyone asks I’ll simply say that you’re some talented kid who enjoys wasting his time on playing around with wood as a hobby and I decided to indulge you.”\par
Orodan smiled.\par
“That sounds perfect.”\par
\par
The last hours till noon and the awakening of the war machine were spent sawing wooden logs into functional construction wood pieces, working further on his Construction skill, and even gaining a point in Laboring.\par
And finally as the announcement came and went and he could hear the distant sounds of explosions and fighting in the tavern, he simply kept working even after the old man and the crew had run for their lives to the local barracks.\par
He eventually saw the ancient metallic titan awaken and shatter the mountain with its rise, and the jewel on its forehead glowed an ominous red.\par
But this time… even as everything around him turned red and disintegrated… Orodan yet lived.\par
It burned, quite badly if Orodan had to describe it.\par
But his Mana Resistance was much higher, and he also utilized his new Mana Black Hole skill to pull as much mana in towards himself as possible. Of course, none of the skills levelled up, given their rarity, they were much harder to level than skills of lower rarities.\par
And so he stood there, amidst the ashes of the former construction worksite on 4 Ale Road, the only living thing for hundreds of miles. Everything he could see on the horizon had been turned to ash and the ground was cracked and shattered with remnants of the familiar red energy furiously flitting about.\par
Ogdenborough was completely wiped off the map. And Orodan got a feeling nothing natural would grow here for many years.\par
\textbf{[Quest Failed → Battle of Ogdenborough - Ogdenborough has been completely destroyed]}\par
It felt… unpleasant. But Orodan couldn’t feel too bad given that everything would restart eventually. Still, knowing the stakes of his failure now put in his mind that one of his end goals long term would be to ensure that he perfectly completed the Quest and saved Ogdenborough.\par
As far as he had come, this poor town was still his home.\par
But for now, he had work to do. And as the menacing metal titan loomed over the apocalyptic landscape, for the first time he called upon his new Blessing in relatively safer circumstances.\par
He called for death to take him, and it did.\par
\par
”Hmm, not bad Orodan… have you done Woodworking before? Wasn’t aware you had the skill,” Old Man Hannegan spoke.\par
“Say old man… how do carpenters improve their ability to fashion these raw logs into beams and boards? Do they have training exercises? Surely sawing the exact same board hundreds of times on end can’t be the most efficient way to level Woodworking?”\par
“First of all… who’re you calling old?!” Old Man Hannegan exclaimed, but with no real heat. “But, to answer your question it depends. When I worked with a carpenter in my youth he had me saw in a certain amount of time, and for some of his more talented apprentices he told them to saw while holding their breath and while blindfolded… crazy teacher he was. Still, there’s also the Tool Mastery skill once you work at things enough, which functions as an amplifier type skill.”\par
Orodan smiled.\par
\par
\textbf{[New Skill → Tool Mastery 1]}\par
The new skill had then levelled up to 8 over the course of his loops and constant Woodworking, which had also gained.\par
“Well I’ll be… have you been dabbling in Woodworking without me knowing?” the old man asked.\par
“I wouldn’t say it was without you knowing,” Orodan replied with a relaxed and knowing smile on his face. “Now then, if you don’t mind, I’ll be practicing something.”\par
And a blindfold came on over his own eyes.\par
“This…! I heartily approve of such practice… but to waste the wood of my work site on it…”\par
\par
“Orodan… these beams and boards are… quite good. Honestly, given the quality of the wood that the supplier shorted us on, this is probably the best we could hope for,” Old Man Hannegan spoke. “You could honestly claim you’re an Apprentice at Woodworking if you put in a few more months of hard work and study.”\par
“I’m only at level 18 Woodworking, I have a ways to go before I dare to say I’m at the Apprentice-level as a Woodworker,” Orodan replied.\par
“Level 18?! When the hell have you been wasting that much time on crafting?! You’re one of the most talented fighters to come out of our shoddy town and you want to waste your time on Woodworking?!”\par
“Hey… don’t scream too hard, you might strain yourself at your age old man,” Orodan teasingly replied. “Anyways, explain how a board made from poor quality wood can be improved upon further.”\par
“You…!” Old Man Hannegan exclaimed with a red face, and then reigned himself in. “Look, this wood isn’t the best quality, but even then there are some ways of trying to improve the durability of the wood. Cutting strictly along the grain is one part of it, as is tempering the board and treating it, some of those prodigies at the Guild even say they can talk to the material and make it a certain way… I think that's hogwash though.”\par
Orodan paid attention and took mental notes.\par
\par
The question was… how did a Woodworker ‘talk’ to their wood?The story has been taken without consent; if you see it on Amazon, report the incident.\par
Orodan looked crazy to the crew as he spent multiple loops trying to hold a conversation with the boards and beams he sawed, but to no avail.\par
He didn’t understand how wood was treated or tempered either, so that was put to the side until he finished up his loops at the construction site and found a proper carpenter shop or lumber yard to work at.\par
But he did try various experiments.\par
First, and the primary path which Orodan felt would eventually yield a result that would synergize well with him… was attempting to ‘feel’ the material and mentally concentrate and push his will into it almost as though it was an extension of his own body.\par
While under the strain of death he had managed to acquire skills which came from mentally commanding his own body to toughen, such as Iron Body. So he figured the same could work here.\par
Second, he examined existing pieces of wood which were of superior strength to the beams and boards he made, such as the beams that laid the initial foundation for the warehouse, and his shield. And he tried to understand what strengthened wood should look like. Having the idea in his head of what the next ‘stage’ of wood should be and what he should aim for helped.\par
And third… was that his vacation had to end and he needed to put himself in the crucible of combat if he wanted to advance his ability to mentally connect with and strengthen the wood.\par
Orodan felt that this was important if he wanted to retain his equipment and have it remain useful throughout his rampage at Eversong Plaza. A blast from just the Elite-pyromancer would utterly disintegrate all his clothes and equipment, and even if he avoided that, his sword and shield simply weren’t up to par in the melee against the undead Demonic Berserker fielded by the Master-necromancer.\par
And so he got to work.\par
\par
The great arrow pierced right through his shield but harmlessly bounced off his Iron Body.\par
“Damn… you’re probably the weakest Adept I’ve fought in my life and my shield still isn’t strong enough to take even your pathetic shots?”\par
The militia really was a local group of bumpkins who had utterly garbage quality equipment. True, they were merely Apprentice level at the Ogdenborough barracks, but none of their equipment could stand up to a regular attack from even an Adept.\par
The archer outside the Temple in Scarmorrow really was a complete weakling in the grand scheme of things.\par
Now that Orodan had fought Adepts of all kinds he decided to come back here and attempt to work on his Woodworking against the weakest foe he knew.\par
Orodan used the shards of his now ruined shield and attempted to block the now furious shots from the insulted archer. Still, it was for naught and would take many more loops.\par
He knew his weak wooden shield inside-out. The rounded shield might not remember him, but Orodan remembered it throughout every loop as he woke up next to it. So he figured that if he was going to communicate with anything, the shield was his best bet to start with.\par
His fifty-fourth loop yielded an unexpected result.\par
\textbf{[New Skill (Rare) → Weapon Aura 1]}\par
And it allowed him to successfully stop a great arrow with his shield, even if the shield was partially pierced through.\par
It would undoubtedly be a fantastic skill which amplified his battle power by a scary degree once he trained it up. But this still wasn’t what Orodan wanted. Communing with the material, the wood itself, was what Orodan needed.\par
But he now had a way forward.\par
He went back and forth, some loops deciding he’d spend the day working alongside Old Man Hannegan, some days deciding he’d test his shield against the great arrows of the weakest Adept he had ever met.\par
And slowly but surely he was getting somewhere.\par
\par
His new skill, Weapon Aura, now at 13 allowed him to not only strengthen a weapon by enforcing his will onto it, but also feel the weapon, almost as an extension of his own body.\par
This was great for studying the material and understanding exactly what the wood that composed his shield was, and hopefully communicating with it.\par
To the side, Old Man Hannegan and the crew were giving him weird looks as he spoke to the shield.\par
“You’ve saved my life countless times, we’ve been through thick and thin… can’t you at least help me understand and talk to the wood you’re made of?”\par
The shield of course, did not reply.\par
By the next loop he now started attempting to wield an entire tree in his hands and extend Weapon Aura to it as he swung it around. And the act while strange and somewhat taxing of a strange energy source within Orodan, yielded fantastic results in terms of levelling the Weapon Aura skill.\par
But it still wasn’t quite what he wanted, and so he spent even more loops seeking out various wooden objects to extend Weapon Aura to and seek to understand.\par
The wooden cart Old Man Hannegan’s mules pulled to the work site every day, the wooden beams of the under-construction warehouse, the door to his hovel, the trees, the bushes, the saplings.\par
Orodan wanted to understand them all.\par
What was wood?\par
It was a form of life, communing with it required understanding it, getting at its nature.\par
Hundreds upon hundreds of loops passed, and unlike sets of loops with a combat objective, Orodan didn’t have a singular goal like he did in a fight and thus allowed himself to lose count of how many loops exactly passed.\par
He studied different sorts of wood. He extended his Weapon Aura to them. He tested the strength of them in battle and constantly attempted to commune with it.\par
He extended his Weapon Aura to trees and tried to coerce them to pull nutrients and water from the ground faster, he tried extending it to saplings and young trees and coerce them into growing a certain way where the sun would reach them easier.\par
And bit by bit, he began to understand the nature of wood itself, and felt as though he briefly touched upon its place in the overall scheme of life.\par
He wasn’t a researcher or an academic, but this form of practical hands-on experimentation was greatly soothing and interested him deeply.\par
And eventually, he got it.\par
\textbf{[New Skill (Legendary) → Wood Communion 1]}\par
It was the next loop.\par
“Old man, can you tell me how a board made from poor quality materials can be improved upon further?” Orodan asked.\par
After his usual grumblings about being called old, Mister Hannegan answered. “Well, aside from making sure to work with the grain when sawing, or treating or tempering the wood, the only rumour I’ve heard is that some of the Elite-woodworkers in the Capital talk to their damn wood. How weird is that? I doubt anyone here will be doing that anytime soon.”\par
“Hmm… like this perhaps?”\par
And Orodan acted.\par
The Wood Communion skill allowed him to mentally commune with any wooden material, and just that alone would likely get him poached. But Orodan took it a step further and used his Weapon Aura skill alongside it.\par
What would otherwise be a negotiation process as wood resisted the changes he suggested, was instead a guided transformation where he strengthened the wood with his Weapon Aura and then convinced it of the results that could be achieved if it naturally adopted the changes itself and became stronger.\par
The wooden pole he had expertly carved out of a log was no longer the poor quality wood it once was.\par
Old Man Hannegan rushed over with a disbelieving look in his eyes and immediately began conducting stress tests on the weapon.\par
After it cleanly cracked a rock into pieces with a single swing from his civilian hands he returned it to Orodan with a trembling grasp.\par
“What in the Gods’ name… this is… this is wood that could be used in an Adept-level weapon!” Old Man Hannegan exclaimed.\par
And the entire crew gathered around, disregarding their fear and wariness of him for once as they stared at the wooden pole in wonder.\par
It was six feet long, and the wood was far darker in color than it was prior to Orodan working it. It also carried a subtle glow which was almost magical. It could likely serve as an excellently made haft for a halberd or spear, but even without it, it could right this instant serve as an Adept-level weapon for a staff-Adept.\par
The pole could probably shatter rocks into powder without taking a single scratch. And that was without Orodan’s Weapon Aura empowering it. The downside of Weapon Aura was that it effected only what Orodan was wielding and empowering with it. A poor quality plank being empowered to Adept-level would go back to being just a poor quality plank once done.\par
But now, Orodan could create wooden products that were strong in and of themselves.\par
“What have you been doing in your spare time Orodan?! The crafting guilds will now want to poach you! This… is going to be a headache for you if you want to stay in the militia…” Old Man Hannegan warned, worry in his tone.\par
Truly, the man had watched out for Orodan ever since he’d moved to his hovel on Briar Court as a 14 year old, and the genuine concern in the man’s voice caused a smile to crack on Orodan’s normally stern visage.\par
“It’ll be fine Mister Hannegan… I assure you the Guild has bigger things to worry about than me today,” Orodan replied cryptically. “Anyhow, I have to work further on improving this new skill, so let’s see if I can turn the shoddy quality wood you have into something better.”\par
And the rest of the loop before Ogdenborough was destroyed was spent turning the already set foundation, frame and existing wood pieces into something far stronger than they should be.\par
The entirety of the wood used in the construction of the house was turned into Adept-level material, and even the young woman who was the architect began to sweat in nervousness and constantly complained that she’d be made to vanish and as would the owners of the house she was building.\par
Orodan had an inkling that what he was doing on the scale he was doing it… shouldn’t be economically viable for the average person, or even a far higher-levelled Woodworker, particularly since he felt a drain.\par
Throughout the whole process Orodan felt a minor drain on the nearly bottomless well of energy he felt the inklings of ever since he drained the orb within the control chamber and gained his Mana Black Hole skill. He suspected it was mana, and he had an absolutely titanic amount of it within him thanks to his skill.\par
And most unfairly enough… every time Ogdenborough was destroyed Orodan recovered a thousand times the energy he spent empowering the wood by simply pulling in the energy from the destructive blast emitted by the metallic machine.\par
And the energy he gained remained throughout loops, so Orodan had an ever-growing source of virtually infinite mana for the sake of empowering wood.\par
\par
A few hundred more loops passed as Orodan continued working on these crafting skills he had come to become strangely enamored with.\par
And this loop he found himself having finally done all he felt he could accomplish.\par
Before him, in the span of about six hours, stood a completed warehouse. Something that wasn’t slated to be complete for at least a few more months.\par
Orodan had experimented with many techniques, and empowered every piece of wood involved in the building of this warehouse. His final touch was to place his hand on the building… and use Weapon Aura and Wood Communion on the entire warehouse itself to cause wood at joints and gaps to blend together and fuse seamlessly. This gave the structure a level of integrity and durability that nothing else in Ogdenborough could compete with. Frankly, even some of the richer houses and fortifications in the County might be inferior to his work.\par
Of course, this came at the cost of a frankly colossal amount of mana that he felt drain from his reserves. But again, the amount drained was a drop in the bucket compared to what the end of each loop gave him during the destruction of Ogdenborough.\par
“…what even are you?” she asked.\par
Vilia Coventor was the architect in charge of the building of the warehouse on 4 Ale Road. She was a graduate of a middling crafting academy in the County and was of average talent with not even an uncommon skill to her name. For her, this project was her first job she took after graduation and even then she only got it through the job board at the town hall of Trumbetton where lower paying jobs were frequently posted.\par
For an architect of average talent, such was their life when starting out.\par
But with a building like this under her name? Even if she had no relevant skill whatsoever, people would give her regard simply because she was able to secure a talent like Orodan who could build such an incredible house. Furthermore, she quickly realized using any other material besides the scary man’s empowered wood was a waste, and so quickly drafted a new construction plan that utilized only wood to make the warehouse, something which gave her increased levels in Architecture.\par
Frankly, the owners would face a tragedy as the empowered wood would undoubtedly be stolen and the house damaged and maybe they would even be killed, as this was akin to building a house made of gold without having the appropriate personal power or security in place to protect it.\par
But that wasn’t Vilia’s problem. She would have a head start now with a completed project under her belt, and she could market herself to one of the more established architects in the bigger towns and secure a well paying apprenticeship for herself.\par
Vilia normally held an attitude of caution and wariness towards Orodan. Whichever powerful backer had allowed a monstrous talent like him to play crafter in the poorest town in the greater Capital area… was none of her business. But for once the normally ragged looking woman showed emotions beyond just caution and a hint of fear towards Orodan.\par
“I just wanted to say… thank you… really; I mean it,” Vilia spoke sincerely. “I’m just an Apprentice-level Architect, but you forcing me to adapt my plans on the fly gave me skill levels, plus I finally have my first completed solo project under my belt.”\par
Orodan finished cleaning up and looked at the ragged looking woman with dark circles under her eyes. Low Physical Fitness, but at least she looked like she worked hard at her craft.\par
Orodan decided helping her build this warehouse was something to add to the list for his longer loops if he ever managed to get past the day.\par
“It’s not a problem. But if there’s something you could do for me… how about referring me to a good lumber yard who’ll teach me further about Woodworking?” Orodan asked.\par
\par
It would ordinarily be a two hour trip for Orodan, if he had the skills of himself before the loops.\par
But with Physical Fitness combined with Sprinting, it became a ten minute sprint to the town of Velestok which bordered the sprawling Aenechean forests and where where Vilia had recommended a particularly good lumber yard in the previous loop.\par
Orodan had specified that he needed a place where he had plenty of material to work with, alongside teachers of decent skill who would simply let him work.\par
And so Orodan asked around and stood before the supervisor of the lumber yard.\par
A thick, bushy beard. A body that looked fat but Orodan was certain held a stout and muscular frame underneath, and a beer gut. Orodan looked down upon the fierce looking supervisor.\par
Who was a dwarf.\par
Orodan was a street rat who had struggled and grown up in Ogdenborough, the poorest town in the greater Capital area. And even once the loops had started, he was too bull-headed to consider anything but grinding his head against the wall that was his obstacles.\par
Exploration? Going to new places and obtaining exotic skills, training and treasures? For a stubborn brute like Orodan such things were not on his mind.\par
So it was his first time ever seeing a dwarf.\par
“Well? Is the beard thick enough? Am I sufficiently short for your liking? Would you like to gawk some more?”\par
The dwarf’s words brought Orodan out of his hypnotized staring and he felt a bit of shame.\par
“I apologize… I’ve never seen one of your kind before. The continent is rather… human-dominated,” Orodan replied. But still couldn’t help but sneak a few looks to make sure what he was seeing was real.\par
“Feh… ‘human-dominated’ until the Dokuhan mountains where you lot are too chicken to settle,” the bearded supervisor replied with a bit of heat. “Our under-mountain holds are built sturdier than any of your human kingdoms and ‘republics’.”\par
“Of course, you are correct, I didn’t mean to disrespect you,” Orodan amended. “I’m actually here to seek work. You have trees that need chopping and construction wood that needs sawing? I’m a good hand at Woodworking, Apprentice-level. My Physical Fitness is also decent and I feel I can pick up Lumberjacking rather quickly.”\par
“Hmmph… well at least you have enough sense to get to business than try and waste my time with pleasantries,” the dwarf said as he pulled out an Observer orb. “Go on, put your hand on it. Let’s not waste any time.”\par
“Actually, I’d prefer not to undergo an examination by the orb… I’d rather show you my ability and let you decide if I’m worth keeping around.”\par
The dwarf gave Orodan a piercing gaze, but whatever he saw must have satisfied him.\par
“I’ll humor you boy, but if you’re wasting my time a beating is the least you’ll get,” the dwarf gruffly allowed as he beckoned Orodan follow him. “We have daily quotas that must be met, and today your test is to chop down a tree and process as many two by four pieces of lumber as you can… in an hour.”\par
The lumber yard was on the border of town, near the beginning of the Aenechean forest, and so it was a few seconds before they reached the copse of trees designated for chopping.\par
“You need an axe, or did you bring tools of your own?”\par
“That won’t be necessary,” Orodan replied with a smirk. “My hands will suffice.”\par
And before the stern dwarf could take offense to the presumption that Orodan was playing around, a fist cracked a massive hundred feet tall tree and it fell.\par
Right towards the two of them.\par
And as the dwarf’s expression of awe was replaced by one of terror and attempting to dive for safety, Orodan simply stopped the falling tree with one hand… and threw it back in an arc the other way.\par
Over the next minute, the tree was de-barked with incredible speed and two by four construction wood began to be carved by a saw Orodan had ‘borrowed’ from the construction site at 4 Ale Road.\par
Within five minutes the entire tree had been converted to a nice stack of construction wood.\par
And the dwarf was silent for at least ten seconds before he spoke again.\par
“…well then. When can you start?”\par
Orodan mentally summoned his Status and smiled.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Woodworking Apprentice}\par
\textbf{Title 2: Empty}\par
\textbf{Available Titles: One Who Has Experienced Death, Sword Adept, Shield Adept, Physical Adept, Unarmed Combat Adept, Master Slayer, Wrestling Apprentice, Cleaning Apprentice, Woodworking Apprentice, Combat Adept}\par
\textbf{Rewards: Permanent +1 Action Increase}\par
\textbf{Skills: Sword Mastery 62 (Adept), Unyielding Vitality 60 (Adept - Rare), Pain Resistance 59 (Adept), Dying Struggle 59 (Adept - Uncommon), Shield Mastery 58 (Adept), Combat Mastery 57 (Adept), Dying Struggle 56 (Adept - Uncommon), Bleeding Control 56 (Adept), Physical Fitness 55 (Adept), Damage Mitigation 54 (Adept), Death Rage 53 (Adept - Exquisite), Unarmed Combat Mastery 51 (Adept), Power Strike 44 (Apprentice - Uncommon), Perfect Parry 42 (Apprentice - Uncommon), Wrestling 42 (Apprentice) Iron Body 41 (Apprentice - Exquisite), Mana Resistance 39 (Apprentice - Legendary), Tool Mastery 39 (Apprentice), Woodworking 37 (Apprentice), Impregnable Bladewall 36 (Apprentice - Exquisite), Weapon Aura 35 (Initiate - Rare), Evasiveness 34 (Apprentice - Uncommon), Cleaning 34 (Apprentice), Surprise Attack 32 (Apprentice), Wood Communion 31 (Apprentice - Legendary), Sprinting 30 (Apprentice), Laboring 27 (Initiate), Construction 21 (Initiate), Impact Resistance 21 (Initiate), Slashing Resistance 16 (Initiate - Rare), Club Mastery 15 (Initiate), Piercing Resistance 14 (Initiate - Rare), Lightning Resistance 14 (Initiate - Exquisite), Shield Throw 12 (Initiate - Uncommon), Parkour 11 (Initiate), Maintenance 8 (Initiate), Mana Black Hole 8 (Initiate - Legendary), Intimidation 7 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Deception 4 (Initiate), War Cry 3 (Initiate - Rare),}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor, Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark, Death’s Call - Whenever you will it, Death takes you]}\par
“Right now.”\par


\section*{Chapter 8 - Meeting An Ancient}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 8 - Meeting An Ancient}%
\par
Orodan didn’t have good experiences with noble houses.\par
From a young age he’d been told to avoid nobles and their soldiers and had often been at the receiving end of beatings and subjugation at their hands.\par
And then the time loops started and his hatred for House Argon grew, and this began to at least partially color his view of noble houses in general.\par
But he felt this would be unfair to House Simarji, the owners of the lumber yard he currently found himself laboring in.\par
They were a smaller house that had come to prominence with the liberation war that formed the Republic. Their house originated from the eastern kingdoms and emigrated to the lands of the now-Republic. When the time for war came, they bravely contributed and earned themselves a designation as a noble house.\par
Of course their main income was farming and forestry. Their house alone was responsible for a sizeable portion of the Capital’s food yield and lumber supply.\par
As employers, they seemed to be very fair and respected.\par
They still had Adept-level guards keeping watch over the lumber yard as any sensible business owner of means would, but their workers spoke well of Count Rohanus Simarji, the eldest son of the house and an Elite-level healer who was known for having savvy business sense and always treating his workers well.\par
The man’s magic was at least partially responsible for the abundant growth of the farms and forest preserves House Simarji owned.\par
For Orodan’s purposes, this meant that he was never bothered much during the course of his work. If anything, aside from the grim-faced supervising dwarf - Ogrik Dothrilrock was his name - the other workers were all rather happy and carefree as they seemed to genuinely enjoy their jobs.\par
There wasn’t even the fear and wariness of Adept-level people present in these workers like there was at the old warehouse at 4 Ale Road. If anything, the workers treated him with a subtle sense of respect but nothing too reverential, which was a great improvement over being treated like a walking weapon one needed to tread lightly around.\par
Most importantly, this meant that unlike the old worksite, the supervisor here didn’t worry about facing repercussions for a talent like Orodan working here or poaching him outright.\par
House Simarji was a noble house in their own right, and they had a rumored Master-level individual in their house who preferred to stay out of the public eye.\par
Orodan still had the Adept-level guards approach him over the course of the loop; his Physical Fitness must have drawn some attention with how easily he threw trees around and carved through wood as though it was air. They approached him in quite the friendly manner and asked him who he was and what his interests and goals were.\par
Orodan saw no harm in answering honestly and he was certain someone in the overlooking tower was taking notes.\par
The training and practice for his Woodworking skill was fantastic at the lumber yard. He had all the material in the world to work with, and the carpenters in the woodworking area were all more than eager to help teach and give tips and advice to someone who worked hard and produced a veritable flood of material in record time. He also gained the Lumberjacking skill.\par
And in this loop he hadn’t even used Wood Communion alongside Weapon Aura to produce some truly high quality wood.\par
Near the end of the loop, an hour before the announcement preceding the chaos at Eversong Plaza, Orodan spotted a figure calmly walking towards him.\par
The man looked positively ancient. With a wrinkled face of bronze skin, flowing white hair and a long beard. He stood as tall as a young man, but still used a long pole wrapped in cloth as a walking stick.\par
Orodan paused his work for a moment. He had exceeded the entire lumber yard’s quota for the next week altogether.\par
It wasn’t exactly unprecedented for the occasional wandering genius with ridiculous Physical Fitness to come by a work site and dabble in such things, but for one to stay as long as Orodan did and then have the relevant skills, was a bit much.\par
“Can I help you?” Orodan asked.\par
“Help me? No… but you can help yourself young man,” the old man spoke with a certain level of gravity in his voice. “I strongly recommend you leave the County altogether and make your way East. Something calamitous will occur soon.”\par
Now that truly made Orodan pause and take the man in seriously.\par
Just who was this old man? For him to know about the destruction that would ensue soon. Orodan decided to bite the shot and test the waters. His third Blessing gave him a way out should things devolve.\par
“Then why is nobody trying to do something about it? That machine beneath Mount Castarian will awaken soon and the entire county will be turned into a red wasteland of chaotic mana!”\par
Now it was this old man’s turn to look at Orodan sharply.\par
“And just how does a sapling like you know of these things? I initially sought to warn you given the rare talent you’ve shown for your age… but you also know about the games being played under the mountain?” the old man asked.\par
“Of course I do, I keep reliving this same day over and over! I’ve slowly begun to come to terms with it, but I still have no answers about the politics and why the hell the Republic and people like yourself know about it but are so content to send only a token force to Eversong Plaza at noon,” Orodan exclaimed. “Just what sort of game is being played here?!”\par
And the old man’s eyes actually opened a slight bit wider and he held Orodan’s gaze for a few seconds before speaking.\par
And then he laughed.\par
And once he was done with his throaty chuckle, he spoke.\par
“Heh… just… amazing… time magic of such a scale cast on one so young and ignorant,” the old man almost crazily spoke in a mutter. “Tell me child, how many times have you died over the course of the spell you find yourself in?”\par
“Thousands? At least more than ten-thousand times by now… I lost count during some sets.”\par
“That many? No mortal on this world would have enough mana to keep such a spell going for that many times… and I haven’t heard any of the famed Master-level chronomancers raising a ruckus about time being convoluted or rewound…” the man muttered as much to himself as he did to Orodan. “Which Gods are you in contact with? It could only be something done by them… but even then… the Cathedral has said nothing is out of the ordinary…”\par
“I’m not in contact with any Gods… this time loop… even the Gods are unaware of it. When I told Ilyatana the last time she tried to ‘give’ me something that would make me serve her better in finding an answer for her… thankfully the God of Death saved me by granting me a Blessing that allowed me to take my own life easily.”\par
“Soul manipulation… filthy magic… you were fortunate to have avoided that. Still… this tale of yours sounds absolutely insane and almost fantastical in how nearly-impossible it is,” the old man said with a raised eyebrow. But he didn’t outright reject it?\par
“Nearly impossible? So there still might be an explanation for what’s happening to me?” Orodan asked.\par
“Perhaps there is… come child, let us have some tea and you can tell me the details about this time loop.”\par
\par
“So even the Quest is reset once the loop restarts, even if you’ve completed it… have you tried completing it once again then?” the elderly man asked.\par
“No… after I realized there was no escape in sight I’ve spent the loops since just honing my Woodworking and obtaining skills such as Weapon Aura and Wood Communion. I haven’t really bothered returning to the Plaza, although I certainly could go and drain the orb once more and complete the Quest that way,” Orodan explained.\par
“Hmm… not the worst idea; sometimes a warrior must meditate on things beyond just battle,” the aged man spoke. “Weapon Aura is a decent force multiplier and a must-have for any warrior who hopes to get anywhere. A shame that the curriculum for academies nowadays is so pathetic. Could you not have consulted some of your teachers to tell you more? That it took you thousands of loops before you discovered it is a bit shameful.”\par
Orodan grew slightly annoyed at this and barked back. “I had no academy!”\par
“Truly? Who were you before this started then?”\par
“I was… I am, Orodan Wainwright. I’m a member of the Volarbury County Militia in Ogdenborough, I’m a mere Private. I had no fancy academy, I had no mother or father to guide me. I grew up struggling on the streets of Ogdenborough and later spent my years till I came of age in the Lady Sashwari Home for the Wayward… but despite all that I still got accepted into the County Militia at the age of 16.”\par
At this the old man, who had been looking at Orodan like one might look at an interesting child, now finally showed some change. His eyes softened a bit, and Orodan would daresay he saw an inkling of respect in his gaze.\par
“…that’s good,” the old man quietly replied. “I don’t have a real answer for you about why you’re supposedly in a time loop that even the Gods are unaware of… but I will say that if anyone was meant to succeed in such a scenario, it would be one such as you. You are without a doubt… a true idiot.”\par
“…huh?!” Orodan protested, but the old man put a hand up to stop him.\par
“But you are also a true warrior. I… cannot even say that I would be willing to be torn apart thousands of times on end with no rest simply to make progress against an undead Demonic Berserker by attempting to fight it toe to toe at the Adept-level. Whichever divine power beyond the Gods is responsible for your plight… they chose well in picking a stubborn stone-headed idiot like you for this time loop.”\par
Orodan’s head grew hot with vexation. “Surely you didn’t say all this just to insult me old man?!”\par
“Putting the young in their place and reminding them of their shortcomings is one of the few ways I amuse myself at my age,” the old man quipped back, much to Orodan’s irritation. “Anyhow, has anyone explained Gods to you in an academic sense?”\par
“The only explanations about the Gods I received was from the Temple and the matrons growing up. The Gods are supreme and all-powerful, that’s all I was told,” Orodan explained.\par
“That is… not necessarily correct. The Cathedral will of course happily peddle whatever dogma serves them and their divine overlords… but the truth is a different matter,” he spoke. “Tell me boy… do you know what the System is?”\par
The System? Did the old man mean the messages he received from on up high whenever his skills increased?\par
“Isn’t that too under the domain of the Gods?” Orodan asked in return.\par
“No. The System is something that has existed, and will continue to exist long after this current crop of Gods have turned to dust,” he explained, and Orodan leaned in and paid rapt attention as his worldview was being turned upside down. “The priests of the Cathedral will fervently label any who say it a madman and a heretic, but it’s common knowledge among the Master-level that even the Gods themselves rose to their station through the System.”\par
“So there existed Gods before the Prime Five?” Orodan asked incredulously. His upbringing as a bumpkin didn’t allow him to ponder on such forbidden knowledge till now.\par
“A long time ago… when I was just a young lad like yourself, there were whispers of a God of War before Agathor. The whispers and hushed knowledge were already ancient even when I was a lad, and now as the hundreds of years since then have passed, those whispers have vanished entirely,” he explained. “I always thought these Gods might have died… something the Cathedral will deem impossible, as they swear up and down that Gods cannot be slain. But some of my old friends thought that at least some of these older Gods advanced to an even higher level. For this time loop you’re in to evade the notice of even the Prime Five… perhaps something beyond even them has chosen you for this.”\par
“So you actually believe me then?” Orodan asked with some disbelief in his tone. “Usually it takes a priest communing with their God to understand that something is wrong, and even then the priest doesn’t believe me, they simply relay what their God says.”\par
“And that would be entirely normal and understandable for them. As becoming a priest of a divinity requires blind faith in dogma, obedience and levelling skills which makes them more of a pliant puppet to their God’s will at higher levels. I must suggest you don’t train in their skills if you wish to retain your independence of mind,” the elder explained, and Orodan agreed given the scare he received at Ilyatana’s hands.\par
“So why do you believe me then?”\par
“Because, lad… I know what the initial wording of a Quest message says word for word. Not the fanciful fictional accounts, nor the lies of charlatans. After all, I fought alongside a man who received a Quest to slay a desert worm the size of an entire mountain range.”\par
And Orodan found himself sitting their, jaw agape at the words of this venerable elder, and the time-looper asked a question people normally asked him whenever he displayed impossible abilities.\par
“Just… just who are you?”\par
“You haven’t yet earned the right to that until you’ve impressed me, now come, show me what thousands of deaths in a time loop can achieve,” the sagely elder spoke.\par
And the aura around the man suddenly turned very, very heavy. Neither the High-Burgher nor the Novarrian beneath the mountain had made Orodan feel this sort of… pressure.\par
Orodan steeled his nerves and drew his weapons.\par
\par
It wasn’t a fight to the death.\par
But Orodan still felt like he was in one.\par
The elderly man refused to use more than one arm, and he refused to utilize the wrapped long pole he kept held behind his back. But even with just that… Orodan felt pressured in a way he never had before. Even Ovuru the Guzuharan ogre-man, who was a Master-level warrior himself, hadn’t pressured Orodan this much.\par
He activated Death Rage and every possible supporting skill he could think of, and he was utterly overwhelmed and sent flying through dozens of trees with a single slap each time.\par
Weapon Aura and Wood Communion combined together to strengthen his shield so incredibly much that it would shatter if he poured any more mana into it. It could likely take the blow from a Master-level warrior now. And yet it too was smashed to smithereens with no regard.\par
“Come now… if you're in a time loop as you claim, has constant death made you complacent? I’m not going to kill you, but I do expect you to adapt to the pressure and come up with something,” the dastardly old man spoke with a calm smirk on his face. “We’ll have to break this bad habit of yours of using death as a crutch. Focus, and genuinely treat this as though it’s your last try and struggle with all you have.”The story has been taken without consent; if you see it on Amazon, report the incident.\par
Easier said than done!\par
This monstrous old man’s expectations were simply too high!\par
“Do you know what talent is young one?” his opponent asked as he thrashed him hard enough to bypass all his resistances and break a rib. It would heal in time, but it was still a frankly colossal hit delivered with such casual ease.\par
“There are two kinds of talent,” the elder spoke as he delivered another chop with his left hand that sent Orodan into the ground and formed a crater. “The first, is the talent of hard work, this you already possess. The ability to grind and persevere no matter what. But it’s merely one part of the recipe for success.”\par
“The second kind of talent, is that of a genius. The ability to grasp things almost immediately and instinctively,” he spoke as another series of thrashings were delivered unto Orodan’s now battered and bleeding body. “People will say this sort of talent is something one has to be born with, but that isn’t true. It requires the first talent, hard work, being applied to the extreme.”\par
Another series of horrendous beatings descended upon him.\par
“So what if you weren’t born with the innate talent to instantly comprehend things? So what if you aren’t a natural genius?” a chop brought his attempt to stand back to his knees and the old man stopped for a moment. “Stand up boy, and receive my attacks. Concentrate till your face goes red and your eyes leak blood, focus till your brain explodes, cram as much thought, experimentation and ingenuity into every thousandths of a second till each second itself becomes equivalent to an hour of dedicated hard work! Adapt! Think of this as your last try for the next blow I’ll land will kill you!”\par
Orodan was crazed. Time loop? He had forgotten about such things in this moment.\par
Right now, time almost seemed to freeze as the impending blow came for his face, and in his last moments, he realized that death was a crutch, one that was holding him back.\par
He forgot who he was, and madly strained as though this was his last. He felt his very soul strain under the pressure of attempting to cram every bit of focus and thought into each thousandths of a second. It almost felt as though two of him were thinking using the same mind.\par
\textbf{[New Skill (Rare) → Soul Manipulation 1]}\par
This wasn’t the auto-piloted death grinding of the loops, but something altogether more strenuous and laborious.\par
He vied for each and every edge he could get against this upcoming attack, mentally he called forth all of the near bottomless mana within himself and poured it towards something, towards whatever would help him in the near instants before his death.\par
His entire being, the very soul that he felt strain as he crammed as much focus into thinking in these instants of time, his entire mana pool, it was all poured into this one thing. And the last ingredient poured in was all his emotions, all his experiences, all the hard work, the stubborn willpower he had adamantly held onto throughout the thousands of deaths.\par
His own fist rose, charged with all that was him. This strike contained all that was Orodan Wainwright.\par
But he still felt and knew that it wasn’t enough. And on the eve of death, he decided to apply whatever it was that allowed him to think as though there two of him using the same mind, to the physical world.\par
His right hand tore through the air towards the attack… and in an impossibility… another right hand occupied the exact same moment in space and time and also tore through space to meet the old man’s attack.\par
Two actions performed at the exact same moment in time, occupying the exact same space, almost as there was two of him occupying the exact same position.\par
It was impossible, but the power of his attack multiplied by two.\par
And an unfurled halberd was forced to meet it as the old man had a mad grin on his face.\par
\textbf{[New Skill (Legendary) → All-Strike 2]}\par
The surrounding mile was turned to ash, and in the distance, half of Velestok was… gone. And the rest was turned to rubble.\par
As was Orodan’s own arm and half of his entire body and face.\par
The old man’s crazed grin never subsided as he spoke, and he looked unharmed by the attack that could have killed a Master-level combatant.\par
“Hahaha! Now this is talent! Don’t you ever allow death to make you complacent and forget this feeling of true hard work again!” the man exclaimed. “Assuming enough deaths will let you achieve something is a good way to miss out on the insights you could have if you simply strained with your all in the moment.”\par
“Orodan Wainwright… my name is Adeltaj Simarji… you might hear the name if you pick up a book on ancient history. And it took you long enough to figure out what the Reward from that Quest did!”\par
Orodan couldn’t speak in response, his body utterly ruined and his soul feeling a level of strain it hadn’t ever experienced.\par
But with this result… he could finally accept death and consider the loop a success.\par
“Now hurry up and use that third Blessing from Malzim you spoke of and find me in the next loop, your training is quite lacking and we must erode many bad habits of yours… can’t even use this new skill without blowing up your own arm and body… tsk, tsk!”\par
As Orodan was poised to activate his third Blessing, he decided that he would not be immediately rushing to this crazy old man the second the next loop began.\par
Not till he figured out just what this new power of his was.\par
\par
A keening wail ringing in the night sky awoke him.\par
Orodan awoke and customarily brushed away the Quest messages, and he immediately rushed out of his hovel, shield in hand.\par
The new legendary rarity skill wasn’t what he wanted to test.\par
The skill was nice, incredibly powerful even, but it was just another offensive skill. One that would undoubtedly give him the power to really threaten higher-level warriors now. But it’s power output was tied to how much mana he had stored via the Mana Black Hole skill. And he had expended the entirety of multiple loops worth of mana absorption from the destructive attack of the ancient war machine.\par
And the mana stored inside Mana Black Hole was essentially dry now and so he’d have to spend a few loops recharging to replicate the same effect again.\par
All-Strike was still incredibly powerful he could feel, but its implications weren’t anywhere near the Quest Reward whose function he had just discovered.\par
The Reward which was the +1 Permanent Action Increase.\par
A Shield Throw was poised to fly towards the harpies flying overhead in the distance, but Orodan recalled the feeling of what he’d done in the last loop against that crazy old man.\par
And as before, the familiar feeling of impossibility and an unnatural break in reality itself overtook him.\par
And two Shield Throws were sent, occupying the exact same moment in time and space, and even somehow conjuring an extra shield which Orodan knew was the exact same as the shield he normally used.\par
Four harpies didn’t even have the time to cry out in outrage as they were cut in two by the shields flying through them. And after a second, one of the shields flying into the horizon… abruptly disappeared.\par
“Incredible…” Orodan muttered to himself.\par
It was as though he had thrown two separate Shield Throws in the exact same moment in time and space. Yet he only used the energy of one!\par
This was… mind boggling and he would need to test out the implications of such a thing.\par
But if this was what he thought it was, even if the other ‘action’ stopped after a single second. It was more than enough time to do absurd things, like double his attack rate as each blow could be simultaneously thrown alongside another in the exact same moment in time.\par
It was as though reality bent to allow him to do one thing and another thing at the same instant of time!\par
“I have to test this!”\par
He exclaimed excitedly, but then remembered he had essentially lost his shield for the rest of the loop.\par
\par
“What the hell… since when do you know magic Orodan?”\par
These were the words of Old Man Hannegan, who looked on with a disturbed expression on his face, as it appeared as though two of Orodan had appeared, occupying the same spot in space and time, and were simultaneously working on stripping down the log into useful construction wood.\par
He had tested the limits of the +1 Action Increase, and it seemed that while the effects lasted only one second… there was nothing stopping him from performing other actions consecutively. And the energy and stamina expended were the same as though he had done only a single action.\par
There were certain oddities such as if doing one action which was trivial and doing another such as All-Strike, the more energy intensive action’s cost would be paid. But this was still an incredible boon.\par
Even by simply working as normal, Orodan could now think with two minds, and looked as though he had a weird clone flitting in and out of his body and doing things independently of him only to disappear within one second of staring the action.\par
His mental thought process and speed being boosted by two essentially allowed him to think and learn two times faster than before.\par
To others it appeared as though it was a slightly disturbing form of esoteric magic. But to Orodan who knew exactly what it was really doing, the implication that he was breaking reality and affecting causality by performing two things at the exact same time wasn’t lost on him.\par
He traveled down the length of an entire chopped tree in seconds, simultaneously stripping it of bark and chopping it into pieces suitable for construction. What was a process that took ten seconds before, took five now as there was essentially two of him working at the same time, two minds focusing on the same task, working in perfect synergy, capable of each performing an action of their own.\par
“This is… I feel like a God…” Orodan muttered to himself, but then recalled that scary old man Adeltaj Simarji. He certainly hadn’t felt like any kind of divinity when fighting that scary old monster of a man. “But I still have a ways to go.”\par
His All-Strike, amplified by two due to his Action Increase, had destroyed the entire town of Velestok.\par
Just how powerful was he now?\par
He hadn’t had the time to go to the next town and peruse the library, so Orodan asked Vilia Coventor the fledgling architect about who Adeltaj Simarji was.\par
While her academic knowledge on history wasn’t extensive, she had gone to a crafting academy and it let her share that nearly seven-hundred years ago in the Eastern Kingdoms a terrifying desert worm the size of an entire mountain range was devastating the inland Aswarthian Peninsula. A hero was given a Quest by the world to slay the calamitous beast, and one of the hero’s companions was a halberd-wielding warrior known as Adeltaj Simarji.\par
While such history would normally be obscure and foreign in the Republic, House Simarji proudly spoke of their heritage and proudly venerated Adeltaj Simarji, whom they regarded as one of the founding ancestors of their house and a proud link back to their roots in the Eastern Kingdoms.\par
And given the House’s close ties to the Republic, the history lesson was rather widely taught in the martial, magic and crafting academies throughout the Republic of Aden.\par
The old man was apparently quite famous. Although when asked if he was still alive, Vilia could only look at him strangely and almost sarcastically remind Orodan that it had been seven-hundred years since.\par
Which, for someone like Vilia to be skeptical was understandable. She was a crafter, and she was part of the common masses of society in seeing Master-level individuals and beyond as mere rumors and myths.\par
The Republic’s official education in the academies and the news never confirmed nor denied the existence of Masters, people whose skill level exceeded the threshold of 90.\par
But Orodan knew they existed. He had fought and killed a Master after all.\par
And if Adepts had their lifespans extended by fifty years and Elites were known to live up to three hundred… then for a Master to be very long-lived, perhaps even to the order of seven-hundred years like Adeltaj Simarji apparently was… wasn’t out of the question.\par
But he wondered if the knowledge that he was alive and acting as some kind of hermit was widespread even within his own House.\par
He thanked Vilia for her knowledge, and after finishing up the warehouse - without empowering the wood this time as his Mana Black Hole lacked the reserves in it - he made way for Velestok.\par
\par
“Adeltaj Simarji! Come out! I wish to feel your halberd for myself!”\par
Ten minutes after he had marched to the lumber yard in Velestok and boldly shouted such a brash summons and given the Adept-level guards who tried kicking him out a beating, it wasn’t Adeltaj Simarji who came to greet him, but a pair of two people. One a man wearing robes, the other a woman in heavy armor with a mace on her hip.\par
“Young man, has nobody taught you that it’s rude to go around beating people up and demanding to see someone?” the calm voice of the robed man spoke. “I don’t know what academy you’re from or whose little Adept prodigy you are, but who are you to walk into House Simarji’s lumber yard and thrash our loyal guards? Are you asking for the kind of beating you gave them?”\par
Orodan didn’t reply but simply clenched his fists, and in response the woman drew her mace and the man’s hands erupted with sharp gale winds and the entire lumber yard went silent as the battle was on and the workers had long since evacuated.\par
One minute later, both Elite-level individuals were given a decent walloping and lay before him, battered and bruised.\par
“I just came by to see the venerable elder Adeltaj Simarji, I have no quarrel with you!” Orodan exclaimed.\par
“No quarrel he says… as he walks in and gives us a beating…” the woman muttered from the ground, and Orodan felt guilty. Perhaps his headstrong way of approaching things wasn’t exactly ideal.\par
“Young master… soon Count Rohanus will undoubtedly arrive to speak with you. I implore you wait for his arrival as I’ve sent word to him,” the man spoke as his communication amulet glowed.\par
And so Orodan allowed the Elites to leave peacefully and waited a whole fifteen minutes before the arrival of Count Rohanus Simarji, riding a silver-feathered griffin. He was flanked by two other silvered griffin riders.\par
The man furiously touched down on the ground alongside his accompanying allies and angrily marched towards Orodan.\par
“You! State your business and why you’ve assaulted my loyal men! I don’t recall House Simarji ever daring to offend anyone, and we would swiftly punish any within our own ranks who dared do so without just cause!” the bronze skinned man in flowing silver robes angrily exclaimed.\par
Robes implied he was a mage, and the rumors did say Count Rohanus Simarji was an Elite-level healer. So for him to so boldly march towards someone who was carrying a sword and shield meant that either the man was stupid… or he was confident in melee combat if it came to it. And people who made it to the Master-level weren't stupid.\par
From what Orodan heard of Elite-level healers, they either focused purely on healing… or healing was but one aspect of their skillset.\par
“I came here seeking Adeltaj Simarji, I wish to test myself against his halberd and learn from him!” Orodan proclaimed loudly, causing a grimace to appear on Count Rohanus’s face.\par
“Look… I don’t know who’s backing you, but you’re undoubtedly an incredible talent for your age to be capable of beating two seasoned Elites. And my sworn man Exelos tells me he feels Agathor’s Blessing upon you,” the Count began. “But I cannot simply call out the honored ancestor of my House whenever I feel like it. Furthermore, you’ve barged in and given a beating to many loyal sworn soldiers of House Simarji… do you think you can just walk away without providing any compensation? Who’s your backer? Which House are you with? I don’t recognize you…”\par
What was left unsaid was that anyone who was capable of beating up Elites at Orodan’s age could only be a famous prodigy. Count Rohanus knew of all the people in the Republic and nearby under the age of 20 who had the battle power of an Elite. That he didn’t recognize Orodan was making him even more suspicious.\par
“I have no backer. I’m a Private in the Volarbury County Militia.”\par
“And Burgher Ignatius simply lets a talent like you walk around saying you’re a Private? What kind of game is this?” the man asked with mounting anger evident in his voice.\par
“It’s the truth, if you don’t believe me, what else can I say?” Orodan asked, his own battle-lust coming out.\par
Both parties were by this point spoiling for a fight.\par
Count Rohanus’s affairs had been interrupted when he was called to deal with this, and the indignation of having his loyal men thrashed was grating his nerves.\par
“You don’t need to say anything further,” the Count replied calmly all of a sudden, and Orodan’s fists clenched in preparation for a fight. “Since you were generous enough to allow my men off with a simple beating, I shall return the same to you. You’ll learn a harsh lesson today about the difference between an Elite and a Master.”\par
The rumors claimed Count Rohanus Simarji was a mere Elite-level healer.\par
But the man’s own words and the magically enhanced earth armor forming around his fists spoke a different story. As did the first crisp straight right jab that came for Orodan’s face.\par
All of Orodan’s skills were activated and he immediately reciprocated the violence. And soon an absolutely titanic clash of fists and kicks took place that began to crater the ground the two were fighting upon.\par
The Count’s two Elite-level guards hung back, likely at the request of the man himself. And because they wouldn’t be of much help against someone who could clash against a Master.\par
To his credit, while the Count’s eyes widened at the fact that Orodan could keep up in an exchange of blows evenly, the man quickly schooled his expression into one of utmost focus as the earth armor now covered his entire body.\par
The frenzied exchange carried on for fifteen more seconds, and some things became apparent.\par
The Count’s earth armor quickly deteriorated and lost all integrity and magical augmentation whenever it contacted Orodan. And the Count’s Physical Fitness was at the Adept-level and his Unarmed Combat Mastery wasn’t yet at the Master-level.\par
But the man’s healing was.\par
And this meant that the Count could take a beating.\par
For once Orodan had to wonder if he’d met someone as dogged about outlasting opponents in a fight as he was. Even if Orodan’s abilities and amplifiers gave him an advantage in a melee exchange, the Count was keeping up.\par
The Count couldn’t hurt him thanks to all of Orodan’s defensive skills, but despite the crazy amount of punches he’d landed, a glowing golden light simply enveloped the man and made the damage of the blows vanish. And Orodan didn’t want to use All-Strike and potentially kill the man, even if it would be weaker without the bottomless mana pool he had prior.\par
This was a Master-level healer.\par
But even still, Orodan was fighting someone who was primarily a mage. The outcome was lopsided in his favor.\par
A full minute of beatings ensued, and finally, the damage Orodan did began to outpace the Count’s ability to heal it in time, and with an ugly look on his face the Count finally leapt backwards.\par
“Are you really as young as you look?” the Count asked.\par
“I’m seventeen years of age, yes,” Orodan replied, although this was correct physically, but it would be a lie mentally and chronologically.\par
“…are you perhaps a reincarnator? The only other one I know of is serving as the Emperor’s advisor in Novarria, the oracles would have sensed it if another had emerged…”\par
“I am not a reincarnator, the only life I know is the one as Orodan Wainwright,” Orodan swiftly shut down.\par
The man’s eyes took on a contemplating gaze at his reply but finally came to a decision as he now ordered his two Elite-level guards forward. And they were both melee fighters.\par
It should have been a foregone conclusion. Orodan could now pulverize Elites like they were nothing.\par
But what should have been a foregone conclusion turned into five minutes of furious battle in which Orodan kept beating the two heavily armored swordsmen with his fists and the glowing golden light kept on healing them.\par
Turns out the Count’s ability to heal others was even stronger than his ability to heal himself. Additionally, Orodan would swear that the golden light was also making them stronger, as no other Elites he had fought were this good at melee.\par
Finally, it was a sense of experimentation with Mana Black Hole and utilizing his Action Increase that ended the fight.\par
Two Power Strikes were thrown simultaneously with each hand, and in the same moment in time, two more Power Strikes were launched as reality was twisted. The quadruple attack simultaneously focused on one of the fighters, and Orodan used the opening to swiftly rush towards the Count and wrapped both hands around the man’s head.\par
He sensed the man’s mana pool, and pulled.\par
The Count recoiled and his skin turned pale, and although it was painless, it was as though the exhaustion had suddenly set in, causing the man to fall to his knees. On Orodan’s end he felt the previously dry pool of Mana Black Hole suddenly become slightly more rejuvenated from draining a Master-level mage's entire mana pool.\par
The golden light surrounding the Count’s two guards vanished due to the lack of mana supplying it, and they suddenly drew their weapons and protectively stood in front of the man once they reached him.\par
“I have no quarrel with you… I just seek Adeltaj Simarji,” Orodan replied.\par
And behind him, Orodan heard a voice that was definitely not there before.\par
“Now who’s going around causing a ruckus and asking for an old man like me?”\par
Orodan turned around to see none other than the old man himself.\par


\section*{Chapter 9 - Harsh But Effective Training}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 9 - Harsh But Effective Training}%
\par
“Interesting, and so I actually told you my name and unfurled my weapon?”\par
“Yes! As unbelievable as it must sound, that’s exactly what happened!” Orodan exclaimed.\par
“Well that sounds like an utter bunch of hogwash… a sapling like you making me unfurl my weapon to deal with an attack of yours? A time loop? What nonsensical fiction comes from the the minds of the youth nowadays… tsk, tsk…”\par
A vein on Orodan’s head became prominent in anger as his face reddened.\par
“Old man! You were quite willing to talk to me last time! What games are you playing now?!”\par
“Such a loud and rude tone to take with your elders… for a man caught in a time loop shouldn’t you have better manners?” Adeltaj Simarji asked in that infuriatingly mocking tone of his.\par
“Considering you gave me a thrashing last time, who’s the one with poor manners?!”\par
“I don’t recall doing that, but it must have been a beating you undoubtedly asked for,” Adeltaj quipped back.\par
That was Orodan’s last straw, and he decided to draw his weapons and activate all his skills.\par
And in response Adeltaj Simarji simply brought his right hand wielding his cloth-covered weapon behind his back, refusing to use it, and his left came out in front of him as though inviting Orodan to come at him.\par
The old man had a smirk on his face.\par
And so it started.\par
Even with the full power of Death Rage, Weapon Aura and whatever else he could scrounge up, Orodan felt as though he was fighting a trained warrior and he was but an infant. Even the Action Increase, when used consecutively to make it as though there was two of Orodan and doubled his battle power, failed to make a difference.\par
“Multiplying zero by two is still zero you know?”\par
“Fuck you old man!”\par
“Rude… my turn. Allow me to give you the beating your parents never did,” Adeltaj said, as he began casually giving one of the worst beatings of his life to Orodan.\par
Orodan would have liked to be enraged at the comment about his parents, but the power of this old man was simply too overwhelming.\par
Although, his Action Increase did allow him to resist the beating better than he did the last time.\par
And finally Orodan had enough and decided he would throw all his chips into one basket.\par
The reserves held within Mana Black Hole weren’t anything compared to what he originally held from draining the orb, but it was still all he drained from a Master-level mage, and so it would have to suffice.\par
Action Increase allowed him to use it twice in the same instant while only costing the amount of energy of one.\par
But it was still an incredibly draining skill which took his vitality, physical stamina, mana and whatever strange energy came from his soul… and poured it all into a titanic attack.\par
And as all of Orodan Wainwright coalesced into his sword’s edge and the weapon tore through space towards Adeltaj Simarji, Orodan roared.\par
“I grew up an orphan!”\par
Count Rohanus Simarji, who was watching from the sidelines with an awed expression on his face, leapt away further to create more distance.\par
It wasn’t on the magnitude of the last time he had used it. But as he launched it now he realized that his skill level wasn’t high enough and his body wasn’t strong enough to channel all of the energy he tried pouring into All-Strike the last time.\par
Most of it had been wasted before.\par
Now as he threw it, he realized that the attack was still at least a quarter as powerful, and this was the safe level at which he could launch it without having his body obliterated.\par
The surrounding mile was turned to rubble, and at least ten more miles of the Aenechean Forest they had wisely decided to venture deep into… was flattened.\par
It wasn’t the kind of city-destroying attack he launched last time, but it also didn’t obliterate his own body.\par
And before him, Adeltaj Simarji unfurled his weapon, although he was holding it lazily with one hand.\par
“Hmm… well I suppose this does, if barely, meet the qualifications for an attack that could make me unfurl my weapon. But only because I don’t want to dirty my hand stopping it.”\par
“Do you believe me now?” Orodan asked, a challenging tone in his voice that implied he was ready to fight further to prove his point even if his body was utterly drained of all stamina and energy.\par
“Oh, that? I knew you were telling the truth right from the start, I have a skill that allows me to tell if the speaker believes what they’re saying.”\par
“What?! Then all of this…?!” Orodan angrily exclaimed as he did a double-take.\par
“How else am I supposed to ascertain your current level of power if you want me to teach you?” the old man asked. “The youth these days… such a coddled education you receive in the academies that the thought of a master evaluating a potential student’s worth is something outrageous.”\par
“I never went to an academy… I’m self-taught,” Orodan said in response.\par
“Well that explains why your work ethic is decent at least, the spoiled children in these fancy schools are handed everything on a silver platter,” Adeltaj lectured. “But… as spoiled as they are, it’s still a formal higher level education.”\par
“I know my education is lacking, and likely has quite some gaps. Everything I’ve learned has been through word of mouth, experience, and discovering it myself aside from the year of training the County Militia put me through,” Orodan began. “But… I’m confident I can bridge the gap and still prove myself a worthy student.”\par
“Boy… you at least know how to read and write?” the old man asked, and Orodan was almost offended in response.\par
“Of course! The matrons at the orphanage taught me that much, although nothing too complicated…”\par
“Hmm… well you’ll learn eventually, after all, you’re a mighty time looper aren’t you?” Adeltaj mockingly asked and Orodan bit down his indignation and didn’t rise to the bait for once.\par
“Does that mean you’ll teach me? That I’m your student?” Orodan asked, hope in his voice.\par
“Before I make a decision on that, here’s an Observer orb, put your hand on it. I need to know what I’m working with in concrete numbers,” Adeltaj demanded, and Orodan was hesitant to comply until the next words followed. “You’re hesitant? Worry not, this one doesn’t transmit anything anywhere.”\par
“My Status and skill levels are… something that have drawn undue attention in the past, from even Gods. Is this truly necessary?” Orodan still asked, almost cautioning the old man.\par
“Young man… I assure you, whatever incredible Status you think you have, I’ve likely seen better. I’m almost eight-hundred years old,” Adeltaj spoke. “The fact that you can fight Masters at your age and level, while incredible in the context of the current day and local political powers… isn’t world-shattering when evaluated across time and the world itself.”\par
“Suit yourself,” Orodan replied, and then placed his hand on the orb. He also switched his titles and allowed whatever came his way to transpire. Malzim had given him a safe way out of true trouble if it came to it.\par
Orodan called up his own Status as well as he willed the orb to display it.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Master Slayer}\par
\textbf{Title 2: One Who Has Experienced Death}\par
\textbf{Available Titles: One Who Has Experienced Death, Sword Adept, Shield Adept, Physical Adept, Unarmed Combat Adept, Master Slayer, Wrestling Apprentice, Cleaning Apprentice, Woodworking Apprentice}\par
\textbf{Rewards: Permanent +1 Action Increase}\par
\textbf{Skills: Sword Mastery 62 (Adept), Unyielding Vitality 60 (Adept - Rare), Pain Resistance 59 (Adept), Dying Struggle 59 (Adept - Uncommon), Shield Mastery 58 (Adept), Combat Mastery 57 (Adept), Dying Struggle 56 (Adept - Uncommon), Bleeding Control 56 (Adept), Physical Fitness 55 (Adept), Damage Mitigation 54 (Adept), Death Rage 53 (Adept - Exquisite), Unarmed Combat Mastery 51 (Adept), Power Strike 44 (Apprentice - Uncommon), Perfect Parry 42 (Apprentice - Uncommon), Wrestling 42 (Apprentice) Iron Body 41 (Apprentice - Exquisite), Mana Resistance 39 (Apprentice - Legendary), Tool Mastery 39 (Apprentice), Woodworking 37 (Apprentice), Impregnable Bladewall 36 (Apprentice - Exquisite), Weapon Aura 35 (Initiate - Rare), Evasiveness 34 (Apprentice - Uncommon), Cleaning 34 (Apprentice), Surprise Attack 32 (Apprentice), Wood Communion 31 (Apprentice - Legendary), Sprinting 30 (Apprentice), Laboring 27 (Initiate), Construction 21 (Initiate), Impact Resistance 21 (Initiate), Slashing Resistance 16 (Initiate - Rare), Club Mastery 15 (Initiate), Piercing Resistance 14 (Initiate - Rare), Lightning Resistance 14 (Initiate - Exquisite), Shield Throw 12 (Initiate - Uncommon), Lumberjacking 11 (Initiate), Parkour 11 (Initiate), Maintenance 8 (Initiate), Mana Black Hole 8 (Initiate - Legendary), Intimidation 7 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Deception 4 (Initiate), War Cry 3 (Initiate - Rare), All-Strike 2 (Initiate - Legendary), Soul Manipulation 1 (Initiate - Rare),}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor, Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark, Death’s Call - Whenever you will it, Death takes you]}\par
The display began displaying… and kept displaying. It was far longer than the average Status display.\par
And Adeltaj Simarji suddenly grew quiet.\par
He looked, and he looked. And he occasionally briefly gazed at Orodan, as though inspecting something, and then looked back to the display again.\par
Finally, he spoke.\par
“How many loops have you been through by now? A rough estimate?” the old man asked.\par
“Well… at least ten-thousand I think? I’m not too sure on the exact count, but at least that many.”\par
“And each loop, it lasts the whole day?”\par
“No. I choose to end the loops roughly nine hours after waking up, when the ancient war machine awakes and devastates the entire county,” Orodan explained, but then added. “But even that’s a recent thing for the last few hundred or so loops. Prior to that each loop lasted less than an hour on average as I immediately ran headfirst into my death till I succeeded in whatever I was attempting.”\par
“Ten-thousand… even if this was ten-thousand full days, your chronological age would now be in your forties. And given how quickly the loops end each time… not even thirty years of age yet…” Adeltaj muttered to himself, as his eyes took on a strange look.\par
Count Rohanus Simarji stood at the edge of the cratered dead zone from Orodan’s All-Strike. He dared not approach the meeting between his revered ancestor and this monstrous existence. Almost two whole minutes passed in utter silence after that as Adeltaj simply kept looking at the display and occasionally back at Orodan.\par
“I too have a Legendary skill, but Mana Resistance, this Legendary skill of yours… how did you acquire it?” the old man asked.\par
“I kept being burnt to ash by an Elite-pyromancer. My deaths were so instantaneous that I barely had time to focus on developing a skill to resist fire, so instead after dying hundreds of times I started to delve into what composed a magical attack itself, and tried to actively develop a way of resisting it with nothing but my own body.”\par
“Incredible… and Iron Body, how did you acquire that?” Adeltaj inquired.\par
“I died thousands of times trying to fight a Master-level necromancer’s undead Demonic Berserker toe to toe bloe for blow,” Orodan spoke, and the old man looked as impressed by that as he was last time given the near imperceptible widening of his eyes.\par
“Even I would not have risked such an impossible feat at your age… Demonic Berserkers are ferocious forces of wicked nature, and even if they’re weakened when reanimated as undead… being empowered by a Master-level necromancer, there should have been no way for one of your level to kill it, let alone doing it while trading blow for blow.”\par
“It was a particularly brutal set of loops… but an integral crucible which forged me anew and helped take me from struggling against Elites to being able to fight Masters,” Orodan added.\par
“Hmm… not bad. Now tell me about…”\par
And so on did the discussion go.\par
The venerable Adeltaj Simarji continued to question his skills, what they did, how he acquired them, his Blessings, and so forth. They discussed the time loop, and the political machinations and the game being played with the awakening of the ancient machine.\par
Turns out the machine was in fact a key capable of sundering the boundary between dimensions. The awakening of the machine was just the first part. The plan was for whichever faction that controlled it to use the machine to shatter the dimensional boundary at a safe location and create a permanent passage to the hells.\par
It would sound nefarious to anyone, and to Orodan’s uneducated upbringing it definitely did. But Adeltaj explained that the last great invasion of hell was over five-thousand years ago, and the Arch-devils had been slain and the hells had been utterly weakened since.\par
Furthermore, since that time the Cathedral and the priesthood engaged in the practice of regular demon summonings with the purpose of summoning and permanently slaying demons. Of course the demons caught on and stopped allowing themselves to be summoned to the world after a while, but this severely hampered their ability to gain power.\par
Additionally, the Cathedral would once every few years organize a crusade where a temporary breach in the dimensional barrier would be opened, and adventurers, powerful experts and members of the priesthood seeking battle experience would essentially launch a raid into the hells.\par
That the hells were filled with various treasures that could not be found anywhere else, was also a prime reason for the ‘crusades’, and likely a strong reason for wanting to open a permanent dimensional passage to them. Whichever nation had access to such a permanent passage… would undoubtedly gain great wealth and power. It was essentially the promise of being able to colonize the hells.\par
After at least half an hour of talking the old monster finally stopped.\par
“I do not know who has put you in this time loop that seemingly defies even the Gods themselves… but they have chosen well in the stone-headed and stubborn mule that is you,” Adeltaj remarked, and Orodan decided to take that as a compliment this time.\par
“So then… does that mean you’re willing to teach me?”\par
“Yes… I haven’t had a student in nearly five-hundred years, but I suppose for someone whose talent exceeds even the most monstrous Chosen One I’ve heard of… I would be remiss to pass up on this opportunity,” the elderly man replied. “But… from talking to you, it seems you have some serious gaps in your education. Much as I detest them, an academy, even a crafting one, might do you some good down the line in a later loop just so you can broaden your horizons and pretend to be civilized.”\par
Orodan found himself agreeing. Adeltaj spoke of many things regarding politics, kingdoms and skills that Orodan didn’t really know about. Such things were undoubtedly taught in theory classes in an academy, or imparted onto the children of wealthier families by their parents. Orodan was but a dumb brute however.Stolen from its original source, this story is not meant to be on Amazon; report any sightings.\par
“That being said, we will start your training now,” Adeltaj remarked, and Orodan got a bad feeling in his gut. “I never quite liked the academy way of coddling youths in a classroom and a controlled environment. Given how you’ve told me you acquired your high rarity skills, it only makes sense to push you this way.”\par
Adeltaj Simarji’s hand came up, and he took a stance. And Orodan knew he was in for a world of pain.\par
\par
The wisdom and knowledge of seven-hundred years of life must have amounted to something, for Adeltaj Simarji was a better teacher than his Militia trainers by a mile.\par
Orodan received severe beatings in which he was pressed in each and every combat skill he had to the utmost limit of their levels, but he never went to a level Orodan could not reach yet. And he constantly pressured Orodan into adapting, experimenting and improving his skill levels every time he used them.\par
And once Orodan was utterly bloodied and his body devastated, Adeltaj would force him to hone his crafting skills while near the brink of death. He would also impose additional ‘training challenges’ such as stomping on Orodan’s hands and turning them to a mangled mess, thereby forcing him to craft with his feet. Or he would punch Orodan’s eyes and cause them to swell, thereby making him craft while blind.\par
It was utterly horrendous, but it was good training.\par
So the day went. Thirty minutes spent taking a beating which put him near death, with two hours spent after recovering as his Unyielding Vitality allowed him to now heal and recover over that time.\par
Adeltaj was a very demanding teacher, but he never once left Orodan without explanations at critical junctions. He would only not fully explain something if he thought Orodan would be better served intuitively understanding it himself, and in those cases he would explicitly say so. Such as when Orodan wondered how to improve Unyielding Vitality further, and Adeltaj simply hinted that he was wasting time setting his own bones in place manually.\par
And incredulously, his skill levels showed growth; all in a single loop which he had only spent six hours in!\par
“Truly, you are a glutton for punishment. I had a hunch that this sort of training might be most effective for you,” the old man snarkily remarked. “But compared to being torn apart by a reanimated undead, is this not easier?”\par
In a sense it was, but it also wasn’t. Orodan received a break every time he died at the hands of the undead Demonic Berserker where he woke up in his bed again.\par
This constant hours long torture in one loop was genuinely exhausting. But it was rewarding.\par
“I suppose it is…” Orodan remarked. Which was apparently the wrong thing to say as Adeltaj felt that the intensity of the training could now be increased.\par
The recovery times were now halved, and Orodan was essentially forced to mentally pressure his body to regenerate mid-beating if he wanted to keep up.\par
The third cycle of this yielded a beautiful result.\par
\textbf{[New Skill (Exquisite) → Regeneration 1]}\par
And his wounds began to visibly heal at a far faster pace than simply Unyielding Vitality would allow. And the old man smiled eerily.\par
“There we are. Was that Regeneration? The accounts of how one would go about acquiring that skill always were spotty, but it’s good to know the old and reliable method of guided torture turned out to be true,” Adeltaj spoke, and Orodan nodded. “Now then, we can shorten the rest times even further.”\par
And even more beatings came his way.\par
Eventually however, the announcement played and Orodan’s eyes widened.\par
“Master! The ancient machine is about to awaken!”\par
“Yes? And? Does that mean your training is to stop? And here I thought you were the diligent sort… tsk, tsk.”\par
“But master… it’ll destroy the entire county and your whole house!” Orodan tried protesting, but all he received in response was a beating.\par
And then in the distance as he was thrashed he saw the ancient metallic beast awaken, and the jewel on its forehead glow red, and even Adeltaj Simarji stopped the beating he was delivering for a moment to simply unfurl his weapon.\par
The tidal wave of destructive red mana crossed the distance, and the old man simply spun.\par
It was impossible to keep track of how fast the man was spinning, but the very air around him, in the surrounding miles, began to spin with him.\par
And in the aftermath, the destructive wave of red mana that annihilated the rest of whatever it touched, seemed to avoid the town of Velestok and the surrounding miles altogether.\par
The old man was the eye of a storm, everything else outside of the range of the winds from his skill was utterly devastated by the red mana.\par
\textbf{[Quest Failed → Battle of Ogdenborough - Ogdenborough has been completely destroyed]}\par
Orodan didn’t have the time to care about such a Quest message right now.\par
“Haven’t used that one in a while… good to see it still works as intended.”\par
What even was this monstrous old man? Was this his teacher?\par
And it clicked in Orodan’s mind that he obviously couldn’t see the entirety of the County from wherever he was at the time of the destruction. And that certain places undoubtedly had their own preparations and countermeasures due to knowing about the awakening of the ancient machine ahead of time.\par
“If you’re this strong… why don’t you just destroy that machine?” Orodan incredulously asked.\par
“While I could trash that rusty old thing… it would upset the pampered children who want to use it to open a passage to the hells. And then they’d go crying to their masters, and I’d face an awkward meeting about why I violated the Grandmaster non-interference pact.”\par
Grandmaster.\par
Orodan didn’t think it was a real level one could reach.\par
Of course, stories and legends spoke about them. But in the fictional and metaphorical sense, as an ideal to aspire to. In practice, the average person could go their entire life not seeing even an Elite. To the common masses, Adepts were the most they would see, and even then from a distance most of the time.\par
Even the Republic’s official education system never confirmed the existence of Masters.\par
So for the existence of Grandmasters, the mythical status attained at level 100 of a skill?\par
Unfathomable.\par
“Grandmasters… are real?”\par
“I know your education was lacking in your formative years, but surely you can count past the number ninety?”\par
He could of course count past ninety, but Orodan couldn’t even muster the indignation at the insult. The revelation that Grandmasters were real and that his teacher was one who could also defend a wide area the size of an entire town against the county destroying attack of an ancient war machine, was quite shocking.\par
“I know that skill levels beyond ninety exist, but that’s still just the realm of Masters… but 100? Such a thing’s possible?” Orodan asked.\par
“Of course it’s possible, and not just in one skill. As aged and talented as I am, I’m merely a Grandmaster halberdier,” Adeltaj remarked, and Orodan would take issue with calling one’s self ‘merely’ a Grandmaster at anything. “And that’s almost all Grandmasters out there. But in my youth I met a dual-Grandmaster once, and she was a real terror.”\par
“Incredible… I feel like a frog at the bottom of a well, thinking the sky I saw till now was the world…” Orodan muttered.\par
“But that’s enough of that. It’s time to resume your training, you’ve been slacking a bit much… how the work ethic of the youth have fallen… tsk, tsk.”\par
And so Orodan’s battering resumed.\par
\par
It was an interesting experience, to see how the Republic reacted to what was essentially an entire county being destroyed. And in some ways the reaction was in line with what he expected. Silver-feathered griffin riders furiously fluttered about in the horizon, likely heading to and from towns that had managed to defend themselves via whatever countermeasures they had.\par
But what was surprising was the pair of actual dragon-riders that began doing flyovers throughout the area, maintaining a distance from the metallic war machine, but never turning away from it.\par
After another hour, the machine began to move, Mount Castarian was destroyed as it fully moved out of its resting grounds, and it began moving towards the Novarrian side of the mountain.\par
“You worry overly much my stubborn student,” Adeltaj Simarji spoke. “The Republic isn’t as unprepared for that machine as you think.”\par
“But… even if those dragon-riders were on standby in case it decided to try again… just how much of the county was destroyed? How many towns survived?”\par
“Perhaps a handful of important centers were protected and everywhere else with important assets were evacuated to these centers,” the old man spoke. “I reckon Trumbetton is fine for example.”\par
“But what about the common folk in the rest of the towns?” Orodan asked, a bitter feeling in his gut.\par
“What about them? Given your upbringing you should know how the world is boy, the strong are valued and the weak are expendable.”\par
“But… there were thousands upon thousands of people in the smaller towns. Maybe more than a million if put together… how can the Republic just allow the mass butchery of its citizens?” Orodan asked with heat in his voice.\par
“Well, they didn’t exactly allow it now did they? An attempt to salvage it was made, the attempt failed,” the old man answered bluntly.\par
In response, Orodan could say nothing. Technically, the Republic did send a response to Eversong Plaza, but they failed. And likely a million people had died.\par
He was no bleeding heart. Growing up, he had killed another boy over a piece of stale jerky. He was a warrior who had killed and been killed throughout the time loops.\par
That the majority of Volarbury County’s population had been devastated… was tragic, but nothing out of the ordinary in their world. The Adepts and above had been protected, as were critical population centers, and the pair of dragon-riders on standby were the insurance policy in case the machine piloted by the Novarrians tried pressing the matter.\par
The Republic had vied for control of the machine, and lost. If they had won, Orodan was sure they’d have done the same to the towns on the Novarrian side.\par
In time, the county’s population would recover, aided by magic and the assistance of the priesthood of the Cathedral. In the grand scheme of things, to Masters and above… the devastation of an entire county… really was but a blip in the hundreds of years that their lives could carry on for. It wasn’t even a particularly bad tragedy.\par
But Orodan still felt the embers of dissatisfaction at the outcome burn in his heart.\par
He resolved that he would one day start trashing that stupid machine in every single loop.\par
He owed Old Man Hannegan and that raggedy looking architect in Ogdenborough that much at least.\par
\par
It was an absolutely surreal experience to have the day pass and not be awoken by the harpies flying over Ogdenborough. But Orodan had, for the first time, survived the day.\par
His high skill levels meant he didn’t need to sleep any more, but seeing the moon rise and the sun come up again even as he kept receiving beatings signified a first for him.\par
Adeltaj kept pushing him, claiming that at his level he didn’t need to rest like a commoner thanks to his Physical Fitness and vitality skills. His skill levels were steadily rising throughout the course of the days of continuous, uninterrupted training.\par
After three days of continuous fighting at full power, Orodan began to feel exhausted.\par
On the fourth day of continuous battle he was at the complete bottom of all of his energy reserves. His soul was strained providing whatever fuel it could to his constant All-Strikes, his Mana Black Hole reserves were completely dry, and the stamina of his physical body was utterly spent as well.\par
He had always died before reaching such a point in the past loops. But this time he survived the day, and the ensuing four days of continuous combat without any rest whatsoever, had finally allowed him to experience what actual exhaustion felt like.\par
The ‘crafting’ breaks stopped once he acquired his Regeneration skill, and although it was capable of healing him scarily fast at its current level of 13, it was incredibly taxing on his stamina reserves. Healing a grievous wound via Regeneration was equivalent to the fatigue of launching an All-Strike at times.\par
As this went on Orodan genuinely felt as though he would black out from exertion.\par
The power his soul could provide was running on fumes, his mana was nil, and his stamina was spent. Every single shred of energy was nearly gone. Even his vitality was now dangerously low thanks to the constant beating, and he didn’t have enough stamina in his body to recover his life force via Regeneration and Unyielding Vitality any more.\par
“Feel like taking a break? I fear I might’ve pushed you too hard there,” Adeltaj said in a most infuriatingly smug tone. “Come, let’s get to crafting, the progress is good enough for this session.”\par
But Orodan refused to stop.\par
So what if all of his energy reserves were running dangerously low. He could legitimately kill himself with overexertion at this point.\par
But since when did Orodan fear death?\par
He responded to the old man by launching another All-Strike, one that he squeezed a desperate amount of energy out of his soul for.\par
He was so close to understanding something.\par
From all this fighting he came to understand that the soul was the basis of all energy production. It produced both its own unique source of power, he called this soul energy, and it could also produce a faint amount of mana, undoubtedly where mages got their mana pools from.\par
The soul also produced vitality which flooded the body in the form of his skills, but this drained his stamina reserves whenever he Regenerated.\par
And finally, Orodan felt that as his reserves of everything were completely empty, he realized the very beginning of it all was his soul. And it could also produce stamina if he truly squeezed with his willpower.\par
He felt that if he went down this path he could obtain a skill which allowed him to recover stamina… but merely this wasn’t what he wanted! He knew there was something more grand tying it all together.\par
And so he strained, and he struggled, and as his vision nearly blacked out and even Adeltaj looked almost concerned and was about to order him to stop, he understood it.\par
The soul produced soul energy. This soul energy was naturally converted to mana, the mana could be converted to stamina, and the stamina could be converted to vitality. The soul energy then was the original energy that was converted to and fueled all of his energy sources.\par
So what he really needed was soul energy.\par
And the driving force of his soul, of the production rate of the soul energy itself… was his own willpower and concentration. And if he willed it, it could produce even more soul energy, but at the cost of making his soul feel as though it was exploding.\par
But who was Orodan? Orodan had the sort of willpower that would make him stand tall in the face of thousands of deaths and eternal torture.\par
And so he finally brought it all together.\par
And he ignited his soul. Forcing it to burn faster and faster, even as the very bounds of his soul strained and wanted to falter.\par
He felt his soul tremble dangerously and an all-consuming pain overtook him, but he clamped his infinite willpower down on it and forced it to endure, and another part of him, drove the rest of his willpower to churn and spin his soul faster and faster, to produce more and more power at an increasing rate.\par
Anybody else would have been driven insane and would have lost their personality as their soul went out of control and caused their body to explode in a deluge of energy.\par
But Orodan was not anyone else.\par
His willpower was infinite. He would demand his soul withstand the pressure it was under, while also pumping the soul energy production of it to unprecedented levels.\par
And this increased soul energy came like an eternal reactor, and it fueled all of his other energy pools.\par
\textbf{[New Skill (Mythical) → Eternal Soul Reactor 1]}\par
\textbf{[Title Gained → Wielder Of A Mythical Skill]}\par
Everything seemed far brighter, but in reality Orodan’s eyes were glowing white, and soul energy leaked out of his pores.\par
“Wait… stop! You’ll cause serious damage to your soul even if you wake up back in time!” Adeltaj exclaimed, in a rare show of utter seriousness for once.\par
Certain last ditch attacks involved igniting one's soul to cause a terrifying suicide explosion. What he was doing was the equivalent of someone setting their soul aflame to kill themselves, but Orodan’s incredible willpower clamped down on the boundaries of his soul and prevented it from exploding.\par
This was akin to a boiling pot of sealed water, and as the water boiled hotter and hotter the walls of the pot couldn’t take it anymore. Except Orodan was using his own titanic willpower to continuously strengthen the container that was his soul as the process escalated.\par
And the next All-Strike that Orodan launched, carried the fuel of almost a tenth of a full Mana Black Hole empowered strike. A dramatic step up in power output from the pitiful All-Strike he launched before.\par
His wounds began healing as Regeneration was empowered by his new inexplicable well of energy.\par
Suddenly, he was smashed into the ground by an incredibly strong blow, far stronger than he’d ever received before from the old man.\par
Yet Orodan still got up.\par
“Sorry about this boy… but if you really are in a time loop, then I do this for your own good…” Adeltaj Simarji remarked, as his halberd unfurled.\par
And soon, a second strike blasted Orodan straight into the ground and he lost all sense in his body. His organs, limbs, head, all utterly obliterated.\par
Calling him a glowing white pile of flesh on the ground wouldn’t be inaccurate.\par
But…\par
…he still kept Regenerating.\par
Where the energy came from he didn’t know. All he knew was that his soul felt as though it would utterly explode if he let his willpower slip even the slightest. If his utter concentration flagged even a bit, he would die and cause horrendous lasting damage to his own soul.\par
But his bottomless willpower did not allow it.\par
And as multiple seconds passed, even Adeltaj Simarji stopped his motions for a second attack which would have turned the pile of meat that was Orodan into complete ash and base particles.\par
“How… is your soul not exploded yet?” the old man asked incredulously as Orodan slowly reformed before his eyes. His Regeneration and Unyielding Vitality skills weren’t normally anywhere near this strong, but when powered by an inexplicably bottomless source of energy… even low level skills could become frightening. “…you set your soul alight didn’t you? Right?”\par
Orodan finally reformed enough to reply. His body was in ruins, and whatever he was Regenerating was actively being broken down by the sheer amount of soul energy coursing through him, but he spoke.\par
“No old man… this… is a new skill,” he spoke even as the white light of his soul spilled forth from every opening he had and caused damage on his body that was furiously healed by Regeneration and yet re-damaged again.\par
“Well put a stop to it this instant or I’ll be forced to actually kill you! I can sense the rate of soul energy generation from you is increasing by the second… if you don’t stop, you’ll kill yourself. Your body isn’t strong enough to house so much energy at your level,” the old Grandmaster spoke furiously. He almost seemed concerned.\par
Orodan felt as though the momentum was too high currently, he really was going to have a hard time stopping this new skill of his.\par
So he began converting the soul energy to something that he could house safely within himself.\par
He began converting the soul energy into mana.\par
The process was slower than he would like, but even the slow conversion of this much soul energy into mana, dramatically eased the pressure on his body. He began siphoning the mana into his Mana Black Hole skill, and it hungrily began absorbing it.\par
And it devoured and devoured, till Mana Black Hole was filled thirty percent of the way to full and the skill even gained a level. Finally, the rampant soul energy running through him subsided.\par
And Orodan’s new Mythical skill began winding down as the lack of escalating damage to his own body allowed him to focus on dialing back the insanely increased soul power generation of his soul.\par
As his new skill simmered down, Orodan reflected on the fact that a single use of it was enough to fill Mana Black Hole to thirty percent of its prior reserves. And thirty percent of that previous amount meant that he had generated mana comparable to a third of what the ancient war machine released.\par
That was… inconceivable.\par
“Kid!” the halberd wielding sage exclaimed. “What the hell was that? What rarity is that skill?”\par
Orodan himself hesitated for a moment as the unknown rarity was one he’d never heard of before.\par
“I don’t know, it says Mythical.”\par
The clearing went silent after that.\par
Adeltaj Simarji’s face… it became unusually stoic.\par
“You… you should probably call upon the Blessing Malzim gave you… if you really are in a time loop, this is your only way out now,” the old man solemnly said.\par
Orodan came to learn why, a few seconds after.\par
The sky began blazing gold, and in the sky a comet appeared to be streaking… right towards them.\par
Before a second passed, it reached their position, like a mighty bolt of celestial light.\par
And upon the dust and light clearing, Orodan’s blood ran cold at the sight of Lady Lakshiya, her eyes burning gold, her skin cracked and her body far more damaged than it was last time. This was a host that wasn’t expected to survive becoming an Avatar.\par
But it wasn’t her anymore. It was an Avatar of Ilyatana.\par
\textbf{“I sensed the threads of fate rippling all over the world… and they originate from here. How fortunate that a Favored of mine was so close… tell me, who here acquired a Mythical skill?”}\par
“Whatever way out you have… use it now boy… even Grandmasters are swatted away like pests before the might of an Avatar, especially one whose host isn’t going to be living.”\par
Given his last experience with this dangerous and manipulative Goddess, Orodan wisely heeded the advice and called upon the Blessing of Malzim.\par
\par
A keening wail ringing in the night sky awoke him, and Orodan immediately got to his feet.\par
What even was a Mythical rarity skill that caused the Avatar of a Goddess to descend upon him? The stronger he got... the more problems and complications that came with it. Frankly, he wouldn't be surprised if at some point his very awakening at the start of a loop began to trigger alarms or cause certain parties to seek him out.\par
That being said, it wasn't a bad result at all.\par
For as much as the training with Adeltaj Simarji had been harsh, it had also been effective.\par
And he was eager to repeat the tutelage and see just how much of his potential he could unveil by repeatedly grinding out some training with the man.\par
That annoying old man still had more to teach him.\par


\section*{Chapter 10 - Soul Training With An Avatar\u0027s Assistance}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 10 - Soul Training With An Avatar\u0027s Assistance}%
\par
Given his bad experience, Orodan made it an active habit to stay away from temples and the priesthood. But what was one to do when the priesthood came to him?\par
His loop to seek his teacher the Grandmaster Adeltaj went as normal… right until he began noticing some minor differences as he entered Velestok to make way for the House Simarji lumber yard.\par
Said ‘minor differences’ being the diviners from the Cathedral of Karilsgard patrolling the streets in pairs of two, on the lookout for something.\par
Given that this hadn’t happened in prior loops, Orodan had a weird feeling that it was related to the fact that he’d obtained a Mythical skill and had an actual Avatar of Ilyatana descend to speak to him.\par
Fate and the threads of it were a weird thing which Orodan had only ever heard of in passing, but despite the fact that he didn’t understand what they were he knew that the priesthood of Ilyatana, Goddess of Fate, were capable of using these threads to discern the possible future of people… and they could also be used to track someone.\par
For now though, it seemed the diviners weren’t able to pinpoint him and they weren’t gravitating towards him either. So he decided to make way for the lumber yard.\par
Approximately a minute later as he called for Adeltaj Simarji and gave the Adept-level guards a relatively gentle few smacks when they tried to kick him out, he realized the problem.\par
The moment he interacted with someone, the diviners seemed to know exactly where he was and would follow.\par
Instead of the Elite-level responders of House Simarji… the first four to respond this time were white robed diviners of the Cathedral.\par
“Ah, I believe we’ve found our mysterious man who can cause such powerful ripples in the tapestry of fate,” the leading woman spoke, and Orodan surmised she was at least Elite-level. “Young man, might we have a moment of your time? The Goddess Ilyatana wishes to speak to you. Your fate and influence on the world is… profound!”\par
“But unfortunately, I do not wish to speak to her, so it appears we are at an impasse,” Orodan replied as his hand went to his weapon, causing the woman to frown.\par
“I see… do you plan to attack us here and spill blood? Are you perhaps a heretic or an enemy of our Goddess?” the woman asked as her hands began to glow with a soft light as well. Behind her, the three other white robed diviners prepared for a fight as well, two of them wearing armor underneath their robes.\par
Orodan recalled just what Ilyatana had tried to do to him, and he made his decision. Training with Adeltaj Simarji would have to be set aside for a while, he would have to direct his loops in bashing his head against a new wall that stood before him first.\par
“A heretic? Maybe. But an enemy of your Goddess?” Orodan asked, and then he moved.\par
The leading diviner’s head flew.\par
“Definitely!”\par
Ilyatana could go fuck herself.\par
\par
Approximately three more slain groups of Elite-level priests later, they stopped arriving, and now Orodan stood before a pair of two Master-level individuals who were accompanied by thirty other people, a mixture of priests of Ilyatana and nearby Elite-level experts from noble houses that owed the Goddess a favor.\par
He had ordered the bruised Adept-level guards of the lumber yard to evacuate everyone ahead of time. He had that much respect for the lumber yard and House Simarji at least.\par
They had arrived five minutes after he killed the last group of diviners. Of course, given that Orodan hadn’t bothered to leave and simply remained in the exact same position he had butchered the diviners of Ilyatana in… it wasn’t difficult to find him and arrive in force.\par
“Heretic, enemy of the Goddess, you’ve slaughtered faithful diviners of the Cathedral and offended our most holy… answer me, why have you done this?” the leading Master, an ancient looking woman, asked Orodan.\par
This was one of the Cathedral’s Master-level people. What her name and rank within the Cathedral were, Orodan didn’t know. But she definitely wasn’t a regular priestess, given her ornate robes and the way the Elites behind her hung on her every word.\par
“Ilyatana is my enemy, that is all. My conflict is not with the Cathedral as a whole, but simply with the Goddess of Fate and her followers,” Orodan spoke and his weapons had been drawn and dripping with blood this entire time. “Shall we get on with it?”\par
“Vile traitor… have you been seduced by the evil Gods of Guzuhar? One of our people sensed Agathor’s Blessing on you… was it not enough? Come to wreak destruction on our lands in the name of your foul northern masters?” the old woman asked with a disgusted tone. “It matters not, we shall cleanse you in the name of the Prime Five.”\par
The old woman’s staff was drawn and brilliant light magic erupted forth from it, and the other Master, a warrior, drew his greatsword which burned with a near-blinding golden fire.\par
These people weren’t stupid. If someone was sought after by their Goddess for causing ripples in the threads of fate, and then this person slaughtered three groups of Ilyatana’s diviners, they were looking for a fight. And with that assumption the two Masters didn’t immediately commit to an all-out attack but were instead cautious as they probed Orodan with testing strikes.\par
The greatsword-Master stood beside the Master light mage and chose not to charge Orodan.\par
A wise decision, as the luminous beams of light that could shatter entire city blocks leveled the lumber yard… but left Orodan completely unscathed. His Mana Resistance was far too strong for him to be effected by mages at the Master-level. It simply fed the reserves of Mana Black Hole.\par
And in response, Orodan charged right through the furious beams as though they were a mere illusory light show, something that caused the eyes of the Master-mage to widen in panic. But the greatsword-Master intercepted him before he could kill her.\par
Unfortunately for her, she died anyways as an absolutely savage melee exchange began between Orodan and the greatsword-Master. Wind blades created by the raw pressure of Orodan’s Death Rage empowered sword strikes ripped her to bits, even if the blows themselves never reached her.\par
The man was immediately forced to go all out right from the get-go and failed to protect his colleague and the thirty Elites behind her from the sheer collateral death zone of a melee exchange between two people fighting at the Master-level. The surrounding hundred metres were devastated.\par
“You fucker! That was my wife!” the man roared as his frenzy grew and he fully committed to a fight to the death.\par
“Maybe you should have had her stand farther back then,” Orodan replied as he met the man’s furious blows. Seriously, who allowed a mage within even a hundred metres of a warrior?\par
The man was stronger than Ovuru, but not by much. But what would have once been an impossible struggle just to survive… now became an even battle as Orodan was fighting a melee specialist at the Master-level for the first time without getting killed.\par
Hundreds of attacks were exchanged in the span of a half-second, and the man’s Blessing must have been strong for he possessed a powerful ability to heal from any damage he took even as Orodan hacked and rended his flesh with his Weapon Aura empowered sword.\par
But seconds dragged on, and the seconds turned to minutes, and slowly but surely Orodan’s damage began to overwhelm the man’s healing. And finally, as the man realized he might die, he came to his senses and lost his suicidal mentality.\par
Nobody got to the Master-level by being reckless and overly emotional.\par
He attempted to disengage and flee.\par
Unfortunately for him… Orodan’s second Blessing from Agathor prevented any of his opponents from fleeing or evading his attacks. His opponents would face him as a warrior and win, or they would die.\par
A ferocious All-Strike was thrown, doubled by the Action Increase, and the man’s entire body was disintegrated as the surrounding mile of landscape faced utter destruction. The last look on the greatsword-Master’s face being one of confusion as to why he couldn’t flee.\par
As he stood upon the cratered ground, Orodan paused a moment to reflect on just how effective the training with Adeltaj and his crafting had been. Weapon Aura allowed him to actually use his sword throughout higher level fights, which was a fantastic amplifier as his Sword Mastery was higher than his Unarmed Combat Mastery.\par
Additionally, many of his active combat skills had crossed the Adept-threshold, alongside his Physical Fitness. Finally, Death Rage was a powerful multiplier as always. And All-Strike… it was just too strong, as expected of a Legendary rarity skill which poured all his energy pools into a singular attack.\par
Combined together, all his skills allowed him to hit far above his weight class, which was at the Adept-level but nearing Elite. He could essentially jump two tiers to fight now, which was stupendous. And he hadn’t even factored in his Mythical skill, which he hadn’t used throughout the fight.\par
With the greatsword-Master’s death the clearing fell silent, and Orodan heard the familiar footsteps of an old man approaching.\par
“Quite the destructive play session you’ve engaged in young man…”\par
Count Rohanus wasn’t flying in on his silvered-griffin to respond to the devastation of his lumber yard this time. Perhaps the killing of two Masters had made the man wary?\par
“Grandmaster Adeltaj Simarji, I’ve been seeking you,” Orodan greeted. “I seek your tutelage, but I fear we don’t have much time as the Avatar of a Goddess might be descending upon me as we speak.”\par
Well, depending on how much the Goddess suspected Orodan. Last loop she somehow knew when a Mythical skill was acquired by him, but this loop it wasn’t quite the same.\par
“You come in, beat up the guards, and then trash my descendant’s lumber yard with your scuffle against the priesthood… at least you had the decency to evacuate the people inside… but is this how you approach everyone young man?” Adeltaj asked in that annoyingly sarcastic tone of his. But Orodan could admit his sense of diplomacy and manners was… lacking, to say the least.\par
“Yes, yes, I apologize old man, I didn’t mean to wreck the lumber yard, but I need to ask you some questions before judgement descends upon me,” Orodan quickly directed.\par
“If you decided to destroy this nice lumber yard and a mile of forest preserve while killing dozens of Cathedral mutts just to ask me a question… then it must be quite the question,” the old man assented.\par
“First of all, how can a mortal defeat an Avatar of a Goddess?”\par
“…you really decided to start with such a ridiculous question right out the gate?” the old man mocked, but he continued. “It’s impossible… or at least from what I know anyways. Even Grandmasters are but children before the might of an Avatar, especially if the God possessing it doesn’t care about the life of the host.”\par
“But there has to be a way right? Aren’t Gods just beings that managed to ascend through the System?” Orodan asked, and the old man had an amused smile on his face in response.\par
“Now where did you hear that sort of heretical nonsense?” Adeltaj mockingly asked. “Why I’ve heard heretics say the most sacrilegious things… including what you speak of.”\par
“Then… what direction would one start focusing their training, if one wished to defeat an Avatar? When I was restrained by one before… it was as though the magical bindings weren’t made of mana.”\par
“You’re correct, Avatars don’t use mana, they use something else, and that’s the reason why the host is in such poor shape after,” Adeltaj spoke. “Avatars, and Gods themselves, use divine energy to empower whatever they do.”\par
“And what’s this… divine energy? Can it be resisted?”\par
“I don’t know what divine energy is, nobody I know does… the only thing I can think of that’s vaguely similar but still weaker is the energy produced when a soul ignites when some mad soul mage or necromancer tries a suicide attack,” Adeltaj spoke. “As for resisting it? I’ve never heard of a skill which allows one to do that, it would be patently impossible to begin with, and that’s before you somehow found a source of divine energy to train yourself against.”\par
Orodan ignored the old man’s comments about the impossibility of training a resistance. Adeltaj didn’t know about the time loops here.\par
“So soul energy like this then?”\par
And Orodan activated his Mythical skill, and white soul energy began to leak out from his eyes and pores.\par
“You’ll kill yourself if you do that… just what I needed… a suicidal lout on my doorstep…” Adeltaj muttered to himself. “Such talent too…”\par
But the seconds turned to a minute, and Orodan’s soul distinctly did not explode. And Adeltaj’s eyes widened.\par
“Young man… is that a skill? What rarity is that?” he asked quite seriously.\par
“Mythical. I’ve never heard of the rarity before, but that’s what it says.”\par
Adeltaj grew silent for a few moments and then spoke.\par
“Listen… if you didn’t have an Avatar descending down upon you before… you certainly will now… Mythical skills shake the very threads of fate of the world itself, and their activation is like a beacon for those who can read such things,” Adeltaj spoke, almost in resignation. Orodan could see the slight hint of regret in his eyes at having to tell such a talented person that they would be facing judgement at an Avatar’s hands soon. “I’ve only ever heard of one Mythical skill in my hundreds of years of life, and the man left and was never seen again.”\par
“I see… then my last question… for I sense I don’t have much longer left. How do I improve my soul energy to be strong enough in quality that it can match divine energy?”\par
“The only method I know of… would be to squeeze and compress soul energy till it essentially… becomes denser… but that would be incredibly dangerous and could possibly ignite your soul and kill you.”\par
Orodan mentally made note of everything his teacher had told him, but unfortunately their conversation was cut short by the sky blazing gold and an incredibly luminous comet descending towards them.\par
So it was the activation of the Mythical skill itself that made Ilyatana possess Lady Lakshiya and descend upon him?\par
The Avatar landed upon the cratered ground and the familiar ruined body of Lady Lakshiya glowed a frightening gold color as the divine energy wracked her body and wreaked havoc upon it.\par
\textbf{“Heretic! You kill my faithful and declare yourself an enemy of the divine, and now you dare flaunt a Mythical skill? Which foul dark power has sent you?”}\par
“None, you invaded my mind and tried molding my personality and so I consider you my enemy,” Orodan spoke, and while the face of the host didn’t change, the Avatar glowed brighter with furious power.\par
\textbf{“I do not recall anything of the sort vermin. You dare attempt to stand against the Gods? You’ll make a fine experiment as I dissect you.”}\par
Orodan did not like the sound of that, at all. And he was tempted, so very tempted, to call upon the Blessing of Malzim and escape.The narrative has been illicitly obtained; should you discover it on Amazon, report the violation.\par
But he did not, not yet.\par
He couldn’t even fight a Grandmaster yet; an Avatar would eradicate him like dust in the wind.\par
But he couldn’t advance unless he did this.\par
A part of him, the logical part which had listened to the lectures of Adeltaj Simarji, thought it would be wiser to slowly grow his power, learn, travel the world, unveil secrets and discover hidden techniques which allowed him to better hide from the Goddess of Fate until he was ready to take on an Avatar, and even then in underhanded ways which maybe cut the link between host and Goddess.\par
But that logical part was not Orodan. Where anyone else would have quailed at the thought of what he was about to attempt, not him.\par
He was confident in his infinite willpower and his ability to retain enough of himself to use Malzim’s Blessing before his mind was overtaken.\par
“Dissect me? How about you go ahead and try? Show me what some useless Avatar can do,” Orodan boldly challenged, and his own Mythical skill began flaring at extremely high rates. It was utter sacrilege to speak to a Goddess in such a way… but Orodan had died too many times to too many foes to care about adding one more to the list.\par
\textbf{“You will come to regret that mortal…”}\par
And as the words boomed, a set of glowing gold restraints wrapped around his limbs.\par
Orodan now knew that these restraints weren’t magical, powered by mana. These were instead powered by divine energy, and thus his Mana Resistance didn’t help him.\par
But the utterly rampant soul energy coursing turbulently through his body did.\par
Even though this was the very first time trying it and Eternal Soul Reactor was only at level 4… it still made a massive difference as the soul energy of his body began resisting the divine energy restraints, even if it was by the slightest bit.\par
Additionally, the usual downside of his body being destroyed as the speed of his soul power generation ramped up, was being counteracted by the divine healing energies of Ilyatana that sought to keep him alive for study.\par
Orodan found himself screaming through clenched teeth in pain as he ignited his soul even hotter, to an extent that he never had last loop. His body was suffering damage that should have killed him by now if not for a Goddess healing him, and his Mythical skill began to pick up in levels.\par
He chose not to convert the soul energy to mana and feed it into his Mana Black Hole, but if he did he instinctually felt that it might be even greater than the mana contained in the orb at Mount Castarian.\par
The pain was utterly all-consuming, greater than any physical pain he had ever felt before. To the point that Pain Resistance began to level up as time went on.\par
This was far faster at killing him than Death Rage was, to the point that even the Avatar was now struggling to heal him adequately, and the divine energy restraints were beginning to actually… struggle?\par
\textbf{“Filthy thing… such a disgusting Mythical skill, to torture yourself in such a horrific way for the sake of power… congratulations are in order, it seems your frantic cockroach-like struggles have made it unfeasible for me to dissect you without channeling enough of my power to destroy the body of my Favored entirely.”}\par
Orodan would liked to have replied, but he was in far too much blinding pain to care, and even the slightest lapse in concentration now would truly damn him. Eternal Soul Reactor had now reached level 11 and it now produced a total amount of soul energy each second, that if converted to mana, would be more than the entire mana pool of the ancient machine under the mountain.\par
This amount of power was generated by his soul each second.\par
There was no way he could ever reach this level of power generation without a Goddess healing him. Orodan’s body should have been utterly disintegrated a million times over already, and even the healing Ilyatana was capable of through her Avatar was starting to show its limits.\par
\textbf{“Lakshiya has served me well, even in death her final act of service will be ensuring a cockroach like you is permanently slain. Whichever dark God sent you will not be able to salvage your soul from this.”}\par
And despite the pain he was undergoing, Orodan’s mind snapped to attention at the Goddess’s words as he saw a strange and dangerous looking spear of divine energy materialize in the hands of the Avatar.\par
Permanently slain? Even if he went back in time, Orodan did not want to risk that kind of damage just yet.\par
And so with a titanic act of willpower he maintained his focus and willpower on his Mythical skill while also calling upon the Blessing of Malzim.\par
\par
A keening wail ringing in the night sky awoke him.\par
His entire world was pain.\par
For a split second, he saw the walls of his hovel in Ogdenborough.\par
And then it exploded in a deluge of white light, his own soul energy running rampant.\par
And now that an Avatar of Ilyatana wasn’t healing him, he died to the soul energy being generated by his own soul a few seconds after.\par
A keening wail ringing in the night sky awoke him.\par
And he maintained iron focus and began desperately attempting to convert all the soul energy into mana to feed into Mana Black Hole.\par
His hovel exploded and he died seconds after once more.\par
A keening wail ringing in the night sky awoke him.\par
And this time he began furiously shoveling all the mana he desperately converted into his Mana Black Hole.\par
At least a hundred deaths occurred before he finally brought things under control.\par
His Soul Manipulation had made a huge leap to level 46. The constant and furious use of a skill that involved his soul as well as rapidly converting that much soul energy to mana, had done wonders for it.\par
His Mana Black Hole was… at level 64 from the absolutely titanic amount of energy he had furiously kept shoving into its reserve. He had at least hundreds of ancient war machines’ worth of mana pools inside the skill now.\par
Which should have been a humbling thought, knowing that he held so much utter power within him, even if he couldn’t use it all at once effectively yet.\par
But right now, Orodan could only let out a trembling and shaky breath of relief.\par
The experience of igniting his own soul for so long… was truly horrifying.\par
Pain Resistance had leveled to near Elite, and he felt as though he could finally breathe, for even a single iota of concentration lost and willpower surrendered… would have meant his death. And not just a typical death in a time loop, but genuine soul damage if not worse.\par
Terrifying. True death could genuinely be his fate if he pushed it.\par
But who was Orodan? The man who fearlessly decided to die fighting in his very first life, even before the time loops.\par
So what if training this Mythical skill was so utterly dangerous?\par
His willpower would not falter.\par
He got to his feet and stepped out of his hovel.\par
In the distance the night sky blazed gold as the Avatar of Ilyatana made way for him as he’d activated his Mythical skill inside his hovel this loop as well.\par
He welcomed it, as it was more training opportunities for him.\par
He decided, starting every single loop by attracting the attention of that wicked Goddess was going to be his new goal until he progressed sufficiently in his Mythical skill.\par
\par
“You’re a wicked Goddess that meddles in the lives of mortals and fears them rising above their station.”\par
\textbf{“Blaspheming mortal, I approach you to offer you salvation and a chance to ascend and become a true champion of mine and you dare utter such words?”}\par
And so the loops went.\par
Orodan was starting to get tired of the cold, emotionless and corpse-like face of Lady Lakshiya when she was possessed by Ilyatana the Goddess of Fate.\par
The woman might have been a more pleasant person normally, but Orodan could now only associate her face with the arrogant and booming voice of the Goddess who possessed her.\par
Progress was… surprisingly quick, as by the tenth loop Orodan could genuinely repel the Avatar’s divine bindings which attempted to restrain him. Which caused the host to crackle dangerously with divine energy and begin launching soul damaging spears which Orodan dared not take head on yet, and so he reset by that point.\par
Frankly, Orodan was nowhere near actually fighting an Avatar, or even surviving one. They could flatten him in combat with even their weakest attacks, and it was only by abusing the time loop and the fact that Ilyatana was more intent on studying him and restraining him that he’d made progress at all.\par
And the progress he’d made was mainly in frustrating her and being able to at least avoid being captured by an Avatar.\par
But progress he did. And by the fiftieth loop of this madness he reached a point where the Avatar, upon seeing him and how much soul energy he was emitting, simply decided to immediately send a lethal soul spear his way which forced him to reset before it hit.\par
Throughout the loops Orodan also tried condensing his soul energy like Adeltaj had suggested, and after a while he got a new skill as a result.\par
\textbf{[New Skill (Legendary) → Soul Strengthening 1]}\par
This skill, it was exactly what he was looking for. Something to help improve not merely the quantity of soul energy he produced, but the very quality of it. And perhaps with enough time… he could even rival divine energy in its quality.\par
With this skill acquired, his goal with the current set of loops was done.\par
Satisfying as it would be to continue running into the wall that was the Avatar, Orodan wasn’t even sure how to go about fighting it yet. And he ran the risk of taking a hit from the lethal soul spears.\par
And Orodan simply wasn’t interested in ‘defeating’ the Avatar via trickery or esoteric magic. He would only accept a victory earned through the might of his own arm and soul.\par
Rather, first he needed to seek out proper tutelage and learn certain skills which would allow him to safely take attacks such as the soul-damaging spear the Avatar threw at him. Furthermore, learning how to obscure or defeat the strange fate-reading based divinations that the diviners of the Cathedral were using to locate him would be of utmost importance as well. If he wanted to engage in the loops without the new headache his Mythical skill brought him, this was the first thing he had to do.\par
So Orodan decided to bother Adeltaj again.\par
\par
“How to hide from the detection of the Cathedral’s diviners? What sort of maliciousness have you gotten up to boy?” Adeltaj asked.\par
In this loop, Orodan had already killed the Cathedral forces sent against him, but he hadn’t yet activated his Mythical skill, and pleasantly enough it gave him way more time to question and talk to Adeltaj as the Avatar didn’t descend upon him.\par
“Yes… how do these priests immediately seem to know where I am the moment I talk to someone?” Orodan asked in return.\par
“Well, firstly, divination, particularly the type of divination used by the diviners of the Cathedral of the Prime Five, uses fate-reading as a way to find people,” Adeltaj explained. “Naturally this means any actions which impact other people, will affect the threads of fate and the changes can be seen across the entire tapestry if the person is significant enough… for you to catch their attention the moment you talk to anyone at all… you must be more powerful than you look.”\par
“I see… but how can one avoid this manner of fate reading? How can I prevent the impact of my actions from rippling throughout this ‘tapestry’ of fate? I just want to go about my business without having the hounds of the Cathedral come after me.”\par
“It’s a really shady set of skills you’re seeking,” Adeltaj remarked with a raised eyebrow. “But it’s not something ever taught in the Republic. The Republic and the Empire follow the same tradition of worshiping the Prime Five. Most of Inuan besides the dwarves and elven enclaves do. So as you’d expect, the Cathedral actively stamps out any such skill set.”\par
“But surely, some group, somewhere would know of a skill to obscure the ability to be tracked through the threads of fate?” Orodan asked, his frustration becoming apparent. “What do I have to scour the ends of the north to find such a secret?”\par
Adeltaj had a strange smile on his face at Orodan’s words.\par
“Surely… you don’t actually mean to say my best option is to go north and try to learn it from the foul Northmen scum?!” Orodan exclaimed.\par
“You’re the one who said it, not me,” the old man quipped back. “Where else can you think of that’s outside of the influence of the Prime Five, has its own pantheon of Gods and actively works against the Gods of Inuan?”\par
It… made perfect sense. Orodan just didn’t want to entertain the thought.\par
He hated Guzuharans. And by extension he hated Guzuhar, the savage northern continent from whence the raiders came and killed his parents one fateful day, leaving him orphaned early on in life.\par
What would he even do there? Run across the sea and once he reached the continent simply ask around for the secrets to hiding from fate-based divinations?\par
Orodan was more likely to spend at least a few hundred loops just committing utter genocide and rampaging through every dirty Northman town he could find.\par
But perhaps… that wasn’t a bad idea for a vacation?\par
Hells, he knew just the Guzuharan who could point him in the direction of good places to look around in the savage continent of Guzuhar.\par
“You have a rather disturbing smile on your face young man, should I be concerned about what you plan on doing?” Adeltaj asked, and Orodan’s smile only widened.\par
It was time to challenge the Quest once more.\par
\par
Eversong Plaza was a quiet place right as the loop started.\par
Before Orodan’s intervention, the first Adept he would habitually kill stood quiet watch on the perimeter. The non-Adept guards would silently man their posts, and Lord Aeglos the Elite-pyromancer would peacefully gaze at the stars alongside the few Adepts who were outside at this time.\par
Something which was brought to an end, as it all erupted in a bright explosion from the deluge of power from Orodan’s All-Strike.\par
Eversong Plaza, and the tavern… were gone. Everyone within, killed in one single strike.\par
Once upon a time this Plaza was his crucible… but against his new Legendary active combat skill, which was fueled by the mana from his Mana Black Hole, even a safe level of power which didn’t harm his own body, completely disintegrated everything.\par
And a frenzied Orodan blasted right through the cratered ground to reach the entrance of the tunnels leading under the mountain.\par
His passage through the tunnels was incredibly swift, and eventually it came to a brief pause as a wide-eyed Master Fausta, the necromancer whose undead pet eviscerated him thousands of times in the past, intercepted him.\par
Five exchanges lasting less than a tenth of a second later, all of her undead minions were killed before she even had the chance to empower them via necromantic tether. The undead Demonic Berserker which was once so strong to him… was now no more than wheat before a scythe to the current Orodan who could beat living Master-level warriors stronger than Ovuru.\par
Master Fausta subsequently had her entire mana pool drained and her head torn off shortly after.\par
Orodan’s absolutely furious sprint through the tunnels continued as every single Novarrian in his way was killed before they even knew what happened to them.\par
And finally he reached the gated chamber preceding the main control chamber, and it was lacking guards. Orodan heard the sounds of fighting still erupting from inside, so he rushed forward and blasted the massive metallic gates leading into the chamber off their hinges with a single kick.\par
Inside, a battle was ongoing.\par
Ovuru World-Drinker was clashing against a Master-level unarmed fighter who looked to be struggling, and the Novarrian who Ovuru feared was working alongside Baron Viglas Argon to team up against a scythe wielding Master who was barely holding on.\par
The arrival of Orodan which sent the gates flying inward, made both parties pause however.\par
“Who the hell are you?” asked the Novarrian Master coldly as he renewed his furious assault on the scythe wielding Republic Master, and he silently bade Baron Viglas Argon to deal with Orodan. “Be careful Viglas, he must have dealt with Fausta, I saw nobody else in the initial attack before the scrying eyes were destroyed.”\par
Baron Viglas Argon… head of noble House Argon, the one noble house Orodan utterly despised. The man was known as a cold, ruthless and conniving bastard. And from what Orodan remembered of the last time he was here, the man had no strong emotional reaction to the fact that Orodan had killed his son Lord Aeglos Argon.\par
The man was a slimy tactician, but unfortunately for him didn’t know about Orodan’s Mana Resistance in this loop.\par
Something which caused the man’s eyes to nearly bulge out of his face as Orodan simply ran right through two of the strongest fire spells he had ever cast. He attempted to flee, but found his feet unmoving. He tried to evade, but found his body frozen.\par
The Blessing of Agathor that forced enemies to challenge him head-on… must have been a terrifying prospect for his more cowardly foes to face.\par
Baron Viglas Argon was splattered onto the stone walls of the main control chamber, and the tide of the battle had turned.\par
“Quick! Heroic stranger! Assist me in fighting Duke Arestos! He’s the strongest foe here!” the scythe wielding Master who looked to be on his last legs exclaimed.\par
For his part Orodan quickly complied as getting this over with quickly was part of his plan for the loop.\par
Orodan joined in on the battle as the scythe wielding Master hung back for a few moments to recover, and during those few moments Orodan and the Novarrian Master he now knew as Duke Arestos… began to clash one on one.\par
Prior to this, the Novarrian was undoubtedly the strongest Master he had seen. In fact, till now Duke Arestos likely ranked among the top two, between him and the High-Burgher Sarvaan Ilsuan Arslan, the outcome would be unclear.\par
But what was clear… was that Orodan held the advantage in melee.\par
Both of them used sword and shield, and while Duke Arestos’s skill levels were undoubtedly higher. Orodan’s absolute plethora of other empowering and amplification skills alongside his active combat skills that had reached the Adept-level… truly made the difference.\par
Duke Arestos’s face went red and his eyes held a crazed desperation and anger at suddenly being pressed backwards and overwhelmed in melee by such a young looking man who used the sword and shield just as he did.\par
“I ask again… who the hell are you?! A reincarnator? A Grandmaster playing games? Once my master hears of this you’ll rue the day you dared interfere!” Duke Arestos viciously spat as he wretchedly fought to survive.\par
What should have been his day of victory, was instead turning into his doomsday.\par
“Wait… I surrender… you can have the machine… just let me live!” Duke Arestos finally begged as Orodan had him pressured.\par
Unfortunately for him, his only reply was the All-Strike sent towards his face.\par
Seeing himself now outnumbered three-to-one, Ovuru World-Drinker snarled and brandished his axe once more amid a pause in the fight between him and the other Republican Master. “Excellent! I shall die a warrior’s death today! Agorhiku watch me and witness my glory!”\par
The ogre-man screamed in a crazed manner and charged right at Orodan.\par
But the difference by now was too apparent. Orodan killed a far stronger Master-level opponent in Duke Arestos… so to fight Ovuru? The outcome was never in question.\par
A furious beating ensued, and the sight of the physically smaller Orodan utterly thrashing the far larger Ovuru must have seemed comical, but it was anything but funny for the Chief of Tribe Leviathan. With a final Power Strike to the head, Ovuru World-Drinker was beaten unconscious.\par
“Leave him alive, I have need for him,” Orodan ordered as he strode towards the unmanned orb.\par
“Wait… what are you doing? We’ve been working on acquiring this machine for a very long time!” the scythe wielding Master shouted.\par
In response Orodan had three words.\par
“Fuck this machine.”\par
The glowing red orb was drained. It turned to a pitch black as it was drained of every iota of mana it previously had.\par
Mana Black Hole was far higher in level than it ever had been the last time he drained the orb, and having such a low amount of mana siphoned into the reserve of the skill… was almost unsatisfying.\par
“You… this! Who are you?!” exclaimed the unarmed Republican Master. “I thank you for saving our lives from the situation that dirty traitor put us in… but you’ve set back two-hundred years of preparation… now the orb will take at least two-hundred more years to recharge once more!”\par
Orodan tuned out the two blithering Masters. They were no threat to him even at full power, and they were both wounded now. They knew it too, and so they made no true threats either.\par
Instead, Orodan focused on the message that popped up before him.\par
\textbf{[Quest Completed → Battle of Ogdenborough - Guzuharan leader defeated, Novarrian leader killed, Republic traitor killed, ancient war machine disabled]}\par
\textbf{[Reward Granted → Permanent +1 Action Increase]}\par
Orodan had an inkling of suspicion about the Quest Reward being repeatable… but for it to actually happen… how unfair!\par
But as he tried testing out his new triple action ability via three Power Strikes let loose into the air which dangerously carved deadly furroughs into the stone walls with purely the air pressure of the blows… Orodan realized there was a balancing act.\par
His very soul felt quite exerted at using a triple action in the same instant of time.\par
It was too much to hope he could simply farm the same Quest repeatedly without fail.\par
Using three actions in the same instant seemed to push his soul to its current limits for now. In fact, he intuitively sensed that increasing the quality of his soul energy would allow him to use further actions in the same instant down the line.\par
But for now, this second Permanent Action Increase would have to suffice.\par
The two Republican Masters were rightfully intimidated by him at this point, and stepped out of the way as Orodan approached the unconscious Ovuru.\par
A few slaps later, the ogre-man woke up.\par
“I have some questions about your homeland.”\par


\section*{Chapter 11 - Taking On Impossible Tasks In Another Continent}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 11 - Taking On Impossible Tasks In Another Continent}%
\par
One would think going to an entire other continent separated by the Sea of Uxumar, would be a goal reserved for later. Perhaps after exploring places nearer to home first.\par
Orodan hadn’t even seen the Republic’s capital city of Karilsgard yet!\par
But here he was, Sprinting across the icy waters of the sea in a journey to reach the northern continent.\par
This was still the same loop since he stopped the ancient machine under the mountain at Eversong Plaza.\par
After Ovuru’s explanations and a relatively detailed enough map that Orodan had committed to memory, he sent the ogre-man to the next life and immediately set forth in the direction of the north.\par
Except… there was a slight problem.\par
Orodan had never traveled quite far before, even in all the loops he’d had to date the farthest he’d really gone was the town of Velestok, still within Volarbury County.\par
Orodan would admit he lost track of his direction at least a handful of times until he began getting the hang of traveling and also obtained the Pathfinding skill, which made things dramatically easier.\par
At his current level, empowered by all his skill, Orodan didn’t need to eat or sleep, and he could fight at full power for multiple days in a row, and this was without using Eternal Soul Reactor which could likely allow him to fight forever if he didn’t let the power generation spiral out of hand.\par
With his ludicrous physical power, he simply plowed right through trees, hills and entire mountains in a straight path to the coast north where he finally saw the Sea of Uxumar.\par
It was his first time seeing the ocean, and it was beautiful.\par
And so he found himself using his empowered physicality to simply Sprint right across the water and waves of the ocean. Who knew that high enough skill levels in the relevant physical and empowering skills could allow one to simply run on water as though it were solid ground?\par
The wind on his face felt exhilarating as he ventured deeper north, further into the sea, and even with his travel speed which could now allow him to make a month’s journey by ship into a single day… it still took time.\par
Orodan caused massive tidal waves as his titanically powerful footsteps propelled him forward, but it was halfway into his journey that his travel was interrupted.\par
The ogre-man from Guzuhar had warned him that even his tribe used designated paths through the sea for a reason.\par
And that reason came in the form of a hundred-headed sea snake that erupted from behind Orodan as his furious travel across the sea had seemingly offended it.\par
Orodan was warned that certain monsters within the Sea of Uxumar were exceedingly deadly, and in certain parts of the sea they had hundreds of years to grow uninterrupted. Some of these sea monsters could even rival Master-level combatants in a fight.\par
One-hundred pairs of furious eyes glowed a teal energy as they glared furiously at his form. The serpent had risen to the surface too late and missed being able to block Orodan’s path, and now it could only glare at the annoying human that had caused a ruckus on the waves and interrupted its meditation.\par
It wasn’t willing to give chase and potentially delve into the territories of other similarly strong denizens of the sea either.\par
But what it didn’t expect, was for Orodan to stop, turn around and charge at it with an excited gleam in his eyes.\par
On Orodan’s end, could he even call himself a warrior if he refused to battle a monstrous hundred-headed sea serpent? He had grown up hearing stories of such dangerous creatures, so the chance to actually encounter and fight one was too much to pass up.\par
All one-hundred heads let out a furious hiss at the same time which caused the air to dangerously tremble and a teal energy to begin filling the misty airs of the Sea of Uxumar for the nearby ten miles.\par
The very waters of the sea became empowered and came under the control of the hundred-headed serpent, and it began launching an apocalyptic flood of teal-colored glowing water at Orodan; who promptly ignored the entirety of the mana based attack and instead ran right through the deluge and engaged the monster in melee.\par
The serpent wasn’t stupid. Monsters at the Master-level and above usually were sapient, even if they weren’t capable of or wish to communicate with the civilized races. So when Orodan’s Mana Resistance allowed him to simply ignore a massive part of its arsenal, the creature’s hundred heads all immediately displayed a look of alarm. Or that was what Orodan assumed it was, given he didn’t know what serpent facial expressions meant.\par
The serpent’s scales glowed the same teal color, and all one-hundred heads swooped towards Orodan, rising to the challenge of meeting this strange man who dared intrude on the portion of the sea it considered its turf.\par
Ten seconds of absolutely calamitous melee ensued in which certain conclusions were reached by both combatants.\par
Orodan was definitely being overwhelmed. This sea serpent… might even be near the Grandmaster-level, and the fact that it had a hundred heads wasn’t helping matters.\par
Orodan’s triple action increases and All-Strikes in tandem weren’t enough to bridge the gap. And he wasn’t willing to yet draw the attention of any Avatars by activating Eternal Soul Reactor. This far away from the Republic, who knew what dark Gods’ Avatars would come after him and what esoteric powers they possessed.\par
But one advantage Orodan did have, was his size.\par
The one-hundred heads were each massive, and together it was very difficult for even a few heads to hit him at the same time. And Orodan could in fact challenge one or two heads at once with skillful maneuvering.\par
As the seconds turned to minutes, the battle became one of attrition.\par
And this was where Orodan’s strengths began to shine.\par
He empowered every skill to the limit and fought defensively. Impregnable Bladewall, Perfect Parry, Evasiveness, it all came together with his Death Rage and Dying Struggle as Orodan allowed himself to remain just within the threshold where it would remain active, and a sustained battle occured. His Regeneration and Unyielding Vitality keeping him within this slim margin of life.\par
Thirty minutes passed, then an hour, and then twelve more hours.\par
Orodan was still battling the hundred-headed serpent… but its heads began to lose some of their luster.\par
It undoubtedly had an absolutely titanic amount of vitality, and also likely had a staggering amount of mana. But healing such large wounds on such a big creature took far more energy than healing wounds on himself did.\par
Finally, on the second day of continuous battle, a key event occurred.\par
Orodan’s Weapon Aura empowered sword ripped through the air in an All-Strike that connected with the neck of one of the heads… and broke through the toughness of the scales and carried all the way through.\par
The head went sailing off in an arc and made a loud splash as it entered the sea, and the remaining ninety-nine heads all erupted in a furious and synchronized roar that echoed for many miles.\par
The roar was almost one of frustration, and then the serpent attempted to flee.\par
Which caused Orodan to smirk, as his second Blessing from Agathor wouldn’t allow it.\par
The ninety-nine heads held an expression of shock, before it then turned to rage and the commitment to fight to the death.\par
\par
It took another two days for Orodan to chop the remaining ninety-nine heads off, and even after that he had to do some serious damage to its completely headless body before it died.\par
He felt he now understood his enemies’ feelings at witnessing his ridiculous vitality. This formerly hundred-headed serpent was innately strong, durable and meant to be able to take ludicrous amounts of punishment. He doubted it trained the Unyielding Vitality and Regeneration skills the way he did.\par
Some beings were simply born with natural advantages that others could only obtain via brutal training. Quite unfair.\par
Still, Orodan had wasted four days of his time, but he had managed to kill the damn thing and its dead body lay in multiple pieces across the waters, which were now dyed red for a good hundred metres with the sheer amount of blood the serpent’s body held. A product of its naturally unreasonable vitality no doubt.\par
Mentally he made note of roughly where in the sea this serpent was so that he could tussle against it in future loops. Frankly, this was one of the most fun fights he’d had in a while.\par
With all that done, Orodan resumed his journey northwards towards the continent of savages, towards Guzuhar.\par
Twenty minutes passed and his sheer speed eventually allowed him to see tall mountain peaks and rocky spires piercing the clouds in the horizon. And a little bit later he eventually set foot on land for the first time in four days as his legs touched the snow-covered ground of the icy coastline.\par
Guzuhar, the northern continent.\par
The weather here was as he’d heard, an icy and frigid land. In the distance he could see massive mountain peaks piercing the clouds, and occasionally his enhanced eyes could see shapes flying through the clouds, quite large even at a distance.\par
He didn’t know overly much about the geography, local factions and settlements other than what Ovuru had told him before Orodan put the ogre-man to rest. But from what he heard, Guzuhar’s southern coast, where Orodan had touched down, carried very few if any settlements for fear of Imperial and Republican funded privateers returning the favour the Guzuharans had inflicted with their raids.\par
Additionally, calling them Guzuharans was apparently a rather inaccurate and shallow thing. As Ovuru had explained, the people in this inhospitable waste referred to themselves as Guzuharan only in the broadest manner as figure of speech and when conversing with Inuanans. Guzuhar was simply the name of the continent as designated by the people of the continent of Inuan where Orodan was from.\par
The locals here considered themselves more affiliated with their tribe, such as the Leviathan tribe Ovuru was affiliated with. And as unbelievable as it sounded… apparently not everyone on the northern continent was a bloodthirsty raider.\par
Ovuru’s tribe was one of raiders and uncivilized butchers, but further inland there were supposedly civilized settlements and villages which didn’t go around raiding the coast of Inuan. These settlements were reportedly subject to the attacks of raider tribes just as much, if not more, than the coastal settlements of Inuan were.\par
Orodan found this almost unbelievable. To him Guzuhar was a word he associated with savage and evil. For there to exist… normal people in such a hellscape? He’d have to see it to believe it.\par
His sights were now set on the peak of the tallest mountain he could see nearby. According to Ovuru’s generously provided map, this mountain should be known as Xilirdus’s Ascent and it was a local landmark in the area used to reference and find the way elsewhere.\par
It was a mountain near the southern coast of Guzuhar, and the fact that Orodan could see it upon landing meant that he had veered a fair bit off course during his travels. His Pathfinding skill needed some more work.\par
But, he first wanted to get a lay of the land from atop the mountain.\par
So with empowered footfalls Orodan began making his way up the mountain at a furious pace.\par
Of course, as with the Sea of Uxumar which possessed various denizens, the tallest mountain in the area here was also bound to have various unfriendly and territorial creatures.\par
These came in the form of a flying creature that had a beak and looked vaguely lizard-like but instead of a dragon’s four legs it had only two. Orodan knew there was a term for them, but the last time he picked up a book was when he went through the training for the Volarbury County Militia.\par
These creatures also had a shrill and annoying shriek that made the harpies flying above Ogdenborough seem polite.\par
Naturally, Orodan didn’t like them, and even though the flying pests were rather strong, with them being at least Elite-level by Orodan’s estimation, they still held no hope before him as he butchered his way up the mountain, killing every flying lizard in sight and tracking down any others via the irksome screeches they emitted.\par
Of course, this didn’t make their Master-level broodmothers higher up the mountain very happy, and soon Orodan was mobbed by nearly a dozen of these stronger monsters which were now backed up by a swarm of hundreds of the regular ones.\par
A brutal slaughter occurred over the course of ten minutes as Orodan found weak Master-level beings to be a joke by this point. And soon the mountain was blissfully silent.\par
He climbed for two more minutes and was nearing the peak when the very mountain began moving, and a titanic roar echoed for miles, originating from right underneathe him.\par
It wasn’t that the mountain was moving, it was that the creature sleeping atop it was so massive that it had wrapped around Xilirdus’s Ascent and was peacefully sleeping until the noisy human had come by to cause a ruckus.\par
It had four legs, so it could definitely be called a dragon.\par
And the magically empowered ice attack it sent at Orodan, obliterated at least a hundred miles of terrain in the direction of its breath.\par
Thank the Gods for Mana Resistance, Orodan thought.\par
This dragon was far stronger than the multi-headed serpent he had killed. But even still, Orodan charged through the breath attack and furiously launched an All-Strike containing as much Mana Black Hole charged energy as he could safely deliver.\par
Which merely left a small scratch on the dragon’s nose. An annoyed grunt left its mouth after and the wound swiftly healed.\par
“Hold… human… where are those annoying wyverns?” a booming voice that echoed for miles spoke, and Orodan felt that it was merely the conversational volume of the creature. “And you… a human capable of shrugging off my frigid gales that can freeze an entire kingdom… who are you?”\par
Orodan paused at the sight of the talking dragon.\par
True, he heard that incredibly powerful creatures at and above the Master-level were capable of thought, but for one to even be capable of conversing with the civilized races? And were those things called wyverns?\par
“I am Orodan Wainwright from the lands of the Republic in Inuan, I’ve come to adventure in the northern continent and learn how to evade detection from diviners,” Orodan honestly replied. “And I killed every single flying lizard on this mountain. Their shrieks were incredibly annoying!”If you encounter this tale on Amazon, note that it's taken without the author's consent. Report it.\par
The dragon silently pondered Orodan’s words for a moment before it spoke once more.\par
“Truly?” the dragon asked. “Those wyverns have plagued my restful meditation for at least a thousand years now… the stupid things are drawn by my essence as we share the same draconic nature, even if theirs is of vastly inferior stock.”\par
So he had done the dragon a favor then?\par
“And although more will eventually come, you have given me at least a few years of peace. In light of this boon, I’ve decided to spare your life… killing you would likely involve destroying this most comfortable resting spot,” the dragon spoke, and although it rankled Orodan’s pride to be insulted in such a way, given the pathetic amount of damage a full power All-Strike did, this dragon was at least at the Grandmaster-level.\par
Frankly, Orodan didn’t know if Adeltaj could even beat this thing. The dragon seemed like the sort of creature to have the world bestow Quests on people to kill if it decided to go on a rampage. This was a true monster of calamity that was worthy of being the target of a Quest.\par
Beasts and creatures also held natural advantages and innate abilities that made them in certain cases, far stronger than a member of the humanoid races would be at the equivalent level. The Master-level multi-headed serpent he fought for example, could likely slaughter a dozen Masters like Ovuru. This came at the expense of an incredibly slow growth rate however.\par
“Your ability to resist my icy prowess must be a Legendary skill at least… are you perhaps a fledgling Master hoping to gain insights through battle and adventure to reach for the Grandmaster level?” the dragon asked. “Ah… to be one of the mortal races and lack the ability to absorb world energy… such a pitiful existence.”\par
The dragon’s words seemed insulting, but its tone seemed geninely pitying, as though it felt almost bad for Orodan being born a human.\par
“I’m not a Master, I’m an Adept, although I’m nearing the Elite-level in some of my skills,” Orodan answered, and the dragon’s face made a derisive expression.\par
“Such blatant lies… who do you hope to deceive with such falsehoods?” the dragon mockingly asked. “My Observe skill is powerful enough that it allows me to peer at someone’s Status directly, skill levels and all included, let us have a look shall we?”\par
The Grandmaster dragon’s eyes glowed a fiery orange for three seconds and then the glow subsided. And it remained silent for a while as its face underwent a range of expressions.\par
“I should kill you here and now… reincarnators defy the natural order… but for you to also possess a Mythical skill? You could be a grave threat to the world if I let you live.”\par
Ironic coming from a dragon that itself would be the subject of a Quest if it decided to wantonly rampage.\par
“I’m not a reincarnator, I don’t know what that is yet everyone seems to keep assuming I’m one,” Orodan replied. “I’m caught in a time loop and even the Gods seem to be unaware of it. I repeat the same loop over and over until I die and then I wake up on the day of it again.”\par
“A time loop? And even the Gods remain unaware?” the dragon asked, and immediately its demeanour changed as it suddenly started to regard Orodan very carefully.\par
“Human, we must speak more of this situation…”\par
\par
They spoke for nearly an hour as Orodan recounted all of his adventures, his skills, how he obtained them, and everything he had gone through alongside his enmity with Ilyatana, the Goddess of Fate and his current reasons for being in Guzuhar.\par
“I never liked that meddling woman… a few millenia ago when she was but an upstart fate-weaver in the south, she went about tracking some of the old dragon flights and butchering them to the last hatchling…” the dragon spoke. “It’s good someone of your kind can see her for the manipulative wretch she is.”\par
“She certainly does have quite the superiority complex… I can’t wait for the day I can finally teach her a lesson,” Orodan muttered.\par
“Do not look to the sun when you have yet to cross the clouds human. You struggle and cannot yet even contend with an Avatar whose host is a Favored,” the dragon warned. “The very strongest champions of a God are Chosen Ones, those who have at least three Blessings from their patron God. And they’re usually at least Grandmasters, often in multiple skills. An Avatar using one of them as a host is a threat even I’d be wary of… and I’m a triple Grandmaster who can defeat regular Avatars.”\par
“Are you that strong? Who even are you? You also speak rather… protectively of the world for uh… for a dragon.”\par
“Ah… and does your narrow-mind simply see dragons as the target of Quests bestowed by the world once we decide to go on a rampage?” the icy draconic Grandmaster asked. “While some of my kind have erred in the past… I am a World Guardian.”\par
And Orodan had absolutely no idea what that was, which prompted the dragon to have an resigned expression on its face at the fact that it was speaking to such an uneducated bumpkin.\par
“Human… did you crawl out from under a rock? Did you not pay attention in the academy your kind raise your young within?” the dragon asked, and before Orodan could protest it continued. “World Guardians… are naturally born powerful creatures that serve the will of the world itself and protect it. We prevent great disaster and often step in if a Quest bestowed upon one of the young races has been failed. In return we can absorb world energy at a massively increased rate.”\par
The dragon appeared smug and arrogantly proud of the fact.\par
“Why… just fifteen-thousand years ago it was I who stepped in once the Chosen One failed and put an end to the rampaging eldritch star-beast that threatened the entirety of the world with its corruptive and fell energies! Yes… the legendary dragon noted in mortal history books… was none other than I!”\par
And a proud and imperious roar of regal glory erupted from its mouth after it said this.\par
The seconds stretched on, and the silence became awkward. Orodan had no idea what the dragon spoke of.\par
“How… how stupid are you, human? Have you never read a book?!” the dragon asked. “It’s as though all that monstrous talent came at the expense of any sort of intelligence…”\par
“Of course I’ve read a book!” Orodan defended himself heatedly. He had read the training manuals provided by the county militia of his own accord!\par
The dragon exhaled a gust of frigid wind that was almost akin to a sigh of resignation.\par
“Let us shelve that for now and speak of the meat of the matter,” the dragon spoke. “There are higher levels of Gods which exist. This time loop you are in which you claim has even trapped the Gods unaware… could very well be the work of one of them.”\par
“So you believe me?” Orodan asked. “Who are these higher level Gods?”\par
“A part of me refuses to believe it… but your improbable skill levels, their rarities, and that my World Will skill hasn’t encouraged me to slay you on the spot are good enough for now,” the dragon replied. “As for the names of these rumored higher level Gods, I do not know. Even the most elder dragon I knew when I was but a young hatchling in a dragonflight simply heard rumours of them… and this was at least twenty-thousand years ago.”\par
No real answer then. As Orodan expected. Not that he’d held any hope of getting to the bottom of that question any time soon. His current concerns were elsewhere.\par
While his being on the northern continent of Guzuhar meant that he was effectively outside the reach of the Cathedral’s diviners at this time… he still needed to find a way to evade divination attempts moving forward, or else he wouldn’t be able to get much done efficiently with them hounding him for as long as he was on Inuan.\par
“Fair enough… but I’m not focused on that. Right now, my main concern is finding a method of evading the divination that allows the Cathedral’s people to track me in every loop. It began immediately after I acquired my Mythical skill,” Orodan spoke. “Speaking of, how common is a high-level Observe skill like yours that can unveil even the skill levels of a person? The Avatar of Ilyatana used something similar on me, but should I worry any time I encounter a Grandmaster?”\par
“To answer your second question, all Avatars are capable of peering into your Status unless you received a Reward from a Quest that specifically obscures it. As much as the Gods like to play at being supreme, the power of the world itself is above theirs and they cannot bypass or interfere with Rewards from a Quest,” the dragon spoke. “But as for who else can peer into your complete Status, I would say be wary of any dual-Grandmasters and above… those who have reached level 100 in not one, but two skills or more, have had enough time in their undoubtedly long lives to push the Observe skill to a very high level.”\par
“Understood, and about my first question? Where can I find a way to evade those who perform divinations through the threads of fate?”\par
“I’ve been asleep for thousands of years at least… I wouldn’t know who to go to currently… but a good group to consult would be the shamans of Ozgaric, the God of Trickery and Illusions. The people on the southern continents have always hated him, but if anyone can teach you such a skill, it would be the faithful of that trickster.”\par
“Hmm, I’ll go around looking for them then,” Orodan replied.\par
“Before you go, human,” the dragon spoke. “I need to know… just what do you plan to do with this incredible power of yours? If you plan on causing mass death and destruction that imbalances the world as the loops go on and you grow more and more powerful… I may have to put an end to you myself, even if it doesn’t last.”\par
“I only plan on slaughtering those who’ve wronged me and those who get in my way,” Orodan replied. “A good start will be the raider tribes on this continent.”\par
The dragon pondered for a moment in silence and spoke once more.\par
“I can kill you here and now… but if all you’ve told me so far is true… I cannot kill you permanently. And imprisoning you when you have that Blessing of Malzim is folly,” the dragon spoke. “Given the nature of your time loops… it’s inevitable that you’ll cause massive devastation and might even have a Quest issued by the world against you… but I can only ask that you do not, and in that respect… I have an offer for you.”\par
An offer? Orodan’s interest was immediately piqued.\par
“I have a Quest that was bestowed upon me thousands of years ago to defeat someone… but I’ll never be strong enough to do it,” the dragon spoke. “It’s as dire as it sounds. For a World Guardian to be unable to complete a Quest means the threat is truly great… but we still have one final ability, and that is to grant the Quest to someone we deem capable of completing it… and I Cyvrosdyr the Eternal Winter… wish to grant it to you.”\par
“This sounds suspicious… surely there’s a string attached?” Orodan asked.\par
“That there is… the Quest itself… it will restrict you into acting within the bounds of morality, as all Quests issued to World Guardians do. If you wish for the Reward from this Quest… one of the stipulations is protecting the world, and thus you cannot cause mass devastation like a rabid beast,” the dragon he now learned was called Cyvrosdyr spoke. “You’ve told me of your utterly unfair ability to repeat Quests and continuously acquire the rewards… and I assure you, Quests assigned to World Guardians have particularly powerful Rewards. But the condition is you’d have to remain within the bounds of reason in each loop if you wanted it. Mass devastation and killing of innocents cannot be allowed.”\par
Orodan thought about the icy dragon’s offer for a good while.\par
Another Quest? And another Reward? This sounded like an opportunity he couldn’t pass up. But he still had questions.\par
“What is considered an innocent for the purposes of the Quest? Surely you can’t expect me to show my enemies mercy? I’m a warrior.”\par
“No, innocents in this case refers to uninvolved non-combatants and those who have had no hand in perpetrating sinful actions. Your enemies, and even non-combatants who’ve had a hand in perpetrating evil knowingly do not count as innocents.”\par
“And I don’t suppose you’ll tell me what the Quest wording says before I agree?”\par
“No, either accept or I kill you and end your loop here and now. True, you can find me again, but I guarantee I will never tell you the wording of the Quest until you’ve accepted, this is my personality,” Cyvrosdyr threatened solemnly. “I don’t know what your character is, I can’t risk you thinking the Quest is too difficult from me simply telling you of it and then refusing to entertain the idea from this loop onward. If anyone is capable of completing this Quest… it will be you, with the power of the time loop.”\par
Orodan frowned, but he understood the reasoning. Cyvrosdyr hadn’t seen Orodan’s sheer grit and willpower, the sort of infinite resolve that allowed him to ignite his very soul.\par
For Orodan, there was no Quest which involved fighting an enemy that he would balk at. His enemies were Gods, what did he care if he had to fight some terrifying opponent?\par
“Very well… I accept, I swear to work towards protecting the world and completing this Quest you’re going to bestow upon me. It might not be my immediate goal, but it’ll be one of my long term goals which will eventually be completed,” Orodan stated with sincere determination.\par
“Very well… open your heart and accept the connection I’m forming, simply will it.”\par
And Orodan felt the tether attempting to connect to his very soul, but it didn’t feel harmful or insidious, and he allowed it.\par
\textbf{[Quest Bestowed → The Chosen Eldritch Star - On the eve of the current year the Chosen One of the Eldritch Gods will descend unto the world as a fell comet, defeat this being who is an Avatar of all of the Eldritch Gods and protect the world along the way]}\par
“I… am sorry… you are the only one who can possibly do this… I had two-thousand years to prepare, but I lack the talent. My shoulders cannot bear the weight any longer, you only have six months left till this year ends,” Cyvrosdyr morbidly said as the dragon looked as though an invisible weight was finally taken off its shoulders. “Now it is your weight to bear… I will pray to the world that you do not break in attempting to surmount this impossible wall.”\par
A Chosen One of the Eldritch Gods? An Avatar for all the Eldritch Gods?\par
Orodan couldn’t even beat a regular Grandmaster yet… how was he supposed to do this? How was anyone expected to?\par
“How is this even possible? Does the world not know how impossible of a Quest it bestowed? Surely other Chosen Ones are better suited to receiving this Quest?” Orodan asked, as he felt the daunting weight of what he would be facing settle in on his own shoulders now.\par
“The problem with the Chosen Ones of this world… is that they are only the Chosen Ones of one God. Consequently, they can only be possessed by that one God,” Cyvrosdyr explained. “Whatever is coming however… I do not know how it’s possible, but it’s an Avatar of all three Eldritch Gods… which means it has at least nine Blessings… it is an unfathomable existence that comes for us.”\par
“Why don’t the Gods simply Bless some powerful person with nine Blessings as well then?”\par
“Their soul couldn’t handle it. Blessings are something the soul of a being bears… even three Blessings is stretching the limits of what the soul can tolerate before it is unable to take more,” the dragon explained. “I tried receiving a fourth Blessing once… and although my draconic body can channel energy very well, the same can’t be said for my soul… it didn’t go well.”\par
“This is impossible… just what have you roped me into…” Orodan muttered.\par
“I… genuinely apologize. To inflict this on you… even if you attained Grandmaster-level in multiple skills, I do not know how you would defeat this unknown foe that comes for us…”\par
“No I mean, this is impossible… so thank you!” Orodan exclaimed.\par
The dragon was taken aback and simply sat in silence for a second.\par
“I was wondering what my long term goal throughout the loops would be… but now… I have something to aim for!” he exclaimed. “I was in a rut for a bit after completing the first Quest I had bestowed upon me… and I didn’t know which way to go, but thanks to you I now do.”\par
Cyvrosdyr almost refused to believe it. Who else but a human could have such a reaction to such utterly impossible odds being arrayed against them in an inescapable time loop?\par
But even among humans… Orodan Wainwright was an anomaly.\par
Who else would gladly fight to the death on their very first life? Who else would be torn apart thousands of times? Who else would challenge an Avatar of a Goddess herself?\par
Orodan’s willpower was infinite, and even in hearing the dragon’s words it was stoked to greater heights. Strengthening the soul? He already had a path to that. Receiving multiple Blessings? He would eventually attain this too.\par
And being an Avatar for multiple Gods?\par
Orodan refused to even entertain the idea of needing to play host to Gods to beat this impossible death sentence coming his way.\par
No matter how many loops it took, he would defeat this Eldritch Chosen fair and square. With the might of his own arm and the burning light of his own soul.\par
\par
Cyvrosdyr didn’t have it in him to say much to Orodan after that, and the dragon silently bade him farewell as he departed the mountain, although he did have a strangely relieved expression on his face, as though the weight of many years was suddenly off his shoulders.\par
Orodan now found himself in front of a tribal village, which according to Ovuru’s map, was one of the villages which weren’t raiders. And from a distance he could see a tense stand-off between the outnumbered gate guards of the village and a group of nearly fifty Guzuharan raiders being commanded by an Elite blood mage.\par
How did he know the old woman was an Elite blood mage? It was the casual ease with which she was cruelly pulling the blood right out of a helpless guard’s nose. His militia training taught him that any blood mage capable of controlling their target’s blood directly was typically at least an Elite.\par
Orodan wasn’t a soft person, but he disliked arrogant people who enjoyed torture. It went against his warrior instincts of simply fighting and killing. And he also had an unpleasant reminder of how he was once upon a time savaged thousands of times by an undead Demonic Berserker. The third factor was that he simply didn’t like mages.\par
This all contributed to him walking towards the situation and making his presence known.\par
“You’ve already won, why bother torturing him?” Orodan asked the fur-clad old hag who was sadistically manipulating the guard’s blood.\par
Upon hearing him and noticing the presence of a new person, the mage immediately stopped what she was doing and turned to Orodan. The guard she was torturing sagged to the ground in relief.\par
“And who are you?” she asked, and her eyes held a calculating gaze as she looked him up and down. “Decided to wear the clothes of the soft southerners did you? Got those from a raid?”\par
The woman wasn’t reckless.\par
For someone to approach such a scene with no caution implied a level of confidence in their own strength, and the blood mage was rightfully wary of Orodan for simply waltzing up and interrupting her.\par
This was a world where a wandering passerby could end up being a Master on the worst of days, so people, especially Elites, tended to be somewhat cautious when meeting new people.\par
“No, I’m from Inuan. And I hate raiders,” Orodan declared, and the woman immediately stiffened in response. “Are you lot raiders? Why are you torturing this man?”\par
“I see… well I apologize for offending you… this village owes us tribute and we were simply negotiating the terms. We’re here under the authority of Warchief Bazdugul, who is a Master of course,” the woman backtracked and began explaining. “We were just leaving as a matter of fact, have a good day.”\par
It was funny to see how quickly someone could backtrack out of caution and paranoia. The woman immediately brought up her better’s name as a sort of protection and then proceeded to try leaving. Some unknown wanderer claiming to be from Inuan and intruding on such affairs… was likely able to handle themselves.\par
She was smart. Reckless and stupid Elites were usually the young prodigies, not the old ones like her.\par
Unfortunately for her, her feet refused to move as Orodan’s eyes remained locked onto her own. His second Blessing from Agathor would not allow anyone he considered his quarry to flee or evade. She would stand there along with her entire group for as long as Orodan felt like it, or until she decided to attack.\par
“You there,” Orodan asked the tortured guard. “Is your village under their authority?”\par
The guard quickly shook his head to indicate it was not, an act that caused the Elite blood mage’s face to pale. “These are raiders from the Blood-Dragon tribe! Please assist us hero! Our village is under the authority of Chief Zoricval of the Iron-Bear Clan, he will surely be grateful for your help!”\par
Orodan heard all he needed to, and the blood mage had already begun attacking as she knew talking was a hopeless cause.\par
She threw both of her hands forward, and attempted to take control of the blood within Orodan’s body.\par
Which in reality, thanks to Orodan’s Mana Resistance, made it look like she did a complicated hand gesture which amounted to nothing. As though a child was playing at being an imaginary mage.\par
Her head was torn off her shoulders in the next instant and the other raiders immediately threw down their arms at the Master-level abilities Orodan had displayed.\par
Unfortunately, Orodan hated raiders, and he wasn’t squeamish about executing surrendering enemies if they were as vile as these raider scum.\par
Within two seconds, the group of near-fifty raiders were dead, the snow dyed red with their blood. Even the guards Orodan had rescued looked more than a little intimidated by what had just occurred.\par
The lead village guard, one of the older ones who was near the front of the group, approached Orodan gingerly. “Sir… is there anything we can do for you? We’re deeply in your debt.”\par
And in response, Orodan knew what his next order of business was.\par
“I need to speak to a priest of Ozgaric… I come seeking knowledge.”\par


\section*{Chapter 12 - Peaceful Days In The Most Unexpected Places}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 12 - Peaceful Days In The Most Unexpected Places}%
\par
Before the time loops if anyone had told Orodan that he would be enjoying some of the most peaceful times of his life on the cold northern continent of Guzuhar… he would have thought them mad.\par
But the two days he had been experiencing as a guest of the village of Spearwater were honestly some of the most peaceful times he had spent in a while.\par
It was also the first time Orodan had ever gone a full day without fighting someone. Instead, he spent the two days in a rare period of uninterrupted crafting. This was already the single-longest loop he had ever been in.\par
Frankly, going for so long without waking up to the sound of harpies at night was now getting to be a little weird.\par
He finished using Weapon Aura and Wood Communion to create another Adept-level weapon shaft and handed it to the blacksmith.\par
“An excellent grip for the spear, Aldrun will owe you a life-debt for this young master,” the sweaty man spoke as he hammered away on the spearhead the the weapon they would be bringing together.\par
Orodan would have loved to take up the art of blacksmithing and potentially develop a method of communing with metal, but he didn’t want to expand too broadly while remaining shallow in his crafting skills. He felt it was better to deepen his mastery of his wood related skills first, and once they all hit at least Adept, then he would perhaps consider dabbling in the art of working metal.\par
So he spent the two days helping around the village while word was sent for a shaman of Ozgaric to make way for Spearwater. He helped craft wooden materials, assisted by strengthening existing wood to an absurd quality that turned cheap wood into treasure, and helped in the building projects around the village, including a fortified wooden bunker the non-combatants of the village could hide within.\par
He had essentially increased the wealth of the village by a ridiculous amount, mainly via his ability to strengthen wood to Adept-level, which would be impossible for any regular woodworker to do in the time frame he did. They didn’t have the insane reserves of his Mana Black Hole.\par
While he could’ve decided to run off and make way for the shaman himself, Orodan felt that as a warrior, sometimes periods of quiet reflection where he honed himself in other ways were also necessary. He might just add Spearwater to his loops as a permanent addition moving forward given how he’d been treated.\par
On the matter of his treatment, it was a stark difference. As crazy as it felt to consider the thought, the fact was that Orodan had been treated amazingly by the locals of Spearwater and the nearby villages. His name spread in the last two days, and even though the villagers kept a respectable distance from him so as not to intrude, they were still exceedingly grateful to him for saving their village and improving their lots in life.\par
Unlike the Republic, there was no overarching infrastructure and system of constant surveillance that allowed for talent poaching in Spearwater, the surrounding villages or the Iron-Bear Clan’s territories as a whole.\par
From what Orodan had learned, there was talent-poaching and word was sent to important people whenever an incredibly talented youth was found, but the way things were done was different to the Republic where official bureaucracy and examinations lead to noble houses or even the factions of the capital city poaching talent in a systemized way.\par
Instead, youths were encouraged and guided into apprenticeships or were taken to the town of Vorskard where Clan Iron-Bear’s base of power was, to enter a mentorship under a more powerful individual who could teach them as they grew.\par
Additionally, and the most important part of it all… was that Orodan wasn’t from the continent of Guzuhar. He openly stated he was from Inuan. The reaction was unlike what would occur in the Republic, where if he displayed ridiculous talent some very higher-level people would show up knowing his background - that he was a 17 year militia-man from Ogdenborough - and try to poach him.\par
Now, without a meddling Goddess of Fate tracking him, he could move more freely. And given that he’d already said he was from Inuan, the local people of power simply assumed he was a reincarnator or a Master with a method of making himself look young or obscuring his Status. They didn’t try to immediately poach him and strong arm him into whatever they felt was best for their purposes.\par
Frankly, the northern continent’s relationship with their Gods was vastly different from the stranglehold-like monopoly the Prime Five had over Inuan. And it looked as though the locals were content in keeping things that way as Godly interference and priests going around preaching and tracking would be frowned upon.\par
Orodan… actually found himself liking it!\par
Of course, his personal power and slaughter of the Blood-Dragon raid on Spearwater were still things that caused commotion.\par
An hour after the raid a group of Elite-level members of Clan Iron-Bear came by and asked the locals questions about the raid. After being pointe to Orodan they profusely thanked him and asked who he was and what he was looking for, which Orodan honestly answered, and the head of the group promised to send word to Chieftain Zoricval about Orodan’s actions and his needs.\par
Occasionally, a Master or two would come by to the village as well and stop by to chat with him. This way he had met at least three Master-level individuals of Clan Iron-Bear, and one of them, a gruff woman by the name of Bergthora Fishskinner, challenged him to a brawl far from the village, and upon losing actually attempted to seduce him. She claimed his prowess impressed and ‘excited’ her.\par
Orodan respectfully diverted her attentions. She wasn’t exactly his type, and the difference in power between them made Orodan unwilling to pursue such a thing. He had lain with women before with no commitment, but that was when he was but an Apprentice before the time loops. It was a common problem faced by the strong as they grew in levels, to struggle in finding an equal partner. Not that he even wanted a partner at this time.\par
Orodan never cared for a relationship, but especially now that he was in the time loop he hadn’t had the time to think about such things.\par
As he finished up his crafting for the moment he stepped outside the smithy and heard the clamoring from outside.\par
It seemed Yarostov Iron-Bear was finally paying a visit to the village of Spearwater, and alongside him was a shaman of Ozgaric.\par
The villagers respectfully bowed to the eldest son of Clan Iron-Bear, the ruling force over the area. And the man himself, who was unsurprisingly built like a bear, approached Orodan with an extended hand.\par
Orodan took the man’s offered hand.\par
“My friend! You must be the incredible young hero, Orodan Wainwright, who I’ve heard so much about! I’m glad to finally make your acquaintance!” the man exclaimed in a booming voice filled with mirth. “I am Yarostov Iron-Bear, eldest son of our Chieftain Zoricval of Clan Iron-Bear.”\par
“Good to meet you Yarostov, the villagers speak very fondly of you and Clan Iron-Bear, so when a man of your stature approached I assumed it could only be Yarostov Iron-Bear given how your description matched the stories I’ve heard,” Orodan replied.\par
Frankly, sending Yarostov Iron-Bear to meet with him was the greatest sign of respect Clan Iron-Bear could have shown Orodan on short notice. While Chieftain Zoricval Iron-Bear was the nominal head of the clan, it was his eldest son Yarostov, who was the strongest Master-level individual in Clan Iron-Bear. He was a rare prodigy, having become a Master-level axeman at the age of eighty.\par
“Bah! My people embarrass me! My clan simply tries to look out for our people, that is all, no magical secret to it,” Yarostov replied and then he looked to his left. “And might I introduce Esbetta Ingamiris? The High Shaman of Ozgaric. She was busy with some sensitive duties and was tied up for a few days, otherwise we would have come sooner once we heard the hero who butchered those filthy Blood-Dragon bastards was seeking a faithful of Ozgaric.”\par
Orodan was surprised. He was expecting to perhaps spend time negotiating, searching around and finding a faithful that was an apt teacher. At best he expected to be learning under a decent shaman. But for Clan Iron-Bear to show up with the High Shaman of their Clan herself… Orodan found himself mentally re-evaluating these people. They were treating him very well and seemed to hold him in high regard.\par
“Greetings young hero,” the woman said with a respectful incline of her head. “I’m told you wish to learn how to evade the divinations of the priesthood of Ilyatana and the trackers of the Cathedral of the Prime Five?”\par
At least the woman got right to the point, which Orodan appreciated.\par
“Yes, that’s exactly what I seek… I can’t reveal exactly why, but I need to learn how to evade the ability of people to track me by viewing the ripples in the tapestry of fate,” Orodan replied, and held a bit of concern for if she would refuse unless he stated his exact motives.\par
He need not have been concerned however, as the woman nodded with a mischievous smile.\par
“That’s something that can be arranged,” she replied. “This is an unsuitable place to teach you such things however, how about you come with us to the Iron-Bear Clan’s main city of Vorskard? We have far nicer accommodations for someone of your stature, and there are multiple shamans of Ozgaric in our temple who can facilitate teaching you when working together.”\par
It was a very generous offer, and Orodan looked to Yarostov for his thoughts.\par
The brawny man had a big smile on his face. “She speaks true, it would be unacceptable to have an honored hero like you stay in the village,” Yarostov assuaged. “Clan Iron-Bear would be terrible hosts if we allowed someone who saved a village of ours to remain outside of our hall in Vorskard.”\par
“Very well… I’ll go with you,” Orodan replied with a smile of his own.\par
\par
Orodan had never been inside the Republic’s capital of Karilsgard, nor had he even seen it from a distance.\par
The largest town he ever saw was Velestok, and that… that was nothing compared to the sprawling and bustling city before him that was Vorskard.\par
It was still wintry, as everywhere he’d seen on the northern continent so far was. But despite the ice and snow, the city radiated a feeling of heat, warmth and welcoming that seemed to seep into Orodan’s very soul. He was almost certain there was some sort of magic or skill involved in that.\par
The buildings were primarily wooden, but had sloped roofs, motifs of primarily bears, then wolves and the occasional carving of an owl. Every single house was multiple storeys high, with some of the tallest being dozens of floors in height, and Orodan had never seen buildings that big. Even the smaller buildings here were the size of the town halls he was used to back in Volarbury County.\par
“You look entranced, as though you’re walking into a city for the first time,” Esbetta remarked as the trio of herself, Orodan and Yarostov walked down the bustling streets of Vorskard, the capital city of Clan Iron-Bear’s territories in Guzuhar.\par
The streets were absolutely packed with people, deer-drawn carts and the occasional armored rider atop a similarly armored bear. Orodan had never seen this many people concentrated into a settlement before!\par
Ogdenborough and even Velestok were smaller towns, not on this level. The population was high in Ogdenborough which lead to poverty and a lot of street rats, but not to this extent. Was this what a city was like?\par
“Ah… yes, you’re correct,” Orodan replied. “I’ve never set foot in a city before.”\par
“Truly? So you’re not a reincarnator then?” Yarostov asked.\par
“No, I am not,” Orodan answered. “The only life I’ve known is the one as Orodan Wainwright, local militia member from the Republic of Aden in Inuan.”\par
Upon hearing this even the seemingly reserved Esbetta’s eyes widened a bit, and Yarostov’s face had an incredulous expression upon it.\par
“Then… are you really as young as you appear?” Yarostov blatantly asked.\par
“I’m probably in my early twenties,” Orodan replied. And this was probably the most accurate and honest answer he could give as to how chronologically old he was. Even though he had been through over ten-thousand loops, each loop in many cases was less than an hour long, with a majority being less than even that during certain sets of loops.\par
“Incredible! And you beat Bergthora in a brawl at such a young age… she’s one of the stronger Masters of our clan!” Yarostov loudly exclaimed, causing many heads to turn and the street to go silent.\par
People had already been looking at them as they walked given how famous Esbetta and Yarostov were within their city, but now the Iron-Bear heir’s outburst had confirmed it, people began looking to Orodan as they linked him to the rumors they had been hearing about the young Master-level hero who saved the village of Spearwater and brawled Bergthora Fishskinner and bested her.\par
“Wow… he’s so young-”\par
“How can someone be a Master at that age…”\par
Were among some of the mutters Orodan himself overheard, and he brushed them off and continued walking alongside Yarostov and Esbetta.\par
“Perhaps we’re causing a scene saying such things so loudly Yarostov?” Esbetta gently chided the man, causing him to look embarrassed.\par
“Sorry, I don’t mean to air your business in public Orodan… but still… your talent is incredible! Why not join Clan Iron-Bear? The elders would dote on you and you’d be given whatever you wanted!” Yarostov exclaimed in a blatant recruitment offer.\par
In fact, Orodan actually didn’t mind the idea for this loop! Joining Clan Iron-Bear really might be a good option for him while he uncovered the secrets to evading divinations. Admittedly, jumping right into saying yes to such a blunt offer wasn’t his style, and he’d still need to ascertain what the Gods of Guzuhar were like before he truly committed, but otherwise it seemed like a fine idea.\par
“Er… I can’t commit to a decision on the matter just yet… but if you require my arm for any sort of fight, I’ll gladly lend it,” Orodan replied with what was probably the most diplomacy he had ever shown in his life. A surprise for the usually bull-headed Orodan.\par
“Hahah! Fair enough! I came on too strong there!” Yarostov jovially exclaimed.\par
As they bantered they eventually reached the temple and climbed the steps to enter the building. Of course, either of the three could have rushed to the location far sooner given that all three were Masters, but they had taken the slow and scenic route for Orodan’s sake.\par
The temple of Vorskard was massive. Bigger than any temple he had been to in Volarbury County. Idols of dozens of Gods lined the walls, minor and major Gods.\par
Unlike Inuan, the worship of Gods on Guzuhar allowed for the worship of more than just the major Gods, and consequently there were many more people with minor Blessings on the northern continent.\par
But, there were still seven major Gods worshipped in Guzuhar. And Ozgaric, the God of Trickery and Deception was one of them.\par
The trio walked into an inner chamber usually reserved for higher-levelled faithful of the Trickster God, and the doors were then closed behind them.\par
Frankly, the fact that Yarostov was still tagging along was rather unexpected, but the thought was appreciated. Perhaps the fact that the man could secure a talent like Orodan for his clan had kept him here?\par
“Alright then… Orodan, I won’t ask you to reveal your secrets… but just how powerful are you?” the High Shaman of Ozgaric asked, something Orodan would expect Yarostov to open with instead.\par
“Well, I slew a hundred-headed sea serpent before I reached the continent… and I’ve defeated multiple Masters at once before,” Orodan honestly replied.\par
“That thing?! It’s been nestled in that part of the sea and blocking the shortest route to the Eastern Kingdoms of Inuan for at least a few hundred years now… I don’t know if even I could kill it by myself… and to defeat multiple Masters by yourself? Amazing…” Yarostov muttered.\par
“Is there anything more you can tell us before we start discussing how to avoid divinations?” Esbetta asked.\par
“Well… that depends on the kind of Gods you serve,” Orodan dangerously tested. “Is Ozgaric a kind God? Does he wish to interfere overly much in his followers’ lives? Are there other Gods that hold sway in this city?”\par
“We allow the worship of any Gods in Vorskard’s temple, but I’m the only High Shaman of a God in this city, and Ozgaric is my holy patron,” Esbetta answered. “So while the others hold a roughly similar amount of influence here, Ozgaric would be the most powerful God in this city as he’s the only one who can possess an Avatar here.”\par
“I see… so my question is… would Ozgaric try to bring someone under his thumb if they interested him?” Orodan asked, and the tension in the room began to get thicker.\par
“…no? This is a rather strange question you’ve asked, but I can assure you of this much, whatever your quarrel is with the Prime Five on Inuan, my God Ozgaric won’t help them,” Esbetta replied. “I don’t suppose you’re willing to say what has caused you to be hunted by them?”\par
Orodan then finally decided to bite the dagger and say it.\par
“Well, what if I told you that one of my skills has the rarity of Mythical? Would Ozgaric descend and attempt to capture me for experimentation?” Orodan asked.\par
\textbf{“And what if Ozgaric has been here all along? What would you say then, Orodan Wainwright?”}\par
Orodan’s eyes widened, and the room suddenly went very quiet as Esbetta kneeled on the ground in supplication.\par
Behind Orodan, it was Yarostov who the divine voice boomed from. The man’s eyes held a subtle glow, although unlike the Avatar of Ilyatana that Lady Lakshiya was forced to host, he didn’t look as though he was suffering any damage.\par
“Well then I would ask since when? And I would also ask how the host of your Avatar isn’t taking more damage,” Orodan said.\par
\textbf{“I first noticed you when you killed that hundred-headed serpent in the sea and sent some rather big ripples through the tapestry of fate, and I’ve been keeping an ear on you from then on. You and that old dragon had an interesting conversation I was privy to as well,” }The divine voice boomed. \textbf{“As for Yarostov, he’s a tough warrior unlike many of the soft mage hosts certain Gods choose to descend their Avatars onto. I’m also far more skilled at controlling Avatars and extending my influence than that control freak Ilyatana is.”}If you discover this narrative on Amazon, be aware that it has been stolen. Please report the violation.\par
“I see… so given that you’re implying you’ve heard the entire conversation between me and that old frosty dragon, you’re aware of my whole situation then? The loops, whatever this Eldritch Chosen One is that’s descending onto the world soon… do you have any advice?”\par
\textbf{“I’m well aware of that thing the Eldritch Gods have mutated and are sending our way. Unlike the Prime Five who’ve decided that since it will be landing on this continent they get to ignore it,” }Ozgaric spoke. \textbf{“What they can’t ignore is the foothold in our world that creature’s arrival and subsequent devastation it causes will give the Eldritch Gods. And while the unique situation you’re experiencing interests me, instead of trying to dissect you I’d rather use it to my advantage to solve the real crisis headed our way.”}\par
“You’re talking awfully straightforward for a Trickster God,” Orodan spoke. “Aren’t there supposed to be tricks involved?”\par
\textbf{“The trick was me watching you and everything you did since you set foot on the northern continent. And I’m finding that tricks aren’t helping solve the impending crisis that will land in six months, so it is time for me to employ more direct methods, such as a stubborn warrior like you.”}\par
Orodan couldn’t even say he was offended by that description anymore.\par
“I see… well, I can’t say I’m ready to fight whatever’s coming on this loop. Hells… I might not be ready for a long time, but can I eventually do it? Certainly,” Orodan confirmed. “Even some Avatar of multiple Eldritch Gods is but a wall in front of me… and I’ve gotten rather good at pounding my head against walls till they break.”\par
\textbf{“Indeed, from what I’ve heard, your resolve certainly isn’t lacking.”}\par
“I’m surprised you haven’t simply read my mind or perused my memories to confirm what I’m saying,” Orodan remarked, or had the God already done so?\par
\textbf{“That would be rather impolite. I am not Ilyatana,” }the Avatar answered. \textbf{“Also, given your ability to hold a grudge throughout the time loops… I would rather not acquire a time-traveling enemy I have no knowledge of every time the loops start. Malzim had the right idea when he helped you, I can see you’re rather indebted to him.”}\par
“I see… for what it’s worth, thank you for respecting the sanctity of my mind,” Orodan sincerely said. “I owe the God of Death an eternal debt, if you help me, I will also owe you the same.”\par
\textbf{“I am willing to grant you my Blessing which will obscure your actions in the tapestry of fate, but the problem is… your soul is overfull. I sense three Blessings upon you already alongside two Quest Rewards… from what you’ve told that dragon, you have the unique ability to strengthen your own soul, in the six months before the Eldritch Star lands, you must strengthen your soul to the point that I can grant you my Blessing.”}\par
“That sounds almost too easy… six whole months? That’s a lot of time, I can definitely do that alongside some tutelage from a healer who can teach me how to patch my body up as it gets damaged,” Orodan replied.\par
\textbf{“We will see how long your bravado lasts, now then, I have been speaking through Yarostov for long enough, we shall speak again in six months.”}\par
And with that the subtle glow that Yarostov’s eyes were emitting, disappeared entirely and the man himself seemed to come to attention.\par
“Hmm? Sorry, I lost concentration there for a second, what were we talking about?” the Iron-Bear asked, but once he saw Esbetta kneeling he connected the dots. “Ah! Did holy Ozgaric descend unto me?! What an auspicious day!”\par
Personally, Orodan thought the man sounded far more excited than he’d be if a God decided to use him as an Avatar. But Yarostov seemed to be his usual happy self, so Orodan didn’t worry himself about it.\par
“For our patron to descend unto the world to speak to you… I could not hear what was said... but Ozgaric has left me with a decree,” Esbetta muttered to herself. “It’s decided, we must help train you to reach your full potential as Ozgaric desires.”\par
\par
The training involved things Orodan was familiar with, and things he wasn’t familiar with.\par
Training Eternal Soul Reactor in peace was finally something he could do in the northern continent, as Ilyatana’s divine influence didn’t extend here. From what Esbetta had explained, Gods had their own territories where their powers and influence were stronger or weaker depending on how much faithful they had. And possessing an Avatar and flying them all the way to Guzuhar would not only take a decent amount of energy and burn the host out, but the Gods of the northern continent could immediately sense an Avatar of a foreign God intruding in their domain.\par
Subsequently they could influence the divine energies in the area and force the Avatar’s power to weaken considerably or force the Avatar to expend enough power to counter this that it would burn the host body to ashes outright. And Gods didn’t have so many subservient Favored that they’d want to waste them on pointless endeavors which would yield no results.\par
Divine energy had strange rules it abided by.\par
Thankfully, what this meant was that Orodan didn’t have to worry about Ilyatana descending upon him in the form of an Avatar, at least for as long as he was in Vorskard.\par
What he had been cautioned against however, was leaving the territories of Clan Iron-Bear.\par
Ozgaric seemed like a nice enough God, but further out east in the territories of the nearby Blood-Dragon tribe was the domain of Agorhiku, God of Blood and War, who wasn’t as polite as Ozgaric was. The northern God of War, different from the Inuanan War God Agathor, wasn’t as hands-off about his followers, and frequently possessed Avatars to steer things the way he wanted.\par
Agorhiku’s influence and interference was one of the main reasons why the continent of Guzuhar was rife with raiders who attacked areas on their own continent and sailed the seas to raid Inuanan settlements. Any attempts by the local clans who were suffering at raider hands to band together and launch an offensive against the raiders, were often faced by a burning Avatar of Agorhiku who intervened if the raiders were losing too badly and at risk of being eliminated entirely.\par
Orodan silently made a note to himself, that if the day came where he could ever kill a God, Agorhiku would be at the top of his list.\par
Aside from training Eternal Soul Reactor, the other parts of his training were also going well.\par
Esbetta had started him on training in the very basics of glimpsing the tapestry of fate, but cautioned that it was a very mana-intensive thing to do, and delving too deep could leave one with crippling headaches. While a Blessing from Ozgaric would undoubtedly obscure him in the tapestry, given that he had a Mythical skill Esbetta had warned him that it wasn’t only regular diviners that would be trying to track him, but ones with Blessings as well.\par
And if two people with opposing Blessings clashed, it then came down to skill levels. So for the sake of also being able to evade the Cathedral’s very best diviners who had Blessings related to reading the tapestry of fate, Orodan was encouraged to train the relevant skills himself.\par
It was also the first time Orodan received any kind of formal instruction in the usage of mana.\par
His teachers were both frustrated with, and in awe of him at the same time.\par
Frustration arose from the fact that Orodan barely had any talent in manipulating mana in a fine manner. The initial stages of forming a connection were utterly atrocious, which he was told was a common problem warriors attempting to cross-train in magic faced… but they had never seen anyone as bad at it as Orodan.\par
But the awe emerged when Orodan simply kept training for three days on end, without a single break and without ever needing to recover what should have been the pitiful and undeveloped mana pool of a warrior. Frankly, he didn’t even need to dip into the near bottomless reserves of the storage of Mana Black Hole. A simple three second charge up of Eternal Soul Reactor gave him enough mana to last him for a full day of practice.\par
He was given a strange golden orb, which was a training aid for aspiring Fate-Readers, into which he was to channel mana and the orb would then naturally give him a glimpse into the tapestry of fate. His task was then to let go of the orb and attempt to maintain the connection to the tapestry with his own mana and concentration. It was meant to be a mana-intensive training process, and one that would leave students with frequent headaches.\par
The many attempts he initially made were failed, mainly because Orodan lacked any sort of finesse in handling mana and didn’t even know what forming a connection to the tapestry involved. His usage of Mana Black Hole involved a force of raw willpower used like a battering ram to absorb whatever mana was in reach. His fueling of All-Strike too involved simply cramming as much energy as he could into the attack. Finesse with mana wasn’t his strong suit.\par
But what none of them had expected, was for a monster with inexhaustible mana reserves and endless willpower to give it a shot. And once Orodan had successfully established the connection for the first time and viewed the tapestry… he held on.\par
A whole day passed, and enough mana to fuel a dozen ancient war machines was drained. His head felt like it would explode from the strain, but he still held on in a colossal feat of impossible willpower. And he acquired new skills.\par
\textbf{[New Skill (Uncommon) → Mana Manipulation 1]}\par
\textbf{[New Skill (Uncommon) → Fate Reading 1]}\par
They were both Uncommon rarity skills, and Orodan found himself having an inkling of respect for those who read fate as a profession, as having an Uncommon rarity skill as the bar to entry was rather difficult.\par
His teachers looked at him as though he were a monster in human flesh, and even a strange old woman who Orodan suspected was one of the elders of Clan Iron-Bear came by and looked him up and down before walking away.\par
It was a session of constant and uninterrupted practice, fueled by a virtually infinite source of energy and his eternal willpower, and this eventually lead to gains no matter how untalented at mana Orodan might have been.\par
Mana Manipulation levelled to 13 and Fate Reading levelled to 23. Even though Orodan’s ability to read the tapestry was still lacking in technique… his infinite energy and endless willpower allowed him to simply plow through skill levels in a day. Something that took other students, even the talented ones, months.\par
He didn’t need to stop and recover like they did.\par
Finally, Esbetta had to step in.\par
“Orodan… you’ve done enough, we can stop now,” the High Shaman carefully broached. “Even at level 10 of Fate Reading one can at least see the entire tapestry if their willpower is high enough… and it seems mana capacity is not a problem for you, so we can move onto the manipulation of the tapestry now to prevent the ripples of your actions from spreading.”\par
After ten more seconds where he finally wound down, he stopped his connection to the tapestry and his eyes held a subtle sheen of gold. The gains he made were colossal.\par
He now knew how the hell he was being discovered so easily by the Church’s diviners as soon as he spoke to someone. His own threads of fate were incredibly bizarre and looked like they were essentially… looping. Perhaps that was what Lady Lakshiya meant when she pronounced his were like an Ouroboros.\par
Secondly, everyone’s threads of fate had connections to the world, and then to other people. But Orodan’s had no connection to the world whatsoever, but whenever he spoke to anyone, he formed a thread of fate between himself and them… and the simple act of speaking to them, caused a slight tremor to go from him to their threads of fate… which spiraled into the slight tremors spreading throughout the entire tapestry. Anyone paying attention would notice the whole thing just tremored and would have reason to go seek the cause.\par
And if simply talking to someone caused slight tremors throughout the whole thing, then the activation of his Mythical skill caused the whole tapestry of fate to shudder violently. Even a Goddess would descend upon seeing that.\par
Orodan didn’t like Ilyatana, but he could now understand why she was so adamant on hunting him down every time he activated Eternal Soul Reactor. Frankly, he was almost certain his location had been broadcasted to the world’s fate readers the moment he activated the skill in a loop.\par
But it was now time to take the next step and learn how to obscure his impact on the tapestry.\par
“Alright, what’s next?” Orodan asked as he got to his feet.\par
“Now comes learning the Fate Obscuration skill… it won’t be easy as it’s an Exquisite rarity skill to begin with… I don’t know if you can even obtain it in such a short period of time, but we must try.”\par
Followed by those words, Esbetta instructed him to now start attempting to grasp his own threads of fate that lead outwards towards other people, and every time a tremor went through, he was to try and gently redirect the tremor inwards into the core of his fate, thereby it wouldn’t cause any noticeable outward changes in the tapestry itself.\par
As his first attempt miserably failed, he realized this would be a very long and arduous process.\par
\par
Orodan trained for two whole weeks without any interruption.\par
His mana was endless and his willpower was infinite.\par
But he had to admit he had absolutely no talent in the fine control of mana that this skill seemingly required. He had advanced his Fate Reading and Mana Manipulation greatly, but a skill could only do so much when one didn’t have the talent and their natural inclination wasn’t meant for such a skill.\par
Finally, in a moment of frustration he thought, why not use soul energy instead of mana to manipulate the threads of fate and prevent any tremors from going out?\par
He tried it, and the difference was astronomical.\par
At first he realized that soul energy was incredibly destructive when used to try and manipulate the threads of fate. The tremors he caused by simply attempting to manipulate his own threads with soul energy caused the entire tapestry to shake. But slowly but surely, he began to make critical breakthroughs in the attempts.\par
He decided to forgo the assumption that fine and delicate control was the way. Instead, he began flaring Eternal Soul Reactor at a fast speed, and the colossal amounts of soul energy produced were then set to the task… of forming a shield of soul energy around his fate and completely severing all threads between him and anyone else.\par
Apparently this should have been impossible to do as Esbetta came running towards him in alarm, thinking he had suddenly been killed. Only for her to gape like a fish when she saw that he was still alive, and his eyes were glowing white as soul energy flowed through his body.\par
Second, he began spinning this shield of soul energy rapidly… and maintained a constant spinning spherical barrier of soul energy around his fate. This now had the extra effect of not allowing new threads to extend or form even when people spoke to him or he used his Mythical skill.\par
In essence he was now completely disconnected from the tapestry.\par
\textbf{[New Skill (Legendary) → Fate Disconnect 1]}\par
The energy cost of running this skill constantly was somewhat high, even with Eternal Soul Reactor, but at the hours passed and the skill levels grew he found he was able to maintain an equilibrium point where Eternal Soul Reactor was running, but it didn’t cause his eyes to glow. Instead the soul energy went entirely towards maintaining this new skill which allowed him to completely disappear from the tapestry.\par
“Hmm… it isn’t exactly a skill that allows for hiding in plain sight… in fact, that my threads of fate are trying to find a connection with something that doesn’t exist is quite disconcerting.”\par
It wasn’t Esbetta who spoke, but an old woman who Orodan had seen around before.\par
“Ancestor… we welcome your presence,” Esbetta greeted and bowed.\par
“Yes, yes… now then. What rarity is this skill you’ve developed young one?” the old woman asked.\par
“Legendary.”\par
At this reply, her eyes widened.\par
“Two weeks and you develop a Legendary skill? Such rare talent, why not join us more permanently?” she asked. “How about it Esbetta? He’s a bit young, and he’s dumber than a rock, but a sharp girl like you can keep him in line, no?”\par
The implications of her words caused the High Shaman to choke on air and Orodan to shake his head.\par
“Ancestor! This man… he is too powerful… it would not be a union of equals,” Esbetta meekly protested. And Orodan was inclined to agree. He truly wasn’t seeking any sort of union with a woman, his concerns were far bigger.\par
“Well, I suppose you’re a bit too young for me… unless you have a taste for older women?” she asked and feigned a scandalized look.\par
And at this even Orodan had to suppress a choke and his face gained a slight tint of red. This old woman… was entirely too shameless!\par
“That won’t be necessary!” Orodan quickly replied, which caused the maliciously innocent-seeming smirk on this old woman’s face to widen. “I don’t need to be tied to Clan Iron-Bear to help you, I already gave Yarostov my word that I would help fight in any battles.”\par
“Ah, but that’s no fun. How else is an elderly woman like me to entertain myself if not through matchmaking youngsters like yourself?”\par
“Gods damn it you old granny… get to the point!” Orodan heatedly replied.\par
“Such a mouth on you when you get flustered… hah!” she mockingly laughed. “Forgive me Orodan, but although the Clan can’t stop talking about you, I don’t believe we’ve been introduced. I am Agatha Ingamiris, one of the elders of Clan Iron-Bear.”\par
So that was the woman’s name. Agatha Ingamiris… would undoubtedly get along quite well with Adeltaj Simarji. These two old crones seemed to delight in toying around with young people like him.\par
“It is good to meet you,” Orodan replied cordially. “But can we speak of this skill? I’m maintaining it as we speak, and I’d like to hear your thoughts on it.”\par
“Well, for starters, while you’re completely disconnected from the tapestry of fate… the complete absence of a fate within you will tip off any fate-reader who gets close and examines you face to face. Although that’s still a preferable alternative to broadcasting your location like you were earlier… such a ruckus you caused in the tapestry! Ozgaric is placating and talking to the other Gods even as we speak,” Agatha explained.\par
Ozgaric was… covering for him? Orodan made a note of that and added the Trickster God to the list of people he considered due for repayment throughout his loops.\par
“Additionally, although you lack a fate… that skill you’re running as we speak, even at the relatively low pace you’re churning out soul energy, it’s still a blazing beacon to anyone with a skill that allows them to sense souls,” the old woman elaborated. “While it’s not necessarily a dead giveaway, you’ll have to at least make up some explanation as people might assume you have a Bloodline or are a reincarnator. Or just let them assume and make up whatever they want in their own heads. It’s still an improvement over the tapestry shaking you were doing when you first activated that strange soul burning skill of yours.”\par
Well, at least he finally had a way of remaining under the notice of the Cathedral and Ilyatana. If Orodan simply was someone without a fate and had a stronger than normal soul that burned a little bright… it was something he could work with via excuses or simply staying away from certain people who would sense it and ask questions.\par
Alternately he could simply refuse to answer and go about his business. He would be draw attention to an extent, but it wouldn’t be due to Godly interference, which was the sort of spotlight he was hoping to avoid.\par
Despite the shield he had on, Orodan would have to be careful not to ramp Eternal Soul Reactor up too hard, or he instinctively felt that the shield of energy around his fate wouldn’t hold.\par
“I see, thank you for your words of wisdom and appraisal,” Orodan replied with a respectful nod of his head.\par
“Oh… such manners in a young man, are you sure I can’t interest you in some of the pretty women our Clan has?”\par
At her brazen offer, Orodan could only have his palm meet his face.\par
\par
The remaining months till the descent of the unknown enemy passed by in a blur of training and spending time with Clan Iron-Bear. All his skills grew across the board, and the skill he felt was most necessary to level, Soul Strengthening, had reached level 14.\par
Even at just level 14 the power he felt from his soul, the very quality of his soul energy… was drastically improved.\par
He had worked hard over the months to condense and fold an iota of soul energy inwards till he managed to keep it in that dense form stably, and then he slowly inched towards converting all of his soul energy and the very material his soul was composed of itself, to the denser form. It was an absurdly powerful amplifier type skill for anything that used soul energy.\par
His All-Strikes were at least twice as powerful simply due to the difference in soul energy he poured in, and this was without increasing the strain on his body at having more soul energy flood through it. He also greatly improved his Regeneration to the point that he could keep Eternal Soul Reactor running at far higher rates of power generation, although this would cause his Fate Disconnect to be interrupted as the obscuring shield couldn’t take so much. And the triple actions performed at the same time no longer strained his soul. He could likely complete that Quest once more for another Permanent Action Increase.\par
Orodan felt incredibly powerful, he almost wanted to rush back to Inuan and challenge Adeltaj to a fight now. He genuinely believed he could at least force the old man to get serious.\par
He also began working on developing some kind of Resistance skill for soul energy, but it felt like a goal that was extremely far away and wouldn’t get done in this loop.\par
Admittedly, this was the single longest loop he had ever been in. Who knew if even the thousands of loops spent dying at Eversong Plaza equaled the total amount of time in these six months.\par
And despite his best efforts to avoid it, he found himself engaging in ancillary activities.\par
Activities which involved the woman laying under the luxurious furs next to him in bed.\par
Esbetta wasn’t a warrior, and consequently her Physical Fitness wasn’t very high. So he allowed her to get her rest as he slowly crawled out of bed taking care to avoid waking her. He didn’t sleep, but she did.\par
She was a Master-level spirit mage, a kind of mage he hadn’t heard of before but were apparently more common in the northern continent. Summoning spirits to fight alongside them was their specialty. A less nefarious version of necromancers, Orodan thought.\par
Throughout the months they often fought together against Blood-Dragon tribe raiders, who were starting to become particularly incensed with the losses they were taking at the hands of Clan Iron-Bear since Orodan’s arrival. After a particularly furious battle in which they killed two of the Blood-Dragon tribe Masters, one thing lead to another, and before he knew it the woman had her arms wrapped around his neck and her lips were touching his.\par
He wouldn’t say he was especially deeply connected to her, he had a hard time connecting to anyone anymore since he began the time loops. But it still felt… nice. And while she was slightly disappointed that Orodan didn’t want to form a union, she understood and was still willing to pursue him even after that.\par
He left bed and made way for the temple of Vorskard, and the people walking the streets knew him well by now and his reputation throughout the territories of Clan Iron-Bear… was that of a hero.\par
He entered the temple and its innermost chamber, and silently sat waiting.\par
And soon Yarostov Iron-Bear arrived.\par
The man had become a good friend, but before he could greet Orodan with his usual exuberance, his eyes took on a subtle glow.\par
\textbf{“Orodan Wainwright, my champion. As promised, six months have passed and now you will receive my Blessing,” }the Avatar of Ozgaric spoke. \textbf{“I sense it… your soul has grown… powerful. More than I ever thought possible in such a short time. This is good, your talent is unfathomable, and perhaps that combined with the unique power over time you have will eventually be our only hope.”}\par
“Thank you… I merely tried my best in the little time we had.”\par
And it was true. He genuinely had trained like a dog and fought in as many battles against the Blood-Dragon tribe as he could. None of his skills had crossed unto the Elite threshold yet, but soon he felt many would.\par
His Status looked ridiculous and he didn’t even bother calling it up. But he knew that almost nobody had as many high-level Adept skills as he did. Most Adepts specialized in maybe three skills which they painstakingly brought above the threshold of 50, the prodigious ones had maybe five. Elites, even the prodigious ones had maybe five skills past the level 70 threshold.\par
But Orodan had at least 14 skills above level 60, and their rarities were high. He also had many skills past the Adept threshold of 50.\par
He was slowly advancing in lockstep and trying not to have any one skill hit a threshold too early. But he felt that once he managed to get his crop of skills past Elite… he would be an unprecedented powerhouse. He was already capable of slaughtering Masters, and by now he had yet to meet a Master-level individual, mortal or beast that was stronger than the current him.\par
Unfortunately, the time was coming to an end. Possibly for the entire northern continent.\par
The astrologers had spotted it a month ago, an approaching comet wracked with the most foul and wicked energies ever seen. And in approximately a few hours the comet was predicted to land in the middle of the continent, in the Valley of Spires, out west past Clan Iron-Bear’s territories.\par
\textbf{“Come, time is short and we have a few hours left before it lands, that shield around your fate you have running, deactivate it. It prevents me from reaching your soul with my Blessing.”}\par
Orodan did as requested and lowered the shield, and the message came shortly after.\par
\textbf{[Ozgaric, God of Trickery, smiles upon you]}\par
\textbf{[Received Blessing → Trickster’s Veil - Your Status, fate and soul are impossible to peer into unless you will it]}\par
Orodan felt a strange energy settle over everything that he was. It wasn’t harmful, but it felt odd. And with that, he now had a fourth Blessing.\par
He would have spent time pondering whether he was the only person in the world with four Blessings, but didn’t have the time for it currently.\par
It was time to make way for the Valley of Spires.\par
An Eldritch Star was descending.\par


\section*{Chapter 13 - The Descending Eldritch Star}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 13 - The Descending Eldritch Star}%
\par
The farewell wasn’t as dramatic as he thought it would be.\par
Esbetta wasn’t happy about his departure to go fight something that even an Avatar could not stand against, but Ozgaric must have told her something that satisfied her as the raven-haired woman simply held Orodan in her embrace for a moment and gave him a stern nod upon pulling away. She was a mature and level-headed woman, she had her mysterious allure which lead Orodan to finding her attractive in the first place, but thankfully she wasn’t the overly attached type.\par
They both had their paths in life, and his diverged at this point.\par
Thus he found himself, traveling to the Valley of Spires, alongside various elders of Clan Iron-Bear.\par
The plan was for their group to meet up with elders from various other clans from the north and west. Virtually all the individuals gathering were at the Grandmaster-level in a skill, with at least two being rumored double-Grandmasters.\par
And as Orodan’s group crested the top of a hill, he finally saw it, the Valley of Spires.\par
It was a valley composed of many rocky spires pointing sharply upward, and it had an almost lifeless aura to it. From what Orodan was told, this was the preferred landing spot for the Eldritch Gods’ every time they sent something down in the aims of corrupting the world and establishing a foothold.\par
The scars of previous titanic battles were apparent even if the landscape had shifted and made them look mostly natural over the years. The ground was completely lifeless, and the valley had almost been suffused with a very minor amount of eldritch energy from all the battles that took place here in the past. This was likely the most favorable spot for any invading champions of the eldritch to descend as the Gods of Guzuhar would have the most limited influence here.\par
Overhead Orodan could see Cyvrosdyr perched on one of the larger rocky spires, awaiting the descent of the terrible creature, and beside him were at least two more creatures. A fiery phoenix, and a majestic lion nearly rivalling the dragon in size.\par
Orodan presumed these two new creatures were also World Guardians. The situation truly must have been dire for more than one of them to be present.\par
Upon arrival, nobody spoke to one another. Orodan saw at least three other groups of a handful of old people in each, they were likely all Grandmaster-level individuals, and some of them were likely Chosen Ones, designated as the Avatar for their God.\par
Among Orodan’s own group the designated Avatar was meant to be Urusun Iron-Bear. The strongest Grandmaster of Clan Iron-Bear. When the time came, Ozgaric would descend unto him.\par
The seconds turned to minutes, and slowly an hour passed, and then one more was remaining.\par
It was a bright night with a clear sky, and so Orodan could now see it himself.\par
A strange purple object which looked incredibly distant among the stars, but slowly looked as though it was drawing closer and closer.\par
Time passed and then ten minutes remained, and this was when Orodan noticed certain oddities.\par
He began to hear whispers. He didn’t know of what, but they were whispering in his ear.\par
The shadows began to grow unnaturally darker, and the very color of the world, the life, the natural beauty, began to grow dimmer and fade. Strange physical phenomenon began to occur too, such as certain rocky spires… disappearing and reappearing. Certain smaller rocks on the ground began to flit in and out of existence, and the highlight of this was when the ground began to tremble and rocks began to fall off the spires… only for these rocks to unnaturally stop in mid-air.\par
Five minutes remained, and the descending comet now looked… massive. Far bigger than the largest mountain he had seen. It was close enough now that he could see the abhorrent purple energy surrounding it, vaguely terrifying shapes and growths were jutting out of it and even looking too intently at it made Orodan’s head hurt.\par
The whispers began to grow louder, almost… deafening. He felt as though someone was whispering right into his ear while standing next to him. He heard the voices of Old Man Hannegan, Esbetta, Cyvrosdyr and the people he knew throughout the loops… and they all wailed in horror.\par
Only now did Orodan realize that this was a mental attack.\par
He couldn’t hear anything else, even as he could see purple energy begin to form on the ground and strange horrifying tentacles erupt from the lifeless rock. He turned to see Agatha Ingamiris screaming at him, but he could not hear a word.\par
Everything was drowned out by the whispers.\par
And Orodan looked within himself to see that Eternal Soul Reactor’s production had slowed, and the amount of energy generated now wasn’t enough to maintain the shield around his fate, and thus Fate Disconnect had also failed.\par
That was enough, he decided.\par
His eyes blazed with overflowing white as the energy leaked out of all his pores.\par
He churned his Eternal Soul Reactor harder than he ever had before, and the whispers lessened in volume. He began furiously diverting all of his concentration within himself in a frenzied bid to find just what the attack was and where it was coming from.\par
He struggled for an entire minute and blood leaked from his eyes at just how hard he was pushing his mind to detect even a trace of what the attack was. For he could not defend against it if he did not know what it was.\par
And finally a message came and the whispers were greatly muted.\par
\textbf{[New Skill (Exquisite) → Psionic Resistance 1]}\par
The skill levels began to pick up, fueled by Orodan’s unstoppable willpower and he could finally hear what was happening outside of his own mind.\par
He looked around to see a good third of the Grandmasters were laying on the ground, frothing at the mouth as their minds were utterly collapsed. They didn’t have the sort of willpower Orodan did, even at their high levels.\par
Some Grandmasters lost the edge of desperation and the drive for success as the hundreds of years went on, and this could lead to situations like this.\par
“Orodan! You’re with us once more!” Agatha Ingamiris shouted as the old woman’s body erupted with a fiery aura of her own which was warding off the terrifying psionic attack. “Stay strong boy!”\par
This was… preposterous.\par
The comet hadn’t even landed yet and at least a third of the Grandmasters were out of the fight.\par
The horrid physical phenomenon and psionic assault continued until two minutes till landing remained, and then Cyvrosdyr and the designated Chosen Ones among each group finally took action.\par
The lion which rivalled Cyvrosdyr in size glowed an incredible golden color which seemed to almost return some life to the Eldritch-infected battlefield. Its eyes glowed with power and it became the Avatar for a God.\par
Similarly, Urusun Iron-Bear erupted with power as Ozgaric descended unto him in Avatar form, and the other groups’ Chosen also transformed into Avatars of their respective Gods.\par
And a divine beam of combined energy was fired towards the descending comet with every bit of power the alliance could muster. The beam collided with the descending comet, and pieces of rock and corrupted shell were being torn off by the split second.\par
Eventually, even before the comet reached the ground, a massive explosion occurred, and the entirety of the massive object was covered in a cloud of eldritch and divine energy which obscured it.\par
Of course, Orodan knew there was no way this could be it, and he was proven horrifying correct a split second later.\par
Cyvrosdyr the Eternal Winter, the mightiest dragon Orodan had ever seen. Now had a long grey hand going through his chest.\par
Orodan hadn’t even seen any movement.\par
The next instant, the glorious dragon, the World Guardian… was torn completely in half.\par
The dragon’s body parts hadn’t even had time to hit the ground before every single combatant immediately directed their ire towards whatever had done it.\par
It was massive, grey skin lined with pulsing purple and gray veins, all emitting a sickening glow of grey and purple light. Looking at the gray humanoid the size of a mountain… made Orodan want to throw up and his vision went blurry. He couldn’t even look at it without suffering damage. His very soul felt an increased strain whenever he looked at it. Its lifeless white eyes which lacked any pupils, simply swept over the entire valley and took in the prey arranged against it.\par
How were Avatars expected to face this thing? Orodan even doubted if some Gods could contend with it.\par
The next movement he saw was a flash of purple, and Orodan’s vision nearly went entirely black as he lost all sensation in his body.\par
He had felt this before when Adeltaj turned him into a pile of flesh on the ground.\par
His Eternal Soul Reactor churned faster and faster, fueling his Regeneration to unprecedented levels as he reformed within five seconds. And he came to his senses to find that the surrounding landscape, all the way to the horizon… was an abyssal wasteland of lifeless gray energy and sickening growths. It was merely a large area attack, not even concentrated, and it caused this much destruction and nearly killed him.\par
He looked to the sky to see only two figures fighting the Eldritch humanoid giant. The lion, and an old man wielding only a shield.\par
High in the sky a portal opened, and an elf with glowing green eyes whose skin was cracking at the sheer amount of divine energy, also joined the battle, alongside a dwarf wearing a crown and heavy armor who too was an Avatar. Together the four Avatars, likely some of the most powerful beings in the world, attacked the Eldritch monster in coordination.\par
Orodan thought this might at least pressure the freakish monster, but he thought wrong.\par
Over the next minute… everyone was brutally killed.\par
The Eldritch Avatar took mere surface level damage from the combined attacks. And the regal lion Avatar was the first to be brutally slain as its head was torn off its body. The luminous power reluctantly leaving its mangled corpse.\par
The three mortals died shortly afterwards, with the dwarven Avatar being the last one and had he had his limbs ripped off and was squeezed into a grotesque meat ball within the Eldritch Avatar’s grasp.\par
Every single Avatar that had challenged it… was dead.\par
Orodan didn’t know how the Prime Five planned on ignoring such a threat.\par
The Avatar of the Eldritch had stopped moving enough for Orodan to now finally get a good look at it.\par
It was… an abomination. It didn’t even look like a natural creature, but more like someone had stitched numerous body parts and grafted them together to create some sort of abhorrent gray flesh giant, which had veins of sickening purple and lifeless gray energy running throughout its body.\par
And in worse news, it decided to turn its pupil-less white eyes towards Orodan.\par
\textbf{“One more remains. Such a weak thing… but not without vitality.”}\par
The voice sounded as though three beings were speaking at once, and its next words confirmed it.\par
\textbf{“Your insistence on clinging to life intrigues us, accept our essence and become more than you are.”}\par
A deluge of corruptive eldritch energy was all he saw.\par
He forgot who he was. He felt only the desire to change into something more, the desire to spread the influence of their embrace, the single-minded need to show the denizens of this world the truth.\par
And it felt a voice, a nagging little thing try to tell it to stop. Just who was this annoying little worm to insist it wouldn’t change?\par
Just who was this stupid voice calling itself Orodan Wainwright?\par
The torrents of time would surely win over, after all, that little voice was going against the wills of the three eldest. There was no way it could prevail.\par
As time passed, as days turned to weeks, which turned to months, the little voice never stopped nagging. As though it was endless.\par
As though it was… infinite.\par
A message about failing some Quest came and went.\par
A year passed, and the infinite willpower prevailed.\par
And Orodan Wainwright once again remembered who he was.\par
\textbf{[New Skill (Mythical) → Eldritch Resistance 43]}\par
\textbf{[Psionic Resistance 6 → Psionic Resistance 58]}\par
And as he came to consciousness, he was in a sea of sickly, purple and grayish flesh. Although it found no purchase on his own.\par
Orodan had enough presence of mind by that point to call upon the Blessing of Malzim and immediately willed it.\par
Except, it never activated.\par
\textbf{[The God empowering your Blessing is no longer present]}\par
Orodan’s blood ran cold at the message. And he quickly began to turn his willpower inwards and ignite his own soul in the hopes of ending himself manually.\par
\textbf{“The experiment has awoken? We were wondering when its eternal soul would dim and allow us to corrupt it. But… how curious that it can resist…”}\par
The sea of eldritch flesh parted and Orodan was raised high into the sky by tentacles, and brought before the same gray giant Eldritch Avatar he recalled.\par
For hundreds of miles all around, everything was purple and gray. The sky was filled with a purple haze, the very air he breathed was infectious and the sea and land were covered in horrific growths and massive cloud-piercing trees which spread more eldritch energies into the air.If you stumble upon this narrative on Amazon, be aware that it has been stolen from Royal Road. Please report it.\par
If Orodan didn’t have his Eldritch Resistance and Psionic Resistance skills as high as he did… he would likely be subsumed into the influence of these fell Gods once more.\par
He wasn’t sure what had happened, but he estimated he was under for at least a year.\par
And everything had gone to complete and utter ruin. The world… was likely destroyed.\par
“You… you really destroyed everything?” Orodan asked.\par
\textbf{“Destroyed? We have gifted this world with the touch of truth, of change. Your false Gods either fled or were shown the truth themselves.”}\par
Orodan now understood just how critical this second Quest he had acquired from Cyvrosdyr was. The entire world was at risk. It wasn’t just a matter of some powerful monster causing mass destruction.\par
And so Orodan furiously sped up the burning of his own soul with renewed vigor, pushing Eternal Soul Reactor farther than he ever had before. His body crackled and burned, and his very flesh, bones and organs began melting from the inside out under the power.\par
\textbf{“We see now… you have obtained such a sickening skill which allows for turning away from the touch of the truth.”}\par
The eldritch tentacles pierced his flesh and attempted to infuse him with healing in a bid to stop him from dying.\par
But Orodan now had the Eldritch Resistance skill, and his Eternal Soul Reactor which was constantly running for an entire year… was far stronger now at level 59.\par
The attempts at healing him found no ability to affect his body, and the incredibly powerful Mythical skill now began turning him into ash within a second of churning it as hard as he could.\par
As he approached death despite the frustrated and horrifying alien screams of the Eldritch Avatar, he vowed that he would best this foul creature and the fell Gods it served no matter how many loops it took him.\par
\par
A keening wail ringing in the night sky awoke him.\par
Followed by a Quest message entering his vision.\par
\textbf{[Quest Bestowed → Battle of Ogdenborough - Defeat the Novarrians and their allies as they attempt to activate and commandeer the ancient war machine beneath Mount Castarian]}\par
This was normal, and entirely expected. But the next message following that caused Orodan to breathe a sigh of relief.\par
\textbf{[Quest Bestowed → The Chosen Eldritch Star - On the eve of the current year the Chosen One of the Eldritch Gods will descend unto the world as a fell comet, defeat this being who is an Avatar of all of the Eldritch Gods and protect the world along the way]}\par
He was genuinely worried that the Quest hadn’t come back with him, but thankfully it had. Whatever function the time loop carried, it seemed things that were connected to his soul would travel through time.\par
He idly wondered how Cyvrosdyr was feeling, at the fact that the Quest had essentially disappeared from him.\par
But that wasn’t what was on his mind.\par
For once, he laid back in his bed and simply stared up at the dilapidated ceiling of his hovel, and simply stayed there for a full minute.\par
The Eldritch Gods were horrifying. The year of constant mental assault and attempts by the Eldritch to infect his body… had truly strained his willpower. He had felt constant terror and hopelessness when he was but a small voice within his own body, straining against the near endless willpower that was exerted by an Avatar of three Eldritch Gods. He was essentially battling against the willpower of the Eldritch Gods themselves for a whole year.\par
But he had won.\par
Orodan always knew there was something abnormal about himself right from his first life when he happily fought to the death against the Leviathan Tribe’s raiders. But now he was almost certain that his willpower was not natural.\par
To him, it was simply who he was.\par
He would never quit, he would undergo a whole year of mental battle against Gods. This latest feat made everything else he did thus far look petty.\par
But even he was self-aware enough to realize that a willpower that could contend with and reject three Eldritch Gods, was not normal.\par
Orodan would have to look for an answer as to why, but first, it was time to pay a familiar old man a visit. After paying a certain machine underneath Mount Castarian a visit of course.\par
\par
After trashing everything under the mountain and completing the Quest, Orodan now had a fourth action he could perform in the same instant. This was his new limit alongside his fourth Blessing until he strengthened his soul further.\par
He was now in Velestok.\par
It was a luxurious feeling, to be able to walk around Volarbury County without having diviners of the Cathedral prowling about in force looking for him. His new Fate Disconnect skill alongside his Blessing from Ozgaric was more than sufficient to remove any threat of tracking.\par
On the topic of Blessings, a quick restart of the loop shortly after waking up via calling upon the Blessing of Malzim confirmed that it was working again now that time had turned back.\par
Orodan found himself wondering just who or what was responsible for the time loop.\par
Not even the Eldritch Gods were spared from the effects of it. All their hard work… undone with the death of one man. He didn’t think it was the world either, as the Eldritch Gods had clearly bent it to their will too. The time loops were incredible, and were Orodan’s strongest tool in his arsenal. But he still didn't know who was responsible for them.\par
Velestok and the lumber yard were as he remembered them, but they seemed less impressive now that he had been to Vorskard on the continent of Guzuhar.\par
He walked into the lumber yard and respectfully asked the nearest guard if he could speak to Adeltaj Simarji, and then added on that if the guard didn’t know who he was talking about, to call for an Elite or a Master.\par
This was a far cry from Orodan’s usual brash mannerisms. The year he spent being tortured had greatly mellowed him out! While he was still hot-headed and possessed the same stubborn character, it was now tempered by a calmer and more polite character unless needed.\par
Interestingly enough, his manners lead to an expeditious meeting with the Elites, and his calm explanation and a slight display of his strength led to them swiftly contacting Count Rohanus, who replied back via communication amulet to them to take Orodan to where Adeltaj liked to frequent.\par
It was there, in a clearing surrounded by oddly sharp and pointy trees that Orodan arrived, accompanied by the two Elite-level guards. In the middle of the clearing, sitting in silent meditation was the old man, Adeltaj Simarji. Grandmaster of House Simarji.\par
“Adeltaj Simarji… sorry to intrude, but I come seeking your tutelage,” Orodan called out.\par
The old man continued meditating for at least five more minutes. And while this would have incensed the Orodan of a year ago to no end, the current Orodan had his patience tempered by the harrowing experiences he had gone through. So he too sat and simply meditated, reflecting on the time loops, on life, his goals, and so forth.\par
In the end it was Adeltaj’s footsteps in front of him that snapped him out of it.\par
“If I hadn’t responded, would you have just continued sitting there?” Adeltaj asked.\par
“No, I likely would’ve attacked you at some point to knock you out of it,” Orodan replied, and when Adeltaj had an amused smirk on his face he continued. “I’m seeking to challenge a Grandmaster to see how far I’ve come.”\par
“And just what makes a little sapling like you think that you’re a match for a Grandmaster?”\par
“I don’t know for sure… but I think I could force you to get serious now,” Orodan replied. “In fact, not only would I force you to draw your weapon, I would also force you to use your full power to defend yourself if I struck you.”\par
“Oh ho? Now this is interesting!” Adeltaj said with a genuine look of interest on his face. “You know who I am, seem to know that I’m a Grandmaster, and yet a young man like you wishes to challenge me? Either you’ll quickly learn your place, or I’m about to see something I’ll never forget. I cannot peer into your Status at all, so are you perhaps a Master masquerading as a youth? A transformation potion? A Blessing?”\par
“Neither. I’m in my early twenties and I have yet to reach the Elite level in any skill,” Orodan stated with conviction.\par
Something about his tone must have convinced the old man, because he held a rare serious look in his eyes and seemed to regard Orodan for a moment, as though sizing him up.\par
“Fine, but let us move quite far away from here. It wouldn’t do to damage any of the forest preserves of House Simarji,” Adeltaj agreed.\par
The old man waved the two Elite-level guards away and soon the two of them dashed very deep into the Aenechean Forest, at least a few hundred miles in.\par
“Alright young man, show me what you’re capable of,” Adeltaj challenged, and held his hand out in front of him like he usually did.\par
“I must respectfully warn you to take this seriously from the get go, I’m going to come at you with my full power,” Orodan cautioned as his weapons were drawn and his eyes began glowing white.\par
Upon seeing the white soul energy leaking from Orodan’s eyes, Adeltaj actually drew his weapon and took a proper stance!\par
Which was a good idea because he would really need it.\par
Eternal Soul Reactor was charged to as much as feasibly possible without it breaking the obscuring Fate Disconnect skill, all of his empowering abilities such as Death Rage were activated, and as much soul energy from his soul, stamina from his body and mana from Mana Black Hole were fed into the attack.\par
Adeltaj Simarji’s eyes were focused and serious as he felt the power of the blow coming for him.\par
And then it quadrupled with the +3 Permanent Action Increase.\par
The old man’s eyes widened almost comically as he suddenly realized he could not even evade thanks to a strange Blessing keeping him in place.\par
Adeltaj roared and immediately went all out, using his most powerful offensive active combat skill which was at level 99 and returning a Phoenix Thrust of his own towards Orodan’s attack.\par
The two attacks collided, one a level 99 Phoenix Strike, an Exquisite skill. The other a level 41 All-Strike, a Legendary skill which was quadrupled and empowered by everything Orodan had. Further made stronger by the higher quality soul energy feeding the attack.\par
The terrain for twenty miles was utterly obliterated, and the entire forest around them simply vanished.\par
And although it was a close thing… Adeltaj’s attack was on the losing end, the Phoenix Strike was overwhelmed and he saw a vastly weakened but still strong All-Strike coming his way.\par
It stopped at the last second before touching the old man’s face.\par
“Hells… I really have grown stronger… thank you for the lesson old man,” Orodan muttered and sheathed his weapons as he looked around in awe at the power he had grown to become capable of. “I can actually beat a Grandmaster now… and soon… I’ll even contend with Avatars.”\par
In response, Adeltaj Simarji could only stare with widened eyes.\par
“Who… who even are you?” the old man asked. “There is no way you can be a mere Adept.”\par
“Well, there is a way, but it involves dying thousands of times and venturing to an entirely different continent… at the recommendation of one Adeltaj Simarji of course,” Orodan knowingly teased. “It was an excellent trip by the way. Thank you for that suggestion.”\par
“But I’ve never even met you…” the old man muttered, still in shock at the fact that he had just been overpowered and essentially defeated. If this was a real fight, Orodan could have pushed through and killed him. Fights between regular Grandmasters were usually much closer and a clear victor was hard to pronounce. But for Orodan to overpower his best attack? It suggested a clear power advantage.\par
“You haven’t met me… in this loop,” Orodan said. “Allow me to tell you a fanciful story.”\par
\par
“Ridiculous… your skills, your abilities… an Adept, even a near-Elite one… should in no scenario be able to beat a Grandmaster,” Adeltaj muttered. “But if you’re in this time loop… then that would be the only logical explanation. Hells, I can’t even verify if you’re telling the truth given that you have some strange force obscuring your soul.”\par
“Yes, and unfortunately I’m not willing to lift said force lest an Avatar descend upon my head,” Orodan answered. “Ilyatana is a rather controlling Goddess.”\par
“Hmm… so that’s why you said one of the things you seek to learn is how to defeat an Avatar,” the old man remarked. “But why do you think I can help you with this?”\par
“Well, I thought you were a Grandmaster with seven hundred years of life? You gave me such a good suggestion for my last loop that I figured you’d have good advice for my current dilemma,” Orodan replied. “I don’t know what other avenue to pursue at this time besides running my head against that unfairly strong nightmarish Avatar that descends in six months.”\par
“Yes… that thing you speak of sounds utterly terrifying… even I do not know how it can be beaten,” Adeltaj remarked. “But as for your next steps… strong as you are, your education and formal knowledge are rather lacking. And I mean this respectfully.”\par
Orodan groaned, he knew what was going to be suggested. “Don’t tell me…”\par
“Young man… you might just be best served by trying to apply to an academy,” the old man advised. “Why not live a little? Woo some women, impress everyone in class and show off by trouncing an instructor or two? You can refuse the Observer orb’s examination if your talent is great enough… and in my seven-hundred years I’ve never seen someone as monstrous as you in terms of potential.”\par
Orodan made a strangled noise. “Urgh… but I hate books!”\par
“How else will you broaden your horizons and figure out different avenues of advancement?” Adeltaj asked. “You have the ultimate power which will allow you to become a Grandmaster of every single skill in existence if you put in enough time, and you’re unwilling to put in some work? You’re okay with dying thousands of times, but books threaten you?”\par
At this, Orodan could do nothing but silently take the shame.\par
“You’re right… I just… never thought I would need an academy. Before all this I was an orphaned street rat, academies were something meant for the children of nobles… what am I supposed to do in an Academy that I can’t acquire outside of it?”\par
“Explore the theory of dozens of disciplines and professions, experiment with trying to unlock a plethora of skills, learn more about Republican society and the knowledge and connections that can help you in later loops,” the elderly man explained. “Need I go on?”\par
“I hate it when you make sense…”\par
“An unfortunate side effect of being old I’m told.”\par
Orodan wouldn’t say he was thrilled with the idea of having to study, but it was something that needed to happen if he was to advance himself and make progress in the loops towards defeating that wretched Eldritch Avatar.\par
As much as it pained him to do so, he would likely have to put going to the northern continent aside for a few loops while he just… studied in an academy.\par
How dull!\par
\par
Trumbetton was essentially the center of Volarbury County. If House Firesword could get away with it, they’d call it the capital of the county. The County Militia and House Firesword both had their bases of power inside Trumbetton, and it was a major hub for commerce and consequently had all manner of shops, craftspeople and services in its commercial district.\par
It was Orodan’s first time seeing it with his own eyes, but while it was bigger than Velestok, it was still maybe half the size of Vorkskard, so Orodan wouldn’t say he was awed by any means.\par
He stood in front of the local examination center and prepared to head inside.\par
Examination centers were in every county by the decree of the council of Karilsgard. At the age of 14 everyone was meant to undergo a mandatory observer orb examination, and then afterwards they could re-test if they wanted to join an academy at the age of 17.\par
The inside was spacious to accommodate all manner of destructive testing, and even had a staff consisting of Elites on-duty for ‘special examinations’, in case someone truly talented came along.\par
It was this special examination that Orodan walked in seeking. He ignored the stations for Observer orbs that the majority of people were at and instead made way for the supervisor’s desk behind the main desk.\par
Naturally, this drew many eyes his way as the only people who would make such a show of skipping the orb and the main desk, were either idiots with an inflated sense of how special they were, or genuine talents.\par
And while Orodan had often been called an idiot, he wasn’t untalented.\par
“Can I help you young man?” the Elite-swordsman sitting behind the desk asked. While the man appeared bored, he still paid attention to anyone who simply marched up to his desk. It would either be a waste of his time where he humiliated an idiot, or a chance to send report of a rare talent to the Capital.\par
“Yes, I’m here to take an examination for placement in an academy. Due to my circumstances, an Observer orb will not be an option,” Orodan replied.\par
“I see… come with me then,” the man replied, and Orodan followed him to a spacious room filled with all manner of equipment, measuring devices and even a reinforced arena.\par
The examination consisted of different tests for different types of people. Mages for example, had a magical dummy they were to cast destructive spells at to measure their power. Rogueish individuals had a speed course, and warriors like Orodan had machines to measure their strength and an arena to test their battle prowess.\par
Given that Orodan had marked ‘martial academy’ on the form, he was naturally lead to the section for warriors. The first test before him being a machine that determined lifting strength and measured Physical Fitness.\par
“Rule’s simple, you have three attempts. Put on as many plates as you think you can handle and then attempt the lift. The lift doesn’t count unless the bar reaches this marked threshold.”\par
“Understood,” Orodan replied.\par
And then he put on all the plates. Which caused the examiner’s eyes to widen.\par
This model of machine wasn’t only used for testing prospective students, but also for training by Elite-level warriors. So it naturally could go upto the level where even people with 50 Physical Fitness would struggle. And for Orodan to simply throw all the plates on… he was either about to make a fool of himself, or the monitors observing via scrying eye from the Capital were about to make some impromptu communication calls.\par
Orodan of course, had Physical Fitness at level 65 by now, which was utterly ridiculous even for Masters. But they didn’t need to know that.\par
He threw the entire set of weights up with casual ease, doing more work in feigning a look of exertion than actually having to try. Something which caused the examiner to immediately go silent and begin sweating.\par
Orodan had casually shown that he was stronger than him.\par
The next test was one of striking power, and Orodan was instructed to simply hit the dummy as hard as he could. It was made of Elite-level material and warded with multiple enchantments. It also had a magical sensor that could measure the power of any melee or ranged strike that it was hit with.\par
When Orodan promptly destroyed it in a single blow, the sweat from the man’s face began to drip onto the floor.\par
And finally, the reason the man was sweating, was because he would have to ‘test’ Orodan. Which given how much monstrous ability he had displayed, was likely to be more of a one-sided beating than a test.\par
Thankfully Orodan decided to have mercy on the poor examiner and casually dodged his attacks and quickly knocked him out with a counter-punch to the face.\par
Another group of examiners had to come in and escort the man away after that, and the manager of the entire examination center himself came down to meet Orodan.\par
“Truly fascinating… to be so strong at your age that you can best Elites... I’m Silas Everson. You’re Orodan Wainwright correct? Our records show you’re a Private in the Volarbury County Militia in Ogdenborough, did you perhaps awaken a powerful Blessing or Bloodline?” the man asked. “Don’t mind my questions, you need not answer. The report of this special examination has been sent to the authorities in Karilsgard, someone will be coming by shortly to speak to you about next steps. In the meantime, would you like anything to drink?”\par
The man was almost excessively polite, he might even get a commission off of each candidate at his center that exceeded expectations.\par
Soon enough, five minutes later a trio of people entered the examination center, causing a huge commotion among the members of the public within. The center was evacuated for the time being and the three approached Orodan with friendly looks on their face.\par
The leading man, wearing a set of luxurious clothes with a very nice cape, was Burgher Ignatius Firesword\par
“Mister Orodan Wainwright?” the Burgher asked.\par
“That’s me, to whom do I owe the pleasure?”\par
“I’m Burgher Ignatius Firesword… before the Capital Guard gets here to make a similar offer… how would you like to attend the Bluefire Academy in Karilsgard under a fully paid sponsorship from House Firesword?”\par
The Bluefire Academy… it was the premier academy within the entire Republic. Located within the capital and right next to the Council Palace, it was where the cream of the crop went to study. The Bluefire Academy was known for producing some of the greatest serving soldiers and famous experts of the Republic today.\par
What a stroke of good luck it was to be approached by House Firesword too. The chance to have someone as powerful as him in their ranks meant that they’d accept some stipulations such as no Observer orb examinations. Better to take the sponsorship of House Firesword than to deal with the Capital Guard who might have some strange diviners in their ranks and would likely insist on doing tests on him to verify his background.\par
“That sounds like a great offer, I accept.”\par


\section*{Chapter 14 - Dallying In Noble Circles}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 14 - Dallying In Noble Circles}%
\par
Being given the keys to an opulent guest manor within Trumbetton by the Burgher while Orodan waited for the academic arrangements to be made wasn’t what he was expecting.\par
It was an improvement over his hovel, but Orodan found the larger room quite uncomfortable, as did he dislike the multiple routes of entry to the room. It was a good thing Orodan didn’t need to sleep anymore, or else he wouldn’t have gotten much rest in such a place.\par
The fact that the manor had actual live-in maids was also something that made Orodan uncomfortable. Although, he was certain he had a higher Cleaning skill than at least some of them.\par
Manor aside, the events of the previous day after Burgher Ignatius Firesword had managed to poach him were of note.\par
The Capital Guard had come by on their silver-feathered griffins about ten minutes after he had finished finalizing the deal with House Firesword, and to say they were not happy would be an understatement.\par
The ire wasn’t directed at Orodan of course, but the Capital Guard captain that lead the group was glaring daggers at the Burgher. The smile on Ignatius Firesword’s face never dimmed, as though he knew exactly what he’d done. That Orodan refused to budge no matter what wealth the captain offered was a source of further consternation.\par
Orodan had no plans on leaving House Firesword’s sponsorship behind. While the Capital Guard were the most powerful organization within the Republic aside from the military themselves, they were large, well-organized and to them while Orodan was incredibly talented he still wasn’t above having background checks and divinations performed on him, not at the level of talent he had revealed.\par
House Firesword on the other hand, as a local noble house based in Volarbury County, were always looking to expand and seek local talents who would contribute to their house. They weren’t in as powerful a position as the Capital Guard and thus wouldn’t risk turning a talent away by insisting on Observer orb examinations and background checks by diviners. They would take what they could get, and in the case of Orodan they got quite a lot.\par
House Firesword had only humbly requested that from time to time, Orodan would answer their summons for a task or showing face, even while in the Academy. Which was common practice for many of the students who were talents sponsored by local noble houses as they still wanted their investments who were already strong to contribute to organizational matters even while studying.\par
Students at the Bluefire Academy were the best of the best, missing examinations or assigned self-study material could easily be recovered from via extra tutelage. Keeping the sponsors of the talents at that academy content however, was a higher priority.\par
The communication amulet he had been given was a novelty for Orodan.\par
It sounded utterly inane, for someone as strong as him who could beat a Grandmaster now, to never have used a communication amulet. But it was true.\par
Prior to this he was merely a Private in the Volarbury County Militia, and the communication amulet went to his troop’s Corporal. Thus Orodan was rather unused to the practice of using one of these things, even as it glowed blue currently.\par
Furthermore, they operated on mana, and attempting to reach out to him via mana was a futile effort. So he actually had to be given a modified communications amulet that used mana to directly emit the message via sound instead of emitting it into someone’s mind like a regular one. An invention meant to serve certain paranoid mages who refused to even allow an amulet access to their mind.\par
“Mister Wainwright, how’ve you been? It’s Burgher Ignatius,” the amulet glowed a slight blue as it played the sound of the man’s voice. “I’m hosting a gathering tomorrow evening at the Verdant Gardens, the maids have been instructed to prepare a suitable outfit for you, so can I hope to count on your presence? A number of influential people want to meet you.”\par
“Of course Burgher, that won’t be a problem,” Orodan replied, and the man went on for a bit about how pleased he was to hear it and how Orodan made the right choice in deciding to work with his House before he ended the call.\par
In truth, House Firesword had a rather limited ability to really force the matter if Orodan decided at a later date that he wanted to switch to working alongside another organization or had better things to do. Burgher Ignatius Firesword was only an Elite himself, albeit a higher leveled one. Instead the sponsorship between them was transactional and based on a level of goodwill. Orodan would be called to assist the house in their matters from time to time during his stay at the academy, and even in doing this he would have repaid much.\par
House Firesword’s position as the defacto power in Trumbetton and most of Volarbury County came not from Burgher Ignatius, but from an unknown Grandmaster who preferred to stay out of the public eye, at least this was what Orodan theorized. The last attempt to walk in and bully House Firesword ended with the instigators from House Rockwood leaving the Burgher’s manor with frightened looks upon their pale faces. Who knew what they encountered in there?\par
Night came, and Orodan of course couldn’t sleep, mainly because he didn’t need to. And he was interrupted from training Eternal Soul Reactor at a low level by the intrusion of a maid who came by with a red face to let him know that she was at his service, no matter what form that service took.\par
Orodan sighed and sent the woman out. It was either the Burgher who had instructed her to attempt such a thing, or the woman herself felt daring and thought she could elevate her station in life by getting in bed with a talented Elite. She really wasn’t his type.\par
It was a bad idea too, not for Orodan, but for the woman who so foolishly hoped to lay with someone who was at least Elite-level. Some of the stories he’d heard of what happened to unfortunate civilians who tried seducing martial Elites… were tragic, and that was simply from a moment of passion with no malicious intentions.\par
The woman had no way of knowing whether Orodan had any sadistic tendencies, so he thought her approach was foolish at best.\par
The moon began to sink and dawn came as Orodan’s meditations continued and Eternal Soul Reactor and Soul Strengthening were improved over a whole day of practice. No more maids came by to bother him throughout that period.\par
A maid came by to let him know that breakfast had been served, and that his outfit was ready for the evening. He thanked her, went downstairs and decided to actually experience what food was like again.\par
The bread was quite good, buttered and toasted, the roast meat of some strange bird Orodan had never eaten before was also present and covered in gravy. It was… delicious! Was this what nobles ate regularly?\par
It was quite the stark difference from what Orodan was used to with his stale bread and jerky.\par
In his time in Vorskard he was far too busy constantly training and fighting to eat, and there was a level of respectful distance between him and people who might have wanted to invite him for a meal. His reputation back in that loop was a bit too intimidating to many.\par
But this… was great food!\par
Orodan genuinely thanked the maids before going to the dressing room and putting on the outfit that had been designated for him. It was perhaps the most opulent thing he had ever worn in his life.\par
A majestic black leather jacket with red trimmings, and underneath was an ornate and almost ceremonial looking dress shirt and pants with similar colored trimmings. Finally a flowing cape with the symbol of a flaming sword flowed from his back.\par
It was undoubtedly meant to be a symbol of his allegiance with House Firesword. But Orodan found himself appreciating how comfortable the material felt compared to his peasant-like tunic. Furthermore there was ample space on his belt to keep weapons on, and even a hook on his back, behind the cape for his shield! Fashionable, but practical. Orodan thought that the outfit was meant to portray the image of a civilized warrior who was of high class. A bit ostentatious, but acceptable.\par
He finished donning the outfit and his weapons and decided to take a walk about town to the commercial district.\par
People on the streets gave him a wide berth and heads turned to look at him. His attention-grabbing outfit was somewhat irksome, but on the bright side any shops he walked into immediately showed him their very best merchandise.\par
“Young master, this is a rare potion of titan’s strength! It courses through your veins and will cause qualitative improvements in your physique. Each point of Physical Fitness you have will go farther,” the merchant explained as Orodan stood within this rather well-off alchemy shop.\par
“I see… would it be possible to know where you got this from? Is it a local alchemist?” Orodan asked. He was genuinely interested by the prospect of a potion that could enhance him even further, but he felt that any potion that merely affected his body would simply not last unlike his skill levels and other parts of his Status that were tied to his soul.\par
“The alchemist who made this is none other than Gideon Fusturus,” the merchant replied knowingly. But Orodan didn’t know who that was, and his look of confusion must have made the man feel bad enough to elaborate. “You know… the Elite-Alchemist of House Firesword?”\par
Ah, no wonder the man expected him to know who that was. Unfortunately, while Orodan wore the colors and sigil of House Firesword, he had yet to properly be inducted into it and introduced to people.\par
Perhaps Orodan would get a chance to meet the man at some point and ask him about alchemy and the possibility of making a potion that improved not just his body, but his very soul.\par
He perused some more of the shop’s wares which included various expensive healing potions, potions of virility which Orodan summarily ignored, and potions which restored mana, stamina and even gave more temporary buffs.\par
“And might I call your eye to this one my good sir?” the merchant asked and then pointed to a black potion. “This is a rare obscuration potion which will prevent others from peering into your Status for a set time, quite useful in social settings!”\par
That might have been nice to know many loops ago when such a thing was a problem, but not anymore as Orodan had both a skill and an actual Blessing which filled that role.\par
He thanked the man and left the shop, deciding to peruse more wares until it was time to attend the party at the Verdant Gardens.\par
\par
It was a few hours later when he was perusing a weapons shop that he was begrudgingly forced to respond when Burgher Ignatius contacted him via amulet to let him know that an escort would be sent to his lodgings within thirty minutes.\par
Orodan tried to insist that he could make his way to the Verdant Gardens by himself, but the Burgher pleaded and explained that the escort was as much for his sake and face as it was Orodan’s convenience.\par
Orodan once again, begrudgingly agreed, and made his way back to the guest manor and awaited their arrival.\par
A brown-feathered griffin soon touched down on the ground, and beside it, another brown griffin landed bearing a rider.\par
“Mister Orodan Wainwright?” the man asked, and Orodan nodded. “Burgher Ignatius Firesword requests your presence at the Verdant Gardens sir.”\par
Orodan had to give credit to the Burgher, he knew how to impress. He had expected a carriage being escorted by some troops… but to send an actual griffin rider with a spare griffin for Orodan to ride as well? Quite opulent, and certain to be quite the statement as to his importance to House Firesword.\par
There was no comical fear or bucking around. The griffin was very well trained and undoubtedly used to carrying first time riders often. And Orodan could jump off the tallest mountain in the world and hit the ground without suffering any discomfort. But sailing through the air - without an enemy’s attack sending him flying - was a novel experience.\par
In less than a minute the two griffins made distance and Orodan could see the rather large venue the party was being held in. On the ground he could see a pillar of green smoke rising from a spacious clearing, and this was likely where flying riders were expected to land.\par
They touched ground and the escorting rider, an Elite himself, waved at Orodan.\par
“They’ll be expecting you within sir, it’s been a pleasure. I hope to work alongside you soon,” the man politely concluded as he flew off. Word of Orodan’s strength must have spread faster than he thought.\par
He was ushered from the landing zone to the back door of the spacious venue, where multiple attendants were waiting for him.\par
“Mister Wainwright, we are pleased to have you with us at the Verdant Gardens, Burgher Ignatius is just in the middle of his speech and he’s about to introduce you shortly, please come with me,” the head attendant said.\par
Before Orodan could even ask what the speech was about and why he needed introducing and why he was told to come to the party so late, he was ushered along with urgency until he was on a stage, looking at Burgher Ignatius Firesword addressing the crowd of partygoers from behind. His voice, magically amplified.\par
“-and in hosting this gathering to honor the friends of my house, the hardworking people of action in our county and to celebrate the future of the Republic, I’d like to now introduce a young man of incredible talent who will undoubtedly be a boon to my humble house and Volarbury County, may I present, Mister Orodan Wainwright!”\par
Burgher Ignatius was looking right at him, beckoning him to step forth as he said this.\par
Orodan wasn’t shy about stepping in front of a crowd, after all, one of the duties he had as a member of the county militia was dispersing rowdy crowds. But beating an angry mob into submission and standing before an expectant one as the center of attention were two different things.\par
“This young man recently took a special test at our county’s examination center, and handily bested a battle-hardened Elite! A sense of loyalty towards the county he grew up in bade him to take the sponsorship offer from House Firesword instead of the Capital Guard,” the Burgher spoke. “It’s hardworking young folk like Mister Wainwright here who hold the future of our county in their hands, so let us join together and celebrate our good fortune tonight! Please, dine, drink and make merry! To better days!”\par
The cheers erupted throughout the Verdant Gardens as the speech concluded.\par
Thankfully the Burgher had mercy on Orodan and wasn’t actually expecting him to give a speech of his own as the man gave a slight hand gesture to the artificers controlling the spotlight to cut it off and return the venue to its regular lighting.\par
Orodan saw tables being laid out with absolutely scrumptious looking food he had only ever seen from a distance a handful of times in his life. Barrels of fragrant wine were brought out, and waiters and waitresses dressed in fanciful uniforms came out to serve it all.\par
“I know you come from humble beginnings Mister Wainwright, but this is but a taste of what House Firesword has to offer. We can offer you much if you stay with us,” the Burgher spoke. “I feel it prudent you be warned though… there are plenty of wolves among the guests who have their eyes set on you.”\par
“Wolves? How so?” Orodan asked. He felt rather out of his element here. His comfort zone was in the middle of battle, where both his and his foe’s lives were on the line. “I’ve never been to a gathering such as this before.”\par
“Understandable, after all my people tell me you’re on record as formerly being a Private in the County Militia. It’s good that you chose to bypass them and come to Trumbetton, given your talent your final destination would have been here regardless,” Burgher Ignatius explained.\par
Once he had accepted the Burgher’s offer, the man had quickly made some calls and had him granted the rank of lieutenant in the militia. It was mostly nominal, but also practical in that he could order most members of the militia around with impunity. Lieutenant was also the highest field rank one could have in the command structure of Volarbury’s militia before one started working behind a desk from a command station.\par
“As for the wolves… plenty of people here see quite the opportunity when a young man with the strength to beat Elites appears all of a sudden. You can expect plenty of gifts to make you feel indebted, requests to help solve their problems, and some might even try to introduce you to their sons and daughters in the hopes of you making friends,” Burgher Ignatius explained. “And… I hope I do not have to elaborate how much of a headache it would cause me if you got a girl pregnant?”\par
“That won’t be necessary sir… I’m not so easily swayed,” Orodan answered.\par
“Good, good… one more thing, while most of the guests wouldn’t risk offending me by attempting to recruit you outright… there are some nobles from the Capital here and they might try to tempt you with a brazen offer,” the man said. “Of course, I trust your interests remain firmly with the county you grew up in.”\par
Orodan sensed the man was slightly concerned about that. It really was a momentous occasion when a noble house managed to secure an absurd talent like Orodan, and people of such talent would usually be swooped up by an organization or noble house from Karilsgard, which was the capital.The tale has been stolen; if detected on Amazon, report the violation.\par
But the man needn’t have worried. Orodan’s goals lay firmly in remaining with House Firesword, bettering Volarbury County and acquiring a formal education in the Bluefire Academy. He also wanted to see just how the effects of disabling the ancient war machine extended in a period of six months, and was curious to see what happened in the continent of Inuan after the descent of the Eldritch Avatar. While he knew nothing could stop it, surely the continent didn’t just roll over and die?\par
As for the consequences of draining the ancient machine in this loop? Firstly, the news spread like wildfire that House Argon were traitors to the Republic. He had killed the enemy Masters inside the main control chamber incredibly swiftly and his entire body was shrouded with a cloud of white soul energy which meant that the surviving Republican Masters didn’t get to see who he was. Secondly, with the death of Baron Viglas Argon, the holdings of House Argon were deemed the property of traitors and summarily re-distributed.\par
However, that was the extent of it, and given that Orodan had rushed in at the dead of night, slaughtered all enemies before him and disabled the machine within the span of a few minutes… it really wasn’t a flashy event that anyone heard much about. Thus, the occurrence was only relegated to rumors, and the soldiers of various Republican noble houses swept in and took control of the mountain. Probably in the hopes of eventually activating it again.\par
Even if he had a far bigger problem approaching in six months, Orodan was just glad that he could cleanly complete the Quest he had started this whole mess with and ensure the survival of innocent people like Old Man Hannegan and Vilia Coventor.\par
The consequences of his actions aside, he was now at a social event that required his attention. And there was plenty of delicious looking food on the tables that was practically asking to be savored!\par
But Orodan’s journey to savor some of it was interrupted, much to his exasperation.\par
An older, but not elderly, lady in an ornate dress approached him, a confident smile upon her face. Accompanying her was a calm-looking young man in standard suit and shirt, and a young woman in a rather daring dress that revealed more than normal who had a nervous smile on her face.\par
The trio cornered him as he was making his way to the table to get some food.\par
“Quite the introduction and high praise the Burgher gave you,” the young man spoke. “You must be very strong… I can’t even stalemate an Elite yet, holding on for survival for some time is the most I can do, but you can actually beat one? Incredible.”\par
“Well, it depends on the Elite as well. One with an active combat skill, higher rarity skills, or with multiple skills past the Elite threshold is a different story,” Orodan blatantly lied and undersold himself. “But the fact that you can hold your own against an Elite… even as an Adept that’s impressive itself.”\par
“Perhaps, but not on your level, all I can do is work hard and hope to get as far in life as my talent will take me,” the young man spoke. “I don’t believe we’ve been introduced, I’m Novus Eldragon.”\par
“Orodan Wainwright,” he replied and shook the calm young man’s hand.\par
Orodan had just met Novus but he already held a good opinion of the young man. Calm and hard-working enough to reach the Adept level at his age and even survive against an Elite for a bit, it was pretty good talent.\par
“Boys and their talk of skills and rarities… some things never change…” the older woman interjected. “Novus, will you not introduce your own mother and sister?”\par
At this, the young man seemed somewhat subdued and amended his error.\par
“Mister Wainwright, might I introduce Katareya Eldragon, my mother, and Lucifreya Eldragon, my younger sister,” Novus spoke. “We’re minor nobility, but House Eldragon has served the Republic since its formation.”\par
“A pleasure to meet you,” Orodan replied.\par
“Now then, I hear Burgher Ignatius will be sponsoring for you to attend the Bluefire Academy? It’s quite the accomplishment, you should be proud of yourself young man,” Katareya spoke with a pretty smirk on her face.\par
“If you don’t mind me saying, you don’t look old enough to be calling me young,” Orodan remarked, and the woman’s smile grew just a slight bit wider.\par
“I wouldn’t presume to put on the airs of a younger woman, not since my husband passed.”\par
“My condolences… he left a very beautiful wife behind.”\par
At that, the venue grew a bit more silent, the woman’s face took on a slightly surprised expression and Orodan would swear he saw the lightest tinting of pink upon her face. Next to her, Lucifreya’s face was red in second-hand embarrassment and Novus was giving Orodan a disapproving look.\par
Thankfully Burgher Ignatius Firesword came to the rescue.\par
“The vigor and daring of young men nowadays, eh?” he came in with a joking tone, and even Orodan had to momentarily pause to take in what he’d been doing. He had a thing for mysterious women, but hadn’t expected to get so carried away in flirting with a widowed noble lady in front of her daughter - who he was actually meant to get on with - and her son.\par
“I’m afraid I must steal Mister Wainwright here away before he damages your heart Lady Katareya, for he has some more people who wish to meet him,” the host of the party spoke as he ushered Orodan away. And once far enough away he spoke. “While she really isn’t the worst option… don’t you think trying to seduce a widowed woman from a minor noble house is a bit much my young friend?”\par
“Apologies Burgher… I honestly don’t know what came over me,” Orodan honestly replied.\par
“Well, I do know what came over you, and it was likely a social skill.”\par
“Those exist?” Orodan asked incredulously.\par
“Of course! Not to say Lady Katareya’s level in whichever one she has is particularly high… but if you were naturally taken by her to begin with and your guard was down…”\par
Orodan could see what the man meant now. It was a combination of factors no doubt. But even if it was a skill that made him a bit more forward than he normally was… he wouldn’t deny that he liked her.\par
The Burgher must have seen the look upon his face and thus simply sighed. “Just… make informed choices… Gods forbid you conceive a child? It will lead to an unnecessary burden on your shoulders.”\par
Orodan took the man’s advice seriously.\par
Burgher Ignatius lead him to another group of conversing guests, three men and two women.\par
“-honestly, my attempts at breaking past the Elite threshold in my Enchanting are starting to frustrate me,” one of the women spoke. “I don’t know how you’ve cracked level 70 in Alchemy at your age Gideon.”\par
“Good people, might I intrude upon your conversation here alongside my young friend Orodan Wainwright?” the Burgher asked, and naturally everyone gave him their attention. “Here we have Gideon Fusturus and my cousin Helga Firesword. Given your rather destructive line of work, an Elite Alchemist and an Adept Enchanter are good people to know.”\par
The other three who were conversing in the original group of five took the hint and dispersed to other areas of the party.\par
“Orodan Wainwright? The storekeeper at the potions store I host my failed products at informed me of you, it’s good to make your acquaintance,” the man spoke in a very rapid voice, as though he was rushing and had somewhere to be. “I hear you were looking into the potion of titan’s strength? It’s barely adequate enough to line the shelf of that reject shop, the potion of leviathan’s fury I can concoct is somewhat decent, I’ll have you try that sometime.”\par
“You know about me perusing your shop?” Orodan asked. “And have me try it? Isn’t that an expensive potion?”\par
“Of course I know about everything that goes on in my store. Someone as important as you coming in would naturally lead to the storekeeper informing me about it. How do you think I market superior products to my wealthier clients?” Gideon clarified. “And the cost of one potion of leviathan’s fury really isn’t that high, rather, the understanding I would obtain in witnessing someone as powerful as you imbibe it would be worth far more than the cost of the potion’s ingredients.”\par
“Fair enough, but what I’m looking for is not a potion that merely improves my body physically… but a potion that improves my soul and indirectly strengthens my body as a result, much like the Physical Fitness skill does,” Orodan explained, and the Alchemist went silent.\par
“What you are asking for… it’s been tried quite often, and with oft-disastrous results… I’m afraid it’s beyond my skill level,” Gideon clarified, but at seeing Orodan’s disappointment continued. “But! I can point you towards a Master-level Alchemist who could potentially help you. He was my teacher many years ago.”\par
“That sounds excellent!” Orodan replied.\par
“Are you two done talking shop about your odorous potions Gideon?” the woman finally interjected. “As Ignatius said I’m Helga Firesword, and my cousin keeps me around because I’m rather good at enchanting things.”\par
“Well, I also keep you around because you’re my cousin!” the Burgher added with mock offense. “But yes, she is rather good at making something like your sword capable of things such as burning your enemies, shooting bolts of lightning and whatnot.”\par
Orodan didn’t think he’d be using regular mana based enchantments anytime soon. His own Mana Resistance might cause complications in using the mana-based enchantment weaved by someone else. He just didn’t think mana was the superior form of energy either.\par
“Good to meet you, but I’ve meant to ask an enchanter for a while now… but can enchantments be powered by things other than mana?” Orodan asked. “Such as perhaps, vitality… or soul energy?”\par
“Are you saying a sword that can spit flames hot enough to melt rock isn’t good enough for you because it’s powered by mana?” the diminutive woman asked with an annoyed tone in her voice. “I’ve heard about people in the Eastern Kingdoms using soul energy to power enchantments, but it’s a strange art. And of course, blood mages can power enchantments with vitality, but that’s subject to a whole host of laws in the Republic. Here, we follow the Imperial enchanting tradition, and mana’s what we got. Conveniently transportable in crystal form, can be easily recovered, and it’s standard.”\par
“I see, of course, I don’t mean to imply your mana-based enchanting isn’t good enough for me,” Orodan amended. “That being said, I don’t think I’ll be letting anyone enchant my sword, it’s been with me through a lot of battles and Weapon Aura serves me just fine. I’m also told Weapon Aura interferes with enchantments.”\par
“But Weapon Aura only strengthens the durability of your weapon… what if you had a fantastic forged weapon and didn’t have to care about durability? Combine that with an enchantment and you’d multiply your battle power immensely!”\par
Orodan refused to accept this. He would not trade one for the other. He decided there and then, that one of his goals in the Bluefire Academy would be to experiment with Weapon Aura till he could produce enchantment like effects with it, and he also resolved to learn to power the skill with soul energy instead of mana. He was confident he could show the small woman his own superior way in time.\par
“Well, this conversation is getting a bit technical for my tastes,” Burgher Ignatius interjected. “But the Bluefire Academy is renowned across the world Orodan, so you can definitely find enchanters there among the staff who likely know of soul energy powered enchantments.”\par
“But… I put down ‘martial academy’ on my form at the examination center?”\par
And the Burgher couldn’t help but laugh and fondly put a hand on Orodan’s shoulder.\par
“Ah… I apologize my young friend, but sometimes I truly forget you’re from humble beginnings, but it only assures me of your character,” Burgher Ignatius said and then continued. “The Bluefire Academy is the greatest academy in the Republic and world-renowned for a reason, it is an academy for martial, magic and crafting focused people. The academy existed even before the formation of the Republic and our independence from the Novarrians. The greatest talents of all fields are present in that academy, and they have teachers who are at the Master-level.”\par
Orodan now understood that not only would he be getting a formal education as one would expect in a martial academy, but he would also have access to what was basically a magic academy and a crafting academy in one. In fact, he deduced that cross-training and intermingling among the disciplines was likely encouraged so as to promote innovation and growth.\par
“That sounds… fantastic,” Orodan muttered.\par
“Well, it’s your incredible talent that makes you worthy of a placement there. Frankly, I wouldn’t be surprised if you managed to even secure a scholarship from the academy itself, not that it would matter as our House will gladly pay your tuition all the same,” the Burgher explained. “And who knows? Perhaps you’ll bring great prestige to House Firesword by doing well in the Inter-Academy Tournament held near the end of the year. It would certainly gain you, and by extension us, a great deal of renown worldwide.”\par
Orodan thought about an Inter-Academy Tournament and could only laugh within himself.\par
Perhaps this would have been fair if he applied to the Bluefire Academy at the beginning of his loops. But for the current Orodan who could beat the average Grandmaster? The idea of fighting 17 to 21 year old students in a world wide competition simply made him laugh.\par
No matter what monstrous youths showed up at this Inter-Academy Tournament, he was guaranteed to crush them all with laughable ease. Frankly, the main challenge would be holding back enough to not be scouted out by the Gods.\par
“Anyhow, come Mister Wainwright, we have dallied long enough, there are more people to meet,” the Burgher said, and Orodan internally groaned.\par
When would he get to eat some of the food?\par
\par
The rest of the gathering went smoothly with Burgher Ignatius next to him. The man was using Orodan as a status symbol and a way to flaunt House Firesword’s power as much as Orodan was using him as a shield and guide in annoying social situations.\par
He was dragged into meeting various minor and major nobility from inside the county and outside… and especially their daughters, whom Orodan did his best to respectfully decline at all turns since Burgher Ignatius’s warnings. But also because someone particular had drawn his attention earlier.\par
Watching the Burgher parade him around in front of the two off-duty Capital Guard captains was funny though. The two men were on good terms with Burgher Ignatius and recounted to him how much their compatriot was fuming about missing out on the opportunity to poach Orodan for the Capital Guard, which should have earned the man a hefty commission and accolades for bringing in someone so powerful. When his numerous escalating offers of wealth and whatever Orodan could want were turned down, the man had left in seething rage.\par
The man had let everybody in the Palace hear about his frustrations about House Firesword, something that left the Burgher smiling brightly.\par
Near the end of the night, Orodan finally managed to eat some of the food.\par
Juicy gravy covered meat which nearly melted off the bone, richly flavored and buttered vegetables, hearty starches and succulent fruits. It all tasted amazing and was the best part about the night.\par
Finally, the night ended and Orodan left the Verdant Gardens.\par
But not alone.\par
Which was why he actually slept for the first time despite not requiring it and found himself waking up in the Burgher’s guest manor…\par
…with Katareya Eldragon laying under the blankets next to him.\par
Now how had that happened again?\par
Social skill or not, Orodan wouldn’t lie to himself. He found her mature confidence and mysterious allure attractive. And he liked a scheming woman with a sense of cunning.\par
Admittedly, she was a bit flummoxed too, given that she was expecting her daughter Lucifreya to be the one who tried to seduce him. But here they were, in bed together after a night of recreational activities.\par
“Novus… can’t know of this,” Orodan spoke.\par
“He isn’t stupid sweet thing, do you think he’ll simply pull the covers over his eyes and not realize that his mother didn’t come home with him and his sister?” the older woman asked in that teasing tone of hers that he found so oddly magnetic.\par
“Well… what do I do then?” Orodan asked. “I’m unused to the social conventions surrounding nobility, are there customs I’m supposed to follow now?”\par
“Dear boy, this is why I like you. So much muscle, yet so little brain,” she gently insulted. “Why say or do anything at all? Novus is his own man, but the same goes for myself. I’m the nominal head of House Eldragon. Do you think little Novus gets to say anything to me about who I choose to consort with?”\par
She made a good point. Perhaps the way of nobility was to simply let such things be and neither confirm nor deny? A quiet projection of power, maintained by simply daring anyone to say anything, by saying nothing at all.\par
“Now then… what shall we name the baby?”\par
Orodan paled.\par
\par
Turns out having all these vitality skills and a high level of Physical Fitness meant that he was rather good at making unhappy mistakes.\par
But thankfully, Katareya wasn’t a cruel woman, nor was she in any mood for having another child at this point in her life. So she had the issue taken care of via alchemical means. Something he was eternally grateful to her for.\par
But it didn’t get Orodan off the hook from the meeting he was currently having.\par
“So… Mister Wainwright… have we perhaps learned to better contain ourselves and our impulses from this terrifying experience?”\par
Orodan would have liked to say yes to the Burgher’s question. That he had learned! That he would never engage in such frivolous debauchery again!\par
But the look on Orodan’s face said otherwise, and Burgher Ignatius Firesword must have seen it too, for the palm of his hand met his face and he could only sigh in resignation.\par
“Truly… could you not have chosen someone else at least? Not that Lady Katareya is a bad woman… but we have plenty of older women with haughtily mysterious demeanors in House Firesword!” the Burgher exclaimed with amused frustration. “Now I’ll have to actually begin talking to her again…”\par
“You have a history with her Burgher?” Orodan asked.\par
“Not in the way you’re thinking Mister Wainwright,” the Burgher quickly clarified. “Rather, it was her late husband who was an important retainer of House Firesword. The man fell in battle defending one of my caravans against Guzuharan raiders during a simple escort along the coast. I ensure my fallen man’s family are treated well and taken care of, but I… haven’t spoken overmuch to his widow since then, out of guilt or shame I do not know.”\par
“I see… that sounds like a tragic story. I almost feel strange about laying with her now,” Orodan remarked.\par
“Do not feel so my young friend, Lady Katareya is her own woman and regardless of how you saw it yourself, I assure you things occurred between you and her only because she wanted them to,” Burgher Ignatius assuaged. “You would be wrong to think she’s a helpless woman who stays in the manse while her son trains to be a warrior. Lady Katareya is an Elite diviner and one of the Cathedral’s best trackers. She earns enough through her regular work in this role to pay for her manse and family ten times over.”\par
And Orodan froze once more.\par
An Elite-level diviner of the Cathedral…\par
He… had basically slept with the enemy!\par
How the hell had Katareya not caught on to who or what Orodan was?\par
His thoughts spiraled in a dozen different directions until he forced himself to center them.\par
He had a Legendary skill blocking his fate, and the Blessing of Ozgaric obscuring it. Frankly, unless he met the Cathedral’s most powerful diviner face to face, who was likely Lady Lakshiya, he had nothing to fear from any other diviners.\par
Perhaps this situation needn’t end too hastily.\par
“Anyhow, the real reason I called you here was to let you know that your arrangements have been completed and you’re to report to the Bluefire Academy in three days,” Burgher Ignatius explained. “The lodgings you’ll have should be top notch of course, and I’ll send for a griffin escort to fly you to the academy’s drop off point where an attendant will see to you.”\par
“This sounds rather excessive Burgher… is a griffin escort truly needed? I can honestly run somewhere faster than a griffin can fly,” Orodan said in response.\par
“Running, which at your level of Physical Fitness would cause quite some property destruction if you tried getting anywhere quickly enough,” the Burgher shot back. “Besides, your entrance reflects on my House as well, so have some consideration for me at least.”\par
Orodan agreed to this.\par
“Finally, I was hoping you could do me a favor and help me with a problem my house has been facing,” the Burgher spoke, and Orodan listened attentively.\par
This was the first of many opportunities he would have to pay the Burgher back for his generosity and prove that he was worth the investment. Throughout the academic year the Burgher would oft call upon him for such matters as they agreed upon.\par
“House Firesword owns a mine in the border town of Jerestir, and for a while we’ve been making some decent profits from our ventures there. And the mines are still running well, but recently our surveyors, while tunneling and attempting to sense further underground, have discovered some rather extensive natural tunnel systems,” the man explained. “My surveyors report that these tunnels are full of incredibly valuable Dothril ore.”\par
“But let me guess… there are unfriendly natural denizens who make the tunnels their home?” Orodan asked, and the Burgher nodded.\par
“Precisely. The surveyors using Seismic Sense report that there are thousands of some sort of burrowing creature in these natural tunnels. Could be centipedes, could be something else, we don’t know for sure,” Burgher Ignatius explained. “I can give you some Elites and a few dozen Adepts, and I ask that you lead an operation to clear the tunnels of these things and determine just how far the tunnels go.”\par
“But I assume you want me to handle this entirely within our House so that nobody else shares in the profits?” Orodan asked.\par
“You might lack a formal education, but your rough upbringing has taught you to catch onto the right things it seems,” the man complimented. “Yes, exactly so. If you can, try to handle this yourself and with whatever troops I lend you. I’m not saying you should die trying, and certainly if whatever’s inside is dangerous enough or the tunnels lead even deeper past the civilized depths… then let me know, it might be too dangerous to proceed without the support of the Republic itself at that point.”\par
The civilized depths, it was the depth level that mortal races such as dwarves, drow and certain daring human settlements were willing to live underground at. The monsters were fewer, weaker and support from the surface wasn’t too far away.\par
Beneath that were the wild depths, where adventurers and expeditions would sometimes delve in the hopes of acquiring treasure, mapping the natural tunnels, or clearing out entrenched monster nests which tried raiding the civilized depths. There were rumored to be staging bases and outposts at this level for expeditions even deeper.\par
And beneath the wild depths… were the deep depths, which people knew little about save for certain very heavily-armed expeditions delving to that point to secure incredibly rare and valuable resources. There were some very dangerous monsters at these depths, and history books were full of cautionary records and tales of entire war parties going missing in the deep depths after encountering never before seen creatures. At this depth teleportation in and out wasn’t possible, and communication attempts with the surface failed.\par
Thankfully, his benefactor wasn’t unreasonable and wanted Orodan to stop once he hit merely the wild depths, if the tunnels extended that far.\par
“I’ll head out immediately.”\par


\section*{Chapter 15 - Delving Deeper Than Planned}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 15 - Delving Deeper Than Planned}%
\par
Jerestir was a rather bustling and populous town for one that was on the border. Aside from House Firesword’s mines the other major parts of the local economy were farming and forestry, a lot of which was run by House Simarji. The ground in and around the town was exceptionally fertile and full of energy suitable for not only common crops, but also magical species of trees and plants.\par
Open war between the Novarrian Empire and the Republic of Aden hadn’t reignited since the 120 years of independence, and one would think that perhaps raids and attempts at sabotage would have occurred, but that wasn’t the case.\par
The nobility from both sides were long-lived, and knew each other even before the war for liberation. This translated into the day-to-day operations of border towns like Jerestir remaining unchanged even right after the war.\par
Frankly, the way merchants and common folks went to and from between Novarria and Aden almost made it seem like the war was a spat between the nobility rather than the people themselves.\par
Orodan and his group, which was composed of six Elites and a few dozen Adepts, were now standing in front of the entrance to the mines, the lead surveyor before him.\par
“How far has your surveying shown the tunnel systems to go?” Orodan asked the man.\par
“Sir, our earth mage who has a Seismic Sense of 47 reports that they extend at least two miles down before her detection reaches its limit. Of course, we still have roughly a thousand feet of rock to mine through before we reach these tunnels,” the man answered. He was an Adept metal mage and the one who had detected the deposits of Dothril. “And it’ll take at least thirty minutes for us to tunnel through this layer and create a passage down.”\par
“Alright then, you have my go ahead to get started on that. I’ll stand beside your team as you work and ensure your safety in case anything decides to come burrowing up in response to our downward tunneling,” Orodan ordered.\par
Soon, the work began, and while Orodan could likely have smashed a hole down towards the tunnel systems himself, he really didn’t want to cause a collapse. The survey team knew what they were doing and were trained in safely tunneling to create lasting and stable passages. They also had Construction personnel and an Architect who laid wooden footholds behind the tunneling as it progressed and added supports to ensure the tunnels could survive tremors and the passage of time.\par
The tunneling earth mage, a tall woman with a severe demeanor, had to take frequent breaks to chug mana potions and meditate. The supply of these was no issue whatsoever given House Firesword’s backing of course, and the fact that Gideon Fusturus had decided to tag along of his own volition.\par
The Burgher wasn’t exactly pleased with his Elite Alchemist’s insistence on running underground, but the man was adamant on tagging along and scouring the tunnels for potentially rare alchemical ingredients. He was also someone who had watched the scrying eye recordings of Orodan’s test at the examination center, and given the ease with which Orodan beat up the Elite tester, Gideon knew that Orodan was far stronger than he let on. So he held faith in this venture potentially going into even the wild depths.\par
Finally, with five minutes of work remaining, the tunneling earth mage’s eyes widened and she spoke up.\par
“I sense movement burrowing towards us, at least a hundred!”\par
The warning was followed by the survey crew and non-combatants immediately falling back while Orodan and the Elites of House Firesword took up positions at the front.\par
Two minutes later the rock began to tremble and eventually burst forth. Two pairs of skittering mandibles on the head, and far too many legs.\par
Giant centipedes, and they didn’t seem pleased about the intrusion into their natural habitat.\par
They were decently strong too, with each one being at least an Adept-level monster. Decently strong by the standards of the average newly minted adventurer that is.\par
Within a second, a hundred of them were slain, with Orodan actively trying to hold back so as not to overawe the Elites accompanying him. Yet they still looked at him as though he was a monster. Looks of fear and respect in equal measure.\par
More centipedes skittered through the tunnel they had burrowed, but they all died to Orodan’s fists. Frankly, he didn’t think they were worth drawing his weapon over.\par
The tunnel grew silent for a moment.\par
“I see now why Burgher Ignatius treats you the way he does sir… that was ferocious!” a nearby Elite-level spearman praised.\par
“Glad to know you’re on our side…” another pyromancer muttered.\par
Orodan brushed the comments off and remained focused as he began delving into the tunnel created by the centipedes. It was rough and not as suited to human descent as their constructed and supported tunnel was, but it didn’t matter to Orodan.\par
A few dozen more centipedes came through and tried to assault him during this process, but he tore them apart and his opulent outfit was beginning to get very stained with their ichor. After enough killing, the creatures must have instinctually sensed the difference between them and him, and simply began fleeing the other way.\par
Finally, he and the expedition following behind him who were re-purposing the centipede burrowed tunnel into a human-suitable one, reached the beginnings of the natural tunnels the surveyors had initially detected.\par
It was massive. Illuminated all throughout by growths of a glowing mushroom that were along the walls.\par
And it was filled with giant centipedes, and some even larger and fiercer looking variants that were beginning to gather in one spot. They were preparing to surge forward and attack the expedition in force.\par
“The rest of you, stay here and guard this choke point at the tunnel, I’ll deal with these things,” Orodan ordered as he was the only one who stepped out of their traversed tunnel and into the large natural one.\par
“But sir! This is… too many!” the Elite pyromancer exclaimed. “Even if you’re powerful, some of those larger centipedes are known to be Elite-level, and there are dozens of them!”\par
“I assure you, it won’t be a problem. Simply wait here, and keep quiet about what you see,” Orodan said.\par
Soon, the centipedes must have felt confident as they reached a threshold of gathered numbers. At least a hundred of the bigger and fierce-looking ones were at front, with nearly a thousand of the Adept-level ones behind them. Even the regular giant centipede was the size of two horses. The bigger ones were the size of a two floor house.\par
For a tunnel system in the civilized depths to contain this many monsters was unacceptable. Orodan would have to do his civic duty to make the town a safer place.\par
He looked at the leading centipedes and drew his sword.\par
In response, the flood descended upon him.\par
Two seconds passed, and this was when the centipedes surmised that something was wrong as a dozen of the leading Elite-level pests were killed.\par
Five seconds passed, and the Elites had all died. Now the regular centipedes’ momentum slowed as they were confused as to why their pack leaders had fallen.\par
Ten seconds passed, and thousands laid dead upon the ground. The massive natural tunnel… was eerily silent.\par
Orodan turned around to look at the opening of their own tunnel which lead into this massive one, and he saw only the pale and sweating face of the Elite pyromancer looking out.\par
Orodan put a finger on his own lips and gestured at the man to keep quiet about what he saw.\par
“I think the coast is clear now, they were weaker than I thought they’d be.”\par
And he also finally got a message of advancement he had been waiting for.\par
\textbf{[Sword Mastery 69 → Sword Mastery 70]}\par
\textbf{[Title Slot Gained]}\par
\par
There was no hiding such a ludicrous amount of corpses, and neither could he simply hand wave away the fact that such a horde had abruptly vanished within ten seconds of combat.\par
The Adepts and non-combatants who were further behind simply assumed the Elites had worked together to take care of things. But the Elites themselves who were up front knew the real story.\par
And they could barely stand to look at Orodan straight in the eyes. The atmosphere in the camp had gotten somewhat awkward at the absolutely domineering amount of strength Orodan had displayed.\par
As the Construction crew began setting up a temporary camp and fortifications within the now cleared natural tunnel, the Elite pyromancer approached Orodan.\par
“Sir… you have my word that I’ll remain silent on the matter… but just how strong are you?” the man asked. “To kill nearly a hundred Elite-level monsters leading a horde of nearly a thousand Adept centipedes, that’s… are you perhaps a reincarnator?”\par
“No, I’m not. But if people assume it, that’s their business,” Orodan replied. “I know you’re honor-bound to serve the Burgher, but I don’t actually expect that such a thing can remain secret for long when there are at least a dozen Elite-level experts in our expedition. Even if the rest didn’t directly witness the battle, they saw the aftermath and will surely talk.”\par
“You aren’t wrong sir, be it in social gatherings or word of mouth, such talk tends to spread. After all, fighting is our bread and butter, and talking shop is a great way to pass the time,” the man remarked. “But… if someone of your power tells us to shut up… we didn’t reach the Elite-level by being stupid.”\par
“I don’t mind people knowing that I’m strong… but I don’t need the specifics known,” Orodan stated. “But, bullying you into remaining silent with a threat of force would leave a bad taste in my mouth, so what can I do for you to ensure that the lips of the Elite members of our expedition remain sealed willingly? Or at least so they don't speak of the magnitude of what I did?”\par
It was one thing if footage of him beating an Elite casually was spread and people talked. This was an incredible display of talent and would obviously get him poached and marked for an academy like Bluefire, but it wasn’t groundbreaking.\par
But for him to now have slain a hundred Elite-level centipedes which lead a horde of ten times that number of Adept bugs? It could lead to problems such as the High-Burgher or the Cathedral taking an interest in him. And he didn’t want the attention of the Gods just yet, but nearer to the end of the year at the Inter-Academy Tournament where the loop would be close to the end anyways.\par
The Elite-pyromancer thought for a moment, the man appeared almost nervous. But then he spoke once more.\par
“Mister Wainwright sir, I’m Geldric Sunfire, an Elite pyromancer that humbly serves as a retainer of House Firesword… all the Elites on this expedition are Firesword retainers, meaning we’re not considered actual members of the house as the Burgher and Lady Helga are,” the man who introduced himself as Geldric spoke. “It’s a good life and I have no complaints… but unlike the Burgher who can call upon a powerful figure from above to help aid in his disputes, we retainers aren’t often given the luxury to call upon our masters in return.”\par
It was true. While the retainers of House Firesword owed Burgher Ignatius loyalty for everything he had done for them, they in turn, while undoubtedly receiving protection and great wealth, couldn’t simply call upon the Burgher and the forces of the house for minor things and their personal ambitions and ventures the way the Burgher could.\par
Furthermore, the Burgher himself was the highest-level Elite of the house, nearing a Master, but an Elite still. Even if his retainers did call upon him, the man couldn’t just show up and solve their problems. The Burgher wasn’t strong enough for that. Rather, House Firesword was protected to an extent by an unknown powerful figure who the Burgher didn’t speak of, but who was likely at the Grandmaster level.\par
What Geldric was asking for… was a similar promise of aid and favors from a powerful figure. This figure being Orodan.\par
“I see… and you want me to act as this benefactor of yours?”\par
“We would just humbly request your aid from time to time in… smaller matters that don’t necessarily involve our life and safety, but our personal ventures,” Geldric elaborated. “Not to say Burgher Ignatius isn’t a good master to serve under… but he isn’t quite unoccupied enough to help all his retainers with smaller business where we could use a powerful individual standing beside us. Plus… our head of house is only an Elite himself.”\par
Orodan could understand where Geldric was coming from. What should be noted was that Geldric and the Elite-level retainers of House Firesword weren’t the cream of the crop. They were lower-level Elites, likely all hovering around the low 70s in their highest skill levels. If they were any better they would be elsewhere and not in House Firesword, a local noble house of Volarbury County.\par
Furthermore, House Firesword was in a rather strange position. They had backing from an unknown individual above, and it protected them from any blatant bullying. But the fact that they didn’t have any Master-level individuals like House Simarji and House Argon did was hurting their opportunities for expansion. Having a Master watching over ventures and attempts at seizing opportunities provided a safety net that made a big difference in what the Elites of a house were willing to risk.\par
“Fair enough,” Orodan replied. “And what sort of aid are you seeking from me? Could you give me an example? Surely nothing that would put me at odds with the Burgher himself or cause friction between other noble houses?”\par
Not that Orodan minded fighting, but causing a mess for the Burgher would be poor manners.\par
“Nothing of the sort sir,” Geldric immediately clarified. “As an example, I’ll be leading an adventurer party deep into the Aenechean Forest two days from now… while I normally wouldn’t risk going too deep for fear of drawing the ire of something we couldn’t handle, with you there, we could make some massive profits from securing rarer resources and it would greatly benefit us. We’ll even give you a fair cut of the increased profits.”\par
“That sort of arrangement doesn’t sound too bad. I simply watch over you and make sure you don’t get in over your head?” Orodan asked and the man nodded. “As for the profits, I have little use for money currently so you can keep it.”\par
At this the man seemed incredibly relieved. Perhaps he was expecting Orodan to try and gouge him with his superior strength and status under House Firesword?\par
“Thank you sir, truly,” Geldric replied. “If you help us, not only will the rest of the retainers be in your debt, we’ll even make sure whatever narrative you desire is spread throughout the county and beyond. And of course, should you need it, we'll be at your beck and call too.”\par
What was left unsaid was that Orodan could just make an Elite disappear if they dared to say more than they should. While Elites were important and their loss would most definitely be noticed, the loss of one or two compared to appeasing someone who could beat multiple, was something that could be swallowed by their masters as long as Orodan offered compensation or promises of favors.\par
He had seen it all too often growing up. House Argon could act with impunity even if people went missing, as long as they didn’t offend the wrong people, and as long as they soothed the wound by offering enough compensation even if it was the wrong people. The Republic’s ‘elected council’ didn’t suddenly make the old and powerful people and families irrelevant. The way of the world didn’t change simply because their nation was now known as the Republic and not the Empire.\par
Laws were meant to corral the common folk, and the powerful could work around them however they wished. Be it negotiations, bribery, connections or pure power.\par
There were limits of course, and offending similarly powerful people would still carry consequences, but if Orodan wanted to kill a commoner or even an Elite… if the proper price was paid or he didn’t offend anyone connected to the Elite who was similarly powerful, then who could stop him?\par
“If I might speak honestly sir? None of us would dare reveal what we saw here regardless,” Geldric spoke. “You… are at least as strong as a Master, none of us have a death wish, so if you explicitly tell us to hold our tongues, what can we do but remain silent? I have a wife and children who care about me, I wouldn’t risk that by blabbering about something that isn’t my business.”\par
Quite the pragmatist Geldric was, Orodan thought. Using the opportunity to request assistance while still clarifying that he wasn’t about to intrude on Orodan’s affairs.\par
Shortly thereafter, Geldric convened with the rest of the retainers, and from a distance he could see some of them giving him furtive glances, calculating and appreciative looks in their eyes.\par
Soon, the forward camp and fortifications were set up and the tunnel opening leading to the mines above were as secure as they would be.\par
“Truth be told, venturing forward from this point with the Adepts would be pointlessly dangerous for them. Some of the centipedes were Elites, and in the sort of fighting we might get up to further in the tunnels, many of them will die,” Orodan spoke. “So, this will be the defensive point for now, I’ll scout up ahead, stay here and ensure no bugs get past this point to our mines above.”\par
At this the Adepts had some very relieved looks on their faces, but the Elites still gave him nervous and uncertain looks.\par
“Sir… your strength is without a doubt… incredible. But is going deeper into the tunnels by yourself truly safe? Will you not even bring a tracking and pathfinding expert with you?” one of the Elites asked. “As grateful as I am to hear you’re willing to put yourself first in venturing these dangerous tunnels… the Burgher will be severely displeased with us if anything were to happen to you.”\par
“You’re not wrong that this seems a bit reckless, but I’ll be cautious. The Burgher would want us to see how far we can push with just the strength of House Firesword,” Orodan replied. “Frankly, a hundred Elite-level monsters and a thousand Adepts in just the initial tunnel we entered alone should warrant a more organized and heavy force than just us.”\par
“So should we not contact the Burgher? Will he not want to know about the situation?”\par
“Yes… but then we lose out on the opportunity to make tremendous gains for House Firesword don’t we? Knowing the Burgher, hearing what we encountered initially would make him call the whole venture off and involve the military and other noble houses. He’s a cautious man, but sometimes a bit of daring is a good thing,” Orodan spoke. “I’ll even throw in whatever valuable monster corpses we find in here as a part of your share.”\par
“I concur with Mister Wainwright,” Gideon Fusturus, the Elite Alchemist said. “These natural tunnels could be a treasure trove of rare ingredients not easily found elsewhere. From what I see, even just the bodies of these centipedes contain fantastic ingredients, and in such quantity too! Truly, how did just the group of you kill such a horde?”\par
Gideon was among the non-combatants at the back, and so did not know just how powerful Orodan was as he hadn’t witnessed the battle directly.\par
“Will you truly be going alone though Mister Wainwright?” Gideon asked. “Perhaps you have some swift movement skill or ability to evade detection, but in a tunnel system where we’ve encountered Elite monsters at the civilized depths already… is that not a bit too much daring?”\par
“Yes, I’m confident I can manage. In fact, venturing alone gives me a certain sense of freedom that traveling alongside allies does not,” Orodan spoke, and his tone was final.\par
The Elite retainers were already convinced once they heard of Orodan’s offer to share whatever he found. And Gideon, while uncertain, was no combatant and the promise of further profits swayed him too.\par
With a final look over at the fortifications leading up to the mines, Orodan headed deeper down the tunnels.\par
\par
The expedition had tunneled into the side wall of a natural tunnel. To their right was a dead end, but it was to the left however that the tunnel extended deeper downwards, and the direction in which the survey team reported the Dothril deposits were.\par
Orodan went down this direction.\par
He traveled at a slower than usual pace, partly to ensure any hidden entrances, side tunnels and monsters were spotted. And partly because he somewhat enjoyed the strange and scary ambience of the caves. It was a stupid wish, but he always had a strange desire to fight something truly horrifying in a dark environment and prove himself scarier than it was.\par
The first fifteen minutes were spent moving through the tunnels, keeping an eye out.\par
It was after roughly twenty minutes that he encountered something. It was a centipede bigger than the Elites he had slain prior. It had fierce looking spikes growing out all over its body, and seemed to have a stronger plating of armor than normal.\par
It saw him and hesitated a moment, displaying a level of intelligence far greater than usual. It then turned and promptly attempted to flee, only for it to freeze as the Blessing of Agathor prevented its escape. Once it realized there was no way out, it instead charged straight towards Orodan.\par
A clash ensued, and while it was killed rather quickly, it was strong for an Elite, Orodan thought. Approaching the Master level. This variant was clearly superior to the regular Elite variants of the centipedes.\par
For there to be even stronger centipedes already? Orodan hadn’t even descended into the wild depths yet.The narrative has been taken without authorization; if you see it on Amazon, report the incident.\par
Thirty more minutes of exploration down the tunnel passed, which didn’t have any side tunnels, although it did have plenty of denizens. The centipedes he encountered were similarly powered to the near-Master one he had initially killed. A fact which was beginning to make Orodan think something wasn’t right.\par
Elite-level monsters were supposed to start appearing from the wild depths and downwards. For them to appear at the civilized depths already? It went against what he heard and was told.\par
Finally, he reached a larger chamber, where a hole was leading straight downwards. This chamber also contained a large amount of Dothril deposits, the metallic ore in the walls holding a subtle glow.\par
The only problem was, there were centipedes. The near-Master kind, and alongside them were some massive, fat centipedes which he assumed were a broodmother variant of some sort. These he surmised were at least the Master-level given their even larger size and the deadlier looking exteriors they possessed.\par
The chamber this hole was in, was truly massive, and yet these broodmothers themselves were quite humongous as well. Each being the size of a castle. In terms of size, each one was almost half the size of the hundred-headed sea serpent he had fought long ago. And he counted seven of them.\par
One of the Master-level broodmothers slowly approached him from in front of the horde and spoke. The strange sounds it made with its mandibles and mouth being converted into the universally understood language of the System almost immediately after.\par
“Surface-dweller. Why have you dared to invade our homes?” It asked as its mandibles clattered together in dangerous agitation. “We have not attacked you, and yet your kind decide to tunnel inside and slaughter our burrowers?”\par
As it spoke, the horde and other broodmothers behind it clacked their legs and mandibles together angrily.\par
Monsters were different from the mortal races. They usually didn’t begin to gain the beginnings of intelligence until the Elite-level, and while some gained it sooner, the absolute guarantee of intelligence was at the Master-level, where these broodmothers were.\par
All monsters at the Master-level could communicate with humans, if they didn’t, it was because they chose not to. Furthermore, the System’s ability for all races, species and cultures to understand one another also extended to them. The only prerequisite for communication then, was intelligence.\par
That a monster chose to speak to one of the mortal races in a circumstance like this, could only happen if the monster wanted something, or sought diplomacy.\par
“Well, from what the survey team tells me, your tunnels are awfully close to our mines. From the direction, it seems you’re burrowing closer and closer to the surface yourself,” Orodan replied. “We can’t have a horde of monsters assaulting our settlements above.”\par
Co-existence was possible only for certain species of monsters. The two races known for co-existence with monsters in the depths were dwarves and drow. But humans, which were the dominant race on the surface of the continent of Inuan, while often domesticating surface-dwelling monsters such as griffins, pegasi and dragons, absolutely abhorred subterranean monsters in general. If this hive of centipedes ran into the drow, perhaps an agreement of co-existence could be reached, but to encounter humans? In normal circumstances they would never be able to live alongside one another. Hence the lack of willingness to engage in negotiations until they had their backs pressed to the wall.\par
“We wish to be unrestrained and proliferate further upwards into the rock till we reach less… volatile territory,” the broodmother replied. “The vent of the world’s energy we are atop of, it goes very deep. Deep enough that some very old and terrible things slumber deeper down the shaft. We simply wish for a route, a safe passage in the event the one nearest to us awakens and decides to clamber upwards and annihilate us.”\par
Orodan deduced that this vent of the world’s energy sounded an awful lot like an energy well. He had heard stories of them. They were something coveted by nations, and for House Firesword’s mines to be above one… the Republic itself would now have a vested interest in ensuring the mines were secure and would want to step in.\par
Energy wells were openings on the surface that lead deeper into the ground, and at the bottom they usually lead to a vein of the world’s energy. Energy wells were a strategic resource that nations were willing to fight over, as they would empower the surrounding area in a way regular magic rarely could. They also were popular at attracting monsters which supposedly fed on the energy.\par
On the surface, monsters would often congregate around these energy wells, and towns built around a surface energy well would often have to deal with more frequent intrusions of monsters than otherwise.\par
But, from what Orodan knew, energy wells were supposed to have an opening leading out, being directly accessible from the surface.\par
The deeper the well went, the more potent the energy surrounding the well. With the most well known energy well in the Republic being the one at Anthus, which went all the way into the wild depths.\par
But for an energy well’s opening to start at this depth? Frankly, this energy well didn’t even seem to have an opening to the surface, and nobody would have discovered it if not for the mines above delving deeper to coincidentally be nearby.\par
Officially, by Republic law, all energy wells were directly under the purview of the Council of Karilsgard and therefore Republic property. Their existence, benefits which extended a decent distance, and the potential threats they carried, were too high in magnitude to be left to the ownership of a single noble house. They were a strategic resource which nations were interested in, and entire regions could have their economy influenced by the existence of one. It was no surprise then that House Simarji was able to have preserves of magical trees and plants in Jerestir.\par
The expedition now went from House Firesword hoping to keep things within their House, to a situation that would have to be disclosed and the Republic’s government involved. Especially if there were more, and stronger monsters deeper down the shaft. Orodan however, would try his best to ensure the Burgher and House Firesword got their fair share of this venture.\par
But, if this energy well’s opening started underground already… then just how deep did this energy well run? Perhaps the slumbering things this broodmother warned of, were best taken seriously.\par
“Just how deep down the ‘vent’ is the nearest monster? How strong is it?” Orodan asked, trying to glean some information.\par
“It is at least at the Grandmaster level… a deadly burrowing worm, responsible for killing the progenitor of our hive and forcing us to flee further upwards along the vent. It's at least five miles further down,” the broodmother replied as her mandibles twitched in fear. “This is useless information to you however, as reaching it involves going through us, and we are not willing to allow you to delve down the shaft and awaken that thing… or worse, till we can come to an agreement. Our destruction would be inevitable if you did.”\par
“And how do you plan on stopping me?” Orodan challenged. “I require the Dothril present in this chamber, it seems more valuable than regular Dothril too, likely from close proximity to the energy well.”\par
“We are not reckless surface-dweller. We have seen you slaughter our hive guards with ease, whichever tribe that can send a warrior like you forward alone as a mere scout… is not one whose ire we wish to draw unnecessarily,” the insect answered. “Given your personal prowess and the threat of reinforcements, we are willing to offer up the Dothril without any further conflict between us, as long as we can come to an accord.”\par
The broodmother was smart. It likely surmised Orodan was far stronger than he appeared and that Orodan was likely still holding back given his confident approach down the depths by himself. Plus, the threat of reinforcements couldn’t be ignored. Although, the broodmother would likely have a conniption if it knew Orodan was mostly the only one of his strength level in the organization that sent him.\par
“And what is this accord you want exactly?” Orodan asked. In truth, both he and the broodmother knew all the power in this ‘negotiation’ was in his hands.\par
“Killing the worm, continued protection and the right to remain here, in return you can mine the Dothril without any resistance from our hive,” the broodmother spoke. “You cannot mine the Dothril without causing enough noise to awaken the worm regardless, and our hive can offer you much assistance in burrowing new tunnels and knowledge of the creatures further down the shaft.”\par
The hive's unwillingness to fight in this main chamber made sense now. Perhaps a fight against Orodan here would draw the attention of the worm situated further below.\par
But it was a reasonable deal.\par
While Orodan could simply slaughter the hive right here and now… they were essentially surrendering and seeking to avoid total destruction. While they were monsters, they weren’t things that actively raided the surface and butchered innocents, from what he knew anyways.\par
Orodan felt it would be going against the spirit of the second Quest he had to simply slaughter surrendering monsters who hadn’t even been the ones to start the fight with him. They simply reacted to detecting the survey team tunneling into their homes.\par
And as unorthodox as it was for humans, House Firesword could learn to co-exist with subterranean monsters under their mines. The dwarves and drow had showed that it could be done. There was no reason it couldn’t be attempted by humans.\par
At least, this was Orodan’s thought process. While Orodan felt this was an advantageous deal for House Firesword, it could only proceed with the approval of the Burgher himself. He could bring this proposal forth to the man, but it hinged on his approval all the same. Furthermore, the bigger issue was how the Burgher was going to deal with the inevitable response and attempt at takeover from the Republic once word got out.\par
But for now… Orodan felt this was an acceptable offer.\par
“For now, tentatively I can agree to this,” Orodan replied, and as he got the sense that the broodmother didn’t like the ‘tentatively’ part, he clarified. “To seal the deal, how about I go down the shaft right now and confront this worm?”\par
“Alone? You may be strong, but even our entire hive of broodmothers and guardians could not slay it,” the chittering mandibles clacked. “Going in without allies would be arrogance of the highest degree! That creature is at least at the Grandmaster level!”\par
They argued a bit more after that, but in time the broodmother came to understand that Orodan would not be swayed on the matter. Eventually, they evacuated the chamber and went elsewhere down another branching tunnel their hive had burrowed, accepting that Orodan was going to provoke this worm by himself.\par
Its parting words to Orodan were filled with bitterness and a promise to flee towards the direction of the tunnels leading up to House Firesword’s mines if Orodan failed. In other words, the expedition he had left behind would encounter seven Master-level broodmothers leading a fleeing hive, which would later be followed by a monster at the Grandmaster-level. It was a logical threat made out of a sense of self-preservation, saying that they whether they floated or sunk, it would be together.\par
Orodan himself paid little heed to the chittering overgrown bug. He was excitedly looking forward to fighting whatever was down the shaft.\par
Everything about his idiotic venture would be decried by anyone of sanity.\par
It was common knowledge that the education system and official sources of news never confirmed or denied the existence of Master-level monsters. So, even just the existence of the seven broodmother centipedes he had encountered would already be of severe alarm to the authorities of the Republic.\par
But if what the monsters told him was true? That there was a monster lower down the shaft at the level of a Grandmaster? Some of the hidden powerhouses of the Republic might be forced to step in. They would likely prevent any and all non-government access to the energy well from then on. So Orodan’s best chance to fight a Grandmaster-level monster for the first time… was now.\par
With those thoughts, he approached the opening of the energy well. It was his first time looking down its depths.\par
It was, as the stories had described them. A big hole in the ground, with lines of glowing energy along the walls of the shaft.\par
It wasn’t a perfectly straight hole into the depths. It went downwards, but with curves and bends that prevented one from simply seeing all the way down and how deep it might truly lead. If it was truly straight, then monsters from the top could easily see monsters below and vice versa.\par
Thankfully, the bends and curves meant that visually, no terrifying monsters from below could see all the way up. Which allowed groups like the hive of weaker centipedes to evade notice and survive.\par
Still, Orodan descended down the shaft rather simply, by jumping in.\par
Falls didn’t hurt him at his level of power, and diving a few thousand feet till the landing which was at a bend, wasn’t risky. Perhaps if it was a straight tunnel, jumping right to the bottom and encountering some utterly unfathomable creature might be risky, but the well’s curvature made such a thing impossible.\par
After two bends, he started to see some side tunnels carved into the walls of the well’s descending shaft. They looked similar to the burrowed tunnels of the centipedes above, and Orodan guessed these were likely the previous homes of the hive, before their progenitor was killed by the creature he was currently seeking.\par
Not long after, he reached a section of the well that had a single massive side tunnel burrowed into it.\par
And perhaps a mile into this massive burrowed side tunnel… was the tail of something truly massive.\par
The worm situated itself near enough to the energy well that it could feed off the world energy, yet far away enough that it could flee if anything more powerful from below decided to venture up.\par
Smart creature.\par
Unlike Orodan, who decided to close the distance and launch as powerful of an All-Strike as he could manage towards its exposed tail.\par
He empowered the blow with everything he had. His sword was strengthened with Weapon Aura, his body empowered by Death Rage, and Eternal Soul Reactor was running at a level just below where it would interfere with his anti-divination skills.\par
And the blow, even quadrupled with his Action Increases… carved a massive gouge onto the worm’s tail… but that was all it did. Even as the surrounding dozens of miles of stone completely collapsed around him from the shockwave of the blow.\par
It’s hide was very tough, it had weakened the power of the blow he sent its way and the portion that had gotten through, while still wreaking decent damage upon its flesh… wasn’t a particularly large wound on a creature of its size.\par
From his encounter against the hundred-headed sea serpent in the Sea of Uxumar, and now, Orodan was starting to learn that certain monsters were far stronger than their mortal counterparts of the equivalent level.\par
This blow he launched, which would have killed or severely injured the equivalent level Adeltaj Simarji, instead merely carved a severe wound onto the massive monster’s tail. But that was merely all it was, a deep blow upon the tail section of a creature whose tail itself was at least a half mile long.\par
On a human, this would be the equivalent of cutting deeply into one of their toes.\par
Worst of all, the flesh immediately began throbbing and attempting to grow new hide over itself and repairing.\par
This worm… possessed a ridiculous amount of vitality that would make even the sea serpent quiver in fear.\par
Beating Adeltaj Simarji by no means meant Orodan could kill this thing with similar ease.\par
His surprise attack failed, and the entire earth trembled as the worm turned around, it’s eyes emitting a purple aura, which soon extended to its entire body.\par
Rocks began floating in the massive tunnels it called home and it opened its hideous mouth to let forth a screech of pure rage as it focused its eyes on the measly bug that was Orodan, less than a fly before its tremendous size.\par
He had heard many loops ago that Adeltaj Simarji was historically famed for fighting alongside a hero who was bestowed a Quest to slay a rampaging worm that was as large as a mountain range.\par
Orodan felt that this was the sort of worm that would be the subject of such a Quest.\par
And it was capable of gravity magic, given the hundreds of thousands of rocks that arose and immediately flew towards Orodan at horrific speeds.\par
A few seconds of this bombardment persisted before it became clear to the titanic worm that the unempowered rocks it was firing were having little effect on the pest that had dared attack it. Somehow, the rocks lost all efficacy and gravity magic empowerment the moment they touched him.\par
Orodan’s Mana Resistance was an unfair advantage against any creature that dared to use mana against him. Be they mage or Grandmaster-level monster.\par
Orodan then put a stop to the tactic entirely by using Mana Black Hole offensively. At the skill’s current level of 69, it was almost Elite. And for a Legendary rarity skill to be at such a level… meant it was monstrously powerful itself and was now capable of draining mana without needing to directly touch something.\par
The very magic in the air was pulled directly into Orodan. The rocks which were glowing with a purple magic immediately lost their empowerment, and the very air seemed to become a bit drier as the natural mana saturating the area was drawn towards the storage of his skill.\par
Even the colossal mana pool of the worm was beginning to be siphoned, albeit given the sheer amount of mana, worth more than many ancient war machines put together, would take a while to fully drain without direct touch.\par
In response the worm immediately charged right for Orodan, realizing that mana based abilities were not the way to go.\par
It would be a scene of awe-inspiring terror if seen from an outside perspective. A man, being charged at by a worm the size of a mountain range. All while Orodan stood among utterly ruined debris, the sea of shattered rock he was in only illuminated by his glowing aura produced from Eternal Soul Reactor.\par
But Orodan did not quail.\par
This worm, despite being at the Grandmaster-level, didn’t possess a hundred heads, and thus its only real option of physical attack was to charge Orodan like a battering ram and hope to splatter him against the rock, like an avalanche upon a single man.\par
As long as Orodan could get onto its body and endure… he could eventually win. His energy and willpower were endless.\par
His All-Strike, powered as high as he could charge it safely, met the absolutely all-encompassing tide of worm that was barreling towards him. It was as though he was a man trying to stand against an entire mountain falling onto him.\par
Of course Orodan’s All-Strike, even quadrupled, was overwhelmed.\par
Overpowering the human Adeltaj Simarji was nothing like facing the full physical might of a worm the size of a mountain.\par
If skills like Physical Fitness amplified the power of the mortal races to a great extent, then the titanic body of such a worm would have its power amplified to even greater heights. It was born with natural advantages a human didn’t have.\par
He was utterly smeared into red paste, and his Eternal Soul Reactor was forced to ramp its power up to a point where Fate Disconnect failed. It wasn’t the worst problem given the Blessing of Ozgaric he had obscuring him still, but the fact that he had to exceed this threshold meant that this battle had suddenly gotten very serious.\par
He began swiftly reforming from the glowing pile of meat he was smeared into, his weapons and shield utterly obliterated by the force of the attack that had overwhelmed him.\par
But he had successfully, even if he was overwhelmed, carved a decent gouge into the head of the worm as it charged him and he met it with an All-Strike.\par
And it was this gouge that he was reforming within.\par
The moment the worm realized Orodan wasn’t dead, it tried everything in its power to dislodge him. Unfortunately for it, Orodan recovered too quickly with his Eternal Soul Reactor empowering his Regeneration skill to scary heights. He reformed to full health in seconds.\par
Another full power, quadrupled All-Strike hit the existing gouge on the worm’s head. This time Orodan cared not for staying within a safe threshold, and the attack was consequently twice as powerful.\par
The gouge was carved deeper, and Orodan delved deeper into the flesh of its head.\par
Purple gravity magic attempted to coalesce around Orodan, but it found no purchase in manipulating him directly. In worse news for the worm, Orodan was now directly touching it and was draining its colossal mana reserves at an alarming rate, which would soon take away its ability to do magic altogether.\par
It now began to furiously thrash and ram its head into the tunnel walls in an utterly berserk manner.\par
“You dirty surface-dwelling pest! I have kept quiet and well-behaved to avoid having a Quest issued upon me by the meddling world, and yet your ever-encroaching kind still dares to attack me?!”\par
It roared in a booming explosion of sound that was nearly deafening. Orodan simply kept launching All-Strike after All-Strike into the wound on its head however.\par
After its one roar of indignation however, it said no more. Showing no intent to negotiate with Orodan or attempt diplomacy for its life.\par
Whether it was the stubborn sense of pride that most Grandmasters carried or the territorial feelings it had towards its spot near the energy well, it seemed intent on fighting for its life. Orodan never once felt his second Blessing of Agathor activate to signify that an opponent was blocked from fleeing.\par
Orodan was now within the worm, furiously launching destructive attack after destructive attack from within, but it still showed no signs of stopping, even as he was certain the entire tunnel came collapsing down atop them. It was nothing he or the worm were overly concerned about at their levels of strength.\par
However, it was an endless battle.\par
Every All-Strike he launched was responded to by the worm’s almost godly vitality forcibly repairing itself wherever he caused damage. Orodan had never felt or seen such utterly titanic life force in a single living thing before.\par
Furthermore, the worm seemed quite skilled in actually manipulating its own life force. Orodan was starting to feel additional vitality flood the worm whenever he launched an All-Strike, almost in tune and in preparation for his attacks. The vitality would retract just before he struck, and would immediately surge to the damaged area right after.\par
It was possibly the slowest battle of attrition against the most durable enemy Orodan had ever faced to date.\par
Throughout it all, he decided to treat it as a training exercise.\par
He began attempting to target All-Strike, not just to have as much power as possible, but to also try and cause as much damage to the very vitality of the worm.\par
After maybe two days of this he was rewarded with a message.\par
\textbf{[New Skill (Exquisite) → Vitality Destruction 1]}\par
This new skill shifted the balance, and the worm began thrashing about even more furiously in an attempt to kill him.\par
The worm didn’t simply accept its own death however, as it repeatedly attempted to throw Orodan out of its body. Often it would use gravity magic on itself to tear out massive swathes of its own flesh and create openings in its body that lead to Orodan.\par
More than once a chitinous spike would then attempt to fish about its own insides in an attempt to spear Orodan and pull him out.\par
But the attempts proved unsuccessful. The spikes were utterly deadly, but anytime Orodan was hit he would simply allow the spike to tear right through him and take entire limbs off and bisect him rather than allow himself to be dragged out.\par
This process continued, and Orodan began experimenting with getting a feel for the vitality of the worm, and somehow attempting to mentally command it inside of himself.\par
More time passed as the endless battle raged on and the depths trembled from the cataclysmic tremors of their battle.\par
Given that he was inside of a giant worm, he wasn’t entirely certain of how much time had passed, but he was certain at least two weeks had gone by as he kept tearing apart the insides of the massive worm.\par
He had truly made massive progress in whittling its vitality down, but even after so long he felt that he had only gotten it down to two-thirds. A long road lay ahead of him. And he had undoubtedly missed his entrance date to the Bluefire Academy by now alongside helping in Geldric Sunfire’s adventurer party.\par
But, finally he was making headway in understanding something all-encompassing about vitality and life force.\par
For so long Orodan had only had the chance to study the life force of only himself. His mortal enemies typically died before he could truly observe their vitality, and they didn’t have enough of it either.\par
This titanic Grandmaster worm however, had a level of vitality that even thousands upon thousands of Orodans could not match. It was almost godly. A naturally powerful body which was rich in vitality, which was likely amplified by many life force bolstering skills.\par
It was a great opportunity for Orodan to engage in extended observation, experimentation and meditation on his findings as he actively tore the worm apart from the inside.\par
Finally, as he quadrupled an All-Strike and sent it in four different directions at once, each direction corresponding to an area of the worm’s body with a different level of vitality… he made the connection. He sensed vitality for what it fully was.\par
Vitality, was produced by the body… but it was also ‘colored’ by the soul, influenced by it. Thus of course each being’s vitality was unique, different. His own vitality was different from the worm’s, as it was different from the sea serpent.\par
But… if vitality could be ‘colored’ by one soul… why could it not be influenced by another, and then stolen?\par
\textbf{[New Skill (Legendary) → Vitality Black Hole 1]}\par
He didn’t know why he was able to obtain the mana version of this skill much easier. Perhaps it was a matter of talent or luck, or even his first Blessing of Agathor which considered Mana Black Hole as being under its purview. But this new skill, Vitality Black Hole was earned through much more grueling battle and meditation than the other one was.\par
He pushed the energy of his soul outwards to corrupt and influence the worm’s vitality, the life energy that suffused its flesh. It attempted to resist, and it was strong at it. But the very quality of his soul energy was higher than normal. His was denser, more powerful now, and his willpower was endless and it naturally carried over to the energy of his soul which refused to yield as each iota of it clashed against the worm’s attempts to defend.\par
This was further amplified by Eternal Soul Reactor running at a furious pace, his body kept alive only through the Regeneration skill which was empowered.\par
And as he converted massive amounts of the worm’s life force to his own, he pulled it all inwards to himself.\par
It was utterly overwhelming.\par
He didn’t have a corresponding skill to resist excess vitality, and so some very uncomfortable growths began to occur along his own flesh at the utter deluge of life force flooding through him.\par
It wasn’t the bottomless reserve of his new Vitality Black Hole that was the issue, it was his crude control over vitality. He had no manipulation skill for it, and so the excess life force spilled into his own body instead of the reserve of the skill where it was packed away like the mana equivalent was.\par
He actively willed Regeneration to stop and his Eternal Soul Reactor churned at speeds he’d never brought it to before, simply to try and harm his own body to burn the life force entering him as it healed actual damage instead of causing strange growths all over.\par
Vitality Black Hole’s reserve was starting to slowly absorb all the colossal amounts of vitality Orodan was directing towards it, and the worm’s thrashing actually began to get slower as devastating amounts of its life force were stolen in horrific pulses that caused the tremors and noises of devastation in the rock to gradually lower.\par
Five minutes later, it spoke.\par
“Filthy surface-dweller… do not reach too deeply… there is far worse than I deeper down the well…”\par
Those words were its last, as its dying throes lasted for another minute before its body went completely still.\par
The wounds on it weren’t terrible, but they would not heal anymore. Its body simply lay motionless, lacking life.\par
\textbf{[Title Gained → Grandmaster Slayer]}\par
Orodan finally let out a sigh of relief as he sensed no more of the beast’s foreign vitality in his immediate vicinity.\par
What a brutal fight that was. He had been fighting for over two weeks at least. Who knew what the hells was going on up on the surface?\par
He tore his way out of the worm’s insides, which were now offered dramatically less resistance without any of the worm’s skills or vitality bolstering it.\par
Upon tearing a hole out, he realized he was of course, completely buried under rock. Which was an annoyance to deal with, but nothing his current level of strength couldn’t handle.\par
Breathing technically was needed once every few hours at his level of Physical Fitness, but with Eternal Soul Reactor and Regeneration, he didn’t need even that. So he slowly began tearing his way upwards through the rock using his bare hands.\par
As he began his slow burrowing upwards to the surface he couldn’t help but lament the fact that the centipedes who’d dutifully surrendered and come to an accord with him were likely killed. He held a slim hope that they escaped to another section of the tunnels they burrowed, hopefully out of reach, but who knew how extensive the cave-ins and collapses from his fight were?\par
Hopefully the expedition members and miners above at least evacuated. Human constructed tunnels were reinforced with additional wooden supports which were amplified by skills, so the tunnels should have held long enough for an evacuation.\par
After nearly an hour of swimming upwards through rock like a fish, he reached the dirt layer and his speed quickened, curious to see what the situation was.\par
The second he broke the surface, he saw people.\par
Lots of people.\par
Republic military, Capital Guard, noble houses, lots of Masters. And even a number of Grandmasters in the back. All looking at him.\par
“Well… if Burgher Ignatius is here, I’d like to let him know I’m alive and have partially succeeded in the task he gave me,” Orodan said as his neck downwards was still buried underneath dirt.\par


\section*{Chapter 16 - Receiving A Lecture \u0026 Being Sent To School}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 16 - Receiving A Lecture \u0026 Being Sent To School}%
\par
Given the sheer response he saw arrayed around him, Orodan presumed whatever the side effects of him fighting a Grandmaster-level monster were… it was a big deal.\par
“Orodan Wainwright! You live?!” Burgher Ignatius Firesword shouted from a distance.\par
The man looked worried and as though he’d aged ten years with the stress he was under. Next to the Burgher was an aged looking man in a simple tunic. A furled weapon strapped across his back.\par
“Yes Burgher, I survived my scouting mission into the tunnels,” Orodan replied with a cheery grin. Burgher Ignatius looked as though he wanted to clap him on the back and also strangle him.\par
Behind the Burgher and the old man were the retainers of House Firesword. It was good to see they had made it out in time.\par
But most importantly, the bigger part of the crowd was all the various Masters and powerful old people with dangerous auras standing near the back. Adeltaj Simarji stood among the group of elderly, signifying they were all Grandmasters, and there were six of them present. And of course, there were plenty of Masters too, including the golden griffins of the Council.\par
The High-Burgher of the Council of Karilsgard, Sarvaan Ilsuan Arslan was also present. And while this might have been impressive to Orodan once upon a time, he could now easily kill hundreds of the man if he wanted. The position of High-Burgher was nothing but a nominal title, and as Orodan had come to learn, the actual powers, the Grandmasters, weren’t interested in playing the game of elected councils and appearing important to the public eye.\par
“Orodan Wainwright… so this is the boy who ventured deeper into the depths by himself on behalf of our house?” the old man next to Burgher Ignatius asked.\par
“Yes ancestor… this is him, the young man who I’ve decided to sponsor for the Bluefire Academy,” the Burgher replied. “His talent at the examination center in our county was extraordinary.”\par
“Hm… burrowing up with your bare hands through how many miles of rock to reach the surface requires strength,” the unknown old man said. “Let me guess… at least 60 Physical Fitness?”\par
The old man was scarily close to the accurate number. Orodan was currently at 65 in his Physical Fitness. Was this what hundreds of years of experience looked like?\par
Orodan neither confirmed nor denied the man’s question.\par
“Either way, you’ve done well to risk so much for House Firesword. I’m sure little Ignatius here will reward you well after, but for now, we’ll have to trouble you to speak with your elders,” the old man spoke and then turned to the High-Burgher. “Have everyone else disperse.”\par
The man essentially ordered the High-Burgher, and the man complied without a whit of complaint. Soon, Orodan found himself standing in front of eight very old people. These were all Grandmasters of the Republic.\par
He could beat one, maybe two at once given his recent performance against a Grandmaster-level monster. But even with his recent increases in power he didn’t hold confidence in beating all eight of them yet. And who knew the differences in strength even at the Grandmaster level?\par
Adeltaj Simarji said once that he was only a Grandmaster in a single skill. Perhaps someone here was more than just that. Orodan hadn’t tested himself against a dual-Grandmaster yet.\par
“So… I take it this audience is to do with my unannounced trip down some natural tunnel systems?” Orodan asked.\par
“Unannounced trip he says! Heh… I like him Adeltaj, standing before old fogeys like us and he still talks so casually,” one of the old men said. “Let me steal him from you.”\par
“Tease him later Kuonthus,” old man Adeltaj Simarji, the only familiar face in the group replied. “Besides, he isn’t even mine per se, my house isn’t the one that sponsored him for the academy.”\par
And Orodan had to wonder if the elderly man had told anyone about their destructive battle deep into the Aenechean Forest in which he had bested the old Grandmaster in a fair fight.\par
“Yes, this has to do with your trip… specifically with the energy well you stumbled upon,” the leading old man said. “We’ve suspected it for a while now but hadn't gotten around to forming an expedition… tell us what you saw as you descended the hole.”\par
“Well, I descended the hole, met a hive of centipedes who I decided to make peace with, but then ended up encountering something very big further down the energy well. At least the size of a mountain range if I recall,” Orodan answered. “I fled shortly after encountering it, and it must’ve woken up or maybe it got into a fight with one of the other monsters deeper down that the centipedes warned me of.”\par
Adeltaj and an old woman frowned at him as he said this.\par
“Boy… that Blessing of yours blocks all perception of your soul, so I cannot even ascertain whether you’re telling the truth,” the old woman spoke up. “But your story sounds like hogwash all the same. The tremors and earthquakes started over two weeks ago, and then once they stop you manage to crawl out of the ground and claim you fled the monster?”\par
Orodan had to admit, his ability to come up with a convincing lie on the spot was pathetic.\par
“Varna, the lad is stronger than he looks… perhaps he simply took time to ascend the surface?” Adeltaj added, and while Orodan was grateful he didn’t feel his story held up whatsoever despite the ancient Simarji’s support.\par
The old woman, Varna, gave Adeltaj a suspicious look. “Do you have some sort of prior history with the boy Adeltaj? Being able to ‘flee’ a Grandmaster-level monster… don’t tell me he’s part of the reason we have that massive crater in the Aenechean Forest near Velestok?” she asked.\par
Adeltaj chose not to comment and that made the eyes of the Grandmasters take on a calculating gaze.\par
“Incredible… the Goddess will want to meet with you young man, why don’t you come with me and we can properly train you?” one of the yet unnamed old men asked. “I’m Heredin Aeronsul, Chosen One of our Goddess Ilyatana. The Blessing that Ilyatana has given me allows me to peer past the unknown Blessing you have shrouding you… but if you would lower that shield you have over your fate, perhaps we can come to work with one another.”\par
This man was intrusive. And he was a Chosen One.\par
Chosen Ones were people, usually at the Grandmaster or above level, who had three Blessings from one particular God. Furthermore, they were the very strongest champions a God had on the mortal plane, and were the living executors of their will.\par
The power of an Avatar depended on the host body the God was possessing. And if a Favored such as Lady Lakshiya could host an Avatar that was strong enough to swat away Grandmasters like pests… then Orodan didn’t want to find out just yet how powerful an Avatar descending unto their Chosen One was.\par
He had seen them fighting the Eldritch Avatar in Guzuhar, but hadn’t experienced their wrath for himself yet. Compared to this man before him… Lady Lakshiya was nothing.\par
“Aeronsul… cease your meddling, he is under the protection of my house,” spoke the leading old man who seemed to know Burgher Ignatius. “You cannot simply go around throwing your weight as a Chosen One around without care.”\par
“For someone at his age to be so powerful… the Goddess insists that I find the answer,” Heredin spoke, and then glared at the Firesword Grandmaster. “Blocking my way when the Goddess herself communes with me and demands it… would be heretical. I simply wish to see what exactly is it that makes him so strong… did he really kill the monster outright?”\par
A tense standoff occurred between the two Grandmasters for a moment, until Heredin Aeronsul finally was the first to break his gaze.\par
The Chosen One of Ilyatana looked as though he was receiving communion from his Goddess and didn’t like what he was hearing.\par
“Tch… have it your way Firesword…” the man muttered. “A brash bully like yourself is suited for being Agathor’s Chosen.”\par
Agathor’s Chosen?\par
With those words, Heredin Aeronsul turned away and departed, and following him was the old woman known as Varna. They seemed to be part of one faction if Orodan’s limited intuition for politics was correct.\par
To the side, Adeltaj Simarji, the old man known as Kuonthus and this Firesword Grandmaster seemed to be another group. The remaining three Grandmasters were seemingly unaffiliated, and soon they broke away with some parting words.\par
“That was some argument they had upstairs huh? Malzim tells me that they’re still arguing with one another!” the leading elderly woman of the unaffiliated three Grandmasters spoke. “We’ll leave you to your affairs then Arvayne… try not to scare the boy overly much.”\par
The parties shared a nod, and then the three unaffiliated Grandmasters also left. And now the man who he pieced together was known as Arvayne Firesword, a Grandmaster and Chosen One of Agathor, was looking right at him.\par
“Alright then young warrior, how about you now tell me what really happened?”\par
\par
There were strength differences between even Grandmasters.\par
Adeltaj Simarji for instance, was a regular Grandmaster, but he was on the cusp of pushing a second skill - his active combat skill which was Phoenix Thrust - to level 100. This made him quite powerful, and Orodan was sure he wasn’t the benchmark for an average Grandmaster. He would become quite monstrous once he passed the bottleneck and hit 100 in that skill.\par
The average Grandmaster would be someone like this friendly and jesting man known as Kuonthus Vexelthun. He was a newly advanced Grandmaster, having reached level 100 in Shield Mastery a hundred years ago. He also looked comparatively less decrepit compared to the other two before him who were older looking.\par
In truth, the word ‘average’ was difficult to use when talking about Grandmasters, as they all had different secrets and tricks up their sleeve. People at the Grandmaster level, due to living for so long, typically had a plethora of high rarity skills which they never disclosed, and these skills at high levels could create nasty surprises for anyone who underestimated them. So, who knew what secret abilities even the ‘average’ Grandmaster like Kuonthus possessed.\par
But if there was an average, then there was a category of the exceptional. Orodan had already met one such exceptional Grandmaster in the northern continent of Guzuhar. The dragon, Cyvrosdyr the Eternal Winter, a World Guardian and triple-Grandmaster.\par
But Cyvrosdyr was technically a monster, a creature born with gross advantages and capable of absorbing world energy. What would an exceptional Grandmaster of the mortal races look like?\par
The answer was Arvayne Firesword. The triple-Grandmaster Chosen One of Agathor who was currently hearing him explain the entire situation he was in. If the Republic had a competition for who was the greatest warrior within it… this old man would be near the top. The furled up weapon on his back, shaped suspiciously like a greatsword, also told Orodan that it would be a while until he could ever hope to trade blows with him.\par
“Hmm… an Eldritch Star descending… a Quest regarding it, your enmity with the Goddess of Fate, and this time loop situation you seem to find yourself in. Did I summarize the main points of your situation correctly?” the old Firesword asked and Orodan nodded. “I see that you’re also prodigiously talented with two Mythical skills, something I’ve never heard of before. I understand how you acquired them and the hard work you had to put in… but… why are you so stupid?”\par
“What?”\par
“Not to disrespect you young man… but my lord Agathor would absolutely adore you. Which is meant as a backhanded compliment about your intelligence,” Arvayne explained. “I have so many criticisms to make about your course of action throughout the loops that we could sit here for another hour.”\par
“Wait a moment… aren’t you supposed to approve of my course of action given that you’re a Chosen One of Agathor?!”\par
“Agathor is the God of War… but there is a more strategic and intellectual side to war than even my lord cares to appreciate,” the Chosen explained. “Agathor is flexible about how the results are obtained as long as war is waged and battles are fought with honest zeal. I’m almost two-thousand years old and have been commanding armies and pioneering tactics for much of that time. Having an executor of his divine will capable of some thought beyond mindless battle, is of great benefit to my lord.”\par
“So… you’re a tactician? A general? How does someone sit at the back of a formation and claim glory in Agathor’s name?” Orodan asked.\par
“And who said a general cannot lead from the front? The history books speak of a flaming greatsword leading charges into the thick of battle while also subtly directing formations, executing stratagems and most importantly… managing logistics before and after.”\par
Orodan couldn’t help but be a bit flummoxed. The Chosen One of the God of War wasn’t what he was expecting. He thought someone with the demeanor of himself would be more likely to be a Chosen of Agathor. But, it made sense.\par
This venerable elder before him… not only lived and breathed war and battle, but also studied and meditated on it in a more intellectual sense too. Who knew how much of the tactics used in warfare today were pioneered and developed by this man over the course of his life?\par
“So then… what have I been doing wrong so far?” Orodan asked, his mindset finally shifting into one of humility and willingness to learn and see where he could do better.\par
“Before I start allow me to clarify that your work ethic, the stubborn drive that pushes you to die thousands of times to acquire simply a single skill, is excellent. You have the spirit of a true warrior,” the old general explained. “But your decisions throughout the loops could use some work… such an utter lack of efficiency…”\par
“How so?”\par
“For starters, how did it take you this long to consider getting a formal education? Surely Adeltaj has explained to you by now how important it is to know of the world?” Arvayne rhetorically asked. “Your progress could have been doubled if you simply knew where to go, the most efficient way of going about things, and whatnot. For instance, instead of wasting time trying to train your Mythical skill against an Avatar - which is incredibly dangerous given their ability to permanently damage souls - you could have simply fled to Guzuhar immediately and trained there, but even that wouldn’t be necessary if you’d just thought to approach the Chosen of any other God but Ilyatana and maybe Halor.”\par
“My experience with Gods had been rather negative till that point,” Orodan tried to justify.\par
“A negative experience with the tyrannical Goddess of Fate does not necessarily mean the same with the others,” the elder calmly spoke. “Did you never stop and consider that it was only diviners of Ilyatana and her faithful that were tracking you during those loops? Did you never think to approach a Chosen of Agathor or any other God for protection?”\par
“I didn’t know who the Chosen were… even the existence of Masters was but a rumor when I was growing up,” Orodan admitted.\par
“Something you are thankfully looking to rectify now. If you had a formal education, you would know of where to go and what to do. Facing down an Avatar by yourself at your level… did not need to happen. You have time, and there are ways to train against divine energy that involve less risk of permanent soul damage.”\par
“And what are some of those ways?”\par
“Finding artifacts that channel divine energy and using them as a training aid to resist the divine energy. It’s how I trained myself to channel Agathor’s energy better for when he descends unto me as an Avatar,” the Firesword explained, and Orodan admitted he could see the logic in it. “There are museums and vaults that hold such artifacts, you could have broken in, stolen it and fled at your level of strength.”\par
“Should you be advocating such things?”\par
“You’re in a time loop, laws and morals are a relic of your first life which will only hold you back. You must do what you need to in order to succeed young man. Do you think we Grandmasters got to where we are by perfectly following every little rule and law?” Arvayne asked. “I had to seize every chance and lucky opportunity that came my way, even if it meant stepping on somebody else.”\par
Ruthless, Orodan thought. But then again, he grew up the same. Killing another boy over food was something he had done before the time loops. Who was he to disagree with this philosophy.\par
“Anyhow, you should have trained your Eldritch Resistance in a similar manner… you nearly experienced a permanent end in that loop from what you tell me. Did it not cross your mind to try seeking out some naturally occurring Eldritch creatures in the deep depths and beyond before you were to encounter an Avatar of multiple Eldritch Gods?”\par
“It… did not,” Orodan had to admit. His habit of simply rushing into situations like a charging goat wasn’t exactly efficient he was learning.\par
“Frankly, some form of Psionic Resistance should have been one of the first things you prioritized once you realized you were in a time loop. Mental attacks are one of the few things alongside soul damage that can cause lasting harm in your situation. That Mythical skill you have that churns your soul is a mere stopgap measure, you should immediately prioritize the Soul Defense skill.”\par
And so on the lecture went.\par
Arvayne Firesword was a fair critic. His methods of training in the loops for each skill were complimented for the things he’d done right, but also criticized. And Orodan felt as though the criticisms outnumbered the praise.\par
But Orodan couldn’t even protest as every single thing the ancient Chosen One pointed out was entirely logical.\par
Orodan initially thought to argue that the old man’s critiques were steering him into too safe of a direction for growth, that he wouldn’t have gotten to where he was without a sense of daring and willingness to take risks. But the man then countered by saying that the danger wasn’t the issue, it was the lack of efficiency and direction.\par
He was chided for not trying to obtain several basic active combat skills such as Lunge, Multi-Strike and Taunt, which would have amplified his battle power further since energy consumption wasn’t an issue for him. He was further chastised for not attempting to combine skills to make a skill of higher rarity, something Orodan didn’t even know was possible.\par
These critiques all tied back to Orodan’s lack of a formal education which would have taught him that such things were possible, and in an academy the teachers would have actively worked with him to unlock new skills and combine them given his level of talent.\par
“If anything, this loop is incredibly important. You’re actually going to be receiving an education for the first time and once you have it, it will multiply your rate of growth dramatically. New skills, potential skill combinations, items which bolster and aid in training, alchemical potions, rare treasures and training areas… you haven’t used any of these things before,” the old man explained. “It boggles my mind how utterly impossible your talent is to make it this far and have so many skills at such absurd rarities without even training efficiently. If you had an education earlier… imagine the heights you would be at now.”\par
Orodan was both thoroughly shamed and praised at the same time.\par
He always felt that academies were institutions with books and learning and had nothing to offer him that he could not obtain through battle and hard work.\par
But… if they instead taught him the knowledge of what he could do to multiply his rate of progress? Perhaps receiving a formal education would make a real difference for Orodan.\par
“Thank you for your guidance… truly… but I missed the date I was supposed to start. I was fighting the worm for two whole weeks,” Orodan replied, and the old man could only shake his head.\par
“The Bluefire Academy accepts new students year-round. Especially if they’re as monstrous as you. Your entrance date will not be an issue, rather it will draw attention as someone entering late implies they’re an exceptional talent.” Arvayne Firesword explained. “But you’ll have to moderate your strength at least somewhat lest you kill anyone or cause me headaches as I have to make up some excuse that you’re a reincarnator who hasn’t fully unlocked their memories. Beating Masters is ludicrous but within possible expectations, but avoid beating any Grandmasters in public. And try to avoid making too many ridiculous breakthroughs in front of other students, your progress will skyrocket rapidly with proper support and guidance. So try to do most of your experimentation in the private training chambers.”The narrative has been illicitly obtained; should you discover it on Amazon, report the violation.\par
“Then… you’re going to help me with this situation moving forward? Why?”\par
“Even if you weren’t in a time loop, a talent like you in my house is an auspicious occasion. Ignatius is a good lad, but he lacks potential. The Firesword name has lacked anyone strong for a while and I tire of watching the house stagnate as it has without even a Master to its name,” Arvayne explained. “But mainly, the descent of that Eldritch Avatar you speak of is concerning, if it truly did destroy everything after a year as you said… then it’s in my best interests to ensure you grow strong enough to beat it. Agathor has also decreed I assist you to this end.”\par
“And I won’t have to worry about Ilyatana hunting me down?”\par
“Agathor is the strongest of the Prime Five. Moving forward, find me in Karilsgard in each loop, explain your situation and prove your claims and her meddling will not trouble you.”\par
“So all those loops I spent trying to desperately find some way to hide myself from the eyes of a Goddess… I could’ve just sought out a Chosen of Agathor?” Orodan asked, both the old man and himself. Could the solution truly have been so simple if he had known what to do?\par
“Yes, and that’s why an education and knowing about the world is important. So many problems you had could’ve been solved far more efficiently if you simply knew the common things that an academy will teach you,” the ancient Arvayne explained. “But make no mistake, the lessons you learned and the hard work you put in were quite valuable in their own way. Some of the skills you obtained… I’ve never heard any documented methods of acquiring. The academies are fantastic tools… but they also spoil the youth and hand them everything without any adversity at times. In this regard, your low beginnings and being forced to learn the value of hard work are the biggest advantages you have. Do not allow the silver spoon of the Bluefire Academy to make you lazy and complacent.”\par
“Of course not, nothing can compare to the rate of progress gained from life and death battles and pushing myself to the very limit with dangerous experimentation,” Orodan immediately replied. “Can I even call myself a warrior if I allowed myself to slack?”\par
“You would be surprised how often people are spoiled by a bit of flattery and pampering,” the old man spoke. “Now, let us go over more particulars about this time loop and what some good courses of action might be.”\par
“I’m surprised you so willingly believe me,” Orodan remarked.\par
“Agathor verifies the oddities such as him not recalling giving you two Blessings. And your power is impossible. Even the strongest reincarnator I’ve known wasn’t as strong as you at this point of his life. A time loop is the only explanation that makes sense,” the elder Firesword answered. “Now then, let’s talk about what your next steps will be.\par
\par
The discussion lasted for another hour. Adeltaj and Kuonthus exchanged pleasantries and had left quickly once Arvayne Firesword began earnestly lecturing Orodan, citing some poorly thought out excuses as though they were desperate to get away.\par
He was instructed about how to best approach certain problems. He was given a brief rundown on who to avoid and what the political relations of House Firesword were, and who the associated hidden powers behind their enemies were.\par
For starters, the Chosen One of Ilyatana, Heredin Aeronsul, was also a triple-Grandmaster, although old man Arvayne was confident that not only could he defeat Heredin in a regular fight, if both were empowered to Avatar state he would also beat Ilyatana’s faithful. House Aeronsul also mainly held its base of power in the Eastern regions of the Republic, whereas House Firesword and Volarbury County were closer to the Capital. So Orodan's odds of running into House Aeronsul's operations or territories were low.\par
But it wasn’t Heredin Aeronsul who Orodan was cautioned to be most wary of. It was someone who hadn’t shown up as response to Orodan’s earth-shaking battle with the worm.\par
House Rockwood were known rivals of House Firesword. A while ago they had attempted to come by Burgher Ignatius’s manor and bully him, only to be turned away by the presence of Arvayne Firesword.\par
House Rockwood was an aggressive house with plenty of powerful Elites and unconfirmed Master-level individuals serving in the Capital Guard and the Republic military. They were always attempting to greedily expand through coercion, poaching talents and bullying. People they offended in the process were smoothed over via bribery, or appealing to friends in powerful places. They were possibly the house that had expanded the most since the Republic’s formation. They operated under the leadership of Alarduin Rockwood, the nominal head of house. And protecting them was another Chosen One.\par
The hidden powerhouse behind them was a Chosen One of Halor, the God of Life and Nature. Alcianne Rockwood.\par
Arvayne outright admitted to Orodan that in a fight between himself and Alcianne Rockwood, Arvayne did not hold the advantage. The woman was a healer and unarmed fighter of incredible power, and her healing in tandem with her wrestling and unarmed abilities… made her a fearsome foe to battle.\par
While Arvayne and Alcianne themselves didn’t have any conflict or rivalry, the same couldn’t be said of their houses. So Orodan was cautioned about going too far and provoking House Rockwood to call upon their Grandmaster-level powerhouse. He was told that House Rockwood would certainly attempt to test and provoke him given their rivalry with House Firesword.\par
As for the problem of the Eldritch Avatar, Arvayne told him that Agathor would be working on mobilizing the Prime Five to head to the northern continent to lend their aid against this dire threat near the end of the year.\par
Orodan could only wait and see if the addition of five more powerful Gods and their Avatars would make a difference in the battle in this loop.\par
About the time loop and his training itself, Orodan was given a brief list of who some important people were to contact and given a long and extensive paper list of what potential skills and fields of study he might focus on and what their benefits might be. Some of the esoteric fields and skills, he didn’t even know existed!\par
And naturally, he was told to keep the fact that he was in a time loop, a secret. Currently only Adeltaj, Arvayne and Kuonthus Vexelthun were the three people who were aware of this aside from the God of War himself. Arvayne assured him that the three of them were allied and that Orodan needn’t worry about the information getting out. And if it did, Agathor’s protection would still prevent any Avatars of the Prime Five from descending.\par
Then came the issue of his level of strength. While the other Grandmasters who left and were coerced into not pressing the issue by Arvayne would have an inkling of Orodan’s strength, they would be fed the lie that Orodan was a reincarnator who had yet to awaken his memories and also had a powerful Bloodline and Blessings from Agathor. This would explain Agathor’s interest in him to outside eyes.\par
But, Arvayne Firesword still cautioned him against actually revealing his level of strength. Currently, the logical assumption was that he had been empowered and been host to an Avatar to defeat the worm. And it would be in Orodan’s best interests to play along with this assumption and let the Grandmasters assume it was the reason for his strength. This theory also played into Agathor’s interest in him via Arvayne, and the assumption would be that he was a powerful Favored of Agathor, which was in a sense true as he had two blessings from the Inuanan God of War.\par
Finally, from what Orodan was told, the collapsed tunnels leading to the energy well would slowly be excavated and the path rebuilt, albeit with a proper joint expedition composed of Republic military and powerful Grandmasters. Even Arvayne would participate when the time came. The energy well was simply too important of a resource to let lie, as one that extended so deep could have rare resources at the lower levels that even Grandmasters would like to get their hands on.\par
Until then, and while the excavation worked, the depths would be under constant monitor by a team of Elite earth mages with a high level in Seismic Sense, to ensure that no unwelcome intruders decided to burrow upwards from the well. Which would be unlikely given that monsters preferred soaking in the rich density of world energy nearer to the well.\par
In somewhat good news though, Arvayne had managed to argue that since Orodan killed the worm underneath, the corpse would go to House Firesword and due to them clearing out the centipedes and actually discovering the well, the Dothril deposits in the chamber where the well’s opening was… would also go to House Firesword. Which was a tremendous gain of wealth for the house and would pay back Orodan’s sponsorship a hundred times over.\par
Sadly, there was no word on the centipedes who’d struck an accord with him. Orodan could only hold slim hope that they had made it out elsewhere through the other branch of tunnels they took before he went down the energy well. He resolved to get strong enough to kill the worm without causing such collateral destruction in future loops.\par
“I believe that will be all. I haven’t spoken this much to someone in a while, and I tire of this and wish to go back to my meditations,” Arvayne said. “Your new start date for the academy is tomorrow, everything has been arranged by Ignatius at my command.”\par
“I… am grateful. You’ve told me so much, I don’t think I’ve ever learned as much from anyone as I have you,” Orodan sincerely spoke. “Is there any way I can repay this favor in the future?”\par
“Bah, just find a way to kill that thing descending from the stars and I’ll consider it more than repaid,” the old man brushed off. “I wouldn’t complain either if you decided that helping House Firesword in future loops was a priority.”\par
“Honestly, your house gives me a luxurious level of freedom. The Burgher doesn’t question my background or insist I reveal my Status. I don’t think the Capital Guard or military would allow me the same leeway if I were to accept their offers of sponsorship,” Orodan replied. “Just the convenience alone would make me want to associate with the Fireswords every time.”\par
Arvayne and he exchanged a few more words before he left Orodan be and finally every Grandmaster had left the area. But there were still many Elite and Master-level individuals around, and Orodan decided to cross the distance and walk up to the House Firesword group to finally speak to the Burgher himself.\par
The man looked frazzled, as though the stress of the events had added ten years to his face.\par
“Burgher, apologies for the interruption. As I was saying, I partially succeeded in the task you gave me,” Orodan said with a smile, and the Burgher looked as though he was going to explode.\par
\par
In truth, Burgher Ignatius Firesword, who was merely at the level of a powerful Elite, was not an individual who could meaningfully lecture Orodan. He couldn’t have before when Orodan showed how easily he could best regular Elites, but now?\par
Now when rumors were abounding that he slew a ferocious monster underneath the mines and discovered an energy well? That he was the cause for the tremors that had lasted for more than two weeks? That the Grandmasters had muttered whispers of him being host to an Avatar?\par
Under such heavy scrutiny and the investigation around the tremors the Elite retainers of House Firesword had also been interrogated about the situation, and as much as they wanted to keep a secret, when the Grandmaster Arvayne Firesword asked them of what happened and people with lie detection skills were present… they could only begrudgingly add their own details about how Orodan had slain the horde of centipedes by himself.\par
Truly, his attempts at remaining under the radar in this loop had gone to the hells.\par
But, regardless of the difference in personal power between the two of them, Burgher Ignatius seemed to have faith enough in Orodan’s character that he gave him a worried lecture about staying safe all the same. It was almost touching.\par
“Anyhow, I trust you will exercise prudence from now on Mister Wainwright… if I might speak honestly, my house cannot afford to lose a young man as powerful as you, not to such risky ventures,” the Burgher spoke with a serious tone. “The Firesword name has stagnated for too long, and people are now talking about us from all the way in Karilsgard thanks to you.”\par
“Oh? And what are they saying?” Orodan asked.\par
“Our supporters and those who have pleasant acquaintanceship with us are of course speaking highly of the talented young man who will help revolutionize the banner of the flaming sword and spread our power to the capital itself. Somewhere we’ve never really had a strong foothold in aside from my duties as one of many members of the council,” Burgher Ignatius answered. “But those with a… lukewarm disposition towards House Firesword are muttering that we’ve gotten lucky and that you’re a golden goose who won’t stay with a ‘failing house' such as ours for long.”\par
Personally Orodan felt the ‘failing house’ comment was a bit exaggerated. House Firesword was rather well known and powerful within Volarbury County… but who knew? Maybe it said something about their power that they simply let House Argon run rampant in Ogdenborough inside their county for so long.\par
“Well, I have no interest in going anywhere else for the time being, and wherever I do go it will be with the interests of your house in mind,” Orodan answered, and the Burgher’s face lightened. “You and the old man have done a lot for me.”\par
“On the topic of the ‘old man’, I believe the honored ancestor spoke to you about the arrangements made for your slightly delayed entry to the Bluefire Academy?” the Burgher asked, and Orodan nodded. “Good! It’s as he said, I’ve made arrangements for you to enter tomorrow. A griffin straight to the academy and your own personal student guide will be waiting for you. As for classes, you need not worry about missing the first two weeks. The faculty have been informed and you’ll have personal tutors assigned to you. Your lodgings will be befitting of someone of your stature as well.”\par
“This all sounds a bit much Burgher… you know I’m not fond of making grand entrances even if I agree to them for your sake. But personal tutors and rich lodgings too?” Orodan asked.\par
“My young friend, such things are merely part of what the Bluefire Academy offers to its students. Are you perhaps concerned about the costs? Don’t be,” the man explained. “The tuition fee at Bluefire is extravagant, and every student at that academy is either a talent well-worth cultivating or the child of very wealthy nobility who can afford such a good education for their progeny.”\par
Orodan was starting to realize now that the stories he heard of academies growing up were about the ones that were bottom barrel or middling. The name Bluefire was spoken of as though it was a fairy tale, and nobody he spoke to in his first life had ever met someone associated - even tangentially - with that academy.\par
It was the finest academy in the Republic and world-renowned for a reason. Their alumni counted several famous and powerful individuals. And students often went on to become members of prestigious organizations or work in highly specialized and lucrative fields.\par
A part of Orodan, the uneducated bumpkin, still felt as though he was stepping into a fantastical story of wonder when he dwelled on the fact that he the orphaned street rat from Ogdenborough would be attending the Bluefire Academy.\par
He came from the lowest of beginnings, but he had come far. However, despite the time loop a small part of him still recalled the days when he was but a young man dreaming of reaching the Adept-level over the course of his life and then butchering the harpies around his town so he could sleep restfully.\par
He didn’t need to sleep anymore, which was strange. The System and skill levels allowed for some incredible things, but Orodan had never quite paused to reflect on the fact that he could destroy ten miles in a single All-Strike nowadays thanks to all his skill levels.\par
Sometimes it felt as though he was a rat in a wheel, running furiously so that the contraption would light up further. But Orodan didn’t mind being the rat who ran non-stop, and seeing the contraption run brought him joy.\par
For Orodan, being the stubborn and driven rat who ran like a rabid beast… was a point of pride. His upbringing had taught him that hard work was the only thing that could change his lot in life.\par
Even as he starved while a street rat, even as he fought with the other children for scraps before he was finally enrolled in the orphanage, and even when he still struggled while under their care due to the poverty of the town… his Status and skill levels were the one constant he had.\par
Getting pummeled by the guards of House Argon, stealing from the vendors around town, intimidating the other children into getting what he needed to survive… and killing another boy his age in an alleyway for a stale piece of meat. It was all a part of who he was, his desperate struggle to survive and secure a better lot in life for himself.\par
And most importantly, all this had taught him that his skill levels would go up the worse the experience he went through.\par
Tomorrow, he would show these coddled rich youths from wealthy families what the difference between him and them was. To them, an education was something to advance themselves, a natural course of their lives.\par
But for him who had nothing and had struggled like a desperate dog for so long without any real direction? An education would be a world-shaking multiplier.\par
He would take every advantage of this opportunity that he could get.\par
But before that, it was time to pay someone an impromptu visit.\par
\par
The rays of dawn shone through the windows of the master bedroom in Eldragon manor, illuminating the cup of tea in his hand as he sat across from pleasant company.\par
Orodan didn’t know why he had a preference for women with strange and mysterious demeanors, but here he was sitting across from the mystifying and charming Katareya Eldragon.\par
“I don’t think I’ve ever had tea before,” Orodan remarked. It was strangely sweet, but with a hint of… something herbal underlying it?\par
“Tea in the mornings is a somewhat dear tradition in this household,” the woman replied as she sipped on hers in a dainty manner. “And I would be a poor host if I didn’t offer a cherished guest a cup.”\par
“Your children aren’t here today?” Orodan asked while trying to ignore the heat creeping up his neck at the way she emphasized ‘cherished guest’. There was certainly a lot of cherishing the night prior.\par
“Not so. Novus is at the academy and little Luci is off apprenticing with her blacksmith master. It is a day of the work week after all,” she remarked with a teasing smirk which implied Orodan too would have work to get to today. “Of course, with both of them gone it can get lonely in the manor on working days. So your company is appreciated darling.”\par
He returned her smile and spoke. “Lucifreya apprentices under a blacksmith? I… didn’t quite picture her working with metal when we first met.”\par
“Well, if your gaze wasn’t so focused upon myself at the party once I spoke, you might have noticed the roughness in her hands and how awkwardly she fit into that dress,” Katareya spoke with a teasing smirk which caused Orodan to clear his throat in embarrassment. “Truly… to think I actually dressed her up with the intent of catching your eye… some things are best left to the experienced it seems.”\par
Orodan had an inkling that her daughter was the one intended to try and woo him, but it still caught him off guard for her to so brazenly admit to it in front of him.\par
“Oh, don’t give me that look,” Katareya lightly scolded. “It’s a common custom to try and tie powerful people to a family. Even where you grew up, did you not have at least one or two people talking about their daughters to you? I simply do away with the pretense of pretending it doesn’t happen.”\par
Which was a fair point. Orodan could recall long ago being spoken to by his neighbors about how a hard-working young man like him should have friends, and their daughters and sons happening to approach him shortly after. Not that those situations went anywhere aside from perhaps one brief tryst he had with the tailor’s daughter.\par
“You’re not wrong,” Orodan muttered while still embarrassed. “Anyways, I almost forgot to ask, but which academy does Novus attend?” he asked, trying to steer the conversation in a less flustering trajectory, which Katareya caught onto given the smirk on her face. But she mercifully let him move on.\par
“The same one you’ll be going to dear boy,” she answered. “He’s a second year student at the Bluefire Academy. He’s doing quite well too, although not at the point where it becomes news-worthy.”\par
“Ah, you heard about that?” Orodan asked. They hadn’t talked very much when Orodan had decided to visit last night, so the actual conversation about the events in Jerestir was being broached now.\par
“Given how Lady Lakshiya essentially ordered us all to delve deep into the threads of fate and scour it for any trace of one Orodan Wainwright, I would say I more than just heard of it,” she answered. “The Lady isn’t usually so zealous in giving out an order, so it can only mean her senior must have directed her to do so. Caught the attention of a Chosen One have you?”\par
“You seem awfully calm and accepting of this, shouldn’t you be attempting to divine me as we speak?”\par
“I’m off the clock until another two hours, and that would just be impolite,” Katareya explained with a delightful smile. “And I try not to make a habit of non-consensually divining combat specialists who are sitting right in front of me. Even if it’s a sweet thing like you… such a habit isn’t good for the life expectancy of a diviner.”\par
Orodan wouldn’t think of hurting Katareya, but he had to admit her line of thought was logical. Orodan was a warrior, a combat specialist, he was the one called upon to battle and fight foes. But not everybody in society was a combat specialist.\par
Lady Katareya Eldragon was an Elite-level diviner of the Cathedral… but she was a diviner. Her combat skills would undoubtedly be of a low level, and she likely knew and accepted her place in society as a non-combatant.\par
To her, offending a combat specialist like Orodan would be a rather foolish move without anyone of equivalent power around to protect her. The daily life, social position and norms of someone like her who wasn’t a fighter… was different to Orodan. In a sense, they could be said to live in two different worlds.\par
Orodan’s world was one where he would brashly approach people with little regard for manners, and if they fought, so be it. Fighting was what he did. Even before he was strong, he was still daring and reckless.\par
Katareya Eldragon’s world however was a different one. It was a world where she had to navigate complex social relationships and power dynamics, remain aware of politics and always watch how she spoke lest she offend someone who could simply kill her. Her deceased husband was a fighter, but an Elite only, which meant she still had to maintain a sense of caution and decorum. She had a certain amount of protection under the Cathedral, but combatants among the faithful couldn’t always be around, and there were limits to how far their protection extended if Katareya were to hypothetically offend someone too strong.\par
Orodan’s personal strength then, was a freedom, a privilege he earned through his might. Most people in society didn’t have the privilege to speak as freely or act as recklessly as he did, even without a time loop being brought into consideration.\par
“You look as though you have a lot on your mind. Do you perhaps think I fear you harming me?” she asked. “Worry not, you seem like a young man of good character, and I like to think I’m a good judge of it.”\par
But Orodan felt uncomfortable the longer he dwelled on it. He had killed… a lot of people. His entire existence was battle, violence and bloodshed or perfecting better ways to engage in it.\par
Even in his first life he had killed a boy over a piece of stale jerky. He didn’t understand how or why Katareya felt so safe in having a dalliance with him. Even in the way she spoke to him, it was a big risk she was taking. Perhaps seducing him was her own way of being daring and seeking to expand within the system of social bounds that a non-combatant like her was in? It was the most thinking on social and power dynamics that Orodan had done in a while.\par
“You… are a rather daring woman huh?”\par
“I beg your pardon?”\par
“Nothing… don’t mind me. I just feel as though I got a glimpse into another world for a moment,” Orodan answered, and Katareya’s narrowed eyes told him that for once, it was her that was caught on the backfoot at not being able to understand someone.\par
“Hmmph… well it’s good to see you actually thinking and using that brain of yours young man,” she haughtily said in an attempt to recover. “You’ll need it for the academy, given that you have at least two weeks of classes to catch up on.”\par
They spoke for a few more minutes as they sipped the excellently prepared tea, and finally the sound of a griffin’s wings beating could be heard approaching the manor.\par
“As delightful as this rendezvous has been, I must go now Lady Katareya,” Orodan said as he rose from the chair. “I believe my ride to the academy awaits.”\par
“Ah, how time passes when one is having a good time,” she remarked. “Do tell Novus his mother misses him won’t you?” she asked and then not so subtly winked at him.\par
Orodan would not be telling Novus that, and he ignored her teasing request and amused smirk.\par
As he exited the Eldragon manor and made way for the two griffins waiting for him on the landing zone outside, he mentally called forth his Status.\par
He now had three Elite-level skills, and his Status was looking monstrous and would only grow more so.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Grandmaster Slayer}\par
\textbf{Title 2: One Who Has Experienced Death}\par
\textbf{Title 3: Sword Elite}\par
\textbf{Available Titles: One Who Has Experienced Death, Sword Elite, Shield Adept, Physical Adept, Unarmed Combat Adept, Grandmaster Slayer, Wrestling Adept, Cleaning Apprentice, Woodworking Apprentice, Wielder Of A Mythical Skill}\par
\textbf{Rewards: Permanent +3 Action Increase}\par
\textbf{Skills: Sword Mastery 70 (Elite), Mana Black Hole 70 (Elite - Legendary), Unyielding Vitality 70 (Elite - Rare), Unarmed Combat Mastery 69 (Adept), Shield Mastery 69 (Adept), Death Rage 69 (Adept - Exquisite), Combat Mastery 68 (Adept), Physical Fitness 65 (Adept), Weapon Aura 64 (Adept - Rare), Iron Body 64 (Adept - Exquisite), Pain Resistance 63 (Adept), Bleeding Control 62 (Adept), Damage Mitigation 61 (Adept), Power Strike 61 (Adept - Uncommon), Dying Struggle 59 (Adept - Uncommon), Eternal Soul Reactor 59 (Adept - Mythical), Soul Manipulation 58 (Initiate - Rare), Psionic Resistance 58 (Adept - Exquisite) Impregnable Bladewall 57 (Adept - Exquisite), Perfect Parry 56 (Adept - Uncommon), Wrestling 53 (Adept), Shield Throw 53 (Adept - Uncommon), Evasiveness 48 (Apprentice - Uncommon), Mana Resistance 44 (Apprentice - Legendary), Eldritch Resistance 43 (Apprentice - Mythical) Tool Mastery 43 (Apprentice), Woodworking 41 (Apprentice), All-Strike 41 (Apprentice - Legendary), Impact Resistance 39 (Apprentice), Wood Communion 38 (Apprentice - Legendary), Cleaning 34 (Apprentice), Surprise Attack 32 (Apprentice), Sprinting 31 (Apprentice), Fate Reading 31 (Apprentice - Uncommon), Regeneration 29 (Initiate - Exquisite), Laboring 29 (Initiate), Mana Manipulation 26 (Initiate - Uncommon), Construction 21 (Initiate), Vitality Destruction 21 (Initiate - Exquisite) War Cry 20 (Initiate - Rare), Slashing Resistance 19 (Initiate - Rare), Piercing Resistance 18 (Initiate - Rare), Club Mastery 15 (Initiate), Soul Strengthening 14 (Initiate - Legendary), Lightning Resistance 14 (Initiate - Exquisite), Lumberjacking 11 (Initiate), Parkour 11 (Initiate), Fate Disconnect 13 (Initiate - Legendary), Maintenance 8 (Initiate), Vitality Black Hole 8 (Initiate - Legendary) Intimidation 7 (Initiate), Repair 7 (Initiate), Thievery 6 (Initiate), Deception 4 (Initiate), Pathfinding 4 (Initiate),}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor, Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark, Death’s Call - Whenever you will it, Death takes you, Trickster’s Veil - Your Status, fate and soul are impossible to peer into unless you will it]}\par
He left his titles as is. Given the Blessing of Ozgaric upon him he wasn’t concerned with anyone being able to peer into his Status or his soul which blazed like a beacon to anyone with Soul Sense.\par
His Status was monstrous, but now it was time to see just what insane growth he could achieve in the greatest academy in the Republic.\par
If he had come so far without any proper education, guidance or external resources. Then what could he do with countless teachers, training aids, rare resources and items that would bolster his growth?\par
It was time to find out and get a formal education in the Bluefire Academy.\par


\section*{Chapter 17 - The Bluefire Academy I}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 17 - The Bluefire Academy I}%
\par
Based on his reputation in this loop, he could be considered famous. But fame was inspiring to some and intimidating to others.\par
And the accompanying griffin rider - an Elite retainer of House Firesword who hadn’t tagged along on the expedition in Jerestir - hadn’t met Orodan and gotten to know him firsthand. To the man, Orodan was a distant and awe-inspiring figure who was rumored to be a Favored. Consequently his escort was rather subdued and elected to spend the ride in silence as his and Orodan’s griffins soared through the skies towards Karilsgard.\par
Which suited Orodan just fine as he spent the time meditating on Eternal Soul Reactor.\par
In a few minutes, he saw glimpses of it.\par
There was another massive mountain that stood between Volarbury County and the Capital. This meant that wherever Orodan went within the county in his loops, he never quite got to see the spires of Karilsgard in the distance as the mountain would be in the way.\par
But now that their flight had gotten past the tall mountain for the first time?\par
He saw it.\par
And it was the biggest city Orodan had ever seen. Easily ten times the size of Vorskard in the northern continent.\par
Massive spires and towers the size of smaller mountains, glowing lights and so so many people. The city was surrounded by walls which were almost as tall as some of the smaller towers, and many of the towers and buildings had walkways connecting them to other tall buildings and at some points even to the walls themselves.\par
It was incredible.\par
And in the center of the city he could see it looming over everything, almost as tall as Mount Castarian. It was the Spire of Karilsgard, the tallest building in the Republic of Aden and one of the tallest in the world.\par
He saw various other famous landmarks and buildings.\par
The utterly massive Cathedral of the Prime Five. Surrounded by five massive statues of the Gods the size of castles. The splendorous Palace of the Council of Karilsgard, where the rulers of the Republic convened. And the commercial section, which glowed with such bright lights even in daylight and had such crowds of people flitting through that Orodan thought it alone held more people than the entirety of Volarbury County . Frankly, he thought the city itself likely outnumbered the surrounding few counties in terms of total population.\par
A few million people in Volarbury County? That was nothing before the likely tens of millions Karilsgard held.\par
Orodan now understood why House Firesword would want to hold some influence here. This place was a population center and base of power of titanic proportions.\par
As the griffins flew past the walls Orodan noticed tall towers with mages on them who were performing the task of monitoring air traffic in and out of the city. There were also various anti-air defenses and lethal looking siege weaponry atop these towers, with a tower being present every half mile of the walls. Archers, peltasts and mages were present in force upon every tower.\par
Any assault upon Karilsgard would face heavy resistance. The city’s defenses were prepared diligently and honed over a long period of time. Orodan felt that even an Avatar attempting to assail it would find a formidable amount of firepower sent their way, and who knew what other esoteric defense systems the Capital had in place?\par
Finally, as the griffins passed the Palace of the Council, Orodan was able to see the ethereal blue flame atop a tower behind the Palace.\par
This was the main tower of the Bluefire Academy. It was situated behind the Palace of the Council and located right in the center of Karilsgard.\par
The academy itself was at least half the size of Trumbetton, with a ludicrous amount of buildings and people frolicking about between them. Near the tower, was a truly spacious open area with multiple pillars of blue fire surrounding it. This was the landing zone for all aerial traffic and it looked large enough to accommodate even Cyvrosdyr if the mountain-sized World Guardian ever decided to land here.\par
They were directed to land, and before they did his escorting rider spoke. “Sir, it’s been an honor to escort you this far. It would be improper for someone like me to land, so I must turn back. The academy’s staff will look after you from here,” the retainer spoke, and then then gave Orodan a formal salute and turned his griffin in the opposite direction and flew off.\par
The pomp and social customs felt strange to Orodan, but who was he to argue?\par
His griffin touched down onto the ground, and now that they were within the bounds of the academy proper Orodan noticed the academy itself had an air traffic control tower which was subtly helping guide griffins to the ground.\par
But there was another flying creature on the landing zone as well… a pegasus! Two of them to be precise.\par
Pegasi! Orodan had never seen them before! He had heard stories of them being more common in the Eastern Kingdoms and down south in the peaks of the Dokuhan mountains where the dwarves had their mountain holds. But actually seeing the lustrous white winged horses was quite something compared to simply hearing stories about them and the famed pegasus knights of the Eastern Kingdoms.\par
The owner of the two pegasi - a dark skinned girl - looked at Orodan’s enraptured gaze and approached him with a smile.\par
“Is this your first time seeing a Pegasus?” she asked with a friendly tone and Orodan nodded. “They are rather shy creatures and take time to warm up to any potential riders, but I dare say they have far more personality and intelligence than the griffins in these lands do!”\par
“Personality? How so?” Orodan asked as he dismounted his griffin and it then promptly flew off back towards Trumbetton. “I’ve only ever ridden griffins a handful of times so far, so I don’t have much to compare with.”\par
“Not to say the griffins you ride in the Empire and Republic aren’t cute creatures, but a pegasus is akin to a dragon and gains intelligence once it reaches the Adept-level. Compared to griffins which gain intelligence at Master-level like any other creature, the difference is quite stark,” she explained. “Olsinius here for example, can talk to you… if he cares to.”\par
“And I do not care to at this time,” the pegasus remarked with a grunt that the System translated to the universal tongue. It caught Orodan entirely off guard as he was unused to a talking mount.\par
“You can talk?” he asked.\par
“You… have you never met an intelligent being that wasn’t human before?” the pegasus asked with a grunt of indignation. “Of course I can speak!”\par
“I’ve met a dragon that could talk, and a worm too, although it wasn’t too friendly… and centipedes,” Orodan began listing off. “I’m aware that intelligent creatures exist… I just wasn’t aware that pegasi were a species of advanced intelligence akin to dragons.”\par
“Well consider this a lesson then, I’m not one of those mindless griffins you people ride around like slaves,” the pegasus, Olsinius replied with neighs and whinnies. “Us pegasi gain intelligence around the Adept-level. My younger brother here will soon become capable of speaking in a few months as well… although he’ll be akin to a child for some time initially.”\par
It was quite interesting Orodan thought. While he knew monsters - which non-mortal species such as pegasi were technically classified as - gained intelligence at differing points depending on their species; Orodan learned today that this intelligence went through a process of growth similar to how human children would learn to talk.\par
“What arrangement do you have with your riders then? Do they ask for permission? Do you have designated work hours?” Orodan bluntly asked.\par
“How do you function at a job? Does your employer ask for your permission before putting you to work?” the mouthy pegasus fired back with a grunt.\par
“Well… sometimes, yes? At my old job, I was often expected to follow orders without being given a choice in the matter,” Orodan replied, thinking of his militia days in Volarbury County. “My sergeant wouldn’t exactly ask for my permission before giving me the order to deal with something.”\par
“While it’s not quite like what you military and guardsman types are used to, it’s more like a civilian job that you would be at liberty to leave,” the winged steed explained. “She’s managed to sweet talk my younger brother into becoming her companion… so I begrudgingly accompany them and ensure his training is proceeding well.”\par
“Pegasi engage in training? That’s quite familial of you to aid your younger brother.”\par
“Do you humans not engage in training? Is it shocking to consider that other intelligent beings would also hone their abilities?” Olsinius remarked with a tone of annoyance. “While I would have accompanied this heavy-hooved sibling of mine regardless… the elder of my clan bade me go as well, if only to ensure this girl remains safe during her education at this academy.”\par
“Speaking of! I don’t think we’ve been introduced! I apologize on behalf of Olsinius, he’s grumpy but he cares about his brother and I,” the girl interjected. “Mahari Ilya Vedharna at your service! I hail from the Kingdom of Ravastaran in the East, and I’m here to study alongside my older brother.”\par
“Orodan Wainwright,” he replied while extending his hand, which the girl shook with vigor. “I’m here to get an education, House Firesword is sponsoring me.”\par
“Wainwright… Wainwright…” Mahari muttered to herself. “Sounds familiar, I feel like I heard a bunch of the older students saying something about that name. But I don’t keep up with the rumors and gossip much, so I’m sorry I can’t be of more help!”\par
“That’s more than fine by me,” Orodan replied. “I prefer to keep my head down and focus on my work as well. Say… why are you waiting at the landing zone anyways?”\par
“Ah, I’m waiting for my older brother to return with his pegasus Ostronor. He went to grab some harder to find ingredients to mix into the feed. He says it’ll make them stronger,” Mahari explained. “I don’t want to keep you if you’ve got somewhere to be though! He’ll take a while to get back, especially if he’s getting into arguments over the quality as he always does…”\par
With that Orodan nodded and bade her and the grumpy Olsinius farewell as he began walking towards the academy proper.\par
He was told he’d have a personal academy guide, but since he landed Orodan hadn’t seen anyone waiting for him specifically. There were groups of students and staff scattered about on the large and straight path to the academy tower, but nobody appeared to be keeping an eye out for him.\par
He kept walking until a small and unassuming voice interrupted him.\par
“M-mister Wainwright?” a female voice spoke.\par
Orodan looked to his right to see a woman he would almost mistake for a child based on her stature. Short, wearing glasses that covered nearly her entire face and a comically oversized book in her hands.\par
“Yes?”\par
“I apologize sir… I wasn’t aware of what you looked like and this is my first time being an academy guide. I-I’m Lucille Carrotfoot, I’ll be helping you get situated today,” she introduced herself and spoke in a shy and nervous voice that had Orodan feeling somewhat bad for her.\par
Her words were quiet, but not quiet enough however. His conversation with Mahari was in an area of the landing zone where nobody was within earshot. But now that they were on the path to the tower there were plenty of groups walking to and from or simply hanging out waiting for people. And at the mention of the name Wainwright many pairs of eyes suddenly flocked to him.\par
“Wainwright? I heard he’s the one who-”\par
“This is the guy who-”\par
“-grandfather says he discovered the energy well-”\par
“-monstrously strong!”\par
Were among the brief snippets of gossip and chatter Orodan suddenly began hearing about himself. Fame could be useful for some, but given Orodan’s experience with it in his loop in the northern continent he preferred being away from the center of attention.\par
Which he was doing a poor job at this loop given how everyone was now looking at him, some faces in the crowd having calculating gazes, some awed, some stand-offish as though he threatened their own sense of self-importance by existing. And poor Lucille looked mortified at all the attention she was getting for walking around with him.\par
“Perhaps we can walk a little faster and make way for wherever I need to register?” Orodan asked, as much as for his own sake as for Lucille’s.\par
She gladly complied and they walked as fast as her little legs would allow. Orodan hoped to avoid too many people coming up to talk to him as it sounded profoundly exhausting and he would rather get to training and learning.\par
Thirty seconds later however, the inevitable happened.\par
“Excuse me, are you Orodan Wainwright?” asked a young man, who looked the same physical age as Orodan. Red hair, green eyes and a confidently assertive demeanor. “I must say it’s an honor to meet someone like you. I’m Elucian Arslan, of noble House Arslan. You may have heard of my uncle, the High-Burgher who leads the Republic’s council? I believe he responded to Jerestir when the fight between you and that fearsome monster caused tremors felt all the way in Tooksten County.”\par
Elucian and his group of followers confidently approached Orodan, like hawks swooping for their prey. The Arslan’s tagalongs seemed almost mindless in their following of him, and Orodan would admit he felt a magnetic pull of charisma from the young man, likely a social skill. One Orodan easily ignored.\par
“Yes, that would be me. And I’ve seen your uncle and that big hammer he carries. Can I help you?” Orodan asked. “I’m in a bit of a rush to get the administrative parts of my arrival settled.”\par
“Ah, but that’s simply no problem at all. How about I show you around to where you need to go?” Elucian asked confidently and likely flared his social skill as he saw even Lucille begin to seriously consider the idea.\par
“That won’t be necessary, I have a guide already and I’m more than happy with her,” Orodan replied and he saw the inklings of frustration on the Arslan’s face, something which he immediately schooled thereafter. “We really should be going, no?”\par
Lucille looked almost dazed as Orodan spoke to her, finally snapping out of whatever impact Elucian’s social skill had. “I-if you insist m-mister Wainwright…” she meekly replied.\par
“I do.”\par
“Before you go Orodan, hope you don’t mind the informality by the way,” the man remarked in a self-confident manner that implied he had every right to call Orodan by his first name. “You really should stop by the Helmward Hall on the academy grounds sometime. It’s the most popular spot on campus to grab a drink and a bite to eat. I think you’ll come to find that making friends is an important part of the experience here at the Bluefire Academy, and it’s important to make the right sort.”\par
Orodan didn’t push the almost cocky man on what ‘the right sort’ was, but he did nod and quickly made his exit.\par
With some distance made between them, Orodan spoke. “Who even is Elucian Arslan? He gave me a slimy feeling.”\par
“H-he’s not slimy!” Lucille defended suddenly. “He’s one of the best leaders seen in generations! He’ll definitely become High-Burgher one day himself.”\par
“Oh? He wants to become High-Burgher like his uncle?” Orodan asked. “A lofty goal, but social skills alone won’t make him powerful enough to lead a nation and step in when the Republic’s enemies need to be reminded of its strength. How strong is he?”\par
“He reached Elite-level by the time he was a second year!” she passionately exclaimed. Perhaps she fancied the man? Or maybe it was the effect of his social skill, but her defense of him was the most spine he’d seen her show thus far.\par
But being an Elite really wasn’t as impressive as she made it sound. At least by Orodan’s standards. What was Elucian's battle-power? Could he fight at least a tier above? These were the factors that separated the greats from the average, and Elucian had a long way to go if he wanted to step into the boots of Sarvaan Ilsuan Arslan, who was on the high end of power even by the standards of Masters.\par
That being said, Orodan could understand why Lucille emphasized Elite as though it was so important. Unlike other academies, the Bluefire Academy did in fact teach its students at higher levels that the Master rank existed and gave them a slightly more comprehensive rundown of society’s power structure. But reaching the rank of Elite was still considered impressive and likely the height of what many students at the academy would ever achieve. To them, the Master-level was what they would dream of. Unlike any other academy where reaching the Elite-level was considered an incredible success story. In Bluefire, some monstrous talents entered the institution at the Elite-level, such as Orodan himself.\par
Therefore, to say Elucian was an Elite… was to say he was a real talent among the student body.\par
Orodan decided not to press the issue any further and simply continued the trip towards the tower in silence. Apparently the first floor of the massive building was where new arrivals would register.\par
Thankfully, no more people decided to interrupt them. Either they were too intimidated by Orodan’s reputation, or they saw him talking to Elucian Arslan and thought they weren’t of the requisite stature to speak to someone like that. Whatever the reason was, Orodan was thankful.\par
Up close, the tower was truly massive. It was the second tallest building in Karilsgard after all. The massive double doors leading inside were open at all hours and they had two golden armored Capital Guard captains standing guard around the clock on either side of the doors.\par
They entered the gargantuan structure, and within Orodan saw thousands of students and staff on just the first floor alone. There were actual teleporters with signs saying they lead to different floors of the tower and campus, and there were plenty of administrative desks, and the walls were adorned with flyers for various products, services and even programs and activities organized by the academy or the students themselves.\par
The administrative desks had a small line leading to them and there was a Capital Guardsman managing the queue as people walked up and directed them to various lines depending on what they needed.\par
“G-greetings, I have Mister Orodan Wainwright here, for registration,” Lucille thankfully whispered to the guard.\par
The guard’s reaction to hearing the name wasn’t subtle. His eyes snapped to Orodan and his posture suddenly became a bit straighter.\par
“Right this way sir,” the man ushered, and Orodan was directed to the back and made to bypass the line entirely. Something which caused a few angry mutters and looks of curiosity as to who he might be.\par
“I’ll be waiting for you outside Mister Wainwright,” Lucille said as they separated. Orodan wondered if she didn’t have her own classes to attend.\par
He was then directed to a desk at the back where an older man sat, the placard on the desk noted him as a supervisor.\par
“Mister Wainwright! It’s good to have you with us,” the older man spoke. “I’m Karthic Bushnell, day shift supervisor for the academy’s administrative department. We’ve heard a lot about you in the past two weeks, the Bluefire Academy is glad to accept a talent like you as one of our students.”\par
“Thank you, I hope to get to learning as soon as I can,” Orodan replied.\par
“Then I shan’t delay you sir, this will be quick,” the man spoke.\par
And then Orodan was treated to a unique display of telekinetic magic where papers and pens animated themselves magically into filling out forms while the man didn’t move a muscle. Various papers floated right in front of his face as he read them, and the only thing Orodan saw was a glowing tattoo on the man’s hand light up as the magic occurred.Stolen from its original source, this story is not meant to be on Amazon; report any sightings.\par
“Curious about the body enchantment Mister Wainwright?” Karthic asked. “While I wish I could say I was skilled in Telekinesis, the truth is the enchantment does all the magical work while I direct it with my mind. It’s a common mana-based body enchantment given to our administrative staff, both in the academy and throughout the Republic.”\par
The man was rather forthcoming with his explanation, correctly assuming that Orodan had never seen it before. Which was appreciated.\par
“Does it drain your mana pool when you use it?”\par
“Quite, but the drain is negligible when the items lifted are of such light weight,” the man replied. “I also have a mana battery in my drawer that I can lay my hand upon to slowly recharge my reserves. Lasts me the entire work day.”\par
“I see… how skilled would someone have to be in order to carry out body enchantments? Is it still the Enchanting skill involved?” Orodan asked.\par
“Good question and one that speaks as to your inquisitiveness and thirst for knowledge,” the man praised. “The answer is, it depends on the enchanter. As you’ll learn here, there are often multiple skills which can achieve the same result. The enchanter who worked on my telekinetic body enchantment is Master Gormir Eltros, he teaches many of the higher-level Enchanting courses at Bluefire and also services important clientele outside of the academy. He’s rather famed for being one of the few to have unlocked the Living Enchanting skill and his work on body enchantments is therefore a touch superior to any regular enchanter you’d find who uses merely the Enchanting skill.”\par
“Fascinating…” Orodan muttered, but he meant it. He hadn’t even registered and yet had already learned about a field he didn’t even know existed. “How common are body enchantments?”\par
“They’re more common than you would think, plenty of craftspeople use them for convenience in their trades much like how I use mine to aid in managing paperwork.”\par
“Yes, but how common are they among warriors and mages? Among combat specialists that is,” Orodan clarified.\par
“Ah, you’ll often see some people capable of limited flight, or their body becoming tougher mid-battle even though they aren’t mages. While I’m not as knowledgeable on the affairs of battle as you are Mister Wainwright, I assure you that they’re used extensively in combat, even if their use isn’t broadcasted often since… clothing tends to cover the enchantment up.”\par
“No wonder I never saw any glowing marks on all the Elites and Masters I’ve killed so far… I don’t know if what they used was a skill or an enchantment… although I did kill a Master with a glowing fiery sword once…” Orodan muttered. And perhaps it was a bit too loud as he saw Karthic visibly gulp and his face take on a more nervous and subservient look.\par
“You must have quite the decorated record as a warrior Mister Wainwright!” the man nervously praised a little too quickly. And Orodan had to remind himself that not everyone was a combat specialist. Going around casually talking about how he’d killed Elites and Masters would probably make any non-combatants nervous, as casual as the act was to Orodan himself.\par
“Erm… thank you. On a different note, do you know if it’s possible to create enchantments and body enchantments that are powered not by mana… but perhaps vitality or soul energy?” Orodan asked. It was a question he had ever since he spoke to an enchanter for the first time at the Burgher’s welcoming party.\par
“That I’m afraid, is something I wouldn’t know much about. I’ve heard the topic bandied about occasionally and know that we follow the Imperial tradition of mana-based enchanting here in the Republic. But aside from telling you that blood magic is heavily regulated I’m afraid I can’t be of much help. Perhaps you can choose to sit in on the classes offered by a Master? At Bluefire anyone can sit in on any class as a spectator, or even participate at the discretion of the teacher.”\par
“I see… I might just do that,” Orodan replied.\par
Soon, the conversation turned to silence as papers were shuffled and written upon by magically animated pens. He was asked some brief questions about his background and asked to put down a signature which magically copied onto every document.\par
Finally, he was handed a schedule.\par
His classes would mainly be during the day time, and included such things as ‘Soul Defense 100’, ‘Applied Skill Combinations 410’, ‘Warrior Skills 100’, ‘Mental Defense 100’ and ‘Monster Studies 210’. Of course, the ‘Politics 100’ and ‘World History 100’ were rather pointless additions Orodan felt.\par
The number denoted the course code, with numbers in the 100s meaning they were first year courses, and 400s meaning fourth year for example.\par
“Who even decided on this schedule? I can’t say I look forward to studying politics and world history…” Orodan complained.\par
“It’s usually decided by your benefactor, but let’s see here… signed by…” the man spoke, and his face then went paler and Orodan could see the beginnings of sweat upon his forehead. “…Arvayne Firesword.”\par
“That old man… I suppose I can’t complain. He does have some good advice and this is a direction I also agree with but… do I have the option to add more courses at least?” Orodan asked.\par
“Of course! Your benefactor graciously left quite a few free periods for you to slot courses into,” Karthic answered. “You can choose up to four more courses, although this might leave your days rather packed.”\par
Which wasn’t a problem for Orodan. He didn’t need to sleep or do anything else unless House Firesword called upon him, so frankly… he could even pick overnight courses and cram up to eight more if he truly wanted. But for now he would leave the overnight free for personal training and experimentation after the day of classes.\par
“Alright then… I want classes on Alchemy, Enchanting, Blacksmithing and Woodworking.”\par
And the administrator’s jaw hung agape.\par
“A-are you sure Mister Wainwright? For a martial student to take so many crafting related courses… not that I would presume to know better… but would your benefactor approve and not perhaps say you’re spreading yourself a bit thin?” Karthic asked. “For example, given your talent, why not take ‘Combat \& Sparring 434’? Surely there is much to be learned?”\par
“I won’t gain much by beating up the students and instructors,” Orodan casually replied, which caused the man’s face to pale even further at the revelation of his strength.\par
“U-understood… I’ll have the 100 level courses for all of those slotted into your free periods as well.”\par
After that, the registration didn’t last much longer and Orodan was handed his new schedule, and he was also handed a sealed letter which his benefactor had left for him, to be given to him upon registration.\par
He opened the envelope to find a written list from Arvayne Firesword detailing all the potential places and people that would be of use to him, and a comprehensive list of skills, professions and fields that he could dabble in. There was a small note at the bottom to take his reading seriously and to not approach things stupidly.\par
Orodan mentally cursed the old man for the insult and emerged from the back offices to find people were now staring at him and muttering. Word apparently reached the tower about who he was. Fantastic.\par
Before he could leave the tower and meet up with Lucille just outside, a burly man stood in his path.\par
“You must be the mighty Orodan Wainwright of House Firesword!” the man bellowed. “I’m Claridin Rockwood, how about we have a friendly duel?”\par
“Certainly! Want to fight right here?” Orodan asked, all too happy for a fight. Avoiding a duel was unfathomable to him. He loved fighting.\par
Even Claridin seemed taken aback by his casual and instant willingness to fight and now had his guard up.\par
“Well… a duel right here would be impolite to everyone around wouldn’t it? How about we settle this here with a different sort of competition if you’re so eager to compete,” the man suddenly backtracked a bit. Who knew if he was wary of Orodan now that he’d shown no concern? “We each take turns delivering a blow to the other, whoever quails first is the loser. Rules are simple, no divine assistance.”\par
Claridin had likely heard the false rumors of him possibly being host to an Avatar and of course felt he had no chance if divine assistance came down. Additionally, given the man’s confidence, Orodan suspected he had several defensive skills.\par
“I agree, let’s step just outside the tower, that way if I send you flying you don’t smash into the walls,” Orodan remarked and while Claridin’s face turned red, he had a vicious grin on his face.\par
Orodan had an inkling of why exactly. The armor Claridin wore was the finest Orodan had ever seen, perhaps this unrivaled craftsmanship was what allowed him to have such confidence?\par
They stepped outside and Orodan saw Lucille’s ashen face looking on in horror as she realized what was going on. Poor girl must have been embarrassed.\par
Finally, the two stood before one another and Claridin drew his mace and greatshield, taking a stance.\par
“I’ll be gracious and allow you to go first!” the man barked.\par
Orodan complied and tested the man with a half-strength power cross delivered directly onto his greatshield. Drawing his sword would be excessive. The fist was empowered by nothing, just Physical Fitness and Unarmed Combat Mastery.\par
The shield dented with a groan, and Claridin’s eyes widened as he saw this. However, despite the dent the man seemed to have some sort of rebounding or damage absorption skill, as the shield and Caridin glowed, and were filled with power.\par
Claridin roared and returned Orodan’s blow, with double the power Orodan had delivered.\par
It was a solid blow, and Orodan felt the wind get knocked out of him as he was hit across the chest by double the power of his own unarmed strike. But he held onto the solid ground and refused to be sent flying, even if one was allowed to get back up and continue as per the rules of this impromptu competition.\par
Seeing this Claridin began to tremble and looked downwards at his own neck at the amulet he was wearing. What even was that?\par
Orodan decided to now up the ante and launched a full strength blow. Still unempowered, but this time it ripped right through the man’s great shield and struck him hard on the breastplate, which dented inwards. But then Claridin’s amulet glowed a deep red, and Orodan felt a repulsive force prevent his fist from reaching the man’s body.\par
Claridin looked incredibly nervous now that his shield had essentially been ripped through. As Orodan pulled his hand out, the man couldn’t help but yell.\par
“What kind of freakish strength is that?! You… you must be using divine assistance! Or an item!”\par
“Which is rather ironic considering that amulet around your neck which glowed and caused a shield to block my fist,” Orodan quipped back.\par
Claridin roared as his body and weapon glowed brightly with raw power. And then he swung, returning Orodan’s full strength blow with twice as much power.\par
It struck Orodan’s chest, but this time he felt a few cracks in his sternum and was actually sent backwards a decent distance, but slid along the ground and still remained on his feet. The very minor damage healed almost instantaneously.\par
His defensive and vitality skills far outpaced his offense. So for Orodan to be hit by his own power twofold… wasn’t all that bad.\par
“Alright, you hit pretty decently for an Elite. It’s been a while since someone of this level managed to injure me, so you’re quite talented,” Orodan praised as he began walking towards Claridin, whose face was now ashen. “I’m not going to kill you, but this next hit will hurt. And it might overtax that amulet you’re using to shield yourself.”\par
Death Rage came on, and Orodan’s knuckles popped with such strength that light shockwaves erupted from his hands as he clenched his fist. He delivered the blow at half-power, as Death Rage was just too strong of a multiplier at its high level now.\par
Claridin’s mace which launched a full power attack - thereby breaking the rules of their competition - desperately tried to meet Orodan’s fist in a bid to stop it and slow down its power.\par
It was pointless.\par
The mace was obliterated, Claridin's breastplate shattered and the amulet glowed a dangerous color of bright red and the magical shield protecting the Rockwood barely held for a moment before it strained and shattered with a massive explosion. Orodan stopped his fist at the last instant before it would have torn right through the man.\par
The force of the shield’s explosion sent Claridin flying away like a ragdoll all the same.\par
He took an entire ten seconds before he decided to get back up.\par
“Your turn again,” Orodan said as he deactivated Death Rage.\par
Claridin forfeited.\par
\par
Casually trouncing Claridin Rockwood while making it look easy was apparently a bigger deal than he thought it would be.\par
For starters, nobody had told him that Claridin was the third strongest student at Bluefire, and that he could fight a Master evenly and even defeat a weaker one on a good day. The two students stronger than Claridin also couldn’t have made it look as easy and casual as Orodan had.\par
In Orodan’s opinion the praise and acclaim were somewhat embarrassing to even consider. He had trounced an Elite-level warrior, one who could beat a Master, true… but still a mere Elite! For Orodan to be praised for beating up a student was… shameful.\par
His battle power was such where he fought Grandmasters and was hoping to eventually fight Avatars. This was just disgraceful and he didn’t know why he had expected any better from Claridin in the first place.\par
Orodan quietly resolved to avoid fighting students from then on. It just felt low.\par
Burgher Ignatius had contacted him via communication amulet to praise him for embarrassing House Rockwood and showing the strength of Firesword of course, but Orodan did not want to be reminded of the situation any longer.\par
Lucille looked both in awe and fearful of him at the same time, and her mannerisms became a lot quieter. Which was about the best he could expect.\par
He was lead to his lodgings and from then on Orodan informed her that he would be able to make his own way around.\par
As for his lodgings…\par
…excessive would be how Orodan would describe it.\par
It was a personal manor on the edge of the campus, far larger than the guest manor the Burgher had housed him within in Trumbetton. It had a staff of maids and butlers, and Orodan made it clear to them that he would likely not be within the manor much if at all, which they graciously accepted with relief and disappointment in equal measure.\par
Orodan didn’t have anything in the way of belongings that he had to bring along, and so there was nothing to drop off at his personal manor. In other words, he left without even bothering to enter the manor proper.\par
Rather, the day was still young and classes had yet to start.\par
Technically, his official start date for classes was tomorrow. But the classes ran on the same schedule every work day, so Orodan decided he would simply begin attending classes today. And the first one on the list, was ‘Warrior Skills 100’. Which began in less than ten minutes according to the schedule.\par
Of course, when one could Sprint at speeds fast enough to tear terrain apart… that deadline wasn’t an issue.\par
He kept his speed reasonable, not wanting to cause undue property damage, but students around him were still somewhat surprised even if he made sure to avoid running into anyone. Which at his speed might be fatal for them depending on their strength.\par
Of course, it wasn’t exactly unprecedented. Orodan saw at least a few other martial students rushing to classes and moving about in the same way. They were a rarity and likely talented fourth years, but still present all the same. Physical Fitness and Sprinting was just a convenient combo.\par
He arrived at the Agathor’s Sanctum building with time to spare. It was where most lower year martial lessons were held. The 100 and 200 level courses for warriors were typically held here. It was a decently large building with a rather massive reinforced training yard behind it with a wide variety of equipment, most of which Orodan had never seen before.\par
Inside, were lecture halls where the actual speaking and theory work would occur. But unlike a typical classroom he had heard of, even the indoor lecture halls had an arena style arrangement, with the seats up high surrounding a large stage where the instructor would speak from. He could imagine bringing equipment in and arranging duels and demonstrations on this stage would be a simple matter.\par
Most students had settled in by the time Orodan had arrived as there were a few minutes to spare. He thus took a seat at the very back, and it seemed nobody noticed him, or his appearance wasn’t too well known as of yet, for he wasn’t bothered.\par
Then, it began.\par
“Good morning, today we’ll be picking up where we left off yesterday. More demonstrations of the various movement skills in the hopes that you lot can pick some of it up,” the man spoke, with magic amplifying his voice to reach the entire hall. He was tall, and had a fierce looking demeanor. A spear was strapped across his back.\par
“Now let’s review, what are movement skills? Can anyone tell me?” the man asked, and a student near the front raised their hand to whom he gave the floor. “Mister Vastoros.”\par
“Skills meant to traverse distances or change positions. Even something like Teleportation would be considered a movement skill,” the student answered.\par
“Correct. Movement is not only done in straight lines, but can also consist of traveling through space. As long as your position changes… that is the important part,” the man explained. “Some even subscribe to the somewhat radical view that time magic is also a form of movement skill, as you change position in time itself. Personally, I’m a warrior and prefer to keep things simple and consider movement within three-dimensions, which is what we’ll go with for the purposes of this class.”\par
The man then gestured and nearly a dozen more instructors came out and onto the stage. He explained that they would be demonstrating various movement skills.\par
“Given how difficult it can be to obtain a skill for the average warrior, I have my fellow instructors up here with me. Somebody possessing multiple skills, while not too rare, is still quite difficult to manage. Can anyone explain why?” he asked, and the same student raised their hand. “Mister Vastoros once again.”\par
“Because obtaining new skills is a very difficult process and the reality of Calledro's Average.”\par
“Correct. And that’s why most of you are in this class. Calledro’s Average is a hundred hours, which is to say, the amount of hours the average person needs to obtain a new skill with constant and guided training in the environment of an academy is roughly a hundred. And that’s simply for a common skill. A lot of active combat skills are at the Uncommon rarity, so to that end acquiring them can take even more work. And Exquisite… unless you’re a truly hard worker or have great talent… forget about it. Even I only have one Exquisite rarity skill, and I’m a Master.”\par
“But…” Orodan interrupted from the back. “Would the stress of life and death battle not improve the growth rate of skills?”\par
“Ah, decided to sit in on the class have you? I don’t recognize you mister…?”\par
“Orodan Wainwright.”\par
The class fell silent and devolved into hushed whispers. Orodan almost wished he hadn’t said his name as the effects of fame were starting to become a little annoying.\par
“Mister Wainwright! Your reputation precedes you. I was told you would be starting from tomorrow, but it speaks to your diligence that you’ve decided to come in today,” the man spoke and even his demeanor changed. “To answer your question, yes, life and death battles would in fact lead to tremendous gains despite their risks. Some of the greatest heroes oft have stories of surviving hellish battles and coming out with skill gains that changed their lives. Of course, this requires surviving the battle in the first place, and we can’t all tussle with a deadly monster deep underground like you can.”\par
Orodan brushed off the attempts at flattery. “I gained the Perfect Parry and Evasiveness skills after maybe… a few hours of continuous battle in which my life was on the line?” Orodan remarked after a quick calculation of how much actual time he spent fighting the archer in Scarmorrow. “Definitely didn’t take me a hundred hours.”\par
Mutters filled the room. Some of indignation and outrage, some of quiet awe and envy, some of disbelief. The instructor himself simply had an approving look on his face and a calculating glint in his eye.\par
“Yes, and it’s called Calledro’s Average for a reason Mister Wainwright. I don’t think the famous scholar had a monstrous talent like yourself in mind when he postulated his theory,” the man said with a smirk. “How about we have the class come down to the stage now? I feel some hands-on practice and attempts at acquiring some skills by watching our instructors is called for.”\par
The class was then ushered down from the seats and onto the stage, which was large enough to accommodate the entire class of a thousand students. It was a decent crowd and Orodan assumed he would be near the back given his initial seating, but the crowd of students parted as the instructor approached him directly.\par
“Mister Wainwright, I’m Astiphus Marlston, the instructor for a majority of the lower year courses at the academy. It’s not often we get someone of your stature taking a mere first year course,” the man introduced himself and spoke. “I’ve spoken to the venerable Arvayne Firesword and he’s told me about your desire to acquire a formal education here and how there may be certain gaps in your knowledge and skillset, to that end, we’ll do our best to support you here and help you acquire the skills you seek. That being said, I don’t see you remaining in this class for long given your talent.”\par
Orodan thanked the man and soon enough the support took a form Orodan wasn’t expecting.\par
The rest of the class was on the massive stage, however Orodan and three other instructors, including Astiphus, were to the side and had taken a space of their own. Having three instructors move to tutor him personally was… extravagant, but Orodan appreciated the potential for guidance and acquiring a new skill.\par
Naturally, some of the other students weren’t overly happy about it. Whether they felt slighted and less important in their own statuses or because they were ardent defenders of equality and fairness, Orodan did not know. But at least some of them were giving him jealous looks, even if they didn’t dare say anything about it.\par
Astiphus gave a few more introductory words to the class about movement skills, and that they’d be working on the Sprinting skill first today, followed by demonstrations of the Charge skill afterwards. The final skill worked on would be the Lunge skill, which was of uncommon rarity simply so that the students could see what the difference between the two initial common skills and an uncommon skill like Lunge was. Obtaining an uncommon skill was difficult, and the students weren't expected to actually acquire it unless they were lucky or talented.\par
Orodan came to learn that the building, alongside every other classroom in the academy… was enchanted with powerful time dilation effects. It turned an hour long class in real time, into what was effectively a six hour block of training. It was Orodan’s first time in a time dilation chamber altogether.\par
Bluefire truly spared no expense if they could afford to have time dilation on all of their classrooms. He had never heard of such a thing anywhere else, likely due to the tremendous costs involved. No wonder Bluefire graduates were head and shoulders above the other academies in the Republic. Their students all had access to six times the amount of training hours.\par
“Mister Wainwright, as we’re focusing on movement skills today we’ll be helping you by showing three movement skills at first. Sprinting, Charge and Lunge. Have you encountered any of these before?” Astiphus asked after he was done lecturing the rest of the class and now moved to assist Orodan personally as the other instructors took over his spot in walking among the class and giving pointers and demonstrations.\par
“I already have Sprinting, it’s at 31 currently. And I’ve fought and forced a man using Lunge to retreat before, it was a dangerous skill and I can see how it’d be useful. Haven’t heard of or encountered the Charge skill however,” Orodan explained.\par
“Your Sprinting level is quite high! Most people, even at the Master-level don’t train the fundamental techniques of that skill, instead using raw Physical Fitness to get around. But of course, you must be quite fast at getting around with that and your Physical Fitness working in concert,” Astiphus praised. “As for Charge, it’s essentially an inferior version of Lunge, without much of the same distance traversal ability. Which is understandable given that Charge is of common rarity and Lunge is uncommon.”\par
“I’d like to see both if possible,” Orodan said.\par
So the training began. As the rest of the students were getting demonstrations on Sprinting and some of the more advanced ones were being shown Charge, Orodan was watching demonstrations of both Charge and Lunge.\par
“For the Charge skill, one must immerse themselves in the very mindset of crossing the distance and crushing enemy ranks. It’s a slightly limited skill in that it only works when moving towards an enemy or target you intend on destroying, but it can be a powerful multiplier for someone who is already strong,” Astiphus explained as he watched over Orodan attempting the skill.\par
Over the course of almost two hours Orodan experimented with getting the Charge skill down correctly and engaging himself in the proper mindset for it. It was a common rarity skill, but without the pressure and adrenaline of a life and death fight, it wasn’t easy to acquire. He actually had to put genuine thought and focus into the form of what he was attempting and direct his physical energy towards it.\par
But try as he might, he felt dissatisfied, as though he was missing something critical.\par
Charge involved almost empowering yourself in preparation for the inevitable collision with the enemy, the bracing for impact, the energy buildup within, and the execution of the attack. It was a movement skill in name only as the ability to traverse some distance with it was merely a byproduct of the increased empowerment in the body meant to be used upon arrival.\par
Lunge on the other hand focused more on a burst of distance traversal, meant to reach the target as swiftly as possible in the shortest amount of time. To that end, all the physical power of a warrior’s body should be dedicated to the movement itself. The attack upon arrival was merely a consequence empowered by the movement. This was a true movement skill, as the attack itself wasn’t as empowered by the skill as he thought it was.\par
But… Orodan felt discontent at the thought of acquiring something that did one or the other. Furthermore, he felt as though he had more energy in him than just the physical power of his body. What if he were to fuel mana into the attempt as well? He could even try adding soul energy to the mix, although that was best done in the private training chambers the academy had.\par
Five hours of the six passed, and Orodan kept experimenting. And halfway into the fifth hour, he had results.\par
Mana and physical power synergized together. His body was empowered for a furious attack, but it simultaneously was empowered for a bursting movement of titanic proportions.\par
Orodan’s eyes widened as he tore through the air like a shot from a magic siege cannon. He was going almost too fast to stop his own momentum.\par
He crossed the entire length of the large lecture hall and continued through the walls. Going through one classroom after another. Thankfully he aimed upwards and didn’t hit anyone. The energy buildup within him was begging for release, and he obliged by releasing the empowered strike as well, which tore completely through the ceiling… and caused the clouds above to part.\par
\textbf{[New Skill (Exquisite) → Flash Strike 1]}\par
He landed on the roof of the Agathor’s Sanctum building and looked down at the path he tore through multiple classrooms all the way to the ceiling.\par
It was a decent distance, but Orodan thought he saw a happy smile on Astiphus’s face.\par
And he hoped the tuition House Firesword paid covered the damages.\par
Because he had just disrupted the time dilation on multiple classrooms.\par


\section*{Chapter 18 - The Bluefire Academy II}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 18 - The Bluefire Academy II}%
\par
Orodan descended down to the classroom, the hole leading skyward still awkwardly present. The atmosphere was silent for a moment, but was soon broken by whispers and muttering which slowly grew louder.\par
“The walls should be able to take Master-level-”\par
“So him beating Claridin wasn’t a fluke?”\par
“-will want to hear of this.”\par
The chatter continued for a bit as Orodan simply gave Astiphus an uncomfortable and apologetic smile at having destroyed what was undoubtedly an expensive setup.\par
The head-instructor didn’t appear too bothered however and still had a smile on his face. Soon, Orodan found out why.\par
It was a weird sixth sense he was starting to develop, but he could somehow instinctively tell when someone was dangerous. And it was a feeling he uniquely got from Grandmasters nowadays.\par
A rather grumpy looking ancient woman made her presence known with a loud grunt, walking out to stand near Orodan.\par
“Sigh… prodigies and their damned destructive habits. Always interrupting my meditations…” she muttered. “You, boy. From now on restrict your destructive experiments to the private training chambers at the top of the Bluefire Tower. They’re capable of taking the full power strikes of a level beyond Masters.”\par
The training chambers at the top of the Bluefire Tower?\par
“The rest of the private chambers aren’t similarly reinforced?” Orodan asked. “I thought they were all the same?”\par
“No, they aren’t. The overwhelming majority of students aren’t ever going to reach the Master-level, so most private training chambers across the academy are reinforced only to that level,” she explained. “Of course, in the rare case that we get a prodigy among prodigies like yourself… we have specific training chambers at the very top of the Bluefire tower.”\par
“Wouldn’t they be in use by important people?”\par
“When someone at your level of power shows up, they are the important people. Just walk in and tell someone that Yallista sent you, and if they hassle you just beat them up,” the old woman casually explained. “After all, given what I’ve heard, you certainly like fighting don’t you Orodan Wainwright?”\par
“Does everyone know about me now? I haven’t even been here a day…”\par
“Blame yourself for brawling a worm in the wild depths for two weeks straight. Did you think the earthquakes you caused wouldn’t be felt?” she asked pointedly. “Young men… no thought for the consequences of their actions,” she muttered and sighed.\par
“Alright… I understand. I’ll use the training chambers at the top of the tower from now on… but how am I supposed to experiment in class then? I don’t want to just sit around and wait till nighttime to train in the chambers.”\par
“You aren’t even supposed to be frolicking about in a first year course with these regular people. I bet that old codger Arvayne put you in here so he could have some entertainment. He’s probably watching through the scrying eyes as we speak,” she said, and then promptly shot a glare towards the nearest glowing scrying eye orb in the room. “What rarity is the skill you just acquired?”\par
Orodan didn’t think the old general was apt to get his kicks in such a manner, but when you were two-thousand years old… who knew how bored he got?\par
“Doesn’t the old man have Grandmaster things to do?” Orodan asked.\par
“Sigh… you have no sense of tact or manners… you can’t just go around openly blabbering about the fact that Grandmasters exist. These common students will feel inferior and have their sense of self-importance shattered, and then they’ll go crying to their sponsors about how they can reach such a level, and then their benefactors come to us whining about how we're hurting their feelings and causing emotional disturbance in their house,” Yallista remarked in a tone that implied she didn’t care a whit about it. “The headmasters and headmistresses will then give you a stern lecture about it. Anyways, rarity.”\par
Of course, the fact that she was lecturing him about it in conversational volume in front of a room full of a thousand students was a bit ironic.\par
“Exquisite.”\par
“And you acquired this in… six hours of experimentation and training?” the old woman asked with a serious tone.\par
“…yes? Is that outside the norm? I instinctively attempted to combine what I saw of two separate skills and this was the result,” Orodan explained.\par
“So you didn’t even acquire the two skills… you just ‘saw’ them and somehow experimented and came to a combination which granted you an exquisite rarity skill?” she asked, a bit of incredulity in her tone.\par
“Yes, precisely so.”\par
“Boy… give me your schedule, let me see what other stupid junior classes that old fogey tried to have you attend,” she demanded, and Orodan handed it over. “Trying to squander the potential of a little monster like you… has he truly gone so senile?”\par
“Erm… headmistress… perhaps we should dismiss class before you have such a conversation with Mister Wainwright?” Astiphus interjected and asked deferentially all while Headmistress Yallista looked over Orodan’s schedule.\par
“Hmm? Yes, go ahead and disperse the rabble,” she said with an utterly dismissive and disrespectful gesture which the student body looked quite offended by, but wouldn’t dare to do anything about. “Now let’s see here… soul and mental defense classes? All these crafting courses that you elected to take yourself? Were you perhaps dropped as a child? Hmm… Arvayne did say you were stupid… perhaps such is the price of talent?”\par
Orodan did his best to remain quiet in the face of her casual remarks about his mental capacity. Concurrently, Astiphus ordered the students out of the classroom saying class was dismissed for the day.\par
“Hmmph… well we might as well get this farce out of the way before classes officially start for you tomorrow,” Yallista said. “Go ahead and attend all these classes you have today. If you exceed all expectations in a class, it’ll be changed moving forward. Who knows? Perhaps we’ll find a weakness somewhere. I expect the mental defense and soul defense classes will likely challenge you at least a bit.”\par
Orodan didn’t think they’d challenge him at all. Not the first year courses on the topic at least.\par
“Alright… now how is this damage going to get fixed? Do I need to compensate the academy?”\par
\par
Turns out he didn’t need to compensate the academy. Damages were expected during the course of the students’ education. And the exorbitant tuition fees covered everything. Especially in the case of people who displayed ridiculous talent like Orodan did.\par
Orodan had never encountered chronomancers before, but this was one of the rare moments he found himself somewhat wary, intimidated and thankful for his Mana Resistance.\par
Because Yallista was a scarily powerful dual-Grandmaster in chronomancy and telekinesis.\par
As she worked, she explained the rules and limitations of the chronomancy she used. Using chronomancy to affect local areas was possible, and it could be selectively applied to certain objects, with the mana cost increasing depending on what was being restored.\par
Things such as restoring lives and priceless artifacts was impossible even for her as the mana cost would be near-godlike. Something which gave Orodan ideas for far later down the line.\par
But when it came to repairing a building and the enchantments placed upon it? It was well within her purview. Additionally, she used telekinesis to ensure all the destroyed pieces of the building were within the local area before she began using chronomancy to revert time for the building itself.\par
Within moments, the damaged Agathor’s Sanctum building was completely restored. Time dilation wards included.\par
“So is the mana cost higher because you’re also restoring the wards to before they were destroyed?” Orodan asked.\par
“Yes, without a doubt. If I was just restoring material, it wouldn’t be so tiresome. The more mana something had, the costlier it is for me to revert time and restore it.” she explained. “It’ll also be a severe cost and likely push me to my limits if I try to bring all the students back to the building as well, as the cost increases if I extend my chronomancy to them since they’re farther away.”\par
“That’s… incredibly powerful. But if you’re saying you have to pay the mana cost to restore something in time to when it was whole, depending on how much mana it had… can you then gain mana by reverting something to when it was destroyed or lesser? Let’s say someone you’re fighting decides to empower themselves or restore their own mana or vitality with a potion… could you revert that and just… pocket the difference?” Orodan asked.\par
Yallista looked at him strangely for a moment and then just smirked. “Well, turns out there is a brain in there after all. Yes, I suppose that might be an apt way of looking at it, and why a chronomancer would be feared.”\par
“How does anyone beat a chronomancer without the Mana Resistance skill then?”\par
“How do you even know about that skill? Wait… don’t tell me…” she muttered and then sighed. “And here I was… looking forward to bullying you a bit. Go ahead and ruin a woman’s fun why don’t you?”\par
Orodan preferred not to be subject to whatever bullying or pranks this old hag had in mind, so he was grateful for his Mana Resistance.\par
“Your unprofessional fondness for pranking a student aside, how would someone beat you? Surprise attacks?” Orodan asked once more.\par
“Well, roguery and ambushes aside… chronomancers are often countered by skills that can drain mana or counter and reflect spells and magic. Additionally, having a massive pool of energy or being a tier above the chronomancer tends to help,” she explained. “An Elite-level chronomancer isn’t taking control of and winding a dragon back in time.”\par
“Even still, the ability to counter you seems… limited,” Orodan remarked.\par
“We chronomancers aren’t all-powerful boy. If we could act with impunity, you would see a society ruled by nothing but chronomancers,” she said. “Plenty of places are warded heavily against time manipulation, and anyone worth their salt has at least one item that protects against chronomancers directly manipulating them. Plus… mana costs are always a limitation we face. Even an hour of rewinding time is quite mana expensive.”\par
Orodan nodded in understanding, having learned more about these fearsome mages. Well, fearsome for anyone but people like him who had a high level Mana Resistance skill and could just act like mages were casting imaginary play-spells on him.\par
“Don’t let my self-denigration fool you, chronomancy is probably one of the most powerful magical schools in existence. But it’s also one of the hardest to learn given the extreme mana costs for even the simpler acts. This school has one other student with even the first level in chronomancy, and she’s the second strongest student at Bluefire,” Yallista spoke. “Across the world… I maybe know of a hundred other chronomancers, and this includes the fledglings who are in the early levels. Besides, there are plenty of dangerous things out there… have you ever tried fighting a soul mage? Or worse… a psionic? And Gods forbid you run into an Eldritch creature… the very nature of those things is a vile corruption.”\par
“I’ve faced psionic attacks before, and I’ve fought the Eldritch. But I haven’t faced a soul mage yet, are they rare as well?”\par
“You… how have you even faced the Eldritch without standing before me as a ravening and corrupted abomination?” she asked honestly. “I can see why Arvayne himself stepped in as your benefactor. Caused a rather big stir among us… a Chosen hasn’t directly acted as benefactor for someone in hundreds of years. I won’t pry into your story much then… but to answer your question, soul mages are second only to chronomancers in rarity, mainly because training the soul is incredibly dangerous and requires tremendous amounts of willpower and focus to avoid irreparable harm.”\par
Orodan continued questioning the woman for a while longer, and despite her brusque attitude, she answered every question earnestly.\par
He asked about where he might find soul mages to study under at Bluefire, where he might find a good psionic to train his defenses against and where he might look into researching the depths of Weapon Aura and soul energy based enchantments. He basically gave a whole list of his priorities and learning targets to the woman, and while she had jabs and retorts here and there, she took it seriously the entire time and actually seemed to prioritize his education and growth.\par
“You… are seeking to learn too much all at once. You realize that graduates of this academy continue to return and hone themselves in their free time yes? We have former students who have been going back and forth for hundreds of years,” Yallista spoke. “The heights you have in mind… Masters and above take decades, and even centuries to reach. That you’ve come even this far at your age is utterly unfathomable and makes me suspect you’re the most monstrous reincarnator I’ve ever seen, but perhaps your expectations of yourself need to be a bit more realistic?”\par
Orodan didn’t entirely agree with the sentiment. Whether it was the Blessing of Agathor or just the talent of hard work and indomitable willpower, he was certain he could achieve all of these targets. Definitely in less than a century overall too.\par
It just wouldn’t be in one loop at the academy. He knew that, but the reason for asking for so much was so that he could hit the ground running in future loops.\par
“Fair enough. I don’t completely disagree with you, but I wish to learn this all the same. Even if you think my attempts at learning alchemy, enchanting and the blacksmithing crafts are a waste of my time and talent… I still think they’ll be useful all the same.”\par
“And why exactly do you think it will be useful? What’s your end goal in all this?”\par
Aside from getting out of the time loops some day? Orodan had another goal he was slowly coming to develop.\par
“I have a goal… it’s a very long-term one, but something I’ve come to want over time, and especially now that I’ve been having my horizons broaded at this academy. I’ve kept it secret so far…” Orodan spoke. “There are Grandmasters, and even those who’ve reached level 100 in three skills, triple-Grandmasters. But what if… what if I could achieve that level in every skill and craft?”\par
He spoke epically, a grandiose desire that had been slowly growing within his heart for quite some time!\par
And Yallista laughed in outrage and mockery.\par
Entirely understandable given nobody had ever achieved it, and might not even be close to achieving it. He still had a long way to go.\par
But he had time.\par
He had all the time he could ever need to reach his secret goal.\par
\par
The other first year courses he took went similarly.\par
Yallista was wrong to think that the soul defense class would challenge him.\par
He embarrassed the instructors in the class when they tried gently prodding his soul and gradually escalated things from there. The head-instructor for the first year course - a Master soul mage - called upon the headmaster for the school of soul magic to tutor Orodan.\par
The man, Arlin Colton was a Grandmaster soul mage who sent furious assaults towards Orodan’s soul. But… it was no contest at all.\par
Orodan had honed his Mythical skill - Eternal Soul Reactor - through training against the Avatar of a Goddess. It was now at level 59 given all the combat he had engaged in which actively used the skill to churn his soul harder and harder to produce ridiculous amounts of soul energy.\par
His Soul Strengthening - a legendary rarity skill - was at level 14. Which lead to the very quality of his soul energy being denser and more powerful than the Grandmaster’s. Finally, his Soul Manipulation was at level 58, which was from manipulating the utterly massive amounts of soul energy produced by Eternal Soul Reactor. It was a self-feeding loop of progress, and Orodan’s endless willpower which fueled it and kept his soul intact, was the driving force behind it all.\par
It was a shame to say… but he legitimately had not been able to acquire a soul defense skill, because no assault the headmaster of soul magic sent his way ever taxed him. Initially he thought it was because of his Mana Resistance, perhaps the man’s attacks were mana based?Stolen from its original source, this story is not meant to be on Amazon; report any sightings.\par
Some of the attacks were mana based, but Arlin wasn’t a Grandmaster in the art without reason. He then swiftly switched to empowering his soul attacks using soul energy, which finally did get through… only to still have no effect at all.\par
The man’s offensive soul magic ability was at the Grandmaster-level and he was world renowned, but even he was utterly flummoxed at how Orodan simply wasn’t effected by any of his assaults.\par
Frankly, even Orodan himself was surprised. The man’s strongest attacks weren’t mana based, and Orodan consequently had no resistance skill for them. Ordinarily, a Grandmaster would be an even foe which would require his full effort to best in combat. That was the mental benchmark he had from fighting Adeltaj Simarji. He certainly couldn’t just no-sell a martial specializing Grandmaster’s attacks for example.\par
He felt something try to affect his soul, but it just didn’t seem to be capable of doing any harm.\par
It appeared the strength of his soul might be one of the strongest things about him. Even stronger than his martial prowess by a large margin.\par
Arlin declared that Orodan’s soul was like a mountain. It was technically vulnerable to assault, but it was open to assault the same way a mountain range was. Trying to assault it wouldn’t do much, and he explained that Orodan had far too much soul energy constantly being expelled from his soul to even allow attacks attacks to get through.\par
Arlin looked rather concerned as he told Orodan about what he saw of his soul. The man had a Blessing from a God he didn’t name that allowed him to look directly at someone’s soul, which of course allowed him to bypass the Blessing of Ozgaric as the two essentially cancelled each other out. The man then simply sensed Orodan’s soul the regular way and questioned Orodan about why his soul looked as though it was in a constant state of ignition as though a soul mage was launching a suicide attack.\par
Orodan didn’t deign to reveal too much about his skill or its rarity, but did say that intense willpower and disciplined focus were key factors in ensuring his soul didn’t decide to explode and kill him and cause mass devastation.\par
The lesson ended there and Arlin told Orodan to come seek him out directly for tutelage from then on. Wasting time with even the fourth year soul magic courses would be pointless for him. The headmaster of soul magic promised to bring some rather interesting equipment and assistance for him in tomorrow’s lesson.\par
Thus Orodan went on to the mental defense class, where he encountered psionics for the first time.\par
Most other academies didn’t even have psionic teachers and consequently couldn’t offer courses for mental defense or psionics. And those that did have a psionic tended to offer a fourth year course only.\par
Of course, Bluefire was world renowned and had plenty of psionic instructors. Thus even first year mental defense courses were offered, particularly because the benefactors of noble children all agreed that some form of defense against mental attacks was important to have.\par
Much like the first year soul defense class, the regular instructors had a difficult time getting past his defenses. His Psionic Resistance was at level 58. Even a tier above, the Elite-level psionics couldn’t get past a Resistance of such high level, and the head-instructor, a Master psionic while taxing Orodan’s resistance, couldn’t quite break past it either.\par
Finally, the headmistress of the school of psionics decided to pay a visit, and unlike with his soul… he was put to work for the first time.\par
But even she was looking disconcerted as Orodan was kneeling in pain while clutching his head, but still appeared functional.\par
“I’ve broken past your untrained attempts at defending your mind… you’re entirely vulnerable to my attacks now… and yet I still can’t put your mind to sleep,” she remarked. “Child… is it a Bloodline or a Blessing which grants you such unfathomable willpower? I’m pouring tidal amounts of psionic power into my assaults but they still have a hard time finding purchase… how did you get your Psionic Resistance this high?”\par
Ilevida Balmento was the headmistress of the school of psionics and a dual-Grandmaster at the art. But even she, who had battered Orodan hard enough that he felt it even through Psionic Resistance, still wasn’t able to make any headway in actually putting him to sleep.\par
Her psionic attacks weren’t mana based, they were instead psionic, which Orodan thankfully had a resistance skill for. But having a resistance wasn’t all-encompassing, and enough power could still go through.\par
“I’ve been told… I’m rather stubborn…” Orodan muttered in-between heavy breaths as the pain of her psionic assault was tremendous once his defenses were broken past. Unlike the Eldritch Avatar who attempted to slither into Orodan’s mind insidiously, her psionic assaults were like a battering ram, meant to pummel someone straight into unconsciousness.\par
It was like his mind was being struck by a repeating barrage of artillery. Each hit was like an overwhelming sledgehammer, and they came as frequently as raindrops in a storm.\par
But… he would not allow himself to fall into the sweet embrace of sleep that the psionic assaults were commanding him to allow.\par
His willpower was not so weak.\par
“Perhaps we should stop here? This can’t be good for your mind,” Ilevida suggested, and Orodan raised a hand to stop her and almost demand she keep going. “…if you insist. I’ll be going all-out till you’re knocked out then. This staff I have here is a converter for psionic power to soul energy. I had it made specifically to deal with annoying creatures and people with a high level of Psionic Resistance. My next assaults… will be empowered by soul energy.”\par
Her eyes began glowing pink and she looked quite serious as colossal amounts of her psionic power began entering the staff, which creaked dangerously. And then the assaults renewed.\par
And Orodan knew nothing but pure pain.\par
Pure, horrifying pain that invaded each and every part of his mind.\par
The Eldritch Avatar’s attempts at mental assault were more subtle, insidious… but this? This was what a straightforward psionic assault looked like. And he didn’t have any Psionic Resistance skill to help him here as it was empowered by her soul energy thanks to that damned staff.\par
The woman must have been saying something, but Orodan couldn’t hear it. He simply knew pain, and the ever-demanding tsunami of raw mental might that demanded he obey. That he sleep.\par
His head felt as though it would explode. Blood leaked from all throughout his body at the sheer strain of him exerting his endless willpower to its maximal extent.\par
He vaguely noticed various messages for Pain Resistance leveling up.\par
He was like a toddler weathering an attack he had no clue how to deal with. Prior to this he had focused on resisting psionic energy itself, but not on the techniques to stop mental assaults. Now, with no resistance skill, he would be forced to learn.\par
But learn he would.\par
He gestured at her through the haze of the all-encompassing pain to continue, and it kept coming.\par
Orodan wasn’t sure how long it had been, but as Pain Resistance kept rising he was able to think more clearly. And he began experimenting, even as most of his focus and willpower went towards holding on against the mountainous mental attacks that were slamming into his mind at the rate of hundreds a second.\par
Who was Orodan Wainwright?\par
He forgot who he was under the assaults, which rendered him nearly comatose.\par
But the name didn’t matter.\par
The spirit did. And whoever he was… he liked to fight. He would never quit.\par
He was a warrior.\par
And a warrior… weathered every blow they were struck by and returned it.\par
The mountains continued to fall upon his mind… but he persisted. Like a zombie, groaning and screaming in pain… but not falling. And slowly but surely, he began to come to an understanding.\par
In a sense, being hit by something so utterly different to what he was used to… was useful. It was a mental attack yes… but at the end of the day it was an attack.\par
And the warrior found himself meditating on what exactly an attack was. Metaphysically what was an attack.\par
An attack was any sort of offense, or harm directed at the warrior. Then an attack delivered by the warrior himself was also of the same nature, just sent by him to the target and not the other way around.\par
Vaguely, a small part of the warrior’s mind noticed that other people had entered the room at some point, but that was not his concern. Meditations and reflecting on exactly what an attack was… this was what mattered. His senses leading to the outside world had largely been shunted off elsewhere and ignored in favor of internal meditation. The pain? It was no longer a concern.\par
Ruminating on the subject was all the mattered.\par
To attack… to be attacked.\par
What was an attack?\par
The word began to sound strange as it was repeated in the warrior’s mind.\par
But he meditated.\par
Vaguely, the warrior understood that three days passed. The small part of his mind that insisted on calling itself by some stupid name was keeping track of such things. This annoying part told him that new people had arrived, and that the source of the mountains falling upon the warrior’s mind had begun drinking strangely colored potions and that someone else had come in and was periodically inspecting and making adjustments to the weapon the source of the attacks was using.\par
But the warrior cared not. The warrior simply meditated on what an attack was.\par
Two days passed, and then five more. A week went by, and people periodically went back and forth as the named part of his mind informed him. But the attacks never stopped.\par
And neither would the warrior.\par
Who was finally beginning to understand what an attack was.\par
To attack, to direct harm against a target. This was fundamentally what an attack was, no matter what form it took. It involved targeted harm no matter what the target was.\par
To the warrior however, receiving an attack was acceptable… but not returning this attack… was unacceptable.\par
A warrior took every blow, and returned it. Even if the warrior didn’t understand the nature of the attack. An attack was an attack. Thus, the warrior willed, and this was the demand he made of the world.\par
The warrior recalled a battle it had against an inferior foe, and took inspiration to complete the final part.\par
All attacks would be returned, with double the power.\par
This was the warrior’s way… this was…\par
… the Warrior’s Reciprocity.\par
\textbf{[New Skill (Mythical) → Warrior’s Reciprocity 1]}\par
The warrior weathered the barrage of attacks upon his mind, which had grown even stronger since it first began.\par
And the warrior returned every attack.\par
The attacker’s eyes widened. She struggled to hold on against her own attacks, returned twofold. Her eyes glowed with raw power and the staff shattered. But she could not hold on against the Warrior’s Reciprocity.\par
An amulet around her neck glowed and shattered, and the woman collapsed to the ground and began screaming.\par
The small part of the warrior’s mind that insisted on a name protested at this, and the warrior smiled, and finally returned to deep within. Forever a part of the soul.\par
For this was who he was, a warrior.\par
And Orodan Wainwright remembered who he was.\par
The people in the room around him looked on in shocked silence. And the old man Arvayne Firesword who definitely wasn’t here to begin with, had a smile on his face.\par
Orodan’s first reaction however was to immediately rush over to the woman who had helped him for so long, giving up so much of her own time for it.\par
Only to see her with a content smile on her face as her screams subsided.\par
“Sorry… I may have gone too far…” Orodan muttered in embarrassment and shame. “Are you alright?”\par
“Why… I’ve never been better…” she muttered with a pleased look on her face. “Come here child.”\par
She then wrapped Orodan into a hug.\par
“Eh?”\par
“Thank you… I was at the bottleneck for so long in my Psionic Mastery, it had been at level 99 for decades… but then you come along and give me the perfect target to practice endlessly on in one uninterrupted session,” Ilevida explained. “So thank you… truly. If this old woman can ever help you in any way, all you need to do is ask.”\par
She had achieved Grandmaster-level in another skill thanks to him?\par
“Shall I break out the Novarrian vintage I have? It’s at least three-thousand years aged,” spoke the ancient Arvayne Firesword. “Rather apt for celebrating a new triple-Grandmaster in our little Republic.”\par
Triple-Grandmaster?\par
“You’re a triple-Grandmaster now? With only a few days of practice on a hapless student?” Orodan asked.\par
“Ah yes… the hapless student who can best a Grandmaster… not quite as hapless as you want us to believe. And it’s been over a week,” Arvayne quipped back. “Ilevida here is a friend of mine, so I’m quite happy to see her join our little club. At only twelve-hundred years old too… quite the talent you are Ilevida.”\par
“It’s all thanks to Mister Wainwright here,” she praised with genuine gratitude in her voice, which was something unexpected coming from a Grandmaster. People who were notoriously reticent. “I might have struggled for another few hundred years if not for the insights I acquired from weathering that incredibly powerful mental attack you sent at me. What even was that? There’s no way you’ve suddenly become a psionic capable of launching an attack of that caliber.”\par
“I don’t know… I just returned the attack. I’m not even sure of the exact specifics of it. All I know is that you sent attacks my way, and I returned them,” Orodan explained. “It’s a Mythical rarity skill.”\par
Ilevida and Arvayne both went silent for a moment at that revelation.\par
“Gods damn it Orodan… you can’t just say such things so casually…” Arvayne muttered while giving Ilevida a probing look out of the side of his eyes. “While Ilevida here can be trusted to keep such things secret, you really shouldn’t go around broadcasting the fact that you have a Mythical skill.”\par
“Don’t Grandmasters have Mythical skills? I recall old man Adeltaj telling me he knew of someone with one who was forced to flee, but I take it they didn’t have the protection of a Chosen?”\par
“Orodan… Adeltaj likely didn’t tell you out of respect for my wishes… but I also have a Mythical skill. But I only have one,” Arvayne explained. “There are only two other wielders of a Mythical skill in the Republic and they also have one each. But you… this would make it-”\par
Arvayne suddenly cut off mid-sentence as he went silent and had a pondering look on his face.\par
Then his eyes began glowing orange.\par
\textbf{“That would make it three Mythical skills you possess now, Orodan Wainwright. For someone who is such a phenomenal warrior… this meeting between us is long overdue.”}\par
The voice utterly boomed in a way Ilyatana’s never had. It sang to his heart, to his blood. It made him stand taller and desire battle, it made him want to conquer the heavens themselves and participate in eternal battle and glory forever.\par
This… was Agathor, descended unto his Chosen One.\par
Around Orodan, everything had completely frozen, unnaturally. Ilevida Balmento included. This was… time magic?\par
“I thought you’re the God of War? How can you freeze time?” Orodan asked.\par
\textbf{“A trifling matter once you wrestle time into submission,” }the God of War casually explained. \textbf{“It’s a far more advanced application of a realm of power that you are just beginning to explore with that new skill of yours. How did it feel? The oneness with the warrior within? Feeling reality itself bend to allow things which should be impossible?”}\par
“It felt… dissociative… as though I was there and wasn’t. It was still me doing the meditations… just a part of me I didn’t even realize was there all along,” Orodan spoke.\par
\textbf{“The warrior itself… even I do not fully understand what it is or where it comes from. Some say you must be born with it, others say you develop it over time. But what holds true is that only those with a truly warrior-like disposition are the ones to have it,” }Agathor explained. \textbf{“Arvayne is my strongest Chosen upon this world, but even he isn’t in touch with the warrior within. Nobody on this world was… until I saw you.”}\par
“Surely I’m not that unique?”\par
\textbf{“From what you spoke of regarding the time loops… who else would valorously commit to dying like a dog to perform the feats of legend you have? Ask yourself if rushing to death against impossible odds on your first life was a normal course of action.”}\par
Orodan found himself seeing the point Agathor was making. “What’s the next step then? How can I push this ability even further?” Orodan asked.\par
\textbf{“Continue to focus on training it… focus on demanding reality bends to your will with naught but your warrior spirit. In time you may find that there is a level beyond even Mythical rarity.”}\par
Beyond Mythical rarity? It sounded utterly ludicrous given how much of a target he became with just a Mythical skill. If he achieved something even greater, would the entire world begin hunting after him in every single loop? Perhaps consolidating his own power and getting stronger before doing that was a good idea.\par
“Is it similar to how the second Blessing you gave me works?”\par
\textbf{“Very much so. That Blessing of mine which prevents cravenly foes from escaping their honorable fate, it bends reality itself. Continue honing your skill, and in time you may be capable of similar things. Now then… descending unto him is still somewhat uncomfortable for Arvayne, no matter how gentle I make it, so I will leave you in his care with one final decree. Strengthen your soul before the eve of the year, I wish to grant you another Blessing and make you a Chosen of mine.”}\par
Arvayne’s eyes stopped glowing and the presence of the God of War left the old Firesword Grandmaster.\par
“Ahh… always leaves me a little sore whenever he does that,” the old man said while stretching. “To think he would descend just to talk to a rockhead like you.”\par
Rockhead? That was an insult, a verbal attack.\par
The warrior returned all attacks.\par
Without thinking about it, Orodan instinctively activated the skill… and Arvayne grunted and his eyes narrowed.\par
“What was that? It felt as though you deeply offended me… was that some sort of social skill?” the old man pointedly asked.\par
“No… it’s my Mythical skill… apparently it can return all attacks… even if they’re verbal.”\par
“We’re testing this immediately.”\par
\par
The private training chambers at the top of the Bluefire tower were quite durable. Which was a good thing because they’d caused enough destruction in their experimentation with Orodan’s new Mythical skill that even the walls of that absurdly tough chamber were left with cracks and tears.\par
Old man Arvayne had brought along all manner of experts to test Orodan.\par
Arlin Colton’s soul magic assaults were rebounded with twice the power whether he empowered them with mana or soul energy. Yallista Arthurius’s chronomancy was peculiarly reflected back causing her to revert herself back in time and even hostile tracking magic, insults, curses and the like were all rebounded back to the caster.\par
The attacks still hit Orodan. He still had to experience their negative effects. The headmistress of the school of curses was particularly painful once she started using soul energy to fire curses at Orodan.\par
The warrior just insisted on sending them right back twofold to the sender, even at level 1 of the skill.\par
It was now level 2 from all the experimentation, and Orodan felt that the skill’s ability to return any and all damage was absolute even at level 1, but level 2 increased the amount of damage rebounded.\par
Orodan could see his enemies essentially killing themselves by hitting him at higher levels.\par
It sounded utterly unfair.\par
“Thank you all for assisting Mister Wainwright,” Arvayne spoke. “For now, that will be all.”\par
The assortment of headmasters and headmistresses from differing schools then left with pleasantries, and Orodan and Arvayne were left alone.\par
“That was informative, that skill of yours is… powerful,” the old man muttered. “I’ve been thinking about this for a little bit… but near the end of the year when that Eldritch Avatar descends, I’d like you to join the battle against it. Your new skill might prove more useful than you think if you can stay alive to receive some of its damage.”\par
“I was planning on fighting it regardless, how else will I grow if I don’t struggle against the strongest enemy I’ve ever encountered to date?”\par
“Fair enough, I shouldn’t have been concerned about your willingness to fight it seems,” Arvayne replied. “Anyhow, as I’m sure you’ve heard, your classes will be different moving forward. I may have decided to entertain myself by seeing you run roughshod through the first year classes.”\par
“Does that mean I can skip the politics and world history classes as well?” Orodan asked excitedly.\par
“No. You’ll sit down and read your books, or I’ll have personal tutors sent to hound you. You’ve missed more than another week of classes, which is fine given that the academy expects this and the value of obtaining a Mythical skill outweighs some mere book learning,” he explained. “But it’s time for you to take your education seriously.”\par
Orodan sighed but nodded. There was no getting out of reading it seemed.\par
How horrible.\par
“What’s this?” Orodan asked as Arvayne handed him a metallic badge with the logo of a blue fire emblazoned on it.\par
“What you should’ve gotten initially if I wasn’t interested in watching those first year rabble get humbled a little,” Arvayne explained. “It’s a pass which marks you as being in a mentorship, under myself. You won’t attend regular classes anymore except for your crafting and educational ones. Your lessons in things related to fighting will now be given by personal tutors which I’ve requested.”\par
“Isn’t this a bit-”\par
“Look, I know you’re not used to this sort of treatment, but this is just how it is in our society,” the old man interrupted. “A talent like you can’t be wasting time in regular classes, it’d cause too much disruption for the rest. You’re also operating on a deadline till the end of the year, and if we fail… then it will all rely on you. You have a rather large responsibility to shoulder, so get used to special treatment because you’re in special circumstances.”\par
Fair enough. Orodan wouldn’t complain or bring up that line of thought again.\par
“Now then, your crafting classes start next. I’ll also be waiting for you in this chamber once classes have ended for the day, and we’ll train your Combat Mastery throughout the night until the sun rises and you need to head to class once more. You’ll also report any breakthroughs you’ve made in class to me so we can focus on how best we can accelerate your growth,” Arvayne said. “You don’t need to rest anymore so we’ll make every single second of your time count. Only on the two rest days of the week are you allowed to leave campus and do as you wish, be it visiting that predatory widow or helping little Ignatius and his people with whatever they need. I might also ask you to accompany me to fight some rather dangerous creatures from time to time, it’ll be good experience for you and broaden your horizons.”\par
It sounded utterly insane and demanding beyond reason, but Orodan loved it! He wholeheartedly agreed with every bit of this educational plan.\par
This was exactly the sort of training he needed.\par
Continuous and endless grinding and growth.\par


\section*{Chapter 19 - The Bluefire Academy III}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 19 - The Bluefire Academy III}%
\par
For once, it was nice not to be stared at and have people mutter about him within earshot without any care for subtlety.\par
There were still some mutters about a big and mean looking martial student carrying weapons and waltzing into the ‘Alchemy Basics 100’ class, but these students were for the most part the milquetoast scholar types who wouldn’t dare say anything to his face.\par
Unsurprisingly, the crafting classes at the academy were filled with mostly crafters. And while the drama and gossip between the two groups still overlapped quite often, the topics of prime interest were quite different.\par
For example, instead of gossiping about who the strongest student was, the crafters would understandably care more about which student was the greatest crafter of their generation in specific fields. Unlike combat specialists, there was no unanimous title of strongest student when it came to crafting, only who the best was within the specific field, and even then some were good at certain aspects of a craft.\par
When it came to combat specialists, fields overlapped and students of differing martial schools and fields of magic could still fight one another to answer the question of who the strongest was.\par
Among the non-combatant crafters however their discussions were more focused on the field itself. The alchemy students’ gossip involved talking about who the best alchemist was. There was no cross-comparison between the best alchemist at Bluefire and the best enchanter for example, nor were there any urgings or desires to see the two fight. It would make no sense.\par
There were still monstrous geniuses of crafting of course, who excelled at multiple fields. But even these crafting prodigies still had a particular field they focused on primarily, and the gossip surrounding them was mainly about their chosen specialty.\par
But, removed as the crafting students might be from the gossip of the combat specialists, they didn’t live under a rock. And given that the beginner’s alchemy course had at least some combat-specialist students who took it, they could still tell that Orodan was perhaps someone of decent fame given how these few combat specialists looked at him.\par
Nobody quite wanted to sit next to him, which was just fine by him.\par
Until a familiar face came along.\par
“Orodan! You’re here?! I didn’t know you liked alchemy!” spoke a very enthusiastic dark-skinned girl whose hair looked disheveled as though she spent far too long riding through the skies on a pegasus.\par
“Well, I can’t spend all my time hitting things, so this is a rather good distraction,” Orodan spoke. “I’m actually quite looking forward to this if I’m being honest.”\par
He really was looking forward to it. Growing up he had always looked at the alchemical concoctions for sale at the stalls of Eversong Plaza with wonder. The glowing colors of the bottles, the magical auras surrounding the products, the things he had heard they were capable of. He truly wanted to learn how to make potions himself… and perhaps delve even deeper into the arts.\par
“That’s right, I heard everyone talking about you beating someone up or something, I wasn’t paying much attention to be honest,” she remarked. “But me too, learning alchemy is quite important for an aspiring pegasus knight. We have to feed our companions and ensure they stay in good health, and mixing growth enhancing concoctions into their feed is an important part of supporting the pegasi.”\par
“That sounds quite interesting,” Orodan remarked. “For me, I’ve always seen these fancy glowing bottles growing up, so I want to learn how to make some myself.”\par
And Mahari looked at him and giggled.\par
“You really are as simple as just wanting to make ‘glowy’ potions of your own huh?”\par
“Well, there’s more to it than just that,” Orodan replied while feeling a small bit of embarrassment. “I have certain… exigent circumstances that require me to get my hands on potions that will strengthen my soul and thereby indirectly strengthen my physique or other attributes. Potions that simply affect the body won’t do.”\par
“Must be quite the set of circumstances, sounds like it’d go over my head, so I won’t pry!” she happily exclaimed with a grin. “I also want to make potions to help my pegasus grow and get stronger.”\par
“What’s his name anyways?”\par
“Oh, he’ll choose for himself once he reaches the Adept-level and can start talking,” Mahari explained. “Choosing one’s own name is a big deal in pegasus society, and I’d offend his clan and the elder pegasi back home if I dared to take that away from him.”\par
That sounded quite fascinating to Orodan. He never really heard of creatures having their own societal customs like these pegasi seemed to have. A pegasus clan and elders? Perhaps Orodan would have to pay them a visit in one of the loops when he decided to venture into the Eastern Kingdoms.\par
“Perhaps I’ll visit one day when I have the time,” Orodan said, knowing full well that he had time but other priorities took his attention currently. “Why’re you and your brother here at Bluefire anyways? Surely there’s an equivalent academy in the east?”\par
“Oh, we’re a border house in Ravastaran, and given our close ties and friendship with the Republic our house decided to send us here to get education,” Mahari explained. “Plus… we can’t all be the talented golden children of the main line of House Vedharna who get to go to Rubywater Academy at home.”\par
Orodan sensed a bit of bitterness in the young woman’s tone as she uttered the last part, but he decided not to pry.\par
Soon, the assortment of instructors arrived amid their chatting, and class was soon officially in session. Much like the first year martial classes there were at least a thousand students, thus the instructors were a dozen.\par
Even though one hour was officially allotted, thanks to time dilation wards on the building the class would be six hours in practice.\par
The head-instructor was a Master-level alchemist, and Orodan would be sure to thoroughly pick the man’s brain today. Unlike the martial class where a Master-level instructor was perhaps a bit unqualified to teach him, here he was but a complete beginner. Who had not a single level in Alchemy whatsoever.\par
Orodan sat near the front alongside Mahari, which wasn’t too hard to get a spot in as crafter students tended to be a notoriously anti-social lot and many preferred sitting farther back. This of course meant the head-instructor could see him just fine.\par
“Ah… Mister Wainwright! We are glad to have you with us today. When I heard of your interest in our class from the administrative department I was pleasantly surprised,” the man spoke. “I’m Castillius Van Estrados, Master-level alchemist at your service. Might we help catch you up on the curriculum with an instructor of your own?”\par
Orodan gladly agreed, by now used to and accepting of special treatment. Alongside him Mahari was also invited to have a personal tutor and she happily accepted.\par
Alchemy was not what Orodan was expecting. Initially, it required reading books… and Orodan hadn’t read a single book since he started the time loops. Frankly… he had gone so long without reading anything besides the morning paper that he was almost certain to have developed a level of rust.\par
Thankfully, Orodan wasn’t illiterate. He would sometimes read the morning paper in the barracks in Ogdenborough before shift start. But this textbook was decently technical. However, the textbook did explain every single thing in great depth, which was critical for Orodan’s basic understanding.\par
Frankly, what actually intimidated the instructor… was Orodan’s reading speed once he put his endless willpower and focus onto the book.\par
Most scholarly students, even fast readers, could read quite fast. Taking in and comprehending information was their bread and butter after all. And while Orodan wasn’t as smart as them, what he did have was the reaction time and permanent action increase.\par
It was utter insanity. His minds were quadrupled, and they read four pages at a time in the same instant of time. Furthermore, this was amplified by his Combat Mastery and Physical Fitness that allowed him to think and react faster than any crafter in the Republic ever could. If he could launch hundreds of attacks a second, then why could that speed not be applied to reading?\par
The book, was nothing more than an opponent. And Orodan would demolish it.\par
In less than ten minutes the fifteen-hundred page thick textbook was finished. And Orodan spent another five minutes pondering on everything he had read and committed it to memory.\par
Orodan didn’t even know he could do this! Were books truly so easy? Had he been so utterly intimidated by the prospect of learning from them due to his poor experiences in the orphanage that he was held back from trying a book all this time?\par
It really was as everyone said…\par
…Orodan was stupid.\par
But he wouldn’t be for much longer!\par
“That was it? Is this the only book you have? Bring me another and I’ll destroy it too!” Orodan almost demanded like a madman, and the instructor who watched his frankly insane reading speed and strange magic that made it look as though there were four books and four sets of him in the same space, was utterly intimidated but complied.\par
“M-mister Wainwright… what you just read was a theory textbook for beginners on the fundamentals of alchemy. Here is the next book which details the introduction to applied alchemy, and another book after that on a glossary of herbs and common ingredients used in Initiate and Apprentice-level potions and concoctions,” the man explained while handing Orodan two more textbooks.\par
Orodan happily got to work, once again treating these two thick books as though they were foes that he would outlast. How could the thickness of a textbook compare to the willpower of a man who held on against the corruption of an Eldritch Avatar for a whole year?\par
His speed of comprehension wasn’t anything special, rather it might even be below average. But when one could think at speeds far surpassing the untrained scholar… a low level of comprehension speed wasn’t as hindering as one would expect. Plus, he took to what Adeltaj had suggested in their first meeting.\par
To strain and struggle like a dog and apply maximal effort in every waking moment.\par
And as his four minds read and focused and comprehended, he learned. He learned, so very much.\par
It was as though his eyes were opened to a whole new world. Alchemy was such a complicated subject even from just the introductory textbook he had read. The book described all kinds of fundamental theories, assumptions and terminology which one needed to know in the Imperial tradition of alchemy.\par
It spoke of measurements, of equipment, techniques and recipes. It even gave economic breakdowns of the standard values of potions dependent on their purity and potency. This section must have been a draw for those from poor backgrounds who were looking to better their lots in life.\par
Orodan wasn’t too economically knowledgeable himself, so hearing that a perfect Apprentice-level health potion was worth a full gold piece, was quite eye opening. He could have a whole year’s salary in the militia if he made just one of those. Although making a perfect potion of anything was incredibly difficult.\par
The key take-aways Orodan had learned from the textbook, was that the Imperial tradition of alchemy used standardized equipment at the lower levels. The Eastern system however was more focused on cauldrons and made different products. Higher levels of alchemy in both systems started to look similar however.\par
Furthermore, alchemy was a magical craft. Mana was used to synthesize even the most basic potion, whether the mana came from the alchemist or an item or aid didn’t matter. It could get rather intricate at higher levels where mana was used to purify ingredients, empower them, and potentially even empower a finished potion itself right before imbibement.\par
Potions were differentiated on two factors, the purity of the potion, and the power of its effect. Sometimes, a potion could even drastically increase in value if the alchemist managed to add secondary or even the incredibly difficult tertiary effects. As an example, a healing potion that also gave one improved regeneration for a duration of time would be highly valued compared to a regular healing potion.\par
Orodan however was reading books which dealt merely with the Initiate and Apprentice level of alchemy. At this level Initiate and Apprentice-level potions used mainly herbal ingredients aside from a few rarer recipes. This was a good thing for beginners as it meant the quality of the ingredients would always remain consistent, as the majority of the Republic’s supply of alchemical herbs came from standardized herbal gardens and preserves where the quality was strictly controlled.\par
Wandering alchemists who sourced their ingredients from the wild for instance, were often subject to inconsistent potion power as the ingredients could either be very good, or rather subpar. Which made potions trickier to make sometimes as certain recipes required ingredients to have similar levels of power.\par
There was much in the textbook that Orodan had perused.\par
However, prodigious as his reading speed might have been, his ability to retain information and comprehend had its limits currently. Which would be something he’d have to rectify later once he moved deeper into alchemy as the textbook mentioned that higher-level recipes involved a lot of memorization, hence high-level alchemists used memory skills.\par
Another twenty minutes passed and he finished the glossary of herbs he was handed. It was a good source of knowledge on what each herb was, the relative rarity, the types of effects it had and the common potions it was used in. Given that it was a Republic textbook, the glossary also listed where in the Republic one might find such herbs, and for the herbs that came from elsewhere… where the Republic sourced them from.\par
Finally, Orodan began on the textbook which dealt with the introduction to practical alchemy, which was a guided textbook meant to walk the reader through their first steps and acquiring the alchemy skill.\par
Upon seeing Orodan open this book the instructor who was assigned to him interjected. “Mister Wainwright, I can help guide you through this textbook personally, as every page involves practice experiments and guides you towards creating a potion for the first time and hopefully acquiring the alchemy skill.”\par
Orodan accepted the aid, and soon basic alchemical equipment was laid out before him. Beakers, flasks, tubes and a mixing container. Alongside a neat package of abundant basic ingredients for concocting the very basic healing potion of Initiate-level.\par
These potions were mainly used by civilians, non-combatants and occasionally mages with weak bodies. The bodies of combat specialists on average were too powerful to be healed by mere Initiate-level healing potions, as the energy required was much higher. For patching up the cuts and scrapes of a civilian or non-combatant however, these were more than sufficient. At high power and purity, a healing potion at the Initiate-level could perfectly heal all wounds and maybe even ease the wounds suffered by an Apprentice-level combatant with a strong body.\par
Thus, under the guidance of the instructor, Orodan began his attempts at carefully preparing the ingredients. His Tool Mastery skill genuinely helped him in this process as the process of finely chopping up an astragon plant into small pieces and grinding the stem of a hogginsmere flower into a powder were things the book expected people to struggle with if they were doing them for the first time.\par
Which he was, but Tool Mastery helped ease this first time process.\par
The prepared ingredients were poured into a water-filled mixing container and the heater was turned up for a solid five minutes. Finally, came the important step, which was pouring one’s mana into the mixing container, which was designed to accept mana easily and assist in mixing it into the contents. The mixing container was meant to assist beginners and even people with no talent in mana could use a device to feed mana into it.\par
The Initiate-level healing potion was quite popular as a result for its accessibility.\par
Orodan however, had the Mana Manipulation skill. So he managed to direct a steady flow of mana into the mixing container. Frankly, he almost felt as though his Mana Manipulation might allow him to forgo an artificer-constructed mixing container entirely and instead freely manipulate mana himself into whatever he was concocting.\par
“Say, why does the recipe mention not to put too much mana into the mixer?” Orodan asked. “I know the book mentioned that it ruins the potion with an oversaturation of mana… but what actually occurs?”\par
“That is a good question Mister Wainwright, one not written in the book. But I can answer that,” spoke the head-instructor - Castillius Van Estrados - who was watching Orodan’s progress out of the corner of his eye as though he was an honored guest. “Oversaturation of mana can cause unwanted growths in the ingredients, and can even change the very nature of the potion itself. The chopped astragon plant inside can mutate to possess poisonous properties for instance. While very rarely a mutation from excess mana can enhance a potion, it’s still quite random and most of the time leads to undesirable changes.”\par
“I see, but what if there was a way to prevent the unwanted growths from the mana? Perhaps if the ingredients were forced to remain in their natural states while still receiving only the benefits of increased mana?”\par
“That… sounds impractical if I’m being honest,” Castillius replied. “At least without higher-level alchemical aids and a warded and enchanted workshop to assist in such a thing. At which point you have equipment and a workshop of very high expense and you’d be wasting time and money by not concocting high-level profitable potions instead.”\par
“So what if… I used a skill like Weapon Aura on the contents of my potion? To force it to maintain its natural properties even as my mana flows through it?” Orodan asked.\par
The Master-Alchemist had a pondering look on his face. But he didn’t outright deny it.\par
“Hmm… in truth, we so rarely get martial students of your caliber in classes such as this Mister Wainwright. Despite this academy’s structure encouraging such cross-experimentation, I don’t think I’ve ever heard of someone trying such a thing. Or if they have, I haven’t heard of any successful result,” the man answered. “Additionally, from what I know from my colleagues in the martial disciplines, Weapon Aura is incredibly difficult to wrap around things that are not weapons.”\par
This, Orodan thought, was blatantly untrue. Unless he had been doing something completely different and outside the norm with his own Weapon Aura, it was definitely possible and not too hard to extend it to things that weren’t conventional weapons. He had extended it to trees, saplings, bushes and grass. How hard could extending it to a liquid within a container be?\par
The answer, was very very hard.\par
Castillius was on-board with this cross-training experiment and Orodan tried wrapping his Weapon Aura skill around the entire liquid solution that was in the mixing container.\par
And it was incredibly difficult, like attempting to hold onto sand without letting it slip through your fingers. The amount of focus and concentration this would require, was unfathomable.\par
Unfathomable for anyone who wasn’t Orodan.\par
Sweat dripped down his brow as he made the attempt.\par
He had to use his action increase and actually have another mind working in concert to succeed. The liquid solution was so difficult to wrap Weapon Aura around, because not only was it a liquid, but it also had finely chopped pieces of astragon plant and a powder of the hogginsmere flower within it. Mentally, Orodan had to wrap his Weapon Aura around everything in the potion. Every single piece of the astragon plant, every single grain of the hogginsmere flower stem powder. It was a truly ridiculous feat of assiduousness and mental capacity.\par
But eventually with enough titanic willpower and two straight minutes of raw concentration, it worked!\par
Mentally conceiving of the liquid solution as a weapon in his own mind was the final step to succeeding.\par
\textbf{[Weapon Aura 64 → Weapon Aura 68]}\par
And the mixing container shattered and exploded due to the insane amount of mana Orodan was pouring into Weapon Aura to make it work in a manner so outside the bounds of the skill. And the liquid splattered onto the desk.\par
It was a tremendous gain of four skill levels in two minutes.\par
“I think this can work, the only issue was that the mixing container took my mana and converted it subtly while pouring it into the mixing container. Of course, when my mana from Weapon Aura and the slightly altered mana of the mixing container combined, my Mana Resistance skill didn’t agree with it,” Orodan explained. “Can we try one more time?”\par
“Mana Resistance? T-that’s quite the skill,” Castillius remarked nervously. Orodan had lost himself and said that a bit too casually. “But of course! Let us attempt this again, as many times as you like.”\par
The next attempt was made in a very reinforced container. One meant for the concoction of Master-level poisons of a dangerous nature. That it held the ingredients for an Initiate-level potion would have undoubtedly offended its creator if they ever knew.\par
The process of preparing the ingredients was done the same way. This was the easy part.\par
Now came the hard part, as the heat ran for five minutes and reached the critical point. It was time to pour mana into the liquid concoction.\par
Despite having done it once, it was still a chore to wrap his Weapon Aura around the entire liquid contents perfectly. But it was done all the same, netting him one more level in Weapon Aura due to the incredibly difficult nature of the feat.\par
If anything, this experiment was surprisingly good training for Weapon Aura.\par
Finally, he began generating soul energy and rapidly converting it into mana. And this was then poured into the solution. It was his own mana poured in this time, and not by using the mixing container as a medium.\par
He almost instantly reached the level of mana where the recipe warned one to stop at, and then soared right past that threshold.\par
Immediately, the ingredients within sought to rebel, to change into something else. The astragon plant pieces roared at his control, outraged that he would dare to prevent their ascension to a higher form. The powder of the hogginsmere flower trembled in fury, almost violently shaking as it sought the freedom to change and use the mana to grow in a way it desired.\par
The very nature of the ingredients were desperately leaning towards changing. Towards growing in their own way as the amount of mana was so high.\par
But Orodan’s endless willpower kept the vice grip of Weapon Aura tight around it all.\par
Weapon Aura was essentially meant to strengthen his weapons, to toughen them up and prevent any damage. Or prevent any change of a manner he didn’t like.\par
If he didn’t have experience with Wood Communion he would’ve also prevented the positive growth that he did want from occurring, but Orodan allowed for it, even as it truly taxed his mental willpower.\par
He had to activate his two other minds in addition to the two he was already using and bring himself to his current limit of a quadruple action increase.\par
Thirty seconds passed as mana continued to flow into the concoction, and no unwanted changes were allowed by Orodan’s imperious command. The entire classroom had gone dead silent.\par
Finally, even this container began to creak in a concerning manner.\par
“The container can’t take it! It’s best if you wound it down now Mister Wainwright!” Castillius exclaimed, and Orodan begrudgingly complied, if only to see what he had achieved.\par
He stopped pouring mana into the concoction, and once all the mana was absorbed, he cut off Weapon Aura. The skill was now at level 72, it had crossed into Elite purely from some extreme experimentation.\par
\textbf{[New Skill → Alchemy 11]}\par
What a high level gain at the acquisition of this new skill. The potion he created must have been better than he thought.\par
The liquid within the container was glowing a brilliant color of green and almost seemed to crackle with arcs of green mana across the surface. From what the textbook had written as a fun fact, glowing potions were often a sign of the power of a potion as it meant they had a high amount of mana coursing through them.\par
He took out a ladle and was about to put it in to scoop a portion out to place into a potion flask but Castillius stopped him.\par
“That ladle will melt and an ordinary flask won’t do. Use this,” he said as he handed Orodan a ladle made of a strange black material similar to the cauldron.\par
He took it and gingerly scooped up a portion and poured it down the mouth of a gold tinged glass bottle which seemed to be of superior make. A fancy stopper was shoved into the mouth after, sealing it in.\par
“Master… what does Identify show it as?” asked one of the other instructors.\par
The man peered closely at the ornate looking glowing green potion…\par
…and his eyes widened.\par
“T-this is!” Castillius exclaimed while grabbing it furiously and looking it over like a man who was sure a trick was being played on him. “This is an Elite-level healing potion… how? How did you make an Initiate-level potion jump three whole tiers? How did you do this Mister Wainwright?”\par
“What else? I used Weapon Aura to demand the potion not change except how I wanted as I poured mana in,” Orodan answered. “Want to try drinking it to test?”\par
“If a non-combatant like me drank such a thing I might need a trip to the healer or even die due to the excessive amount of life energy and sheer power of this potion!” Castillius replied. “The purity isn’t even all that high… yet for such raw power… from Initiate to Elite. What if you had an even higher ceiling of ingredients to work with? Would you mind helping me test something?”\par
“I don’t mind, this is legitimately good practice for Weapon Aura. I crossed the Elite-level in the skill just from this,” Orodan remarked, shocking Castillius silent once more.\par
To the side, Mahari who was watching all this time finally spoke up.\par
“Well at least you got to make a ‘glowy’ potion of your own Orodan!”\par
Orodan had a beaming smile on his face in response.This tale has been pilfered from Royal Road. If found on Amazon, kindly file a report.\par
\par
The rest of the concoction turned out to about nineteen more potions, which Orodan had little use for so he had a staff member send them back to the Burgher. He was sure the man would appreciate them as a gift.\par
Orodan was brought to a back room which was an elaborate alchemical workshop. He was accompanied by Master Castillius and two other instructors who were Elite-alchemists.\par
“Mister Wainwright, we’ll handle the preparation of ingredients for this potion. All I ask is that you attempt your unique method and perform the infusion of mana into the potion at the critical juncture,” Castillius spoke. “Not only is your method unlike anything I’ve seen done before, but the sheer reserves of mana you possess are… well I won’t pry into how you managed to create that potion. You combat specialists are a different breed when it comes to mana reserves I’m sure.”\par
The average alchemist would need to chug mana potions of their own or have pre-prepared a mana battery device to feed mana into the concoction, particularly for higher level potions.\par
“Alright, but before we do this might I know what the potion is, what the ingredients are and in what form they’ll go into the liquid mix? Extending Weapon Aura over a liquid is harder than I thought it would be, and I have to account for everything within, each individual piece and grain of powder.”\par
“The amount of mental power that would take is ridiculous,” Castillius muttered as he shook his head in disbelief. “But to answer your question, we’ll be making an Elite-level concoction, a potion of overflowing mana. It’s meant to give the imbiber a temporary boost of incredible mana reserves, and unlike many other potions at the Elite-level, this one has a rather simple mana empowerment phase much like the potion you made earlier. Unlike the water base of your last potion, this potion uses dragon tears as a liquid base. A hydra’s heart which will be boiled in the concoction during the heating phase to have its essence spread. A unicorn’s horn which will be ground down into powder and a crushed estrigus mushroom sourced from the depths of the energy well at Arthus.”\par
If they were the source of ingredients used in Elite-level potions, then Orodan could see why energy wells were treasured commodities now. The one at Arthus must’ve been quite heavily guarded.\par
“I see, we can begin whenever you’re ready,” Orodan said and watched the process closely.\par
A Master-level alchemist operated quite efficiently. His two Elite-level assistants were there to assist in handing him things, feeding him mana potions as he magically prepared the ingredients, and in helping move and prepare some of the alchemical equipment which Orodan hadn’t read about in the textbook. High level alchemy was quite the art.\par
Within fifteen minutes the ingredients were prepared and carefully mixed into the liquid. The three alchemists worked very well together as a team, as certain equipment pieces were almost designed to be operated by two people. Even the cauldron that held the concoction looked incredibly expensive, with numerous glowing enchantment lines etched across it.\par
The heating began and one of the assistant alchemists was in charge of managing the fire, which changed color and temperature constantly. He was reading a sheet of paper with sequential directions for temperature changes, almost as though he was conducting music. It was a constant job which he couldn’t step away from.\par
Another was in charge of monitoring the concoction itself, and this woman almost acted as a spotter for Castillius, who she was periodically muttering changes and directions to while she peered into the concoction with a magical monocle. Castillius’s ladle moved in different directions and he occasionally squeezed a drop of what Orodan read was a single-use catalyst, making the reactions within the container speed up as needed.\par
Castillius himself took charge of what looked to be the hardest part, which was mixing the ingredients correctly and giving directions to the temperature controller as needed.\par
Finally, as the heat reached a critical level, it was time.\par
“Mister Wainwright, in ten seconds the mana will completely disappear from every other source in this concoction, then the stage is yours,” Castillius explained, and Orodan got ready.\par
As warned, over ten seconds all the mana from within the concoction disappeared, and the three alchemists backed away. It was now Orodan’s turn to direct this creation.\par
He put all four minds to immediate work in furiously getting Weapon Aura around the liquid as quickly as he could.\par
It was difficult, far harder than when he was doing this with the other potion.\par
The heart held vitality which also needed to be wrapped around, and the unicorn horn powder held traces of soul energy. He had to account for and somehow wrap Weapon Aura around the energies themselves as well as the ingredients.\par
A full minute passed and his four minds worked so intensely that he bled a little from his eyes as the sweat dripped off his brow.\par
Weapon Aura levelled to 74 over the course of that minute, but he finally got a proper wrap around the concoction.\par
And then he began pouring his own mana into it.\par
To call it a titanic rebellion would be an understatement.\par
Once he passed the threshold of mana empowerment where the recipe told alchemists to stop, the sheer volatility of the ingredients was nearly overwhelming. Orodan’s Weapon Aura almost lost control.\par
The estrigus mushroom from the depths of the energy well was the most well-behaved ingredient. It was the other two that were not.\par
Orodan came to learn that ingredients from living creatures were far more volatile and hungry for change in a mana oversaturated environment than plants and herbs were. The hydra heart and the powder grains of the unicorn horn waged a true war against his Weapon Aura.\par
It was some of the most concentration Orodan had ever had to exert. His head hurt in a way comparable to his mental bludgeoning at the hands of Ilevida Balmento. Blood leaked from his eyes as he activated Death Rage to give himself improved reaction time which translated to even more focus crammed into each instant of time. And he had to flare Eternal Soul Reactor to feed the greedy demands of this mana-hungry potion.\par
This was devouring energy comparable to a Grandmaster’s mana pool if Orodan had to make a guess.\par
The mental war raged on for ten whole minutes as more and more mana was poured in but his Weapon Aura retained its grip and levelled up to 75.\par
Finally, a built-in enchantment within the container gave off an alarm, and Castillius bade Orodan to stop lest the very expensive cauldron be damaged.\par
He stopped supplying mana into the concoction, and the sheer amount of mana coursing through the liquid still took a while to die down even after he cut the supply off.\par
Finally, once the mana within completely ran dry, he dispersed Weapon Aura from the alchemical concoction.\par
\textbf{[Alchemy 11 → Alchemy 16]}\par
The liquid was almost blindingly bright, a beacon of pure cyan radiance which lit up the entire workshop. The three alchemists in the room couldn’t even look at it, but Castillius immediately marched up to the cauldron almost desperately, not even waiting for the concoction to be bottled.\par
And he used Identify.\par
The man began to tremble and nearly fell onto his behind if not for Orodan steadying him.\par
“Well? I think it achieved at least something right?” Orodan asked.\par
“It… it’s a Grandmaster-level potion… what even are you?”\par
\par
Old Arvayne Firesword had come by shortly after accompanied by an old woman who was the headmistress for the school of alchemy. This woman took half of the potions from the batch for herself and the remaining half was split between Orodan and the three alchemists who had worked on the concoction.\par
Orodan had no issue with this given that the ingredients were provided by the man and it was his recipe and formula. Plus, while he could sense a tremendous amount of mana within the potion… he really had no use for potions of the sort given his Eternal Soul Reactor. Mana wasn't an issue for him.\par
So he gave his share to Arvayne, which made the old man’s eyes shine with covetousness for once at the ludicrous gift fit for a Grandmaster.\par
The woman was Elona Bursimi, a Grandmaster-Alchemist who informed Orodan that he would be learning alchemy directly underneath her moving forward.\par
Orodan thought this was becoming something of a trend, but decided to keep his thoughts to himself on the matter.\par
They dispersed shortly after with Arvayne lecturing Orodan a bit and simply sighing and looking disappointed at Orodan’s utter inability to lay low.\par
The other crafting classes thankfully weren’t anything crazy.\par
Enchanting went decently, and Orodan discovered he had an average talent for the craft but still managed to gain a few levels in the skill raising it upto level 12.\par
His ability to maintain concentration for an endless period of time, alongside his bottomless energy allowed for him to enchant without interruption and the breaks that other students needed to take. He wasn’t a prodigy by any means and performed no ground-breaking achievements like he did in alchemy… but he still progressed a decent way over the span of just six hours of a class. His endless reserves and concentration however did impress the instructor who was personally assigned to him.\par
For now he was practicing in the Imperial tradition of mana-based enchanting, but the head-instructor who was a Master-Enchanter assured him that once he reached a certain level, the man would introduce him to Gormir Eltros. The Master-level enchanter who Orodan had heard of prior, who was capable of such things like body enchantments and enchantments using soul energy instead of mana.\par
Orodan could have used his reputation to ask for it right away, but he felt that getting a deeper understanding of Enchanting and pushing its levels up the standard way first was better than jumping ahead too quickly.\par
Blacksmithing however, was an interesting class.\par
The class probably had the highest number of combat-specialist students who were cross-training that he had seen. The idea of forging one’s own equipment was a popular one among warriors. Even many enchanters were participating in the hopes of learning how to create a superior product to enchant upon. After all, the better the initial base, the greater the enchanted item that could be made after.\par
He also made the interesting discovery that natural fires, which weren’t mana based, did in fact burn. Even if all his defensive and vitality skills gave him a body sturdy and healthy enough to ignore the burns from the forge, it still raised a good point that Orodan would probably get burnt when he encountered enemies using natural fires or non-mana empowered flames in the future. Still, it was fun sticking his hand directly into the forges to pull things out or adjust the things he was smithing. Perhaps he would obtain the Fire Resistance skill if he did it enough?\par
His talents in blacksmithing weren’t bad. His Physical Fitness allowed him to do some unfair things such as simply pounding metal with his bare hands and bending it into shape. He quickly gained the Blacksmithing skill and raised it all the way to 14, aided by his existing Tool Mastery and Laboring. Additionally, cleaning up the forge and workstation actually gave him two levels in Cleaning! Cleaning up a different environment for once must have spurred the level gain.\par
Woodworking went quite well.\par
The class also held a high number of combat specialists looking to make their own weapons. Mages wanted to make wands and staves, archers wanted to make bows, and warriors wanted to make weapon hafts and shields.\par
He was marked as a decent talent upon entry as the instructors were content with his existing Apprentice-level Woodworking skill. Tool Mastery aided him as per usual, and he actually managed to level Woodworking to 44 and Tool Mastery to 49.\par
His Wood Communion skill was looked upon with incredible favor and the headmaster of the school of Woodworking came down near the end of class to meet with him and spoke for a bit revealing that he too possessed the Legendary skill and offered to give Orodan personal lessons in cultivating it. Apparently the exquisite rarity Wood Whispering skill was common among prodigies, but Orodan was the first student he had seen with the legendary Wood Communion skill aside from himself.\par
Headmaster Osolon Velrayn, was a man of half-elven descent. He openly claimed this, for otherwise Orodan would not have known as half-elves didn’t have any uniquely elven features that made them stand out. Only in very rare circumstances did the elven blood dominate and the pointed ears appear in half-elven folk. A fact that allowed them to blend in rather seamlessly within human society.\par
The man was quite happy to have a martial student of Orodan’s caliber in his school who took Woodworking so seriously and invited him to come by his quarters in the Bluefire tower for tea sometime.\par
Finally, came the Politics and World History classes that Orodan had dreaded. He was assigned personal tutors in each of these classes, but as he had come to learn, the reading wasn’t as bad as he feared.\par
He learned some interesting things about politics.\par
For starters, although he heard it from Cyvrosdyr in a prior loop, dragons had their own society and groups known as dragon flights.\par
They had cordial relations with humanity, but had tense relations with the dwarves who were a race notorious for dragon slaying. Hence the lack of dragon flights near the Dokuhan mountains to the south.\par
The dragons’ one point of contention with the humans of Inuan was the insistence on worshiping Ilyatana, the Goddess of Fate. The dragon race viewed her as a historical mass genocider of their kind. The politics textbooks noticeably did not mention the fact that Ilyatana was once a mortal many millennia ago, but he recalled Cyvrosdyr saying this to him during his loop on Guzuhar.\par
Orodan felt he would get along well with the dragons due to their mutual hatred of that conniving Goddess.\par
Additionally, the Republic had pretty good relations with the local Time Wind dragon flight which flew between Karilsgard and the Eastern Kingdoms. In fact the two dragons he saw flying about many loops ago in the aftermath of the war machine’s destruction of Volarbury County, were actually the famed Master-level dragons Ulrusdun and Arkulnir, who were honoring an old pact between the Republic and the Time Wind dragon flight to render mutual aid to the other in times of need.\par
There were friendly dragon flights throughout the Eastern Kingdoms and elven continent as well, however the Novarrians were infamous for enslaving dragons, and thus there were constant tensions on that front. The only thing stopping outright war was the fact that the ‘dragon flights’ of Novarria were willing to defend the Empire’s practices. The textbook painted Novarrian aligned dragons quite negatively.\par
As for Cyvrosdyr… the World Guardian was quite famous indeed!\par
Orodan could now finally tell the dragon that he had read books about him, even if they were very old legends. The Eternal Winter was quite revered as a guardian of the world and was respected for descending unto the elven continent fifteen-thousand years ago and slaying a terrifying Eldritch invader from the stars after the hero of the elves failed.\par
There were at least two other known World Guardians like him.\par
Sarastuga the Blazing Light, a beloved lion of epic proportions which prowled the Eastern Kingdoms and kept humanity safe. And Elydia the Returning Fire, a phoenix that flew above the Dokuhan mountains and the arid badlands to the south where no civilized life could thrive.\par
Orodan recalled both of these World Guardians bravely fighting to the bitter end against the Eldritch Avatar.\par
Aside from the humans on Inuan and the elves on their own south-eastern continent of Eldiron, were the dwarves. The stout race had a better relationship with the Novarrians than they did the Republic or Eastern Kingdoms, thanks to their shared greed and dragon slaying tendencies. But the under-mountain dwelling race was at frequent odds with the drow who they were steadily beating back in a cold war that had been going on for a few years now.\par
The dwarves were gaining ground on the drow thanks to the intervention of the Novarrians on the dwarven side. The unfortunately isolated drow were losing a slow struggle as they were without allies nearby.\par
Finally, there were the minor races which didn’t hold any significant power on the same level as the major races. Such as the orcish tribes of the Dokuhan mountains who lived above the dwarves and struggled to eke out a living. Wandering goblin tribes who were a constant annoyance throughout the wilder regions of Inuan and were to be killed on sight. And the communities of halflings who had essentially integrated into human society in the Republic and Eastern Kingdoms.\par
Orodan was embarrassed to admit he did not realize that Lucille Carrotfoot was a halfling when he first met her. Apparently Carrotfoot was a halfling surname. He just thought she was a very small woman in their first meeting. Probably helped them integrate rather smoothly.\par
There were also some destinations of note he eventually wanted to see.\par
Energy wells being one of those things. The energy well at Arthus in the Republic was only one of many. And even the one Orodan discovered, while deep, still wasn’t the deepest known in the world. The two deepest ones in the world were unclaimed by humans, but were instead wild and surrounded by some of the largest monster hordes known to man.\par
The first being the one at Suicide Point in the arid badlands south of the Dokuhan mountains. None of the mortal races dwelled in the badlands. Even the hardy dwarves went no farther south than the mountains.\par
It was a completely wild and uncivilized area that even dragons didn’t want to fly near due to the presence of some rather ferocious beasts in large numbers. The energy well at Suicide Point was the second deepest one in the world. And there were rumored to be some monsters down at the bottom that even an Avatar empowered World Guardian would be afraid of.\par
The deepest however, was north of the northern continent, within the Great Zalabian Ocean. It was underwater. The closest spot that any golem exploration attempts had gone, was marked on the map as the Ocean’s Edge.\par
This energy well was the sole reason any northward exploration of the ocean past Guzuhar was impossible. The hordes of sea and flying monsters surrounding this energy well were simply too numerous and strong.\par
One day, Orodan wanted to try his hand at delving it. But that day was a long way away.\par
His World History and Politics classes thus went by without too much suffering. He learned some interesting things about the world, political relations and Republican and Novarrian society that he would no longer be surprised by.\par
His skill creation and applied skill combination classes had been cancelled. It would be handled during his training period with Arvayne, so the only class he had left for the day was ‘Monster Studies 210’.\par
\par
“So that hundred headed sea serpent that occupies this section of the Sea of Uxumar, it’s called a hydra?”\par
“Yes Mister Wainwright, that is the term for it,” the instructor answered. “Although historical records from a hundred years ago note it as having ninety heads, not a hundred.”\par
Well, the historical records were historical. He had killed it a while ago in a prior loop and could attest to the fact that it now had a hundred heads.\par
“And the rumors about them being able to grow new heads once one is cut off?”\par
“Not at the Master-level at least, but the ocean is quite massive... I’m certain there are stronger hydras out there in the deeper parts that hypothetically could do such a thing,” the woman replied. “Monsters have access to the same System we do, and could definitely learn a skill for it.”\par
Monster Studies was an interesting class. There were textbooks detailing a massive variety of monsters, but the class was focused more on theory and as an information hub for students who aspired to become adventurers upon graduation.\par
There were provided textbooks which detailed all known monsters, and there was only one instructor, a Master-level swordswoman who was supposedly a famous adventurer who retired a decade prior and was now teaching students at Bluefire. He recalled reading the name Belinda Arwell in his World History books, but had never heard of the woman in conversation.\par
“What about Demonic Berserkers? How strong are they?” Orodan asked, genuinely curious. “If a Master-level necromancer were to have a reanimated one as their pet… how strong would it be in life?”\par
“Unfathomably powerful, definitely near the high end of the Master-level. You’d need some very heavy ranged or magic firepower to deal with it. Melee combat against a living Demonic Berserker would be suicide for someone on the same level as it, mortals just can’t match that sort of ferocity,” Belinda explained.\par
Orodan simply smiled. He had absolutely matched its violent ferocity blow for blow while unarmed and even forced it to quail when he was but an Adept himself. The Demonic Berserker, even as an undead minion was a great teacher that taught him the value of true savagery and fury.\par
“And how about worms that dwell deep underground?”\par
“You would be a better teacher on the subject than me Mister Wainwright,” Belinda remarked. “My old adventuring friends wouldn’t stop talking about the rumors of someone killing a Dweller Worm in an energy well. And I couldn’t stop hearing about the tremors that lasted for over two weeks.”\par
Orodan thought the woman was being a bit melodramatic, but he appreciated her slightly snarky answer all the same.\par
“To be fair, it refused to die easily,” Orodan replied.\par
“I wouldn’t expect a Dweller Worm - notorious for their cockroach-like survivability - to die easily in any scenario. Two weeks sounds about right for how long it would take a team to kill it while working round the clock. Usually a rampaging Dweller Worm of sufficient size is the subject of a Quest.”\par
Belinda continued fielding questions from various students, all of whom kept a healthy distance from Orodan. Either due to being intimidated or just minding their own business.\par
“Then… in terms of toe to toe melee combat, can you recommend which monster you know of that would be utterly suicidal to fight?” Orodan asked.\par
“You ask some very strange questions that make me concerned for your safety and mental state Mister Wainwright. I almost suspect you’ve either fought or plan to fight the monsters you’re asking about,” Belinda quipped with an amused smirk on her lips. “But, I’ll do my best to answer. Some of the deadliest monsters up close? The Demonic Berserker you’ve asked about is one of them of course, but it can only be summoned nowadays which is quite difficult given how averse demons are to being summoned to our world nowadays. Or you’d have to join the crusade the Cathedral is organizing into the hells next year. Even then the crusaders are reporting that they’re getting rarer and rarer due to the constant incursions we’re making each year.”\par
“Alright, but surely that can’t be the deadliest? Is there not something more… ferocious in melee?” Orodan asked.\par
“A towering muscle bound freak with eight clawed arms, horns, sharp teeth and a rage that lasts for weeks isn’t ferocious enough for you?” the retired adventurer asked. “Well, let’s see… and I strongly recommend you don’t do this. But given your predilections for delving the depths you should at least be aware of Death Roaches. They aren’t even listed in the textbook, but they’re horrifying.”\par
“Are they related to Malzim perhaps?” Orodan asked, a bit hesitant to kill something related to his favorite God.\par
“No, we just named them that for how utterly unkillable they are and how much death and devastation they cause. People talk about regular cockroaches as if they’re tough… but wait till you meet their angry and mutated relative in the deep depths,” Belinda remarked. “It’s a terrifyingly strong and fierce bug that fights with a level of ferocity beyond even a Demonic Berserker. At least the demon’s big and you know it’s coming. The Death Roach is almost man-sized and even tougher. All that power packed into a small frame means it’s deadlier than a Demonic Berserker in melee. It’ll sneak up on you without you realizing it too.”\par
“So are we likely to ever fight one?” a random student interjected and asked.\par
“No, and I pray to the Gods for your sake that you do not. I’m indulging Mister Wainwright’s questions because he’s a stupidly talented prodigy that can wrestle Dweller Worms in the wild depths for two weeks straight. He’s apt to make the sort of questionable life choices that might lead to him encountering one,” Belinda spoke. “But as for the rest of you, unless you’re likely to reach the Master-level, don’t get arrogant. Death Roaches and Dweller Worms, outside of unique circumstances such as an energy well, typically begin to occur from the deep depths and below. There are records of hundred man strong heavily armed expeditions composed of Master-level adventurers and military personnel being wiped out after they ran into a Death Roach while unprepared. Reach the Master-level first and then think about such creatures.”\par
The rest of the class went on as usual, and at the end as students were filing out Belinda gestured to Orodan to remain behind.\par
“Mister Wainwright, Arvayne Firesword speaks highly of your… ‘determination’,” she remarked. “He also told me to avoid insulting you lest the backlash from a skill of yours makes me regret it.”\par
Now that was just excessive. He felt as though he acquired a slight bit of control over Warrior’s Reciprocity at level 2. He could maybe tone it down and actually hold back if she decided to make a comment about his intelligence.\par
But would he?\par
No.\par
Therefore it was good advice the old man gave her.\par
“As long as you don’t make any comments about my intelligence to my face, I think you’ll be fine,” Orodan clarified.\par
“That won’t be an issue. Despite my carefree attitude I’m not so stupid as to directly offend someone who fought a Grandmaster-level Dweller Worm in the depths by himself. Avatar assistance or not, you’re a monster and I respect that,” she spoke with a level of sincerity. “I actually wanted to speak to you about your last question.”\par
“About things that are stronger than a Demonic Berserker in melee? Death Roaches are one of those things right?”\par
“Yes, but what I didn’t say in front of the other students is that Death Roaches are particularly powerful Grandmaster-level monsters. Even though they're of the same level, a Death Roach would tear a Dweller Worm in half if they fought, so be careful. With your monstrous talent at your age, I think with at least a few more decades of training and adventure you’ll be ready to face one, maybe even by yourself,” she answered. “But… there’s something even stronger. It’s probably the most dangerous thing we have records of. The only reason I’m telling you is because Arvayne Firesword explicitly told me to not withhold any knowledge from you like we usually do when it comes to overeager youth who might otherwise run into the depths to prove themselves a prodigy.”\par
“Oh? I’d be interested in fighting such a thing,” Orodan excitedly said, a happy grin on his face.\par
“I assure you, you will die. Even a Chosen One Avatar is but prey before it… at least give yourself a few centuries before you try your hand against it.”\par
“What is it?”\par
“It’s called a Void Horror,” she replied. “The last known sighting of one was maybe… thirty-thousand years ago? It’s an old legend that speaks of a tall, gray humanoid with empty white orbs for eyes. It’s savagery was unmatched in the legends.”\par
Tall, grey humanoid with empty white orbs for eyes? Why was this sounding so familiar.\par
“Where can it be found? What happened to the last one?” Orodan found himself asking, even though he had an inkling he knew exactly where it could be found near the end of the year.\par
“The legends say the last known Void Horror came crawling out of the abyssal depths and caused the collapse of civilization on the entire continent, the Gods then had to send multiple Avatars down to suppress it, and it was sealed into a rock and thrown out into the vast expanse between worlds.”\par
Where it must have undoubtedly encountered the Eldritch Gods and mutated into something utterly horrendous that was now being returned to the sender.\par
What a fantastic show of responsibility and forward thinking by the Gods.\par
“So these Void Horrors… there are more of them down there?” Orodan asked. “Also, while I guessed there are depths lower than the deep depths, the books don’t talk about the abyssal depths. Can you tell me about them?”\par
“I’ve never been there, but I would assume there are more down there, yes. I would be unqualified and likely wouldn’t even make it to that point. The only people that dare to enter are Grandmasters, and even they would only do so in force. The last time such a thing happened was at least a thousand years ago,” Belinda answered. “From what my mentor tells me, the abyssal depths aren’t as densely populated with monsters, but even the weakest one would be a Death Roach or something similar in power. There are some utterly kingdom-shaking treasures to be found… but even Grandmasters don’t want to enter for fear of what horrors lurk down there.”\par
“You know… you’re awfully forthcoming about such a dangerous topic. Aren’t you supposed to warn me away or something as a teacher?”\par
“Would it stop you if I did?”\par
“Not in the slightest.”\par
The depths held some powerful foes. It was an attractive prospect and made his blood boil for combat at hearing about the abyssal depths. But currently he wasn’t sure he could even get through the entirety of the deep depths.\par
Death Roaches that could tear a Dweller Worm apart like a chew toy? Void Horrors that caused the collapse of civilization on an entire continent? Orodan was eager to go smash his head against this wall immediately!\par
But it would be wasteful and inefficient to do so right this instant. It was better to let this loop naturally run its course first and see how the battle against the Eldritch Avatar changed.\par
Would he spend a series of loops just battering against the horrors of the deep? Absolutely.\par
But for now his last class of the day was over and it was time to go training with Arvayne Firesword.\par
\par
“Isn’t this too big of a pile? What am I even supposed to do with all this?” Orodan asked.\par
“Who else am I going to use these natural treasures on? I’ve been stockpiling these for a thousand years, and now’s the time to see them used on the single most monstrous talent I’ve ever seen,” Arvayne spoke. “So get to work, pick up that black orb.”\par
It was an orb of pitch black color, the size of a palm sized fruit.\par
“What’s this and what does it do?”\par
“It’s an endless gravity core, I found it while adventuring in the deep depths when I was younger. The machines warriors use to train their Physical Fitness use artificial ones created by artificers to work. But this one is naturally formed and is the most powerful one in the Republic,” Arvayne explained. “Hold on and channel your mana into it, it’s excellent for training Physical Fitness.”\par
The most powerful endless gravity core in the entire nation? Arvayne was a wealthy man Orodan thought.\par
Orodan did as Arvayne asked, and almost instantly, the gravity upon him grew immensely and even Orodan’s powerful physique was strained.\par
It felt as though each muscle in his body was bearing the weight of a small mountain.\par
Arvayne told Orodan to hold onto the endless gravity core and practice as much as he could.\par
After an hour, his Physical Fitness increased by a level to 66!\par
But, something still felt slow. Something about this sort of training dissatisfied Orodan.\par
It was too safe.\par
“Old man, this is nice and all. But it isn’t enough, I need more,” Orodan spoke.\par
“What do you mean you need more? You want me to throw another gravity core at you?” Arvayne asked with a raised brow.\par
“No, as in we could be doing multiple things at the same time,” Orodan answered. “Why don’t we fight?”\par
“That core requires constant focus, contact and a source of energy to remain active. If we sparred, the gravity effect would just stop, thereby rendering it a waste,” Arvayne explained. “If you’re this eager I’ll add some intense exercises to your training after your session with the orb.”\par
Orodan did not like this explanation.\par
So he pondered and came to a decision.\par
The orb required constant contact and focus? No problem.\par
“What… what are you doing?!” Arvayne asked in shock as Orodan’s mouth opened wide and one hand shoved the orb in as far as he could.\par
It wouldn’t go down comfortably, but it was a good thing Orodan had Pain Resistance.\par
His other fist slammed the orb into his mouth, and a quadruple action increase session began where multiple hands were pounding the solid orb down Orodan’s throat even as his teeth shattered and his mouth became bloody.\par
It settled uncomfortably in his stomach, as though it was grossly unnatural and quite painful. But he had done it. Orodan had successfully swallowed the palm sized endless gravity core.\par
He flared Eternal Soul Reactor to empower Regeneration, only to make a painful discovery.\par
The endless gravity core could also be powered by soul energy.\par
And any activation of Eternal Soul Reactor naturally had soul energy run through his body. Which thereby naturally activated the core.\par
Orodan nearly fell to the ground as the orb was empowered beyond any levels it had previously been. His soul energy was potent and far stronger than his mana. The core’s gravity increased to the point that it was tearing apart the muscles of his stomach and was on the verge of ripping right out of him.\par
He flared Eternal Soul Reactor to empower Regeneration further only to realize that it was making the pressure on his body and the weight of the orb even heavier.\par
He immediately activated Death Rage and the increased strength allowed him to hold on a bit easier even as his life force drained and blood leaked out of his pores.\par
Now this… this was real training!\par
“You! Orodan Wainwright! What are you even doing?!” the old man roared. “No! My lord do not praise his buffoonery!”\par
Agathor must have been telling the old man how he approved no doubt.\par
The pain was quite high, but nothing his Pain Resistance couldn’t handle. Slowly but surely he continued making minor adjustments.\par
First, he began thinking economically. How could he empower Regeneration with the least amount of soul energy for the most buck?\par
Eternal Soul Reactor began to gain levels as this self-mutilating training continued and he began to fine tune the skill. Regeneration improved as well as he learned to do more with less fuel.\par
All the while, his Physical Fitness gained another level and rose to 67 as he strained each and every muscle to the limit and continued honing himself. It was effective training and Orodan couldn’t forget to train the skill the endless gravity core was meant for.\par
He wanted more vitality, but he couldn’t get it from soul energy lest it tip the critical balance. So Orodan experimented and drew upon the reserve of Vitality Black Hole, and threw all the excess vitality into Death Rage.\par
Both skills began gaining some very rapid levels at this unique experimentation, and for a moment Death Rage was beginning to get strong enough that the burden of gravity upon him was beginning to feel light.\par
So he simply cranked up Eternal Soul Reactor once more to increase the weight even further. There would be no slacking off.\par
Furthermore, Orodan began to attempt a unique experiment. His muscles were genuinely being destroyed under the fierce pressure of the now deadly gravitational force of the endless gravity core. So why not flood the destroyed muscles with vitality?\par
He experimented, and worked on different methods of acquiring what he wanted.\par
Even as his destroyed muscle cells were annihilated, any new ones that came to be due to the vitality were still subject to the same pressure. But they needed to adapt, the weak needed to be destroyed to give birth to the new. The pressure on his body wasn’t merely downward, but it felt as though he was being pressured and squeezed into a meatball. Crushed from all directions, every single part of his body was under the pressure, even the interior.\par
He increased the soul energy empowering the core to an almost fatal level.\par
Ten minutes passed and as he was keeled over, bleeding everywhere and felt as though his innards would explode, he finally achieved the adaptation that he was looking for.\par
\textbf{[New Skill (Legendary) → Body Tempering 3]}\par
It started off at level 3, no doubt due to the extreme circumstances in which he acquired the skill.\par
His muscles which were being constantly destroyed and rebuilt, were finally being regenerated stronger. His physique was improving as he constantly destroyed his own body and tempered it to be stronger. It was forged anew.\par
Within the next ten minutes of this, Body Tempering reached level 11, and Orodan felt as though each and every point of Physical Fitness went further. He felt as though he had nearly doubled in strength with just this. As though he had a fundamentally superior body like a monster naturally did.\par
He finally had enough strength to get to his feet. The omnidirectional gravitational pressure from the core was now bearable.\par
He looked at the old man and drew his sword.\par
“Old man! Let’s not waste time! Spar me while I continue practicing with this endless gravity core!”\par
Following his declaration Orodan once more empowered the core to the limit of what he could take. It put him under severe pressure and limited his battle power, but from now on Orodan decided he would keep the endless gravity core at its maximal limits at all times.\par
It seemed like quite the good training tool.\par
In all his years, the old Grandmaster had never seen or heard of anyone using a gravity core like this for training.\par
Arvayne Firesword could only look at Orodan as he finally understood.\par
It was one thing to hear the boy talk about the time loop and everything he did. But it was another thing to see the madness, the insanity that was Orodan Wainwright.\par
To witness what the mad fool considered real training.\par
He now understood how this lunatic had come so far.\par
Who was Orodan Wainwright?\par
As a Flash Strike from a desperately straining warrior - bloody grin on his face - approached, Arvayne Firesword now understood the answer.\par
Orodan Wainwright was a warrior.\par


\section*{Chapter 20 - The Bluefire Academy IV}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 20 - The Bluefire Academy IV}%
\par
When he got down to it, Arvayne Firesword sure knew how to deliver a good beating.\par
Perhaps it was Agathor’s encouraging comments that had angered the old man?\par
Either way, the symphony of pure violence and bodily devastation Orodan was now on the receiving end of was quite intense.\par
Even without an endless gravity core weighing him down to his maximal physical limits, Orodan would be on the losing end of any melee exchange against old man Arvayne Firesword.\par
The man was a triple-Grandmaster and the Chosen One of Agathor. He was the second-strongest warrior in the entire Republic after Alcianne Rockwood. Orodan at his current level wasn’t quite there yet.\par
The old man thankfully had a sense of fairness and accommodated his strength to match the self-imposed training handicaps Orodan was using, but it was still a brutal beating and butchery.\par
“Are your defensive and vitality skills improving? Give me an update,” the old man calmly demanded as he continued hacking Orodan up. “I can increase the speed of my assault if you need.”\par
“Iron Body is improving quite fast,” Orodan quickly said as his arm was lopped right off but regrew shortly after. “As is Slashing Resistance, but I could use some more beatings and stabbings to improve Impact Resistance and Piercing Resistance.”\par
Slashing Resistance had increased to level 45, an insane rate of growth as his limbs were constantly lopped off and he was sliced and diced up like a vegetable at a restaurant. Iron Body had improved to 67, approaching the Elite threshold, and most importantly, Regeneration had made a titanic jump to level 51, crossing into the Adept level. This was due to his experimentation and attempts at making the skill do more while being fueled by less soul energy.\par
His wounds patched together at terrifying speeds now. At the Grandmaster-level, combatants could launch hundreds of attacks a second, but even the average Grandmaster would have some minor trouble keeping up with Orodan’s regeneration now even if he stood still and simply allowed them to butcher him.\par
Arvayne wasn’t the average Grandmaster however. He was the second strongest warrior in the Republic and happily complied with Orodan’s request for more blunt force impacts and more stabbing.\par
Piercing Resistance and Impact Resistance also increased, to levels 41 and 43 respectively, which were massive jumps as well.\par
The real reason this training was so effective, was due to the sheer amount of strain he was under due to the endless gravity core making all his muscles feel as though they were about to explode.\par
Frankly, they were exploding. Whenever he gained a level in Body Tempering, Physical Fitness or Death Rage, his strength would increase and the pressure would become just slightly more bearable…\par
…and then Orodan would immediately increase the soul energy he was feeding the core, and the omnidirectional crushing weight would increase to the point that he could barely hold on once more.\par
It was constant progressive overload. Orodan survived by the absolute narrowest of margins, and he made sure to always remain right near the cusp of death so that he could simultaneously level Dying Struggle too!\par
Multi-tasking, Orodan called it.\par
Arvayne Firesword called it masochism, but still gladly helped.\par
Throughout the entire ordeal, Arvayne Firesword himself had to keep chugging an exorbitant supply of healing potions. It wasn’t for any attacks Orodan himself launched, or rather directly delivered.\par
It was Warrior’s Reciprocity, and at its current level of 8… it was strong.\par
The old man was forced to hold himself back lest he actually hurt himself by hitting Orodan too hard. Furthermore, Orodan hadn’t tested it yet, but he had a feeling that even if a blow came his way that completely killed him, it might still be returned with more than twofold the power.\par
So if Arvayne Firesword hit Orodan hard enough, the old man might actually manage to kill himself.\par
Orodan thought it was an unfair victory that wouldn’t necessarily last or have any impact since the time loop would just send him right back in time.\par
Furthermore, enemies with healing or resurrection abilities such as a phoenix might be able to afford the damage trade. But it still made Orodan feel at least a little proud, knowing that if he got the skill strong enough, he might even be able to kill the Eldritch Avatar if he goaded it into launching the most powerful attack it had.\par
Not that he’d be alive to see the results of course.\par
The two of them continued their spar, as Orodan continued gaining skills in various levels. Death Rage, Pain Resistance, Physical Fitness and Shield Mastery. All four of these skills crossed the threshold into the Elite-level, and Orodan now had eight skills that were Elite. This gave him a monstrous amount of battle power as even monstrously talented Elites maybe had five skills at that level at most. He also had other skills soon to cross that threshold.\par
As his skills improved, Orodan’s battle power continued to steadily increase in the middle of fighting, forcing old man Arvayne to have to ramp up his own level of power in response.\par
“That Death Rage skill of yours is quite savage, very close to the level of ferocity a Death Roach fights with,” Arvayne spoke as the two continued fighting. “But while your temperament is quite suited for being a warrior, your tactics in combat are somewhat lacking.”\par
His tactics were lacking?\par
“Don’t look at me like that. I didn’t say you were a bad fighter nor that you’re unskilled. In fact, your level of unpredictable and savage aggression synergizes well with your existing skill levels and techniques,” Arvayne amended while he drank another healing potion to patch up the damage from his own blows returned stronger. “Rather, you simply attack and attack and press forwards like a raging avalanche rolling down a steep mountain. While this isn’t bad… you could try looking at the fight in a broader lens and perhaps using your attacks in a more strategically advantageous manner?”\par
“What do you mean? Show me.”\par
And Arvayne did show him.\par
A furious blitz of attacks from Orodan came the old man’s way, and the Grandmaster simply waited and bided his time, acting defensively.\par
Then, when Orodan finished with an All-Strike and was at the end of the combo, the Grandmaster suddenly began his.\par
Furious and aggressive attacks with the greatsword that slammed onto him like comets even when he managed to defend, unarmed blows that shattered his bones and pulped entire limbs, and when the greatsword connected, Orodan would be dismembered entirely and forced to regenerate as rapidly as he could to stay in the fight.\par
Just as Orodan got his bearings and was about to mount a defense however, the old man quickly evaded to the side and began launching wind blades of lethal air from a distance, refusing to allow Orodan the time to adapt.\par
When Orodan thought he was getting a grasp on this new form of assault, Arvayne Firesword then immediately closed the distance, wrestled him to the ground and then began savagely pounding his face into a pulp from a mounted position.\par
Despite his Wrestling skill, Orodan was forced to tear his own torso in half to get out from underneath the man and then regenerated from one half.\par
The room looked like a scene out of a poorly regulated butcher’s shop. Orodan’s body parts and blood were strewn everywhere. It was starting to feel somewhat similar to his early loops against that undead Demonic Berserker… and Orodan loved it.\par
Arvayne drank another healing potion as mutilating Orodan in such a grisly manner had done some decent damage to the old man as well.\par
“I see what you mean now… it’s not about just using my skills and being aggressive, but also about how I use them?” he asked as he used Flash Strike to close the distance and engage Arvayne once more.\par
“Now you understand. Your Combat Mastery is near the Elite-level yes? Why is it that despite having such incredible combat instincts, reflexes and intuition that you aren’t advancing in it as quickly?” Arvayne asked. “Did you know that career tournament fighters, even at the Adept-level, will often study scrying eye recordings of their opponents and even of their own fights? They’ll sit down and examine openings, observe the patterns in their own fighting styles and sometimes change their approach to a fight in the middle of battle. You already do this instinctively sometimes, which speaks well of your natural combat genius. But it’s time to adopt a more focused approach and truly concentrate on the tactics and patterns of your own style and contrast them against your opponent’s.”\par
Orodan was grateful for this insight.\par
While he grew up fighting and would say the act came naturally to him, the thought of closely examining patterns and trends in battle like some sort of tactician never really occurred to him. He might’ve done it instinctively, but not with the focused ardor of a scholar of combat.\par
But how could he possibly improve his current style of combat? He was a raging volcano, one that would keep attacking and take whatever came his way. But it was difficult to contend with an opponent that was superior in terms of power, skill and durability to him. Maybe one of the few things Orodan could say he was better in was survivability, but he was otherwise outmatched. And of course the man hadn’t even tapped into his Avatar form.\par
“How can I work on improving my combat style?” Orodan found himself asking.\par
“Well for starters, excuse my crass language, but you blow your load almost immediately the moment you get a chance,” the Chosen of Agathor explained. “All you’re focused on is attacking. You’re a maniac that fights like he has a death wish. The sheer violence and ferocity of your vicious assault is impressive no doubt. Nothing at the Master-level or below could ever hope to stand up to you… but if you want to improve your combat style, how about reserving your aggression and constant desire for attack for more opportune moments? Right now, I can see moments after you launch an All-Strike or a particularly barbaric assault where I can begin my own and cause some serious damage.”\par
“Are you suggesting… that I fight more conservatively?” Orodan asked, the thought of doing so almost felt antithetical to his very nature.\par
“Yes. While my lord fights similarly to you, he also guides his godly rage and aggression along the ebbs and flows of combat with divinely perfected skill,” Arvayne explained. “Tactically choosing the best moments to deliver your brutal aggression isn’t cowardice.”\par
Orodan decided to actually try what the old Firesword suggested.\par
While he was getting utterly demolished, he attempted to mix his skills in a creative way for once.\par
Evasiveness was used to avoid a blow, and Orodan stepped to the side and backwards. Arvayne followed with a Lunge… but the rapidly approaching Grandmaster was met with a Shield Throw.\par
This Shield Throw masked an All-Strike which was summarily blocked, but the sword that carried the All-Strike was simply let go of. And as old Arvayne Firesword’s guard was up high…\par
…Orodan creatively used Surprise Attack in the middle of a fight to catch his opponent off-guard by going low. As long as the opponent didn’t see an attack coming, it triggered the skill.\par
His Surprise Attack empowered his movement and he dashed in low for a double leg takedown and employed his Wrestling skill to try and bring the old man to the ground.\par
Arvayne was taking the fight easy and thus was caught by surprise. A titanic boom echoed across the training chamber as Orodan took the old Firesword to the floor with a tremendous slam.\par
He got on top and began launching a furious barrage of unarmed blows upon the old man. Fingers went for eye gouges, he tried to grab the Grandmaster’s hair, and all the while a quadrupled action increase allowed for multiple arms to rain fists down on him in the same instant of time.\par
He covered his fists with Weapon Aura and any return blows from the old man underneath were countered by one of his action increase selves using Impregnable Bladewall and applying it to his fists to defend while simultaneously mixing in Perfect Parry at opportune moments.\par
He ignored the skill level messages and simply kept fighting.\par
A War Cry roared out from his mouth as he focused like a dog and flared the Eternal Soul Reactor as hard as he could, thereby making his body weight quite heavy, adding to the weight of his body which had Arvayne pinned below.\par
His muscles felt like they would explode, and he felt as though they were being obliterated and reforged to be stronger constantly. Arvayne Firesword’s eyes widened at the assault that took place within the span of a tenth of a second.\par
And then the old man acted.\par
A headbutt coming his way was the only thing Orodan saw before he lost vision.\par
His head had been utterly destroyed by the force and thanks to his incredible vitality skills he keenly felt his own headless body be thrown like a ragdoll and splatter in an explosion of meat and blood against the reinforced walls of the training chamber… which actually cracked from the force.\par
Over the course of a full second Orodan completely reformed from the puddle that he was and back into his own body.\par
Just in time to see Arvayne drop the empty Grandmaster-level healing potion he chugged. The backlash of hitting Orodan so hard had actually wounded the man decently.\par
“Congratulations, you forced me to get serious,” the old warrior said. “The only person to take me to the ground was Alcianne Rockwood, I guess this makes you the second, even if I was taking it a bit too easy.”\par
Orodan’s resulting grin of triumph didn’t last for long.\par
Arvayne could hold quite the grudge.\par
Moving forward, the training was finally just as harsh and real as Orodan wanted it to be.\par
His days off on the non-work days were also cancelled in favor of more training.\par
\par
Like that, an entire month of classes and training had passed.\par
If a single day of extreme hardship backed by training aids and personal tutelage could lead to such heavy gains, then an entire month allowed him to advance meteorically.\par
The old man admitted that Orodan now forced him to fight seriously from the get-go.\par
And while Arvayne could kill Orodan if he went all out, he said that the resulting backlash from killing Orodan might be fatal for him as well thanks to the Warrior’s Reciprocity. He outright admitted he’d have to tap into his Avatar abilities from Agathor to a slight extent if he wanted to kill Orodan without dying himself.\par
But there were still limits and bottlenecks.\par
For starters, while he now had a lot of Elite-level skills, the combination of which actually forced old Arvayne Firesword to get serious right away while training him… the slow-down point seemed to be at level 75. Each level past 75 was incredibly slow and took days or sometimes even a week of training.\par
It came as no surprise to Orodan, but there was no way he could grow meteorically forever. Not within a single loop lasting six months.\par
Even monstrously talented Master-level individuals took decades to reach the threshold of level 90 in a single skill. An example being Yarostov Iron-Bear up in Guzuhar, who was a Master of the axe by his eighties. The man was considered a prodigy just for that.\par
Orodan couldn’t just become a Master in a month. Especially not when he was focusing on so many skills all at once.\par
That he had crossed the Elite threshold and had nineteen Elite-level skills was utterly monstrous and without a doubt made him the single most powerful Elite to have ever walked the world according to Arvayne.\par
The more skills one had past a certain level, the more they synergized and granted power. A dual-Grandmaster was much stronger than a regular Grandmaster for example. Similarly, a monstrously talented Elite with five skills past level 70, would be much stronger than any regular Elite as the skills synergized if they were combat related.\par
So for Orodan who had nineteen skills past 70? Many of which had high rarities? He was an anomaly that could fight two tiers above his own. Who knew how powerful he would become once he crossed 90 in all these skills.\par
He had grown unfathomably powerful in just a month of guided and focused training of an extreme nature.\par
Arvayne had then taken him aside and explained to him where he currently stood within the power structure of society.\par
There was a hierarchy of power even among Grandmasters.\par
The weakest could be considered the average Grandmaster, such as Kuonthus Vexelthun, the jovial shield-Grandmaster Orodan had met a while ago. Newly advanced and a Grandmaster in a single skill. Orodan had handily surpassed this level by defeating Adeltaj Simarji, who was considered a high end Grandmaster on the cusp of becoming a dual-Grandmaster.\par
Then there were dual-Grandmasters, who Arvayne said Orodan was currently on par with. Ilevida Balmento who Orodan helped advance, was formerly one of these. They were incredibly powerful and included the likes of Yallista Arthurius, the headmistress of the schools of chronomancy and telekinesis, and Varna Altamari, one of the old Grandmasters that had aggressively questioned him after his fight with the Dweller Worm and was a part of the Chosen of Ilyatana’s faction.\par
Above that were Avatars which possessed Master-level Favored. Arvayne cautioned Orodan that while he could survive and defensively fight against one of these weaker Avatars currently, it was still incredibly risky and opened him up to the potential for permanent soul damage. Still, Arvayne looked at Orodan in a complicated manner and admitted that given his outrageous survivability he should now be able to outlast one until the host burned out completely.\par
Beyond the weaker Avatars however, were triple-Grandmasters. These exceptionally powerful individuals had lived for many millennia and were often the Chosen Ones of a God, with three Blessings. They included the likes of Arvayne Firesword and Alcianne Rockwood.\par
A step above them were World Guardians such as Cyvrosdyr the Eternal Winter and monsters who had reached the triple-Grandmaster level. Even if they didn’t have Blessings or Avatar empowerment they were utterly fearsome. Monsters who were triple-Grandmasters were far more powerful than their mortal counterparts.\par
Without any divine assistance, a triple-Grandmaster, even a mortal one, could beat a weaker Avatar.\par
And at the top… were Chosen One Avatars. Monstrous beings who Arvayne cautioned Orodan to be wary of until he had gotten strong enough.\par
Mortal Chosen One Avatars were fearsome enough… but what was truly fearsome was an Avatar that possessed a World Guardian. Currently Sarastuga the Blazing Light - the majestic lion he saw fighting near the end of his loop on Guzuhar - was the only known World Guardian capable of this arrangement.\par
Of course, there were stronger things in the stars and deep in the Abyssal Depths, one of which Orodan knew was coming near the end of the year. But that was much farther away for the warrior.\par
His own place in the pecking order aside, he had made tremendous gains.\par
While level 75 was hard to get past, it didn’t stop his existing monstrous talent and ability to pick up new skills and experiment. Arvayne had pressured him incredibly hard, and the result was two skills of excellent rarity.\par
\textbf{[New Skill (Exquisite) → Whirlpool Whirlwind 1]}\par
Was one he had acquired after a day of experimentation. It was now at level 38 after the month.\par
It was a wide area attack that caused lethal force blades to erupt in all directions, even downwards, as he spun continuously while also pulling everything in his vicinity towards him.\par
He was sure it would be great for pulling enemies inwards to their deaths or dealing with crowds and causing a large area of devastation.\par
But the other skill was a real difference maker.\par
\textbf{[New Skill (Legendary) → Endless Blitz 1]}\par
Was one he had gained after a week of experimentation and trying to acquire a skill that allowed for him to chain his attacks endlessly.\par
The old man’s ability to exploit an opening in Orodan’s attack patterns offended him, so he decided to acquire a skill that would make it so there were no openings to exploit. Energy consumption wasn’t an issue, so he wanted to be able to launch an endless chain of attacks, the momentum of one instantly leading into the other.\par
He refused to settle for the pathetic Multi-Strike skill which was of merely uncommon rarity, and even the Furious Barrage skill known for being exquisite rarity didn’t appeal to him. He needed something endless. The momentum of one leading into another, an endless blitz.\par
His desire bore fruit and he created the skill after a week.\par
It was now level 26 and seriously amplified his battle power.\par
While it could be used with regular attacks, the real power multiplier was the fact that it could be combined with any other active combat skill.\par
And Orodan tried combining it with All-Strike.\par
He tried using it to launch terrifying torrents of the skill towards Arvayne. Unfortunately the balancing act was the utterly disgusting amount of energy this consumed even with just a tenth of a second of constant usage. And while Orodan’s ability to produce soul energy and fuel the consumption wasn’t an issue, his body’s ability to conduct all that energy was.Unauthorized use of content: if you find this story on Amazon, report the violation.\par
He nearly killed himself the first time he unlocked it by trying to continuously launch hundreds of All-Strikes in the span of a second.\par
Arvayne turned him into a paste of red on the floor to stop him and save Orodan's life.\par
But in that second where the action hadn’t even been quadrupled… the old man had actually looked as though he was being pushed back.\par
But, new skills in combat aside, his training with the Grandmaster soul mage Arlin Colton took an interesting turn. On their personal tutoring sessions the man brought in a rather dangerous looking spear and decided to stab him with it.\par
The spear was apparently a divine artifact which Arlin had requested to borrow from the vaults of the Palace of the Council. It was empowered by a small amount of actual divine energy, and it was potent at causing soul damage.\par
So for the first time Orodan felt what it was like to have his soul harmed. And it was not comfortable. Not at all.\par
His vision went blurry, his emotions flew all over the place, and he felt Eternal Soul Reactor’s performance become inconsistent and unstable.\par
It took an absolutely titanic feat of willpower to rein things back in order, and Orodan made the discovery that Soul Manipulation aided in quickly repairing and recovering from any damage to his soul. So this was Orodan’s training in the soul, to be continually stabbed in the chest by a strange and dangerous looking spear which didn’t even get past his physical flesh due to his tough body… but it did cause him plenty of harm all the same.\par
He actually was causing damage to the soul of Arlin Colton every time the man stabbed him with the spear due to Warrior’s Reciprocity, which again proved just how broken the mythical skill was. He offered to hold the skill back from reacting, but the headmaster of soul magic insisted that being poked in return by twofold the power of a soul assaulting divine spear was helping train his own Soul Defense skill.\par
Eventually, after a few days of suffering he got the message.\par
\textbf{[New Skill (Rare) → Soul Defense 1]}\par
It thankfully greatly eased any soul damage he received. Furthermore, he found he could essentially empower it with his soul energy. And given that the amount of soul energy wasn’t any issue for him, the skill quickly gained levels and was now at level 33 after a month of training. It was also far stronger than the skill should be at its current level thanks to his higher quality soul energy.\par
He also trained with Ilevida Balmento in continuously improving his Psionic Resistance, which was also good training for her as the backlash from assaulting Orodan psionically helped her hone her defensive mental skills. Psionic Resistance was now at level 70, an Elite-level skill.\par
He was confident no Psionic attack would get through to him when fighting the Eldritch Avatar this time.\par
Combat aside, he also made gains in his crafting skills.\par
He was notorious across Bluefire now for being a madman who never once slept and simply kept working continuously throughout the night. Students didn’t really approach him anymore, thinking he was either crazy, dangerous or both. Even figures like Elucian Arslan kept their distance after he beat up Claridin Rockwood.\par
Frankly, students were beneath his notice at this point. At some point he might do a loop where he pretended to be a normal student in order to devote more time to the crafts, but even then socializing with most of them seemed rather tiresome. He was happy to occasionally run into Mahari and have her talk his ear off like the annoying younger sibling he never had.\par
Additionally, walking around with a constantly empowered endless gravity core in his stomach made situations awkward as he destroyed the floors and caused tremors with each step.\par
It took receiving an enchanted amulet from the headmistress of the school of gravity to sort the issue and let him go about without destroying the environment, even if the pressure on his own body never lessened. He basically walked around with the weight on at all hours of the day. Which was great training for Physical Fitness, which was now his highest level skill.\par
Not being able to eat at all for a whole month due to the gravity core wasn’t as bad as it sounded. He subsisted off of the energies produced by Eternal Soul Reactor. And a few adjustments of his internal musculature each day ensured the gravity core didn’t fall out without his express desire.\par
His Politics class taught him the Observe skill at last, and Orodan finally understood why people made such a big deal about titles. It was eye-opening to see people's titles and how they preferred to show off. He didn't think he would be using it very much, but it was still good to have.\par
As for his crafting classes.\par
Blacksmithing went steadily.\par
Orodan was forced to admit that of all his crafting pursuits, he had the least talent in Blacksmithing. It was only at level 28 after a full month of hammering away. Not that his work ethic and quadruple action increases were lacking, but he wouldn’t be participating in any magical smithing or higher-level crafting in this loop. It would likely take a few loops worth of the academy to get his skill levels up to anything worthwhile. He wasn’t going to be acquiring any Metal Communion skill just yet.\par
His instructors told him that he was still quite the prodigy for gaining 28 levels in the skill over a mere month, but Orodan felt dissatisfied at the slow progress compared to everything else.\par
Woodworking went well.\par
His Woodworking had crossed the Adept-threshold and risen to 51, and his legendary Wood Communion skill was at 44 thanks to the personal tutoring from headmaster Osolon Velrayn of the school of woodworking. He was told he was a decent talent at the craft and to keep at it. With his work ethic he was projected to reach high into the Elite-level over the course of his four years. Additionally, his ability to empower wood near-endlessly using Wood Communion was somewhat unbalancing the economy, and Arvayne told him to cut it out as it was causing him a headache and drawing far too much attention.\par
He was told to stop assisting Osolon in empowering various high-level wood products where the only limitation was mana amount. The headmaster of the school of woodworking became a very wealthy man thanks to Orodan, and was quite indebted to him even with just the two days of work Orodan had done before he was told to tone it down.\par
Enchanting was going rather decently too.\par
The skill now sat at level 34, and the instructors were quite enthralled to see someone with virtually endless mana reserves work on the craft and go from Initiate to Apprentice in only one month. Of course, unlike Alchemy and Woodcrafting this wasn’t something he could just pour mana into endlessly and break ground in. Enchanting was somewhat delicate work which involved etching mana into an object in certain patterns. Whatever he was enchanting could explode if he just wantonly tried to flood it with mana.\par
He had reached the skill level where a meeting with Master Gormir Eltros was coming up, and Orodan would then ask the man about enchantments that worked using soul energy.\par
Alchemy however, was a big one. It increased to level 48 over the month of personal tutelage from headmistress Elona Bursimi! The Grandmaster-Alchemist often dragged Orodan along to help ‘assist’ in making some absurdly powerful potions. He also picked up the Identify skill during his lessons here.\par
Whatever he helped Master Castillius make was merely scratching the surface. The headmistress of alchemy made potions that were at the Master-level to begin with, and then with Orodan’s help she empowered the potion even further.\par
Elixirs of youth, potions of time freeze, alchemical poisons which could chew right through the flesh of a Grandmaster monster. These were some of the products he helped the woman create. And even just working on the mana empowerment phase of these potions lead to some massive skill level gains for Orodan. Not to say it was easy, as unlike lower level potions these often led to Orodan failing to wrap Weapon Aura around the potion in time thereby causing failure. But despite an initial failure here and there the headmistress saw the potential in Orodan’s ludicrous method, which was essentially a ticket to free gold given his endless mana and ability to empower a potion well beyond its intended tier.\par
It got to a point where Arvayne had to step in and bully the woman when she tried keeping Orodan in her workshop past his allotted alchemy time.\par
Still, many of the potions he created went to some powerful people, and some of these people wanted to talk to him.\par
Hence the current conversation he was having with a woman he was explicitly warned to be cautious of. She had just walked in while he was in the midst of alchemy lessons with Elona Bursimi.\par
“Orodan Wainwright, you’re old Arvayne Firesword’s little protégé aren’t you?” the tall and burly looking old woman asked. “This potion you helped create, do you know what it did?”\par
“Lady Alcianne, the young man likely doesn’t kn-”\par
“Come now Elona, I’ve come here to speak to Orodan Wainwright,” the severe woman interrupted gently. Gentle as it was, it still sounded quite threatening, and the Grandmaster-Alchemist wisely stayed quiet. Alcianne Rockwood then held the potion in her hand and spoke. “I know you didn’t make this yourself, yet this potion would never have been made without your aid, isn’t that right?”\par
“I don’t know enough about Alchemy to say for certain that whatever you’re holding couldn’t have been made without me,” Orodan replied. “I think that’s a potion of curse-dispelling though isn’t it?”\par
“That’s correct, it’s a potion of curse-dispelling. I’ve been looking for one powerful enough for a very very long time,” the Chosen of Halor slowly said. This woman, was the strongest individual in the Republic of Aden. Even his benefactor Arvayne Firesword didn’t think he could defeat her. “Tell me, how did you make this?”\par
“Well, I simply wrapped Weapon Aura around the concoction, accounted for every single ingredient within and continuously poured mana into it past the point where oversaturation occurs while refusing to allow any changes of a negative nature,” Orodan answered. “Surely it’s not that profound to have a powerful potion of curse-dispelling?”\par
“Even the famed Ilogaji, a dragon alchemist from the Sapphire Gale dragon flight could not synthesize a Grandmaster potion of curse-dispelling due to lacking enough mana to complete the empowerment all the way,” Alcianne spoke. “If even a dragon - creatures known for having some of the largest mana pools in the world - could not do this, then how did you? Even if your control with Weapon Aura is incredible, the amount of mana the empowerment would require would be incredible.”\par
“Well I have a skill th-”\par
The door was suddenly thrown open, and in walked Arvayne Firesword with an angered but wary expression on his face.\par
“Rockwood, why are you approaching my student directly?” the old Firesword furiously asked.\par
“Firesword, I merely came by to thank this prodigiously talented young man for an incredible act of service he rendered me,” the woman replied. “You chose your student well, from what I hear he’s quite the little monster.”\par
“Yes, and he is my student. Do I go and approach the members of your house without going through you?” Arvayne asked\par
The two stared at each other for an uncomfortably long time. Poor Elona Bursimi who just happened to be in the room tutoring Orodan looked quite afraid as the aura of tension between the two became palpable.\par
Finally, Arvayne’s eyes went to the potion in Alcianne’s hand.\par
“A Grandmaster potion of curse-dispelling? Don’t tell me…”\par
“Yes, your little prodigy made something that finally dispelled the curse I was bearing since the formation of our little Republic. I merely came by to give thanks,” she spoke with a smile on her face. “Must you always be so uptight Arvayne?”\par
The old Firesword simply grunted and only looked slightly guilty in response.\par
“Was this potion really the only thing that could have cured you?” Orodan asked. “It’s been a hundred and twenty years since the Liberation War, was there really no other way?”\par
“The only other way would have involved delving into the abyssal depths to try and find a rare talyotus jewel. I’m not venturing down there alone, and the Grandmasters of the Republic aren't in any rush to enter in a group since the last delve a thousand years ago,” she answered. “When a Grandmaster hex mage uses his most powerful curse on you, recovering from it can be a little complicated.”\par
“Who was it? Is he still around?”\par
“You’ll meet him someday if you venture near the Novarrian capital. Just don’t go around trashing the city like I did, you’ll find out the hard way why they call him the greatest curse master in history.”\par
The greatest curse master in history? Surely she didn’t mean… that reincarnator who served as the Novarrian Emperor’s advisor?\par
“Well, you’ve come here and you’ve thanked him Alcianne. Was there anything else you wanted?” Arvayne interjected somewhat rudely.\par
The burly old woman simply rolled her eyes at him as she rose from the chair and approached Orodan.\par
She laid a hand on his shoulder.\par
“If you ever get tired of this old stickler, come find me. I’ve heard you and Ilyatana don’t get along, which is fine. Halor has a lot to offer for a warrior like you,” the old warrior said as she removed her hand before Arvayne could get too offended. “If you ever need anything, let me know.”\par
With those words she left.\par
“Old man, she really isn’t as bad as you’ve been telling me all this time,” Orodan spoke, and Arvayne had an annoyed look on his face. “She just came by to say thanks, what’s the issue with that?”\par
“Feh… her house has been causing trouble for mine for a while now,” Arvayne replied. “Just do yourself a favor and give her a wide berth.”\par
Perhaps they had some sort of bad blood between them? Even if Arvayne insisted there was no conflict between them the truth might be otherwise. Either way, Orodan didn’t feel like prying and he bade farewell to Elona and stepped out of the alchemical workshop alongside Arvayne as it was quite close to the end of his lesson anyways.\par
“Alright then, I’ll see you in the training chamber tonight.”\par
“Actually, I was going to suggest that you take a break over the non-work days,” old man Arvayne replied, and Orodan actually had to take a moment to process that. Arvayne Firesword, who had cancelled his days off each week… was suggesting he take a break? “Don’t look so surprised. Initially once you showed me your true unhinged nature, I wanted to push you and see how far you’d go. But now that I see you really are an insane lunatic who gets along a little too well with Agathor and enjoys deranged training methods, I’ve learned my lesson. Take a break and enjoy the non-work days. We have work to do once the next week starts, we’re going to delve into the deep depths for some hunting and practice.”\par
“Finally! I was wondering why you forced me to stay cooped up for a month straight in the academy,” Orodan remarked. “Wouldn’t doing this from the start have been better?”\par
“Learning in a structured environment and learning through life and death battle are both important parts of growth. Given that this is your first time in an academy despite all the loops you’ve been in, this was an important first month,” Arvayne explained. “Look how monstrous your growth has been in just one month. All the guided training, time dilation and education was incredibly important. I wasn’t about to interrupt that just so we could go traipsing about the depths without building a proper foundation for you first.”\par
That explanation made sense, but it was good to know he’d finally get to experience a proper fight again. He felt a month was far too long, and the training he had with the old man while good, lacked the risk of death and that rush of pure adrenaline.\par
“So, I’ve heard about these things called Death Roaches. I hear they’re pretty strong. Can I fight some?”\par
Arvayne Firesword simply sighed at his young protege’s bull-headed desire for battle.\par
\par
“I’m Altaj Ilo Vedharna, it’s good to meet you Mister Wainwright,” the man spoke. “My sister spoke about you, she says you were in the same alchemy class as her. Until circumstances drew you away anyhow.\par
Dark skinned like his sister with curly hair. The man also wore heavy armor and had a spear slung across his back. Altaj looked like the image of a stereotypical pegasus knight of the Eastern Kingdoms, it was quite regal.\par
Next to him stood an armored pegasus with a gold trim. Orodan suspected it was an Elite-level creature. The man himself was waiting at the landing zone of the academy, likely for his sister. The sun was setting and it was evening time.\par
“Likewise,” Orodan replied. “I may have caused a bit of commotion in the class.”\par
“A ‘bit’? The name Orodan Wainwright has quickly become the only thing students talk about nowadays,” Altaj spoke. “I’m in my fourth year, and Elucian Arslan has a standing reward out on any information about you. His lackeys are always asking around about Orodan Wainwright. Everyone says you can beat a Grandmaster once Agathor descends unto you, is this true?”\par
Orodan had learned some restraint and chose not to correct the falsehood that he needed a God’s Avatar powers to beat a Grandmaster. Hells, he could now likely survive one of the weaker Avatars by himself!\par
“Hmm, so they say,” Orodan replied in a noncommittal manner neither confirming nor denying and allowing Altaj to make whatever assumptions he wanted in his own head. “I’m more curious about you and your pegasus though. Your sister said his name is Ostronor? Do you two train to fight together?”\par
“I can answer that question,” the pegasus Ostronor interjected with a whinny. “Altaj and I have been battle-brothers for almost a decade now. We’ve been flying together since I was six and he was twelve years old. He’s one of the youngest squires among the pegasus knights.”\par
“Ostronor… such an introduction is not necessary,” Altaj protested, but with no real heat and then sighed. “It’s as my battle-brother says, we’ve been together for very long. It’s true that I’m something of a talent, but nowhere near yourself though Mister Wainwright. When I heard of you thoroughly humiliating Claridin Rockwood I was quite elated.”\par
“Oh? Is he a bully? Has he given you or your sister any problems?” Orodan asked. All too happy to swing by and slap him up if he had annoyed Mahari.\par
“He’s definitely the brash and arrogant sort, and while duels technically are between two people and thus I would lose to him by the rules of an official one… I wouldn’t lose to Claridin if Ostronor and I battled together and he was also allowed a mount,” Altaj answered. “That being said, I’m among the top ten strongest students at Bluefire, so Claridin usually leaves me be and instead focuses on any upcoming newer students who he feels will become a challenge down the line. My sister is thankfully not among them.”\par
It partly explained why Claridin Rockwood decided to try and antagonize Orodan on his first day. Claridin sounded much like the mean children at the orphanage were, always trying to establish dominance and bring people into their hierarchy where they were at the top.\par
Of course, Orodan had terrorized all of those ‘mean’ children by showing them what being mean and vicious actually meant. Just as he had dealt with Claridin.\par
“That’s good. I didn’t want to give him another beating, as embarrassing as it would’ve been to lower myself to that level,” Orodan said, and Altaj shook his head and smiled.\par
“I’d run him through with my lance and have Ostronor trample him into pulp if he dared lay a hand on Mahari. But your offer is appreciated,” the aspiring pegasus knight replied.\par
Orodan nodded, and the two made some more small talk as Orodan waited for his griffin at the landing zone. A few minutes later, a brown feathered griffin approached.\par
“I believe that’s my ride, I’ll be seeing you Altaj,” Orodan spoke and offered the man a handshake.\par
“Be careful down there, I’ve heard you’re going delving into the depths… my uncle died to something in the deep depths back home, so I’ll always caution anyone who dares to go inside,” the man remarked as he took the handshake.\par
Orodan heeded Altaj’s words of warning, but he truly did want to test himself against whatever horrors were within the deep depths. Warning or not, nothing would stop him from venturing in there at some point. Better that it was now alongside a Grandmaster.\par
He got atop the griffin, and it took off.\par
It was sent by Burgher Ignatius to pick him up for the party at the Firesword manor this evening.\par
The griffin tore through the skies, and made it to Trumbetton in good time. Soon it neared the Burgher’s manor which was in the center of town, surrounded by a decent preserve of fields.\par
The lights were visible from a decent distance, but it was less apparent than the previous social gathering he’d attended at the Verdant Gardens. This was a smaller gathering and not one that was as public as the last.\par
The griffin touched down on the landing zone of Firesword manor, and he could see Burgher Ignatius Firesword waiting for him already.\par
“No speeches to drag me into this time Burgher?” Orodan asked light-heartedly as he approached the man and took his offered hand in greeting. “Am I not notorious enough?”\par
“I’m afraid not Mister Wainwright. I’ve decided to take pity on you given how much of the limelight you’ve been under at Bluefire,” the Burgher quipped back. “Have you perchance considered not showing up every other student at the academy? It might help remedy the problem of your own making you find yourself in.”\par
To that, Orodan couldn’t even say anything. The Burgher wasn’t entirely wrong.\par
“I never asked, but what’s the purpose of this gathering?” Orodan asked as they walked towards the manor entrance, maids and butlers walking about with varying levels of urgency. “You simply contacted me via communications amulet to say that I was expected this evening.”\par
“We’re simply celebrating the good fortune of our house once more Mister Wainwright, much of it, thanks to you,” the Burgher Ignatius replied. “Trumbetton and Volarbury County by proxy have prospered much in the past month since you’ve been making waves. Do you know how many people now flock to the town for commerce? How often they ask after the name Orodan Wainwright?”\par
“I wasn’t aware of any of that Burgher,” Orodan replied honestly. “I don’t know if the old man told you, but I’ve been training and studying with his assistance for a month straight. No sleep or days off.”\par
“Indeed, the venerable ancestor did tell me something along those lines. Your lack of being up to date is more than understandable,” the man replied. “Allow me to fill you in a bit. Since you last left the mine has been cleared till the opening of the energy well and the valuable ore within that chamber is now being mined by our house. It’s some sort of enhanced Dothril which is at least twice as valuable. Our wealth has spiraled upwards as a result.”\par
“That does sound nice.”\par
“Indeed! We’ve also secured the rights to the corpse of that dreadful Dweller Worm you slew down there… my earth mages tell me they’re close enough to sense the corpse now,” the Burgher spoke. “I don’t know how you managed to kill that thing, it’s almost the size of a mountain range.”\par
“A lot of time and patience,” Orodan answered. And a lot of violence too.\par
“Fascinating, anyhow there are some more people who want to catch up with you,” the Burgher spoke. “Here we have-”\par
“Mister Wainwright!”\par
It was Gideon Fusturus, the Elite-level alchemist of House Firesword.\par
“Or I suppose you could talk to Gideon first, he does seem almost desperate to meet you,” Burgher Ignatius remarked with a smile, not bothered by the interruption.\par
“Mister Wainwright, you must tell me how you made those potions!” the Elite-alchemist almost begged. “Some of these potions you sent us… an Initiate-level healing potion with the power of an Elite one? You could revolutionize the entire alchemic industry if you shared your method!”\par
“It’s really not a method that would be applicable to any other alchemist Mister Fusturus… it’s something only someone with Weapon Aura and a massive pool of mana could replicate,” Orodan answered, and then the two got to talking.\par
Gideon’s face fell at hearing Orodan’s detailed explanation about how he had managed to empower the potions well beyond their natural capacity. But he did appreciate the explanation all the same and asked if Orodan would be willing to help him empower a few before he left for the depths, which Orodan saw no problem with.\par
“Truly… to think a mere month at the academy has led to you creating such potions and even assisting in the creation of a Grandmaster potion of curse-dispelling,” Gideon muttered. “Incredible… I’m honored to have met you my friend.”\par
“Thank you, but I still have a very long way to go before I can concoct any truly powerful potions without assistance.”\par
“Which is natural of course, but I’m certain you will get there one day.”\par
The two spoke some more before a diminutive woman interjected.\par
“And this is the daring young hero who’s changed the fortunes of your house Ignatius? Are mana-based enchantments still not good enough for you Mister Wainwright?” asked Helga Firesword who had walked into the conversation.\par
“I’ll soon be meeting with Master Gormir Eltros to discuss the possibility of soul energy based enchanting, so I have yet to broach the subject.”\par
“M-master Eltros?! What level even is your Enchanting skill for you to be meeting with him?” Helga asked in surprise. “I didn’t even know you were taking Enchanting lessons at Bluefire.”\par
“I’m currently at level thirty-four of Enchanting, it’s not much, but I hope to maybe reach level forty by the time of the Inter-Academy Tournament,” Orodan replied, and Helga’s face twisted in shock.\par
“How… how are you such a monstrous prodigy in everything…” she muttered to herself. “First Alchemy, and then thirty-four levels of Enchanting in a month? What… what even are you?”\par
Orodan found himself being asked that question more and more often lately. Maybe from next loop he would be a little less public about his crafting pursuits. One person being so talented in this many fields was perhaps a bit much.\par
While there were martial specialists and mages who cross-trained and showed genius aptitudes in crafting, it wasn’t to the extent of multiple fields.\par
Frankly, some more powerful people already suspected or outright knew that he might have a Mythical skill responsible for it. In this loop it was only Agathor’s protection via his Chosen One that kept Orodan from having that meddling Goddess Ilyatana descending upon him.\par
Orodan spoke to some more people at the gathering.\par
Geldric Sunfire, one of the Elite retainers was one of them and Orodan apologized for not being free to help the man with any minor issues he may have had. To which the man vehemently protested and informed Orodan that he and his fellows had received some of Orodan’s Elite-level healing potions, and those alone were absolutely valuable treasures for them at their level of work. They were life savers that could heal wounds in an instant and restore a heavily wounded Elite back to near perfect condition within seconds.\par
Orodan also heard through the social mill that Lady Katareya Eldragon was busy with assisting in the Cathedral’s preparations for the eventual tunneling down into the energy well, and thus could not attend. However he was sure to see her in another month when the tunneling concluded and a joint force of Grandmasters would descend down the well to secure it.\par
Orodan would naturally be invited to this descending venture as an accompanying aid to Arvayne Firesword.\par
The old man himself wasn’t in attendance of course, as Grandmasters almost never attended such parties. He was off doing Grandmaster things. Whatever they were, Orodan didn’t know.\par
Eventually, the night came to a close and Orodan returned to the Bluefire Academy. He had one more non-work day to enjoy, but in all honesty?\par
Even this one day off made Orodan restless.\par
So he simply decided to focus on assisting Gideon Fusturus and once that was done, training till the work week started and it was time to delve into the deep depths.\par
Death Roaches and Dweller Worms were among the Grandmaster-level monsters he could potentially encounter deeper down there. And who knew what else was lying in wait, not happy to be disturbed?\par
It sounded incredibly dangerous, and even Grandmasters would be cautious when going into the lower parts of the deep depths.\par
To Orodan however, it just sounded like a fun time.\par
He was looking forward to it.\par
He mentally pulled up his Status. It had come very far.\par
\textbf{[Name: Orodan Wainwright}\par
\textbf{Age: 17}\par
\textbf{Title 1: Grandmaster Slayer}\par
\textbf{Title 2: One Who Has Experienced Death}\par
\textbf{Title 3: Sword Elite}\par
\textbf{Available Titles: Wielder Of A Mythical Skill, Grandmaster Slayer, One Who Has Experienced Death, Sword Elite, Shield Elite, Physical Elite, Unarmed Combat Elite, Combat Elite, Wrestling Elite, Woodworking Adept, Cleaning Apprentice, Alchemy Apprentice, Enchanting Apprentice, Laboring Apprentice,}\par
\textbf{Rewards: Permanent +3 Action Increase}\par
\textbf{Skills: Physical Fitness 80 (Elite), Weapon Aura 79 (Elite - Rare), Unyielding Vitality 78 (Elite - Rare), Unarmed Combat Mastery 77 (Elite), Death Rage 77 (Elite - Exquisite), Sword Mastery 76 (Elite), Damage Mitigation 76 (Elite), Combat Mastery 75 (Elite), Shield Mastery 75 (Elite), Mana Black Hole 75 (Elite - Legendary), Bleeding Control 75 (Elite), Pain Resistance 74 (Elite), Dying Struggle 72 (Elite - Uncommon), Iron Body 72 (Elite - Exquisite), Wrestling 71 (Elite), Soul Manipulation 71 (Elite - Rare), Regeneration 70 (Elite - Exquisite), Impregnable Bladewall 70 (Elite - Exquisite), Eternal Soul Reactor 70 (Elite - Mythical), Psionic Resistance 70 (Elite - Exquisite), Perfect Parry 68 (Adept - Uncommon), All-Strike 65 (Adept - Legendary), Evasiveness 62 (Adept - Uncommon), Shield Throw 62 (Adept - Uncommon), Power Strike 61 (Adept - Uncommon), Slashing Resistance 60 (Adept - Rare), Impact Resistance 58 (Adept), Vitality Black Hole 56 (Adept - Legendary), Tool Mastery 56 (Adept), Piercing Resistance 54 (Adept - Rare), Flash Strike 54 (Adept - Exquisite), Mana Resistance 53 (Adept - Legendary), Woodworking 51 (Adept), Alchemy 48 (Apprentice), Wood Communion 44 (Apprentice - Legendary), Eldritch Resistance 43 (Apprentice - Mythical), Surprise Attack 41 (Apprentice), Cleaning 40 (Apprentice), Sprinting 39 (Apprentice), Whirlpool Whirlwind 38 (Apprentice - Exquisite), War Cry 35 (Apprentice - Rare), Enchanting 34 (Apprentice), Mana Manipulation 33 (Apprentice - Uncommon), Body Tempering 33 (Apprentice - Legendary), Soul Defense 33 (Apprentice - Rare), Fate Reading 31 (Apprentice - Uncommon), Laboring 31 (Apprentice), Blacksmithing 28 (Initiate), Endless Blitz 26 (Initiate - Legendary), Fate Disconnect 24 (Initiate - Legendary), Construction 21 (Initiate), Soul Strengthening 21 (Initiate - Legendary), Vitality Destruction 21 (Initiate - Exquisite), Warrior’s Reciprocity 20 (Initiate - Mythical), Maintenance 20 (Initiate), Repair 19 (Initiate), Club Mastery 15 (Initiate), Lightning Resistance 14 (Initiate - Exquisite), Lumberjacking 11 (Initiate), Parkour 11 (Initiate), Intimidation 7 (Initiate), Thievery 6 (Initiate), Deception 4 (Initiate), Pathfinding 4 (Initiate), Observe 3 (Initiate), Identify 2 (Initiate)}\par
\textbf{Blessings: Warrior’s Heart - Increased talent and learning rate for all warrior related skills as determined by Agathor, Warrior’s Quarry - Once you see your target they cannot flee. Your attacks will land on fleeing or evading foes and destiny will bend to ensure you find your mark, Death’s Call - Whenever you will it, Death takes you, Trickster’s Veil - Your Status, fate and soul are impossible to peer into unless you will it]}\par
It would soon be time to test his gains against the deep depths.\par


\section*{Chapter 21 - Hunting In The Deep Depths}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 21 - Hunting In The Deep Depths}%
\par
The area they had traveled to was near the western border of the Republic, near enough to the coast that one could see it if they flew or jumped up into the air, but still somewhat inland.\par
Traveling didn’t take long when skill levels were past 70, and neither held the other back overly much. Although Orodan felt that Arvayne was slowing himself for his sake. So a day’s journey for a civilian was made within half an hour.\par
Their destination was the bog known as Ranmere’s Folly. Named as such for the reckless Imperial expeditionary captain who decided to get two-hundred men killed by venturing into the deep depths. The small mountain in the southern part of the bog was an entrance into the depths, and where Ranmere had met his end.\par
“So why travel all the way here? There are plenty of entrances to the depths closer to home aren’t there?” questioned Orodan.\par
“Yes, but not every entrance to the depths leads all the way down, and a lot of ways into the depths take very long and winding routes downwards. I also don’t want to hear any more whining from the Council about tremors that last more than two weeks, so we're a bit farther out,” Arvayne explained. “This is probably the entrance leading downwards with the most straightforward path to the abyssal depths, for when you get to that point. It’s where we Grandmasters ventured in so long ago.”\par
“So it’s hopefully mapped out to an extent?”\par
“Aye, thanks to the Novarrians who died here a few centuries ago,” the old man replied. “It’s officially mapped out till at least a quarter of the way into the deep depths. And unofficially, we mapped out the entire way till the descent into the abyssal depths.”\par
“Sounds fun, shall we descend then?” Orodan asked.\par
“Yes, let’s. But fair warning, we’re only going to descend three-quarters of the way into the deep depths. Going any closer risks finding some rather dangerous monsters from the abyssal depths who might hear us,” Arvayne cautioned. “If you choose to disregard my wishes, I’ll simply leave and you can fend for yourself in there.”\par
Orodan thought it a fair agreement. Plus, if there was a situation where he wanted to risk more, he felt confident that he could look after himself, or at least survive. He wasn't planning on risking the abyssal depths as this loop still had important things coming up.\par
So they entered the mouth of the cavern and began their venture.\par
The first thing Orodan noticed was that the cavern was quite well-lit with glowing mushrooms along the walls. With his education in alchemy he now recognized these as the ostolitus mushroom. They were the same species that lit the walls of the natural tunnels underneath the Firesword mines when he had ventured in there.\par
The cavern seemed oddly quiet, and he soon understood why.\par
Behind the stalactites and stalagmites of the cavern, were numerous man-sized monster bats in hiding. These were quite weak… maybe at the Adept-level only. And they were trembling in fear, anxiously watching the two of them pass through.\par
He learned in his monster studies class, that most monsters had excellent natural instincts and could understand when something was more powerful than them. A popular practice for adventurer parties delving the depths was having a beast tamer whose companion could detect something dangerous before the party could.\par
Orodan, due to not having had the Observe skill for most of his life, also felt that he had the vague beginnings of this ability. He could instinctually tell when someone was a threat to him, particularly when it came to Grandmasters nowadays. Perhaps he would acquire a skill if he focused on it further.\par
He decided to use his new Observe skill for the first time to verify how strong the bats were.\par
\textbf{[Name: Vitality Devouring Cave Bat}\par
\textbf{Title 1: Flight Adept}\par
\textbf{Title 2: Claw Combat Apprentice]}\par
The rule of Adept-level beings having two title slots held true even for monsters. Additionally, even if these non-intelligent creatures couldn’t think, they still received the System in a form that was instinctually understood by them. Hence their choosing of titles.\par
Perhaps it was a way to show off to the other bats?\par
Either way, Orodan thought Observe was quite the convenient skill. Unless one had Blessings, items or the incredibly difficult to obtain Observe Resistance skill, it worked on anything, no matter how powerful. He might even be able to Observe an Avatar, although had no idea what the System would display.\par
The two of them continued on and Orodan continuously used Observe, slowly leveling it, which decreased its mana cost and supposedly at very high levels would allow him to get past Observe Resistance and enchanted anti-Observation items. It also allowed for one to detect the presence of Blessings once the skill hit level 70. But even at level 100 of Observe, Arvayne told him that it still didn’t allow anyone to see skills and their rarities. That was something only Gods were capable of.\par
Finally, after Observing various Adept-level cave creatures such as moles, rats and spiders; and using Identify on various plants and mushrooms, they reached a point of the caverns which began to descend downwards rather steeply.\par
It was some time into descending this downward slope that Arvayne informed him they were more or less in the wild depths now, where they would encounter higher-level Adept monsters and Elites.\par
The monsters still frightfully stayed away or outright fled, but Orodan saw some interesting wildlife.\par
\textbf{[Name: Space-lock Myconid}\par
\textbf{Title 1: Unarmed Combat Elite}\par
\textbf{Title 2: Space Adept}\par
\textbf{Title 3: Combat Apprentice]}\par
It was an Elite-level mushroom man, with thick arms and a glowing aura of distorted space surrounding it. It had three titles as expected of an Elite. But it still smartly stayed away from the two of them.\par
Frankly, it seemed almost peaceful and not as predatory as some of the other monsters he saw thus far.\par
Until it encountered a strange teleporting spider and decided to tear its legs off and begin snacking on them.\par
Never mind.\par
“Nothing in the wild depths got to where it is by being a pacifist,” the old man spoke up. “Those things are the main predators of the phase spiders in this area. They lock down space and prevent the spiders from escaping, and their spatial distortions often cause spiders elsewhere who are teleporting to instead be drawn into their radius as their teleport destination.”\par
“You know, given the packed schedule I’ve had at the academy I don’t think I got the chance to speak to any instructors for space magic,” Orodan remarked. “Teleportation sounds useful doesn’t it? Especially when backed by my skills which render mana concerns obsolete?”\par
“Useful for travel, sure. Useful in combat? Outside of cities and in the wilderness perhaps,” Arvayne remarked. “Almost everywhere of any significance is warded against teleportation nowadays. Entire towns have anti-teleportation wards over them that even Grandmaster space mages cannot break through. The warding is quite cheap too, so this has naturally rendered that branch of magic quite impotent, and people aren’t as willing to study space magic once they find that out. Anti-teleportation items are also ten gold coins a dozen.”\par
Orodan filed that tidbit away for later experimentation in attempting to brute force anti-teleportation wards once he learned the skill.\par
Finally, they got to a point where Orodan saw a different sort of monster. It burrowed out from the rock underneath and looked as though it wanted to speak to them.\par
\textbf{[Name: Axeltugus the Watcher (Species: Depths Mole)}\par
\textbf{Title 1: Claw Combat Elite}\par
\textbf{Title 2: Earth Magic Adept}\par
\textbf{Title 3: Combat Adept]}\par
“It’s named?”\par
“Of course, you have a name don’t you? It’s just an intelligent creature that has its own,” Arvayne replied. “It doesn’t make it special, but monsters have their species displayed next to their name, unlike the mortal races. Small mercies on us from the System.”\par
The mole stood off warily, a good distance from the two of them and spoke in a series of squeaks.\par
“Human… we have no quarrel with your kind and often let you pass through unhindered,” it spoke. “What brings you to our section of the depths today?”\par
“Just passing through to the deep,” Orodan replied. He wanted to ask more questions of it, but Arvayne interrupted him.\par
“Boy, we have representatives of depths dwelling monster species who reside in the academy and can answer all your questions, leave the poor mole alone,” the old man spoke. And while Orodan grumbled, he complied as there were more interesting things down below.\par
The mole seemed satisfied with the answer as well, and bade them farewell and good luck, but warned them that something new had moved into the deep depths just before the entrance to the abyssal depths. It then burrowed through the rock and departed.\par
The depths were not simply full of hostile and territorial monsters, but friendly ones as well. Intelligence could lead to many things, and cooperation between monster species and the mortal races was one of those outcomes.\par
The humans of Inuan were quite averse to officially congregating with subterranean monster species, as he had learned in the academy. But this didn’t mean that certain villages and towns didn’t have an understanding with some monster species from the depths unofficially. It might not have been the full-fledged cooperation that humans officially had with pegasi, griffins or dragons… but exchanging information and occasionally trading goods wasn’t out of the question.\par
Who knew if the group that mole belonged to engaged in friendly interactions with other settlements or groups of humans?\par
In any case, they had more ground to cover.\par
\par
It was after twenty minutes of slow and steady travel that they reached the deep depths.\par
Arvayne told him that the natural saturation of world energy in the air and environment was heavier the lower they went, which meant valuable treasures and materials to potentially plunder. But it also led to the monsters at this depth being rather territorial and power-hungry.\par
The wild depths were more of an ecosystem. Sure, there were dangerous and rowdy monsters in them, but the highest level of monster someone was likely to encounter would be at the Elite-level, and a lot of the time these monsters weren’t outright hostile as they had enough sense to know that killing humans delving into the wild depths was a good way to have adventurer parties dispatched to perform a mass culling in retribution.\par
It was Orodan’s first time in the deep depths and they were a different matter however.\par
It was more of a constant and vicious struggle for survival and power. The naturally denser world energy, while not on the level of an energy well, still meant that monsters were unwilling to give up their habitats and territories. Any monsters that dwelled here were power-hungry by nature and had no issues fighting to defend their lot in life.\par
Elite-level monsters snarled and snapped at them from a distance, happily willing to fight if pushed even by a superior foe. And Orodan started to encounter some Master-level monsters that he was forced to put down, as unsatisfying as the fight may have been.\par
And then he encountered something far stronger, and the fight wasn’t quite as unsatisfying.\par
\textbf{[Name: Ulubulu the Bloodthirsty (Species: Reaver Mantis)}\par
\textbf{Title 1: Blade Master}\par
\textbf{Title 2: Master Slayer}\par
\textbf{Title 3: Gravity Magic Elite}\par
\textbf{Title 4: Blood Magic Elite]}\par
This would be quite the fearsome monster, even by the standards of the average Master-level monster. It had Elite-level proficiency in two schools of magic which it used to amplify its raging savagery. And its Blade Mastery in the form of its deadly front legs was a prominent feature.\par
It was a hunter which prowled the deep depths, and it was among the strongest things Orodan could have encountered down here. This creature could very well be the end of even a Master-level adventuring party if they were caught off-guard.\par
While it was nominally at the Master-level, it’s battle power was approaching the level of a Grandmaster. Prodigies and people who could hit above their weight class didn’t just exist among the mortal races, but monsters too. This Reaver Mantis must have been a real terror within its level.\par
Orodan suspected it would be half as strong as Adeltaj Simarji, who was a very strong single-Grandmaster, if it was allowed to bring the full might of its physicality and both magic schools to bear.\par
Unfortunately for it, Orodan Wainwright’s legendary Mana Resistance skill made him an unfair foe to fight. A massive portion of its arsenal was neutered as its attempts to use gravity to directly control Orodan failed, and any attacks it launched via blood magic were ignored.\par
It also found that attacking the infuriating human resulted in it taking wounds from its own attacks, returned twofold.\par
It then decided to turn its gravity magic inwards alongside blood magic and empower itself to some rather impressive physical levels akin to Adeltaj Simarji. It now felt like Orodan was fighting a Grandmaster, and he actually had to get somewhat serious.\par
Mana Black Hole drained its self-empowerment, and Vitality Destruction paired with Vitality Black Hole drained its life force in large amounts. All this occurred as it engaged Orodan in a furious tornado of deadly melee that shattered many miles of the far tougher world energy empowered rock. Arvayne actually had to leap away lest he be caught in the crossfire of the melee. His role being one of observation and guidance.\par
But despite Ulubulu’s valiant efforts, the Reaver Mantis fell to the unfair savagery of Orodan’s Endless Blitz empowered by Death Rage which caused even this ferocious Reaver Mantis to quail in psychological shock at a smaller being engaging it in a toe to toe melee battle and winning with raw rage.\par
“Is everything from here downwards this tough?” Orodan asked, but not in complaint. It was a good fight, and he eagerly looked forward to something at the Grandmaster-level that could truly make his warrior spirit sing. “It was at the Master-level but fought with as much strength as old man Adeltaj.”\par
“Monsters are naturally more powerful than their mortal counterparts of the same level to begin with,” Arvayne explained. “Furthermore, not all creatures are built equal. If everything else is equal, a Master-level pegasus will be outmatched against a Master-level dragon for example. You just happened to encounter something quite monstrously strong and talented.”\par
“How is an adventuring party in the deep depths supposed to survive when encountering one of these? What do they even do?”\par
“They die. Your talent and lunacy affords you the unique privilege of not having to feel the fear and anxiety of even world-renowned adventuring parties delving the deep depths,” Arvayne remarked. “Why do you think delving the deep depths is so dangerous? You should know that there are plenty of records of expeditions and parties of Masters never coming back. You can do everything correctly and still die by running into the wrong thing.”\par
“That sounds…”\par
“Unfair? Such is life Orodan. The situation you’re in is quite unfair too, being expected to fight that thing coming down from the stars… but here we are. You should know this given your upbringing,” Arvayne continued. “There’s a reason why the backing of a Grandmaster is so highly sought after for such expeditions. The safety net isn’t just for show.”\par
Orodan now understood exactly why Geldric Sunfire would want his assistance in traversing even the Aenechean Forest. Adventuring was dangerous and uncertain work full of perils. Especially in a place like this.\par
While it could be lucrative and make one rich, it also came with the risk of fatal jeopardy. Unless a party had escape-specialists who could cast illusions or someone who could immobilize the monster for a moment… the only outcome would be death.\par
The ever-present grind for power and the struggle to reach upwards was simply the way of the world. When one was born with skill levels and titles, the natural incentive for every being was to claw for more. Even if it lead to them delving the deep depths and dying alone in a horrifying manner.\par
He wondered how many families grieved due to their loved ones meeting something like the Reaver Mantis? How many people waited for adventurers and expeditionaries who would never return home?\par
“Well this is a depressing train of thought, let’s move on,” Orodan said. But in the back of his head, he one day wondered if he could become strong enough that such pointless death needn’t occur in society any longer.A case of literary theft: this tale is not rightfully on Amazon; if you see it, report the violation.\par
How would he do it? He didn’t even know. But if anyone could eventually work on a solution to the issue, it would be him.\par
But such things were very far away for the current Orodan.\par
They were only at the halfway point of the deep depths and had already encountered something monstrous that could fight a tier above its own.\par
What more would await them down below?\par
They continued walking down the tunnels paths which sloped downwards, until at last they reached a truly massive cavern.\par
It possessed all kinds of life, and multiple creatures of serious strength appeared to be battling within.\par
At the end of this massive chamber, near where two of the biggest monsters were battling each other, was an opening leading down deeper.\par
The opening lead to another massive downwards tunnel.\par
The position they were at was higher up the slope, and thus allowed them to look down the massive downwards tunnel.\par
And Orodan could see the color of the stone begin to change quite far down this tunnel.\par
“This chamber where we are is roughly three-quarters of the way down into the deep depths. This is the farthest I’m willing to go personally,” Arvayne explained. “Those two things fighting each other are Grandmaster-level, and the one coming out on top can fight at least a step above its own level.”\par
The two titanic monsters fighting each looked naturally savage and ferocious. They were two giant bugs.\par
\textbf{[Name: Astirisil the Swooping Greed (Species: Soul Devouring Scorpionfly)}\par
\textbf{Title 1: Stinger Combat Grandmaster}\par
\textbf{Title 2: Grandmaster Slayer}\par
\textbf{Title 3: Combat Master}\par
\textbf{Title 4: Soul Combat Master}\par
\textbf{Title 5: Flight Master]}\par
It was an incredibly intimidating looking insect the size of a house. It might not have been as big as some of the absolutely massive Grandmaster-level creatures he’d seen, but its small size made it even more ferocious and deadly.\par
Its wings were beating violently as it flitted about mid-air and launched glowing spears of offensive soul energy from its deadly stinger. It would occasionally then delve closer and have furious melee exchanges with its foe. Hundreds of attacks were exchanged each second and the massive cavern they were in shook due to the deadly dance of violence.\par
Astirisil was not only powerful, but also skilled in combat. It adjusted its tactics and patterns multiple times in the middle of battle. It was rare to see a monster with such knowledge and skill in combat and Orodan was looking forward to testing himself against the natural might of a monster, backed by skill of its own.\par
However, despite its skill and adaptability, the Scorpionfly was losing.\par
It’s opponent? Orodan didn’t know if he was its match.\par
\textbf{[Name: Yamalshuk the Fiery Web (Species: Fire Spider Dragon)}\par
\textbf{Title 1: Claw Combat Grandmaster}\par
\textbf{Title 2: Grandmaster Slayer}\par
\textbf{Title 3: Fire Master}\par
\textbf{Title 4: Combat Master}\par
\textbf{Title 5: Space Magic Master]}\par
It was a damned spider dragon.\par
The size of a small castle and with ominous flames emanating from its deadly looking body. Its eight lethally pointed legs glowed blue with the stereotypical tell of spatial magic, and it belched some absolutely lethal looking fire towards the Scorpionfly that the flying insect desperately avoided.\par
The sighting of a spider dragon was immediate grounds for the mobilization of armies lead by Grandmasters, and they would often be assisted by local dragon flights in the endeavor due to one reason…\par
…dragons absolutely hated the abominations that were spider dragons.\par
Every known dragon flight, even the Novarrian ones… had a standing bounty of generous reward on these foul creatures. Killing a spider dragon of decent strength and presenting the corpse was a quick ticket to earning great regard among dragon society.\par
The rumor was that long ago some malevolent force had succeeded in mixing the blood of dragons and great spiders, leading to the abomination he now saw before him.\par
Dragons were already naturally powerful monsters that were near the top of the food chain. If one were to make a list of beings that were the strongest skill level for skill level due to their physicality and sheer mana pools, dragons would be near the top. Spider dragons consequently inherited this terrifying potential. Each skill level amplified by their powerful eight legged bodies and natural abilities made them a terror in battle.\par
And the dragon flights really didn’t like a species of draconic off-shoots threatening their superiority. That there were some notorious spider dragons at large who’d also killed dragons and managed to get quite strong was another fact that added to the fuel that was dragon hatred of spider dragons.\par
This was a Grandmaster monster, and it was a far stronger species than the Dweller Worm he had fought and killed. In comparison to this apex creature, the oversized Dweller Worm would just be a fat meal.\par
“Come Orodan, let us sit and wait while those two duke it out, then you can test yourself safely against that thing whi-”\par
“Daring to fight without inviting me?! Hope there’s room for one more!”\par
“Orodan wait!”\par
The old man’s warnings were summarily ignored.\par
A Flash Strike immediately closed the distance between Orodan and the two parties who were fighting.\par
It would be no fun to gang up on the losing party, so Orodan’s Flash Strike brought him straight to the dragon spider, whose head received his sword. It was preoccupied with the scorpionfly and wasn’t able to stop Orodan’s Flash Strike empowered sword from burying into its head. The ambush actually gave him two levels in Surprise Attack as it added to the power of the Flash Strike.\par
It was the size of a small castle, and unfortunately a mere stab wound on the head from Orodan’s sword wouldn’t kill it. Strong as the Flash Strike now was.\par
It grunted in annoyance and pain. And Orodan further decided to ruin its day by beginning an Endless Blitz of Death Rage empowered attacks on its head.\par
Finally, it decided to act as the flames around its body were directed towards him… and Orodan learned the critical distinction that it had the title of Fire Master and not the Fire Magic Master title that a regular mage would have.\par
Learning to harness an element was typically done through mana for the overwhelming majority of creatures. But some creatures were naturally capable of certain abilities, such as a pegasus’s flight or a dragon’s elemental breath attacks. For these creatures it wasn’t mana, but their very soul energy that empowered these natural abilities they were born with.\par
And for a fire dragon spider that had the blood of dragons flowing within it? The title of Fire Master said more than Orodan initially thought it did.\par
His Mana Resistance skill was of no use as the flames nearly turned him to cinders. His own monstrous levels in Unyielding Vitality and Regeneration - fueled by Eternal Soul Reactor - were the only things that kept him alive as he acutely felt himself being reduced to ashes.\par
He reformed completely on the ground, his weapons utterly disintegrated. The endless gravity core had unfortunately fallen out of his stomach as a result of the near total bodily destruction he suffered.\par
No more proper training for now… how unfortunate.\par
He was hit by the indirect flames simply emanating from the body of the fire dragon spider and it nearly destroyed him entirely.\par
Orodan didn’t want to test it quite yet, but he felt that completely bodily destruction would kill him. And a focused blast of flames from its mouth would definitely accomplish this.\par
On the bright side, the dragon spider looked horribly charred and was in incredible pain! Attacking Orodan was a poor move on its part as the assault was returned more than twofold!\par
The dragon spider was utterly enraged and Orodan was given no time to recover as multiple portals opened up around him and eight terrifyingly sharp clawed legs came through these portals to assault Orodan.\par
A desperate activation of Endless Blitz, combined with his quadrupled action increase and his utmost focus allowed him to barely counter the assault without getting completely eviscerated.\par
Soon, a titanic exchange of melee blows ensued, and Orodan found himself being pushed back despite all his skills working in synergy. The massive cavern shook horribly, and the world energy enhanced stone they were on was still being cracked and shattered.\par
He took some serious wounds which were healed near instantly, but the backlash also harmed the dragon spider. And he was forced to use Mana Black Hole to drain the magic out of the air and start shutting down the portals spawning all around him through which spider legs came through.\par
As this happened, the scorpionfly finally acted and sent a volley of powerful soul energy projectiles towards the spider dragon.\par
It hissed and chittered, which was translated via the System.\par
“Excellent! Come surface-dweller! We shall slay the interloper together and dine on its flesh!”\par
The response Orodan gave it…\par
…was a Flash Strike to the face.\par
“What’re you getting all friendly for? I’m fighting the both of you, so shut up and wait your turn!” Orodan said as his fist crunched the long tube like appendage on its face that looked quite like a nose.\par
It hissed and immediately threw Orodan off to gain some distance and began pelting him with soul energy beams. Thankfully, his Soul Defense greatly amplified his already existing natural strength of soul. Even though this creature was naturally more powerful at soul assaults than the headmaster of the school of soul magic was… it wasn’t enough to harm Orodan. And it found its own soul assaulted in return every time it hit the warrior, so it soon stopped.\par
Leaving Orodan to fight the spider dragon.\par
“Encroacher! You intrude on my hunt, and then you covet battle with us both like some sort of crazed imbecile? What sort of vexatious pest are you!?” the creature roared and spoke with a noise that sounded like a combination of a roar and a hiss. A truly disgusting noise. Orodan could see why dragons hated these things.\par
“I saw a good fight occurring, and I couldn’t resist! Now give me your all! Fight me toe to toe!” Orodan followed this with a War Cry which didn’t have too much effect but did slightly stun the massive eight-legged freak. “I don’t care how big you are or how powerful your ugly species is… fight me like a warrior blow for blow!”\par
The spider dragon’s rage was terrible, and it obliged.\par
The spider dragon, the size of a small castle, barreled towards him and engaged Orodan blow for blow in a deadly storm of melee combat with its eight clawed legs.\par
It must have looked utterly comical. For a man to barely batter aside, partially deflect and throw head on All-Strike punches towards legs that were the size of small towers… but it was a reality.\par
Orodan might have actually had a higher level Physical Fitness skill than it, but its monstrous size and powerful body thanks to its species meant that each point of Physical Fitness it had went farther. Orodan would need more levels in Body Tempering to bridge this gap in natural potential.\par
But, even if it was superior… the difference in physicality wasn’t overwhelming. And being a smaller being packed with so much power gave Orodan a different kind of advantage in terms of concentrated power.\par
His strikes would dent and crack the tough carapace of its legs whenever they met even as his bones shattered and his upper body was completely exploded from the force at times.\par
Periodically, it would attempt to also belch a focused stream of flames at Orodan, and the warrior desperately avoided this focused stream lest he be killed instantly. But at intervals he did try to futilely grapple with it and slowly but surely began experimenting on acquiring some sort of resistance in the midst of battle from the ambient flames surrounding its body.\par
He lost track of everything else but fighting.\par
He and the spider dragon exchanged blows at a rate that made the air around them heat and catch fire from the friction and sheer energy.\par
A Death Rage empowered Endless Blitz, backed by a quadrupled action increase met eight legs of fiery fury which often not only came from the front, but also came through portals which spontaneously appeared behind, under and above him from all angles.\par
Initially, Orodan was the loser in every damage exchange.\par
He was forced to fight a little unfairly to stay alive in these initial moments. He used Mana Black Hole to drain the spider dragon’s portals and shut them down to prevent it from launching attacks through them. He was being overwhelmed by just a frontal assault and was barely surviving, so receiving attacks from all directions might just kill him.\par
A successful hit from the tower sized leg of the spider would always nearly evaporate his entire body, so Orodan was forced to partially deflect or evade its attacks to avoid death due to not being able to regenerate in time.\par
It was a madly thin margin of error that could see him killed at any moment. But his endless willpower allowed him to maintain a razor sharp state of focus indefinitely and his Combat Mastery gave him the skill and technique necessary to remain in the fight.\par
He was kept afloat only thanks to his ludicrous vitality skills and the fact that the spider dragon didn’t want to hit him too hard lest it receive some unfortunate damage in return.\par
This spider dragon was utterly monstrous and beyond anything he’d properly faced down one-on-one.\par
The world was a big place and the depths had monsters such as this, that made a Dweller Worm look like an oversized weakling. Dragons often received Quests whenever spider dragons dared to even appear on the surface, for so great was the threat posed by one of these things.\par
Many Quests were still in place to this day for certain spider dragons that were at large and had gone into hiding after causing indescribable destruction. The world must have considered them a pretty big threat to bestow Quests the moment they even appeared on the surface.\par
But, despite being the loser in every damage exchange where he was eviscerated and torn apart. Orodan survived.\par
He reformed at frightening speeds thanks to Regeneration, he remained aware when most of his body was destroyed thanks to Unyielding Vitality, and this was all endlessly fueled by Eternal Soul Reactor. Any normal warrior would have been out of energy long ago from using such costly and energy-intensive skills continuously, but not him.\par
And even if it was at a slow rate, his skill levels still increased. The actual threat of death against this spider dragon was far more beneficial than the artificial threat against Arvayne Firesword.\par
This was what an academy couldn’t do. This was what Orodan was missing.\par
At Orodan’s current strength, each skill level made a big difference.\par
Through gaining even a level or two, the balance of the fight was beginning to noticeably shift.\par
He made minor skill level gains after just a day of continuous fighting. A dramatic increase from the month of relatively safe training he underwent at Bluefire where gains slowed down.\par
With these gains, after the first full day of battle Orodan was finally able to stop losing damage exchanges and held on evenly. He stopped using Mana Black Hole to cut off his enemy’s portals and decided to instead clash head on against the mightiest of the melee fury the spider dragon could bring.\par
This of course set him back to being on the losing end of the damage exchanges once again, but it was good training, and Orodan wouldn’t be a warrior if he didn’t continually increase the intensity of his regimen.\par
Even if it meant giving his enemy an advantage.\par
He was sure the old man was shaking his head in disappointment at Orodan’s excellent work ethic as usual.\par
His foe had an ungodly amount of vitality, far surpassing the Dweller Worm. As befitting a creature on par with a dragon that was at the Grandmaster level. It barely slowed down despite how much damage it received from Orodan and the backlash from Warrior’s Reciprocity.\par
But Orodan had gotten stronger.\par
By now his nineteen skills that were all past the threshold of level 70 - the Elite level - synergized together to monstrously amplify his battle power and let him fight beyond his weight class. The Orodan that fought the Dweller Worm would be nearly instantly slaughtered by this spider dragon.\par
But he wasn’t the Orodan of a month ago.\par
After the third full day of fighting, Orodan’s experimentation of skirting along the edges and trying to build a resistance by using the less deadly ambient flames surrounding his foe paid off.\par
A moment came where he decided to risk it like a madman and actually take the focused fire breath head on. He felt he was on the cusp of understanding how to resist the hellish flames which evaporated the rock around them.\par
He would die and the loop would end if this failed.\par
But the gamble paid off.\par
\textbf{[New Skill (Exquisite) → Fire Resistance 1]}\par
His body was charred like a piece of burnt out coal.\par
But he didn’t get turned to complete ash and have his entire body completely destroyed. Which would have killed him.\par
He could now start to survive the focused breath attack of the spider dragon.\par
Even at level 1, this skill began to make a serious difference in helping Orodan survive the soul energy empowered flames of the monster.\par
Even the monster began to get frustrated!\par
“Cockroach! You dare to use me as a training tool to acquire a resistance skill!? I’ll eviscerate you and burn your remains forever!” the spider dragon roared in fury.\par
On the fourth day of fighting, his Fire Resistance was at level 24, and he could now survive a focused fiery breath attack from his opponent with decent damage, but not so much that he couldn’t continue attacking almost instantly afterwards.\par
It was by then that the spider dragon was starting to look quite… broken.\par
It’s powerful scales were cracked and bleeding everywhere. It had monstrous vitality that made it one of the most powerful species in the entire world… but that vitality had been drained over the course of four days through Vitality Black Hole and Vitality Destruction attacks. Its wounds were no longer healing.\par
It’s pace of attacks began to slow down, and it looked like it knew the impending outcome.\par
It tried to turn around and retreat.\par
Which it then found it couldn’t do, courtesy of a Blessing from the Inuanan God of War.\par
It stopped for a moment, and for the first time in days it spoke once more with a hiss and a growl.\par
“Vile roach! What grants a weak mortal such unnatural life force and vigor that even a vaunted spider dragon cannot match? Divine assistance? A bloodline of power that would shake the world?!” the spider dragon roared in outrage. A little ironic coming from a species that itself was created through unnatural means.\par
Orodan’s reply was another All-Strike to its face.\par
It took another half-day of fighting from that point.\par
It’s last words with its dying breath were muttered curses towards the Time Wind dragon flight.\par
The spider dragon never surrendered or begged for its life even as it died. It was a vile species known for having a level of fatal pride that rivalled its progenitor race of dragons.\par
Furthermore, creatures daring to live in the deep depths implicitly accepted the way of life which involved killing or being killed. Relatively few of the monsters he saw in this massive cavern would be willing to flee or give up their territory.\par
The world energy in the deep depths at this level, three-fourths of the way down, was quite rich. For creatures living here it was often an all or nothing gamble they took.\par
But… he finally won, and he had made some excellent skill level gains in just four days of work.\par
He looked around and wondered where the scorpionfly went, only to see his mentor in the far distance sitting on top of its charred corpse, his greatsword buried in its head as he was reading an excessively thick book.\par
Surrounding Arvayne Firesword were the corpses of at least a dozen more monsters.\par
“Old man! You can’t just go around stealing my kills!” Orodan complained.\par
“What else did you expect me to do over the course of almost five days? The creatures here weren’t content with letting me peacefully watch either,” Arvayne explained. “You could stand to develop some patience yourself… maybe I should lock you in a room and have you read books for five days straight as recompense. Who just goes and jumps into a fight like that?”\par
The threat of excruciating boredom horrified Orodan.\par
“I apologize…” he weakly said. “My blood was boiling for battle.”\par
“I know. Agathor couldn’t stop telling me about it as I was trying to read.”\par
Orodan felt a bit weird at having had the God of War as his live audience during that entire fight, but appreciated the support.\par
His attention was then drawn to all the corpses, and especially towards the corpse of the spider-dragon which any dragon flights would love to see. Especially of one that was at the Grandmaster level.\par
“Don’t know how we’re going to carry all of these corpses back though,” Orodan muttered.\par
“That’ll be of no issue,” Arvayne said.\par
And before Orodan could ask him to explain, the man simply waved his hand, and a ring on his finger glowed and the corpses were sucked inside the spatial vortex generated from it.\par
“Of course you have a spatial storage ring… why am I not surprised that you’re a disgustingly rich old codger?”\par
“Hmmph… this isn’t an average ring either. It was made by a dragon enchanter,” Arvayne boasted with a slight smirk.\par
Orodan brushed off the old man’s bragging, and turned to look down the now unhindered massive tunnel leading downwards.\par
It was a truly great distance away that the color of the stone walls began to change, and the mushrooms lighting up the tunnels began to drop off. Near the end, it was pitch darkness.\par
“Don’t even think about it boy. Some of the things down in the abyssal depths… even I wouldn’t survive while calling upon the full power of Agathor,” the Chosen cautioned. “That darkness you see, it leads to a chamber right at the edge of the deep depths. From there it’s a straight hole down to the abyssal depths. This cavern we’re in is the farthest anything in the deep depths will dare to live in. Down in that transitionary chamber, even if it’s still part of the deep depths… nothing dares to live there for fear of attracting whatever vile things are down the hole leading to the abyss.”\par
“What lives down there then? You’ve ventured in there once haven’t you?”\par
“We didn’t get very far, just the very initial few tunnels… and the first thing our group of twenty Grandmasters encountered was a monster Observe called a ‘Sorrow of Magic’,” the old man spoke. “A third of our group was instantly rendered useless as their mana pools and all enchantments were immediately drained dry. Myself and the other Chosen had to immediately enter Avatar states to fight it, and two Grandmasters were killed.”\par
“Are the monsters down there truly that strong?”\par
“To put it into perspective, consider the fact that we have a legend of a Void Horror coming up from the abyssal depths and causing the collapse of civilization on the entire continent of Inuan thirty-thousand years ago. That’s how terrifying some of the things from below can be,” Arvayne spoke. “That pile of scrap underneath Mount Castarian that you took out is one of the creations of a civilization from that ancient time.”\par
“Then what stops them from coming up?”\par
“We don’t know, and I suspect we never will as no mortal will be strong enough to delve any respectable distance down there. Even our expedition which went a mile down was considered rather unsuccessful,” the old man explained. “The deepest delving expedition on record that survived was lead by the first Novarrian Emperor. It went twenty miles down, and any information on what the expedition encountered is kept sealed in a vault in the Imperial capital of Novar’s Peak.”\par
Orodan for once heeded the man’s warnings. He still had many things to do in this loop. And given how difficult this battle against one of the strongest creatures in the deep depths was he wasn’t sure he could win against even the weakest creature in the abyssal depths.\par
Furthermore, he wasn’t even on the level of a Chosen One yet, so diving into the abyss to commit suicide would have to come after he could at least beat Chosen Ones.\par
Although Orodan did vow that he would spend at least one set of loops just grinding his head against the depths of the abyss, if only to see what was down there. If just the first monster encountered took a team of Chosen Ones to defeat while suffering casualties… then who knew what terrors lurked at the lower levels?\par
They made way for the surface after.\par
Orodan had missed the week of classes, but it was of no great consequence.\par
Arvayne also told him that they would be returning again next week to expose Orodan to some naturally occurring Eldritch creatures.\par
The bigger concern however was presenting the corpse of the Grandmaster fire spider dragon to the local Time Wind dragon flight. Arvayne would be accompanying him to their lair personally.\par
It was time to be introduced to dragon society.\par


\section*{Chapter 22 - A Reward \u0026 An Auction}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 22 - A Reward \u0026 An Auction}%
\par
Dragons loved mountains.\par
He found Cyvrosdyr sleeping atop one when he met the World Guardian on the northern continent.\par
The fresh air and easy access to the skies were perhaps why? Dragons were flying creatures after all.\par
And spanning an entire mountain range, was Millennium Roost. The vaunted ancestral city of the local Time Wind dragon flight.\par
Dragons were ageless immortals. They could grow to be much older than any of the mortal races, even the long-lived elves. Consequently the Time Wind’s main settlement which was situated on the Altazhar mountain range on the northern coast of the Republic, was the oldest known city for thousands of miles.\par
Dragon flight settlements in general were the oldest settlements on the continent. Since the cataclysmic Void Horror’s ascent thirty-thousand years ago which destroyed civilization on Inuan, dragon flight settlements were the first to pop back up. And Millennium Roost was almost twenty five-thousand years old.\par
Dragon-made buildings were massive. It looked like entire mountains had to be mined to the ground to provide enough material for all of these dwellings. These structures, could definitely fit dragons within them.\par
A key part of the architecture was that every single building in the settlement, had an opening in the roof which would allow for dragons to enter or exit through flight.\par
As their griffins flew through the skies towards the city Orodan caught sight of dragons of varying sizes. Some were flying about, he saw the occasional aerial spar and moments which almost looked like play-fighting between dragons. And he saw older and bigger dragons who were simply resting atop of various mountain tops. With the higher peaks and spires being claimed by bigger dragons.\par
Atop the largest mountain of the range, Orodan saw something he thought was part of the mountain, but upon closer inspection realized it was a massive dragon nearly the size of Cyvrosdyr. It took up almost the entire top half of the mountain and was wrapped around it. It looked as still as the rock it was sleeping on.\par
“That’s Kultuanir the Frozen Instant, probably the most powerful dragon of the Time Wind,” Arvayne explained from atop his own griffin. “He’s been meditating on the meaning of time since before I was born, and might still be sleeping even after I die of old age.”\par
“I’ve been reading about them, but do dragons truly take so long in meditation? When I met Cyvrosdyr the Eternal Winter he too told me he’d been sleeping for millennia too,” Orodan remarked. “What are they even meditating on for so long?”\par
“Ah… unlike you or I, dragons tend to have a very slow rate of growth despite how naturally powerful they may be. They are an apex species, among the most powerful in our world once they reach Grandmaster-level in anything,” Arvayne explained. “Problem is, even a World Guardian like Cyvrosdyr with the assistance of increased world energy absorption… can take upto ten-thousand years to reach Grandmastery in a single skill. Don’t boast about the natural talent of the mortal races to their face unless you want to offend them.”\par
That was ridiculous!\par
Orodan found himself feeling quite grateful for his own natural talent in comparison. Grandmasters of the mortal races could take a thousand years on average to become a Grandmaster. The talented ones might take half that time.\par
Dual-Grandmastery and triple-Grandmastery might take upto two-thousand years altogether, and by then the natural lifespan limits of most races besides the elves and dwarves began to come into play. Human Grandmasters tended to start passing of old age around three-thousand years. With their physical bodies weakening around the twenty five-hundred year mark, combat also became unfeasible. Even with healing magic, enchantments and the like, nobody had found a method for true immortality that was widely available.\par
Dragons of course, could take ten-thousand years to attain Grandmastery… but they lived forever.\par
The dragon flights were notoriously silent on the question of whether there were any living dragons that were older than a hundred-thousand years. They refused to tell even the Grandmasters of other races of such a thing.\par
Who knew if there was some monstrous old dragon that would view even Cyvrosdyr as a spoiled child? And if there was… where were they when the Eldritch Avatar descended?\par
Last time he fought it, Orodan had awoken after a full year to see everything in his sight till the horizon subsumed by the Eldritch. But maybe the Eldritch hadn’t reached everywhere?\par
Their griffins finally touched down onto the gargantuan landing zone, which was meant to accommodate dragons. The ground here was quite reinforced too.\par
Orodan had new clothes and weapons on his person, as everything had been disintegrated during his fight against the spider dragon. He felt quite dissatisfied with the new weapons. Sure, they were a sword and shield of excellent make. But they just weren’t his.\par
Upon landing two dragon guards approached them. Lustrous metallic armor covered them from head to tail, and it looked expensively enchanted. Their claws were tipped with subtly glowing metal.\par
Behind these two Orodan could see a larger dragon, standing on its hind legs, wielding a gigantic halberd which looked as though it could cleave a mountain in two with just the arc of its swing.\par
Orodan would love to spend a few loops testing himself against this draconic warrior.\par
One of the two approaching guards spoke with a respectful grumble.\par
“Arvayne Firesword, we bid you welcome. Our halls are always open for one of humanity’s Chosen,” the dragon spoke. “Are you perhaps here to attend the auction?”\par
“I wasn’t even aware there was an auction today…” Arvayne muttered. “But why not? We’ve come to visit the treasure hall alongside my student Orodan Wainwright here.”\par
“Oh? So this is the babe who we’ve heard your kind go aflutter about?” the dragon asked. “Slaying a Grandmaster Dweller Worm when at the Elite-level is quite a feat, even by dragon standards. My brother here slew a Master-level one during his Elite ceremony two-thousand years ago.”\par
Of course dragons were so monstrously strong that they too could jump a whole tier to fight. Such was the natural prowess of this apex species.\par
“Well, I slew a spider dragon recently too. We’re actually here to turn in its corpse for the bounty,” Orodan answered. And the landing zone suddenly went quiet as the two dragon guards before them didn’t dare to speak.\par
It was instead the halberd wielding dragon behind the two guards who approached with thundering steps. It spoke in a bellowing voice.\par
“Child, did you perhaps kill this spider dragon yesterday? Was it a fire breathing one?” it asked. “Did it use space magic as well?”\par
Orodan nodded his affirmation to all of these questions.\par
“…incredible. Elder Vantalomir will want to see you immediately,” the dragon spoke respectfully. “You… are only a human child? Have you perhaps reincarnated?”\par
“No, although everyone seems to assume this,” Orodan spoke truthfully.\par
“Monstrous…” the dragon remarked. “Come with me, you as well Arvayne Firesword.”\par
They were guided through the open pathways of the settlement towards their destination.\par
It wasn’t like a standard city full of the mortal races. The dragons weren’t as prolific and heavy in number as humans in their cities were, and consequently aside from seeing them fly overhead, dragons walking the pathways were rarer. It was mainly humans, halflings and the rare elf walking on the ground.\par
Orodan actually stopped and stared at her pointed ears for a while until Arvayne had to drag him away and the poor elven woman looked embarrassed herself.\par
How could he be blamed? Orodan had never seen an elf up close before!\par
Their guide eventually brought them to a massive open hall, there was no roof and it lead to clear skies above. There were splendorous statues of dragons lining the walls of this hall. There were also various displays of some very powerful and opulent looking treasures and enchanted items.\par
At one end of this hall, was the ground entrance, meant for the various flightless visitors. On the other end… was a massive dragon coiled around a golden spire.\par
Before Orodan and Arvayne could even approach, the dragon suddenly appeared before them.\par
Orodan didn’t even bother trying to use Observe. Arvayne had warned him not to as dragons were notoriously secretive about their personal affairs.\par
Paranoid mortals would often have anti-Observation items on them.\par
But dragons took this to another level, as almost all of them deeply valued their privacy. Many knew the Observation Resistance skill, and virtually all dragons had some kind of item which guarded against it. Some could even sense attempts at Observation and would deal with the offender appropriately.\par
“Vantalomir, you are as impulsive as ever,” Arvayne remarked casually as the dragon sniffed the man. The sight looking ridiculous, as the dragon’s head was larger than a castle.\par
“I smell the scent of something heinous and utterly foul upon you Arvayne Firesword… release it so that I may inspect it,” the massive gold-scaled dragon demanded.\par
“Very well, but you may want to get some distance… my student’s kill is rather large,” the old man cautioned, and the dragon obliged.\par
A flash of light was followed by the appearance of a spatial vortex. Out of this spatial vortex came something filthy.\par
The mangled and utterly ruined corpse of a fire spider dragon. In Orodan’s opinion it was hideous in life, but even uglier in death.\par
The pupils of Vantalomir’s eyes shrunk and the dragon hissed as though it was recoiling.\par
“Filthy creature! This… this is Yamalshuk the deceptive murderer!” the dragon exclaimed.\par
The dragon let out a keen roar which carried through the air, and then it looked at the two of them.\par
“Arvayne Firesword, were you the one to kill this abhorrent curse upon dragon-kind?” Vantalomir asked the old man pointedly.\par
“I did say it was my student’s kill did I not?”\par
This caused the gargantuan golden dragon to look directly at Orodan.\par
“You, human child… what is your name?” asked the dragon.\par
“Orodan Wainwright.”\par
“Orodan Wainwright… I have heard the mortals below occasionally whispering this name… are you perhaps a reincarnator? I cannot understand how someone your age would slay this filthy anathema. Did your mentor assist you? Or are you perhaps the host of an Avatar yourself?” the dragon asked curiously in a softer tone.\par
“He is neither of those things old Vantalomir,” Arvayne interjected. “He is my student for a reason… he is simply that strong.”\par
Was that… pride? It felt oddly warming to know that the old man actually felt such esteem at having Orodan as his student.\par
“The flows of time around you do not lie… you are quite young from what I can see…” the old dragon muttered. “How have you done such a thing?”\par
“Allow a young man his secrets won’t you?” Arvayne interjected.\par
Vantalomir the golden scaled dragon, grunted… but acquiesced. It would be frowned upon for a dragon to press someone for their secrets. Dragons took the concept of privacy very seriously.\par
Soon, two more dragons landed upon the open hall, behind Vantalomir.\par
One with white scales and an aura of healing that made Orodan feel at peace. And one with dark scales and a dominating aura of gravity that felt as though it wasn’t powered by mana.\par
“…so it is true. My brother’s Quest truly was somehow completed… which of you is responsible for this?” the dark dragon with a powerful aura of gravity asked.\par
“That would be this young human here, the student of Arvayne Firesword,” Vantalomir spoke. “Orodan Wainwright.”\par
“I was not aware you were in the habit of taking on students Arvayne Firesword,” the dragon remarked. “Your kind tell me you are famously withdrawn.”\par
“Only when they exceed all known standards of talent and growth,” his mentor replied.\par
“Hmm… I have heard your name bandied about by the humans who come by. Where did you find this filthy abomination child?”\par
“In the deep depths near the western coast, from what some of the local monsters were saying, it had just moved in too.”\par
“Yes, this vile hunter is known for moving about through the deep networks under the earth. This allows its kind to evade the notice of the dragon flights. This one in particular… the nefarious Yamalshuk, has scurried about for seven millennia… until now,” the gravity dragon said. “You have slain a beast that has killed many of our kind through its cheap tricks.”\par
Spider dragons were ambush predators and known killers of dragon kind.\par
Many times they would skulk upwards from the depths to ambush some poor dragon they sensed above. They would flee back down to the depths shortly after to avoid the terrible retribution.\par
Dragons who were quite large and preferred aerial combat, weren’t willing to pursue often. The terrain in the depths was a serious disadvantage for a dragon.\par
The creatures were the main reason why dragons stopped using underground lairs and instead preferred mountaintops. The threat of an ambush from a spider dragon was something dragon-kind was forced to live with.\par
Humans and the mortal races on the other hand, were well suited to delving the depths and hunting spider dragons. Provided the mortal was strong enough or brought a sufficient force along.\par
It was why the Republic had a strong friendship with the Time Wind dragon flight. Within the hundred and twenty years since its formation, the Republic sent regular expeditions into the depths to cull all sorts of dangerous creatures. Spider dragons were in this category.\par
Of course, a spider dragon at the Grandmaster-level was a ferocious monster that could evade notice and flee in the deep depths. Any spider dragon that had managed to make it to Grandmaster was undoubtedly notorious among dragon-kind.\par
Which made Orodan’s feat momentous.\par
“Well I’m glad I killed it then,” Orodan replied. “It was a pretty good fight, I didn’t even know portals could be used like that… got torn apart hundreds of times before I finally got the hang of it and wore that dirty thing down.”\par
“Most impressive! Such an act of service is deserving of an appropriate reward,” the dragon announced. “I, Rosvedir the Unrelenting Burden, second elder of the Time Wind dragon flight, hereby grant you free reign to pick any one treasure you desire from the Grandmaster section of our treasure hall!”\par
“Any treasure… Orodan, you must not squander such an opportunity! Let me speak a bit on your behalf first to ask for something that would benefit you more,” Arvayne requested, and Orodan saw no reason to say no. The old man had acted in his best interests thus far.\par
“Arvayne Firesword, what would you ask on your student’s behalf?” Rosvedir queried.\par
“Venerable Rosvedir, my student may be one of the rare few on this world who is capable of learning to use the draconic arts. His reserves of energy are endless, and his body grows stronger by the day,” the old man spoke. “If any mortal could learn the energy-intensive arts of dragon magic channeling, it would be Orodan Wainwright.”\par
Magic? Orodan didn’t see himself becoming some robe wearing weakling who hid on the back lines and slung spells from a distance.\par
But, dragon magic? What even was it? Perhaps it could synergize well with his existing skillset. That spider dragon he fought was certainly powerful and not a coward averse to fighting head-on like a warrior. It used magic as well.\par
“That is… while such a reward wouldn’t be out of the question, the energy demands are titanic by the standards of you humans. Even a hundred Arvayne Fireswords could not generate the amount of energy used in dragon magic channeling,” Rosvedir explained. “Even among our own kind, the channeling method we use in the Time Wind dragon flight is incredibly difficult to achieve mastery in.”\par
“What if I were to show you how much energy I can generate?” Orodan asked, now intrigued by the prospect of learning such a unique skill not meant for his species. “If there is a device that I can pour energy into… I bet I can beat anyone over time.”Unauthorized use of content: if you find this story on Amazon, report the violation.\par
“Hrm… I am not opposed to this. We do have a trial that can measure how much raw energy you can generate. It's a rite of ceremony for dragons at each stage,” Rosvedir explained. “But even if you set the mortal record and surpassed every other human who attempted it… it’s still no guarantee that you’ll be able to acquire the first level of Draconic Mana Channeling. It’s the System name for the skill.”\par
“Beat out other humans? You seem to have misunderstood me,” Orodan corrected. “I intend to beat out every other dragon who has attempted this test.”\par
The hall went silent for a second as the words echoed and were absorbed by the listeners.\par
“Outrageous! Do not make tall claims child! If you surpassed even the average Adept-level youngling in our hatcheries, we would consider you a prodigy,” Rosvedir reprimanded. “We will administer this test immediately, but do not make such boastful claims. Skill levels are one thing, but even young dragons who are fully grown at the Elite-level possess a quantity of mana beyond all but the strongest of humans.”\par
It was true.\par
Even his mentor would struggle in a competition of pure energy generation and endurance. A young adult dragon at the Elite-level had more raw mana than even the strongest of Grandmasters and Chosen Ones.\par
Dragons could launch attacks of terrifying destructive prowess. They could fight almost endlessly and throw energy-intensive attacks around like nothing.\par
Battle power was one thing, but the sheer amount of mana dragons possessed was another. It was why dragon enchanters and alchemists were so revered for the items they would create. They could empower something with titanic amounts of mana that the mortal races could only dream of.\par
While mortal crafters excelled in different aspects, such as fine details and innovation… dragons could push the upper bounds of an item’s raw power simply due to their natural gifts.\par
But Orodan still dared to attempt this and prove the dragon wrong.\par
Arvayne looked somewhat conflicted but said nothing, allowing Orodan to decide his own course from here.\par
“Child, your claims are absurd and something of the like has never been seen,” spoke the white scaled dragon who had remained silent all this time. A feminine tone was translated by the System. “In my twenty-five thousand years of life since the establishment of this dragon flight… I’ve seen less than a hundred mortals defeat a Master-level dragon at this test. Those mortals went on to make history, and one of them is now a God.”\par
Twenty-five thousand years old? Perhaps this dragon really did know someone who became a God eventually. Even if she wasn’t willing to say which God it was.\par
He would have to ask about the process at some point as nobody in the Republic seemed to know about how that occurred.\par
“Perhaps your confidence comes from the belief that you can beat a Master-level dragon in this test?” she asked. “Be warned that the records of Grandmasters of our kind are also on the rankings for this test. So do not speak too hastily.”\par
“I strongly believe, that I can beat even a Grandmaster-level dragon in this test. If I can go that far… will you teach me how dragons channel mana?” Orodan asked.\par
“If you can beat even the lowest ranking Master-level dragon in this trial, then I would teach you myself,” the white scaled dragon answered. “But if you are boasting and wasting our time, then you will leave with a treasure as thanks for your service.”\par
A fair agreement, Orodan thought.\par
But what if he really did beat even a Grandmaster-dragon’s ranking? What if he went even further?\par
\par
They were allowed to keep the corpse of Yamalshuk, the fire spider dragon. It would be a nice piece to sell during the upcoming auction tomorrow. The dragons also wanted nothing to do with the dead body of the foul beast.\par
The test was held atop one of the wider mountains in the range.\par
The rock composing this mountain looked different from the surroundings. It looked sturdier, as though it was painstakingly reinforced.\par
In the center, was a gigantic red orb. Large enough that even the biggest dragon he knew could still lay an arm upon it comfortably without enveloping it.\par
“The test is quite simple. Place a hand upon the orb and suffuse it with as much energy as you can,” Rosvedir explained. “Stopping ends the test. Removing your connection of energy from the orb counts as stopping, as does the lack of any energy going in. You have thirty minutes to generate as much power as you possibly can and feed it into the orb. All forms of energy are accepted, mana, vitality, soul energy, psionic power and so forth.”\par
Orodan nodded in understanding.\par
Before he started, his mentor approached him. “Orodan… you needn’t push yourself this hard for the sake of impressing the dragons. They’re willing to teach you even if you acquire a decent result. You don’t need to cut this loop short because you wanted to prove a point.”\par
“Old man… I’ve gotten a lot stronger in my ability to patch myself up. I also haven’t really strained Eternal Soul Reactor to the utter limit in a while, so this is also an opportunity for me to see just how far I’ve come after all this.”\par
Arvayne nodded and walked off to the area meant for spectators.\par
There were a decent number of dragons in attendance. Word of this test must have gotten around faster than he thought.\par
“Whenever you’re ready Orodan Wainwright,” Rosvedir announced.\par
Subsequently, Orodan put both hands on the orb and activated every single empowerment skill he had to its maximal value.\par
Death Rage helped bring his vitality down to a point where Dying Struggle activated and gave him a much needed physical and mental boost. Regeneration and Unyielding Vitality kept him from death.\par
The stage was then set for all of his willpower and improved reaction time to go towards churning Eternal Soul Reactor as hard as he could.\par
He hadn’t used it to try and kill himself in a while, but with how hard he was now churning it, it might very well.\par
His muscles and organs began to nearly disintegrate, even as his monstrous vitality skills patched him up just as quickly. His eyes were luminous beacons and must have made him look like an Avatar.\par
If anything, people seeing Orodan’s current state might genuinely think he was calling upon the power of an Avatar.\par
But the Time Wind’s test allowed for even this! It was just that even an Avatar’s energy generation wasn’t up to par with higher-level dragons.\par
But Orodan? Orodan was a different beast altogether.\par
As his eyes glowed and burst, and his muscles and skin boiled and reformed… the orb began to glow.\par
It went from lightly shining, to now glowing.\par
He heard the roars of surprise and conversational noises from his draconic spectators.\par
The System translated their words almost instantly after.\par
“Crossing the rankings of Elite-level dragons in less than a minute?!”\par
“Monstrous! It must be divine power! But from which God!?”\par
There were more draconic voices crying out, but Orodan chose to ignore them and focus.\par
His body was beginning to near its limits on how much of his own soul energy it could take. Even if his Body Tempering had progressed a decent amount, he was still coursing an absolutely colossal amount of power within himself.\par
The only saving grace was that the orb was greedily absorbing it all. His body was the bottleneck that would cause him to die if he generated too much power. But the orb was easing the burden on his body.\par
But what if the orb’s absorption rate could be made faster?\par
Orodan then decided to force the issue.\par
He had never tried wrapping Weapon Aura around something so gigantic… but if he never tried he’d never know.\par
He quadrupled his mind, and extended every bit of mental willpower out towards the orb.\par
It strained his mind beyond belief, and an incredibly painful headache was forming. But even as his nose bled he managed to succeed.\par
He then demanded it pull energy from him even faster.\par
And it did.\par
The strain on his body was immediately alleviated as the energy was practically devoured by the orb. It ate his soul energy so fast that he was almost drained completely.\par
So he felt safe ramping up Eternal Soul Reactor even further. Furthermore, he practically threw the accumulated reserves of Mana Black Hole and Vitality Black Hole into the orb as well, which caused its glow to temporarily spike.\par
Two more minutes passed, and the conversation around him erupted yet again.\par
Given how the conversation around him was increasing, he was fairly certain he passed another threshold. But he couldn’t even make out the words this time as he was too engrossed in powering the orb. His vision was white from the sheer cloak of energy surrounding him.\par
He was practically hugging the orb. His quadrupled mind increasing its absorption speed while he kept increasing the generation rate of his mythical skill. It was a cycle, and if the orb fell behind… Orodan might just instantly die from being incinerated by the titanic amounts of soul energy using his body as a conduit to move to the orb.\par
His arms began melting off, and he pressed his head to the orb, desperate to have something in contact with it.\par
He kept generating energy, and the orb kept absorbing.\par
He didn’t know how long had passed as this went on, but soon the orb’s absorption rate began to slowly lower, which alarmed Orodan. Because his soul’s energy generation rate was still incredibly high.\par
Fatally high.\par
“Potions! Whatever you have that can heal!” Orodan roared, even if he couldn’t hear what was being said in reply.\par
Bringing Eternal Soul Reactor to a stop while it was churning this high was difficult. Last time it happened he had to spent multiple loops dying as soon as he awoke before he could get his own soul under control.\par
And while Orodan didn’t care about death, ending this loop wasn’t something he wanted when the secrets to draconic magic were so close.\par
He was in a race against the clock. To wind Eternal Soul Reactor down below the unfathomably fatal levels he had it at before the orb’s counteracting absorption stopped entirely and all the energy within him had nowhere to go. The result would kill him.\par
He gained multiple levels in Soul Manipulation and Mana Manipulation as he converted as much as he could to mana and threw it all into Mana Black Hole’s reserves.\par
Glass hit his back and something wet spilled over him. This alleviated the damage he was suffering quite a bit. More potions of healing were thrown at him continuously.\par
Finally, as the orb stopped absorbing energy entirely, he was very close to dying outright when a warm healing light suffused him. It was stronger than the healing of the Favored Avatar of Ilyatana he had faced long ago.\par
Under the effects of the external healing and his own vitality skills he kept working. The extra breathing room gave his quadrupled minds more time to forcibly slow down the production of soul energy within himself.\par
Another minute passed, and Orodan felt like he was about to wake up in his hovel in Ogdenborough again.\par
Finally, he was practically a few pieces of glowing molten flesh on the ground when he passed the critical tipping point. His own Regeneration began to heal more of his body than was being destroyed.\par
From that point his soul began to slow down further and his body finally reformed, even if his eyes were still glowing.\par
The skill level gains in the relevant skills… were quite good.\par
If anything the orb was an effective form of training.\par
The all-encompassing storm of soul energy surrounding him had also vanished, and Orodan looked around for the first time.\par
The spectator section was empty. The reinforced ground was decently damaged and scarred.\par
Every dragon had taken to the air, and his mentor Arvayne was atop the back of one, healing potions in hand. He would have to thank the old man for his good aim and quick thinking.\par
Beside him in the air was the white scaled dragon, her eyes emanating a golden luminance. Her healing had undoubtedly saved his life.\par
Eternal Soul Reactor was his bread and butter… but it was also one of his most dangerous skills. It ran the risk of killing him and forcing him to spend several very short loops bringing things under control till he stopped dying.\par
His own glow faded, and he smiled.\par
“How did I do? The orb stopped absorbing energy, so I at least passed the Grandmaster threshold right?” Orodan asked.\par
The white scaled dragon remained silent for a while before speaking.\par
“Orodan Wainwright. You… are the new record holder for the trial of abundance.”\par
\par
Rosvedir was quite respectful and apologetic towards him after the whole ordeal. It was almost amusing seeing the black scaled dragon of gravity look at him with regard.\par
“I must admit Orodan Wainwright, I have seen many things in my almost two hundred centuries of life. But a human claiming rank number one in our dragon flight’s trial of abundance… is ridiculous,” Rosvedir spoke. “Are you… perhaps a dragon yourself? You cannot be an Avatar as they’ve tried our trial before and never managed to break past the Grandmaster-level rankings. You can’t be a reincarnator as I would have heard of your skill or Bloodline. Unless… you’re the reincarnation of someone from over two-hundred thousand years ago?”\par
“I’m not a reincarnator, nor do I have any Bloodlines that I know of. I don’t think I’m a dragon either unless there was some passion in my ancestry that I’m unaware of,” Orodan replied.\par
“Ludicrous… it can only be a Bloodline at this point. The battle power of an Avatar possessing a Grandmaster Chosen is incredible, but it’s not their abundant energy reserves that give them this power. Even the strongest mortal Avatar in the world could not generate the energy you did. You truly are an absolute anomaly,” Rosvedir explained. “I maintain… that you are a dragon but do not know it yet.”\par
“Huh?”\par
“Your mannerisms are quite blunt and straightforward, your energy generation is titanic, and you tackle your problems head on,” Rosvedir described. “You can only be a dragon. This is the only explanation I can see… although you’re rather small and your lack of scales will be a matter of much mockery.”\par
“Your antics are not as amusing as you think Rosvedir,” spoke the white scaled dragon. “I am Hymelrass the Everflowing Warmth, nominal head elder of the Time Wind dragon flight. I will be your teacher in the matter of Draconic Mana Channeling. Ignore Rosvedir… he indulges the younglings in the hatchery too much and it bleeds over to his mannerisms.”\par
On the contrary, Orodan felt that he quite liked the dark gravity dragon.\par
“When will we start?” Orodan asked.\par
“Your mentor tells me you also attend a human academy. Your training with me will begin in two days when classes at your academy resume,” Hymelrass explained and Arvayne who was next to Orodan nodded. “You will come here after your classes and receive tutelage from me in the art of us dragons. Also... your ranking in first place in the trial merits a reward. You will receive this later.”\par
Cryptic, but it sounded like a good arrangement to Orodan.\par
“In the meanwhile though… I hear there’s an auction?” Orodan asked.\par
“Aye, we’ll be attending that to sell the corpse of the spider dragon you killed,” Arvayne spoke. “It’ll be a good experience for you to see some treasures and valuable items and get an understanding for what various people want. Knowing what’s valuable and for what reasons is essential information to have.”\par
“I’ve never been to an auction… but why not? Maybe there will be some good training aids to acquire?” Orodan asked, thinking about similar items such as the endless gravity core that he had yet to swallow.\par
“You… I talk about a gathering of fantastical wealth, items and luxuries and all you think of is training aids?” Arvayne asked. “Forgive me wise dragons… my student is a bit single-minded at times.”\par
The old man was being melodramatic in Orodan’s opinion.\par
But, the auction was something he was looking forward to.\par
Not only would it be the first time he was attending one. But it was an auction held in Millenium Roost, the main settlement of the Time Wind dragon flight. Aside from the Novarrian Empire, the dragons were mostly neutral when it came to conflicts between the mortal races. As a result, auctions held in dragon flight settlements attracted goods, traders and people from all over.\par
Who knew what wondrous training aids from far off lands he might have the chance to acquire?\par
\par
The auction was a bi-weekly event.\par
The Time Wind were the organizers as it was their settlement.\par
Humans, halflings and the rare elf or two were walking about the auction hall before the show began and any bidding could start. There were some dwarves in attendance as well, and Orodan guessed that they weren’t affiliated with the under-mountain kingdoms of the Dokuhan mountains where dragon slaying was a popular practice.\par
In typical dragon fashion, the building was gigantic and built to accommodate beings the size of mountains. The dragons had their own areas of seating on raised stone platforms surrounding a smaller arena style venue where the mortals would hawk their wares.\par
Sound amplification systems were present, and dragons with intimidating weaponry were guarding the venue with fierce looks in their eyes.\par
Nobody in attendance was stupid enough to try stealing or causing trouble on the Time Wind’s turf. Dragons were individually some of the strongest beings in the world.\par
“Young master might I interest you-”\par
“You seem like a man with expensive tastes, why no-”\par
Orodan tuned out the various merchants who were trying to hawk their wares as he walked by to take a seat at the front row alongside Arvayne. Their seats were reserved, courtesy of the Time Wind, and thanks to Arvayne’s reputation.\par
The ones hawking their wares weren’t anything too special. It was the items that would be presented during the auction that were the real treasures.\par
Perhaps it was his reputation, or maybe it was Arvayne’s, but nobody bothered them with attempts at socializing. He recognized a few noble house sigils from the Republic among the crowd, alongside sigils from nobility of the Eastern Kingdoms. He was certain he even saw the sigil of House Vedharna somewhere.\par
Soon, the chatter quieted down as the golden-scaled master of the treasure hall, Vantalomir approached the stage. His approach was really no more than hovering his large head over the smaller arena sized stage.\par
He was big, but not quite as massive as some of the other dragons he’d seen. Still big enough to loom over the stage regally.\par
“Greetings, distinguished guests and residents of our humble abode. The Time Wind dragon flight welcomes all to another auction in Millennium Roost,” the dragon spoke. “I am Vantalomir the Splendorous, master of the Time Wind’s treasure hall… and I shall be your host to the treasures that shall be auctioned today.”\par
‘The Splendorous’ certainly suited the gold-scaled dragon.\par
“Now then, first on our docket, we have this powerful Grandmaster-level sword forged by a famed smith from the Eastern Kingdoms. An incredibly potent weapon capable of slicing through mountains when unleashed as the mana-based enchantments spew deadly spatial vortexes.”\par
“You could use a proper sword no? Let’s bid on th-”\par
“No. I miss my old sword… this replacement won’t suffice,” Orodan answered bluntly. “One day, I’ll get good enough to turn my sword into something truly great at the start of each loop.”\par
Orodan thought Arvayne would sigh in disappointment or some other melodramatic gesture as usual. But the old man actually nodded approvingly.\par
“I agree, it’s best not to grow used to powerful treasures and weapons in battle,” the old Firesword spoke. “Better you rely on what you can produce and swing with your own arm.”\par
The next item, was a glowing staff which was introduced as being an excellent conduit for lightning mages. A piece of trash in Orodan’s opinion. That he disliked mages didn’t influence his opinion at all.\par
The following sequence of items were all various mage-related weapons and items. From spell focuses to magic robes. Orodan had no interest in such things.\par
The item after the mage sequence however was interesting.\par
“This contraption we have here is a very advanced model of the vaunted dwarven magic rifles. Its magic shot can allow an untrained peasant to kill even an Adept! And in the hands of a powerful marksman with relevant skills? Who knows what it can do?”\par
The bidding frenzy immediately began on the item. Frankly, Orodan didn’t understand what they were so excited about. Most of the bidders he saw were civilians.\par
“How powerful can that thing even be? Novarria tried introducing those to the militia of certain towns didn’t they? Don’t think it went too well,” Orodan remarked and Arvayne nodded.\par
Blackpowder weaponry was strong… until the Adept level.\par
Adept warriors were more than tough enough to withstand the shots of repeater rifles while entirely unarmored. And even marksman rifles with slightly more sting weren’t anything too special. Adepts could react to and dodge the shot, and unless it was a repeater rifle… the weapon was slow to load. In comparison an archer or peltast at the Adept level who could launch maybe twelve to fifteen attacks a second was considered superior.\par
Additionally, the speed of the shot didn’t really increase with skill levels. And neither did the weapon receive any benefits from the Physical Fitness skill. Blackpowder weapons and crossbows… were inferior to a weapon that also utilized the strength of the body as a multiplier.\par
The Novarrians discovered quickly during their trial run of the weapons that monsters with tough hides were quite resilient to the guns. Any basic level of sturdy armor also rendered the weapons quite ineffective.\par
Admittedly, there was some theorizing that arming cheap and untrained militia en masse with them might lead to some benefits. The idea was quickly shot down after the first field test during a monster hunting expedition lead to a single Adept-level monster managing to get into the formation. The untrained militia suffered serious casualties until the accompanying Adepts responded.\par
Orodan speculated that the weapons might be good enough to kill an unprotected mage, even of the Elite-level if they slacked in their physical training. Partly because pure mages were often a bunch of cowards with little combat instinct and had slow reflexes. But that was also Orodan’s bias against them talking.\par
But magic gunpowder on the other hand. He hadn’t heard of such a thing.\par
“The dwarves supposedly use magic rifles nowadays,” Arvayne spoke. “Admittedly, the ability for this toy to allow a child to kill an Adept is a big improvement over the standard blackpowder model.”\par
Orodan found himself agreeing.\par
If a civilian could kill an Adept with a single shot if they caught them unaware… then the weapon might be worth quite a lot.\par
A fat merchant from Karilsgard ended up winning the bid to buy the weapon. He looked to be discussing ways to reverse-engineer the technology already.\par
Orodan wished him luck. As dwarven technology was said to be notoriously difficult to reverse engineer. And even then, anything that reached an auction up north in the Time Wind’s territory, was likely a pathetic design that the dwarves allowed to get here.\par
After the sale of the gun, the next dozen or so items auctioned were all various magic trinkets focusing on storage with no features that truly interested Orodan.\par
Spatial rings, amulets of dimensional storage and bags of holding were useful… but not currently relevant to Orodan who was more focused on learning skills than hunting things and collecting massive amounts of resources. For now at least.\par
A few more disgustingly opulent treasures came forth, but they were either meant for mages, or something Orodan wanted to make himself eventually.\par
But one particular item that came forth, did interest him.\par
“This lasso was made by a dragon enchanter from the Sapphire Gale dragon flight. It’s powered by a soul energy enchantment and is worth an exorbitant sum! The creator is a good friend of mine. Throwing and getting it around a foe will result in them receiving almost every type of known elemental damage at once as long as the wielder has enough power to provide.”\par
Death Rage and Eternal Soul Reactor flared, his vitality immediately dipped down to the threshold where Dying Struggle activated. None of the other bidders stood a chance against his reaction speed.\par
He shot up…\par
…and placed the first bid.\par
“I bid my corpse of a fire spider dragon! I need that lasso to train my resistance skills damn it!”\par
The auction hall went deathly silent and Vantalomir gave him an annoyed look for being so loud.\par
Next to him the old man could only sigh and mutter.\par
“…why are his training methods so unhinged?”\par
Unhinged?\par
Could the old man not see the gains that could be made by swallowing the endless gravity core and using the lasso upon himself at the same time?\par
Perhaps he needn’t have declared it so loudly. But this…\par
…this was just an opportunity to engage in some more proper training!\par


\section*{Chapter 23 - Draconic Tutelage \u0026 Casting Spells}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 23 - Draconic Tutelage \u0026 Casting Spells}%
\par
Nobody else dared bid on the lasso after.\par
A majority of the auction guests were below the Grandmaster-level. So when someone famed for killing a Dweller Worm decided to furiously bid on a particular item of questionable usefulness for most… they let him have it. Bidding against someone could be seen as an offensive move.\par
People who could channel soul energy were rare to begin with, thus soul energy enchantments were infrequent and not as commonly seen. Furthermore, perhaps if it was a more conventional weapon there would be more bids, but not a lot of people saw themselves using a lasso.\par
He needn’t have offered the corpse of the fire spider dragon though. Arvayne simply paid the exorbitant five-hundred gold pieces the item was worth. But the corpse did sell quite well, as a halfling alchemist from the Eastern Kingdoms paid three-hundred gold for it.\par
The sums of gold exchanged were utterly staggering to Orodan. He made a single gold piece a year as a member of the militia!\par
Yet many of these items were worth hundreds of gold pieces without bids taken into account. The most expensive item he’d seen was an enchanted cape that granted flight and an accompanying suite of auxiliary benefits to assist in flying.\par
It sold for over three-thousand gold pieces to a trader bearing the sigil of House Arslan.\par
His mind couldn’t take it anymore when Arvayne told him that this auction was rather cheap. His reasoning being that none of the dragons had bid on anything.\par
“Ridiculous… how do the wealthy even make this sort of money? I understand that many noble houses own lucrative magic businesses… but to just drop three-thousand gold pieces on a cape?” Orodan asked. “I’ve never heard of such sums of money in my life.”\par
“Aside from gold, what the books you’re reading don’t explain is that sometimes instead of money… favors are exchanged,” the old man answered. “A thousand gold piece item might exchange hands with an agreement to kill a powerful Grandmaster beast, or providing payment through crafting services. Hells, I remember a prince outright removing the tariff on a type of product once, just to buy a magical sheathe for his sword.”\par
“That much I can understand, but at a certain value there’s no way favors are enough,” Orodan countered.\par
“Correct. Which is why the Republic has logistics officers who peruse such auctions and draw from a national fund to acquire items that would be of benefit to the nation as a whole. A lot of the big buyers are often connected to national interests.” Arvayne explained. “The man who bought that cape, he’s the head of logistics for the palace back in Karilsgard. He and logistics staff like him will often frequent auctions. They have a good idea of what Republic military assets could benefit the most from what kind of item, and they’ll quickly snatch something integral up and draw funds from the national treasury to do it.”\par
“So some important commander might end up using that cape?” Orodan asked.\par
“Perhaps. Or more likely he thought it’d be useful and decided to acquire it for future purposes,” the old man said. “Sometimes they simply have blanket goals of adding to the stockpile of magical items. Other times they have targets to reach in obtaining a certain number of items of a particular type. As an example, there’s always a big demand for enchanted items which provide personal shielding. Those never make it to auction as people are clamoring to buy them as soon as they’re made.”\par
“I can’t say I’ll ever become well-versed in economic matters, but I understand a bit more now,” Orodan replied.\par
“You don’t need to become an economist, but it’s good to be informed. With your strength, you have many avenues of generating exorbitant wealth. Continue on your current course and wealth won’t be an issue.”\par
Soon, the auction ended with some words of closing from Vantalomir. The splendorous dragon thanked all the guests and the curtains were closed. The spectating dragons began to take off and the mortal guests soon followed.\par
Orodan and Arvayne also departed the venue.\par
Tomorrow, academy classes would resume. And along with it, Orodan’s draconic tutelage would begin.\par
\par
“Orodan! It’s good to see you!” Mahari exclaimed in her usual cheerful tone. “You’ve been gone for a week or so right?”\par
He had run into her on the campus roads. The first of Orodan’s classes for the day had yet to start.\par
“Yes, that’s right. My mentor and I went on a trip to the deep depths and then visited Millennium Roost,” Orodan answered. “It was a good journey. I never knew dragons made buildings that big.”\par
“Yeah, my companion and I will sometimes fly alongside Olsinius to visit, it’s quite the grand sight!” Mahari remarked.\par
Pegasi could fly incredibly fast and for great distances without tiring. It explained why Mahari could speak of visiting distant locales so casually. Riding a pegasus would make such travels a mere lunch break for her.\par
A whinny interjected. It was Olsinius, the pegasus. The somewhat grumpy older brother of Mahari’s nameless mount.\par
“The older dragons I encountered this morning weren’t very talkative as usual… but some of the younger ones mentioned your name quite reverentially,” Olsinius remarked. “Did you cause another ruckus?”\par
“Nothing of the sort you’re implying,” Orodan answered with mild indignation at the assumption that he caused trouble. He did. But not how the pegasus was thinking. “I took a trial of theirs and did rather well.”\par
“Rather well he says…” the pegasus grunted in what sounded like a mutter. “If you call taking first place in the Time Wind’s trial of abundance ‘rather well’ then I’d be ashamed to hear about anyone else’s results.”\par
“They have a similar trial in your clan?”\par
“Yes, we pegasi also undergo the trial of abundance in our clans. Each time we cross a tier, we are expected to undergo the test as a rite of passage,” Olsinius explained. “But to fill the orb entirely? You are a monster. The orbs are typically used as mana batteries to add power to the defenses and artillery weapons of a settlement. You added at least a century’s worth of power by filling it up to the brim.”\par
“Surely power generation isn’t a problem for dragons?” Orodan replied.\par
“True, the Time Wind can fill that orb rather easily with enough dragons working in concert. But not all civilizations have the energy generation capabilities of dragons,” the pegasus explained. “For most other species, natural energy generation doesn’t compare to what we can get from using mana crystals as fuel. And those can get expensive since we aren't directly mining them like you humans are. Us pegasi would thus greatly favor such an ability. My clan would pay you handsomely if you came by and rendered your services sometime. We can even look into finding a pegasus companion for you.”\par
That was an awfully nice offer. Orodan had no use for a pegasus though.\par
“Not to come across as disrespectful… but any pegasus I have as a mount would only hinder me in battle,” Orodan answered. “That being said, I don’t mind coming by to assist your clan in filling up this orb. The only reward I’d ask for is being allowed to peruse your treasure hall if you have any.”\par
“I take no offense. I’ve heard talk of you battling dweller worms and spider dragons,” the pegasus remarked. “Pegasi must be younglings in the Apprentice-level to choose a rider as companion, so it would be a while before it reached even Elite. Your price sounds reasonable as well, I will talk to my clan elders about your offer.”\par
“Wow… you’re never this pleasant with me Olsinius!” Mahari exclaimed in a tone of playful outrage, and then turned towards Orodan with a look of manufactured sadness. “What does a girl have to do to be treated nicely around these parts?”\par
Orodan ignored her usual hyperactive antics, as an uncomfortable encounter was headed his way.\par
He spotted Novus Eldragon walking down the halls. The Eldragon heir’s path was about to intersect with his.\par
It wasn’t that Novus was of any concern to him. But having to encounter the young man with him undoubtedly knowing about the trysts between him and Katareya… would be awkward.\par
“Ah… Mister Wainwright,” the boy muttered as he approached. “How’ve you been? I hope you’re finding Eldragon manor to your liking during your visits?”\par
He was just going to say it up front was he? So be it.\par
Orodan wasn’t one for sly games. And he had no patience for petty comments.\par
But… his time in the loops was starting to somewhat mature him. He was learning the value of patience and restraint. He didn’t want to outright offend Novus.\par
So a simple but direct question would do.\par
“What are you trying to say?,” he bluntly asked, causing the boy to frown. “Tell me what I’ve done to offend you.”\par
Diplomacy wasn’t one of Orodan’s strong suits. But that was still a better attempt than the Orodan first starting the loops would have made.\par
That Orodan might’ve just told Novus his mother’s bed was quite warm.\par
Perhaps Novus hadn’t intended to come across as outright hostile. Perhaps Orodan could’ve treaded a bit more delicately given what he was involved in. But the thought of playing some delicate social game annoyed him.\par
Who was Novus Eldragon to tell Katareya what to do?\par
“…you are quite straightforward Mister Wainwright! Since you’re getting right to the matter, then so will I,” the boy replied. “I don’t approve of your relationship with my mother.”\par
“Then instead of telling me, who is an outsider… why don’t you tell your mother herself? You’re family aren’t you?” Orodan asked, and the boy’s face held a look of frustration. “She’s an Elite-level diviner of the Cathedral. Can she not decide what she wants to do with her life?”\par
Poor Mahari was looking mortified at the conversation. The girl looked like she wanted to flee.\par
“That is…!” the boy exclaimed but then calmed himself. “Look, you can’t expect me to just be happy that you’re having an affair with my own mother do you?”\par
“I would expect a reasonable son to accept that his mother’s affairs are her own,” Orodan replied. “Then again, I don’t remember my mother or my father, so who am I to tell you about being a son?”\par
Novus’s face reddened further.\par
“You’ll never be a replacement for my father! Why can’t you just leave my family alone!?” Novus exclaimed with an ugly look on his face.\par
The pathway had gone silent and a number of people were staring.\par
“Look… I don’t even interact with you or your sister. How am I interfering with your family when I only ever speak to your mother? I’m doing a poor job of replacing your father if I don’t even talk to Katareya’s children aren’t I?” Orodan explained. “This whole thing is just a tryst, and that’s all I ever intended it to be.”\par
Orodan spoke calmly.\par
He truly hadn't intended to offend Novus. But Orodan had no intentions of playing along.\par
The boy was quite different from the calm persona he displayed at the party a while ago. He was emotionally volatile and angered at the moment.\par
But at seeing the surroundings go silent, Novus calmed a bit.\par
“Tch! I have nothing else to say,” he spat and then turned away and left.\par
Orodan genuinely didn’t understand why Novus was so angry.\par
“I don’t think I’ve done anything wrong have I?” Orodan asked as he looked at Novus retreating. “I’d like to think I gave it my best diplomatic effort.\par
Mahari looked at him a bit strangely, but answered.\par
“You’re an orphan, right Orodan?” she asked, and he nodded. “For most people… when they lose a parent and then someone else comes in, it can be taken rather negatively.”\par
“But shouldn’t he be happy that his mother’s found something for herself?”\par
“Again… you’re used to fending for yourself and haven’t had a mother or father,” she spoke. “A child often reveres their parents, especially if they’re loving. I don’t know what happened to his father, but seeing you come in and have intentions towards his mother… can’t be an easy thing for him to bear. Especially if he’s the eldest son of his family and is expected to be the one who brings the house to greatness. Seeing someone his age come by and seduce his mother isn’t uplifting.”\par
Mahari explained all this with a serious tone.\par
“But he’s never even seen me have intentions towards his mother aside from one time,” Orodan replied. “This is only my second time meeting him.”\par
“Such things aren’t as easily hidden as you think. If he lives in the same house, he more than likely knows,” Mahari continued. “A young man who’s training as a martial student at Bluefire… he has a lot on his shoulders. I’m not familiar with House Eldragon, so they must be a smaller house. The weight of expectations to live up to must be even greater then.”\par
“But what does all this have to do with me?”\par
“Morally? Nothing, if I’m being fair. I’m of the opinion that it’s his mother’s problem for acting in a way that upset her son,” Mahari replied. “That being said, there’s two sides to the argument that both have merit. His mother is a grown woman and can make her own decisions. As a young man himself he should respect that. But… on the other hand she could stand to be a little empathetic of her son, although I still think it’s her life.”\par
“I just don’t have time for petty comments or beating around the bush,” Orodan explained. “I have no enmity with him, but standing there as we engage in some stupid social dance isn’t my cup of tea.”\par
“You handled that situation with as much blunt directness as you always do,” Mahari remarked with a giggle. “But either way, you’ve now made yourself into the villain of his life in his mind. An insurmountable mountain that he’ll either be oppressed by or have to deal with.”\par
“What? I’m not even a villain!” Orodan protested and had half a mind to tell her about the Quests he was dealing with.A case of content theft: this narrative is not rightfully on Amazon; if you spot it, report the violation.\par
Would Quests be issued to a villain? Well, he did have a lot of blood on his hands prior to being reined in by the second Quest.\par
“Oh I don’t know about that~” she playfully drew out. “You as good as forced him to confront you about the affair between you and his mother… how ruthless! Such a bully-like act!”\par
“Maybe he shouldn’t have approached me about it then,” Orodan replied. “The whole thing was one big emotional outburst on his end.”\par
Mahari was being playful and melodramatic about it… but she had a point.\par
To Orodan it was being straightforward and direct. But to Novus for whom it was a sensitive matter… it could definitely be seen as domineering and abrasive.\par
Plus, who knew if all the people he had killed across his loops would disagree with the view that he was a villain? Orodan certainly had killed enough people, not that he was squeamish about it.\par
“Sigh… how does Altaj deal with an annoying blabbermouth like you?” Orodan asked with a smirk on his face.\par
“Hey!” Mahari protested without heat. “I might talk a lot, but I’m not annoying. Or at least my brother doesn’t say so. Perhaps you could learn something from him and tone down your browbeating ways of saying things directly to peoples’ faces.”\par
Diplomacy and tact? Orodan wasn’t sure if he would ever possess such things.\par
Dragons and their straightforward ways were so much easier to deal with. Why couldn’t Orodan have just been born a dragon?\par
\par
“With the amount of power you can generate, I genuinely thought you might be a dragon reincarnated into a human body,” Rosvedir said. “But then I saw your utterly atrocious talent in anything related to mana and changed my mind. Are you perhaps descended from a rock? Maybe that explains why your head is so utterly dense to what Hymelrass is explaining.”\par
Classes at the academy had gone well, with Arvayne promising him that a week from now, they would work on skill combinations to create new ones.\par
But training with the dragons… was not going so well.\par
He had the Mana Manipulation skill and he was experienced in using Mana Black Hole… but he just didn’t have a natural talent for mana.\par
Perhaps it was karma for all the derision he had towards cowardly mages?\par
His endless energy and ability to generate mana, while strong even among dragon-kind, simply allowed him to train without interruption. Which dragons could more or less do with the assistance of items anyways.\par
His Mana Manipulation levelled up, but he still felt no closer to acquiring the first level of Draconic Mana Channeling.\par
Titanic reserves and ability to generate mana rapidly were but the base prerequisite to learning the skill. The other thing that mattered was one’s talent and insights into mana.\par
Which given that Orodan had no real mage skills he bothered using in combat… was a bit low.\par
For Orodan the training would be a two part process. The first part involved acquiring Draconic Mana Channeling. The second part involved learning the common Flare skill and using Draconic Mana Channeling to launch a cast of it.\par
He was firmly stuck on step number one however.\par
“Child, heed not this eccentric fool’s words,” Hymelrass interjected. “Focus on the mana pathways within you, mold them to be denser, thicker. Turn them into an ocean, not a mere road.”\par
Easier said than done.\par
Mana flowed through the body using certain natural pathways. The circuits as they were called, were different in every living being, and bloodlines or species mixing could alter them as well.\par
The mortal races in general had thin circuits in comparison to magically inclined monsters. And among the mortal races, humans had average mana talent. So Orodan had his work cut out for him in expanding his circuits.\par
“Perhaps you would see more success if you didn’t insist on this course of deranged training you’re engaging in?” Rosvedir asked. “Your effort in swallowing that gravity stone is admirable, but it barely fit into your tiny gullet. And this… lasso you’re using upon yourself… its effects are quite distracting!”\par
“I don’t know why it bothers you so much,” Orodan replied.\par
His eye exploded out of its socket as necrotic energy spewed out. His flesh decayed, and his bones were rotting from the inside. He looked like a zombie.\par
All the while, his body was under incredible gravitational pressure. Regeneration was strained trying to keep up.\par
As his soul energy flooded the lasso, it focused on necrotic energy. He felt this would be a good resistance skill to focus on.\par
He wore it like a belt around his waist, the end held in his hand as he channeled soul energy into it.\par
He hadn’t yet acquired any further resistance skills over the twelve hours they had been working. But he felt that eventually he would.\par
Of course, twelve hours in the training chamber was equivalent to one hour of real time.\par
The Time Wind dragon flight were named so for a reason. They specialized in chronomancy and wards that provided a powerful time dilation effect.\par
Dragon energy generation abilities meant that they could have a one to twelve ratio for their time dilation wards instead of the one to six that Bluefire held.\par
He was allotted four hours each night, the rest to be spent with Arvayne.\par
But even with this generous time allotment dedicated to learning the dragon arts. Even forty-eight effective hours per session weren’t enough to help him easily make a breakthrough.\par
Twelve more hours passed as he futilely kept trying.\par
“Incredible, I have never seen such an utter lack of talent,” Rosvedir spoke. “Usually those who wish to learn Draconic Mana Channeling come in with some existing understanding of magic. Child… do you have any ranged active combat skills that purely use mana?”\par
“No, why would I need those when I can just close the distance and fight like a warrior?”\par
“You… did Arvayne Firesword truly send us a stone-headed warrior who has never cast a single spell in combat?!” the gravity dragon exclaimed. “Do you not know any spells?”\par
“Do Observe, Identify and Fate Reading count?”\par
“No… they do not. They aren’t active combat skills.”\par
“I’ve used mana in many of my skills before, I have a Mana Manipulation skill of level 41,” Orodan spoke. “What am I missing?”\par
“Because those skills you speak of are likely not purely cast using mana. There is some other component to them, be it the empowerment of an object, analyzing something, or the usage of your body,” Rosvedir explained. He had taken to sitting in on his training sessions with Hymelrass, claiming he was bored. “A purely mana-based skill, would be Fireball.”\par
“I still don’t understand how it would help me,” Orodan replied.\par
Rosvedir sighed and Hymelrass gave the gravity dragon an unamused look. By dragon standards at least.\par
“Rosvedir speaks harshly, but he speaks truthfully. Every person we’ve taught Draconic Mana Channeling to has had an idea about mana circuits and the flow of mana going into an active combat skill,” Hymelrass explained. “Knowing how to cast a Fireball would help you in understanding your own mana circuits and the feeling of a skill that uses only mana and nothing else.”\par
Orodan thought it was hogwash, but he didn’t snub the dragons outright.\par
He knew that dragons themselves didn’t need to know how to cast a Fireball before they learned Draconic Mana Channeling.\par
And while he was a human without the natural talent in learning this skill that a dragon would have… he was still sure there was a way to acquire it without learning spells first.\par
More time passed, and Orodan’s thoughts drifted towards experimentation.\par
He began to consider the Body Tempering skill. His body was now quite strong, each cell was suffused with vitality. If all else was equal, Orodan would be stronger than someone with the same Physical Fitness as him as each level of it went farther for him.\par
And how did he train Body Tempering?\par
By destroying his body, suffusing it with vitality and rebuilding it to be better under pressure.\par
So the two parts of the formula were constant pressure and Regeneration.\par
Why bother molding his existing mana circuits in a safe manner?\par
Why not do things his way?\par
His empowerment skills all activated, and a gigantic amount of mana was poured into Weapon Aura as he tried wrapping it around the entire building they were in.\par
It was a hopeless endeavor, as the building had far too many inhabitants, items and various wards upon it. Orodan would need at least a dozen more action increases before his mind could account for everything within.\par
But that wasn’t the aim of this experiment.\par
His goal now was to strain Weapon Aura so much that its mana requirements became very costly.\par
The skill wasn’t successful in wrapping around anything…\par
…because he was trying to wrap it around everything.\par
His head felt like it was splitting apart as his awareness expanded and he attempted to consider the area beyond the building his weapon too.\par
It was entirely unsuccessful, but the mana cost of the skill was skyrocketing by the second as his attempt continued.\par
Of course, his incredibly high Mana Resistance was quite the barrier to getting his own mana to affect him.\par
So he then used the lasso.\par
The necrotic energy of the lasso was channeled in a focused manner, and it began slowly decaying his mana circuits.\par
And as his mana circuits decayed, Orodan began to feel where the tiny leaks and imperfections were. The weakest parts of his circuits would spring a leak first as they rotted and faded.\par
His vitality and Regeneration worked swiftly to repair the damage, with the intent of rebuilding it stronger.\par
His eyes were glowing white as Eternal Soul Reactor flared to accommodate the monstrous mana costs Weapon Aura was now incurring.\par
This consequently made the endless gravity core in his stomach incredibly heavy, and he collapsed to the ground. But still kept working.\par
Due to not successfully wrapping around anything, Weapon Aura didn’t gain anymore levels from this. But that wasn’t the goal.\par
Slowly, like a crucible, the imperfections in his mana circuits were being worked upon.\par
Orodan not only focused on breaking down his mana circuits and rebuilding them to be stronger. He also worked on slowly widening them through this cycle of destructive regrowth.\par
He lost all sense of what was occurring around him.\par
His only focus was on strengthening the mana circuits and accommodating his body to make them grow wider and thicker. No matter how many times he had to destroy them over and over with necrotic energy from the lasso.\par
At some point, the lasso began to feel quite hot in his hands. His soul energy connection to it was beginning to slightly lower. He felt that if he kept pushing it, it might suffer damage.\par
But, he had finally accomplished what he wanted.\par
His eyes opened, and Rosvedir and Hymelrass were looking at him with expressions of shock.\par
“…maybe he is a dragon after all.”\par
“How did you keep yourself alive while forcibly expanding your mana circuits in such a way?” Hymelrass asked. “I’m aware of your prodigious vitality as we saw during the trial, but to apply it to honing yourself in such a way… the pain must have been incredible.”\par
“My Pain Resistance is at level 78 currently, so that’s not a concern,” Orodan replied. “I didn’t even realize it hurt.”\par
“See?! This is why my proposal to flog the younglings is a good idea Hymelrass!” Rosvedir exclaimed. “I keep telling you that our young are growing up too softly nowadays. They don’t even have level 20 in Pain Resistance and yet he has level 78 at his age? Why back in my day-”\par
“Cease your prattling Rosvedir. Your proposal also involved throwing them off the mountain upon hatching so their natural flight skills would develop,” Hymelrass reprimanded, and then looked to Orodan. “But that level of Pain Resistance is incredible.”\par
“Indeed! I hesitated to ask it, but with such high Pain Resistance and that lasso…” Rosvedir muttered, and Orodan didn’t like where the implication was going. “Boy… are you perhaps a masochist? I’ve heard some among your kind enjoy such perverse things. Worry not! We dragons do not judge… much.”\par
“I am not inclined towards such things you old lizard!” Orodan replied and the gravity dragon simply huffed. “I’ve expanded my mana circuits as much as I feasibly can for now, what’s the next step?”\par
“Now that you have skipped past what I thought would take three months at your previous pace. We can work on teaching you a basic active combat skill, a spell, which you can flood mana into,” Hymelrass remarked. “We’ll have you learn Flare.”\par
Averse as he was to learning ranged spells like a mage, he thought it fair.\par
How hard could learning a common spell be?\par
\par
As Orodan came to learn, it could be very hard.\par
Especially for someone with an atrocious talent in mana.\par
Observe and Identify were quite easy as it involved mana used internally to analyze something.\par
Weapon Aura, even if it used mana, was used to empower a weapon and used his raw unaltered mana. Orodan suspected it fell under the purview of warrior skills, which he had decent talent in.\par
But Flare?\par
It was a common skill. An active combat skill of the branch of fire magic.\par
And it involved something Orodan had never done before. Which was tuning his mana to be fire-aspected before casting the elemental spell. The technique was known as elemental tuning, and it was a requirement for casting any elemental spell.\par
Was this how all elemental magic was cast?\par
Orodan now understood why people stayed within one school of magic for the most part. Even just getting the elemental tuning down for a single element before casting one of the most basic spells… was a lot of work.\par
“I don’t understand why learning Flare is so difficult,” Orodan remarked. “I learned Fate Reading rather easily with a training aid.”\par
“Yes, but there are unfortunately no training aids for learning a spell like Flare,” Hymelrass replied. “The elemental tuning must be done manually, and you have to structure the tuned mana into an offensive spell and fire it.”\par
What had also been explained to him, was that elemental tuning could permanently alter someone’s usage of mana. Mages who learned too many high rarity spells of the same element or levelled existing ones too high… would face a harder time learning other forms of magic.\par
The elemental tuning for opposing elements in particular, became harder as one advanced down a particular path.\par
Some people were gifted of course, and naturally took to an element. Bloodlines could also be a factor. As an example, he learned that the former House Argon had a fire magic Bloodline. Not apparent to the eye, but it explained why the two members he killed so long ago were both fire mages.\par
Calledro’s Average, something Orodan had been able to ignore thanks to his circumstances… was now keenly being felt. Classes would end and he would go to Millennium Roost, and like that four days of training went by. He had spent well over a hundred hours working on the elemental tuning and getting it down.\par
But with the attempt he was currently making, he thought he would have it.\par
Fire-aspected mana flooded Orodan’s hand, and he formed it into the shape of the Flare spell.\par
If he tried, he felt he could cast the spell now… but why not attempt to kill two birds with one stone?\par
Mana flooded through his now widened circuits, and Orodan began calling an utter deluge through himself all at once. It all went towards the Flare building in his hand.\par
This was what he sought to learn.\par
The method through which dragons naturally launched magical attacks which were many times the scale of their mortal counterparts of the same level.\par
This was Draconic Mana Channeling.\par
\textbf{[New Skill (Exquisite) → Draconic Mana Channeling 1]}\par
As the mana continued to flood into Flare, the skill levelled twice.\par
The flickering flame in his hands was supposed to be a common rarity spell. Meant for signaling people or lighting fires.\par
It wasn’t supposed to be the size of a building.\par
Good thing Orodan had Mana Resistance. Any other mage would have been killed or severely injured by this point by their own Flare getting so large.\par
Even Hymelrass looked as though she wanted to stop it, but held back. Rosvedir simply looked on, excitement in his eyes.\par
Finally, the amount of mana flooding the spell reached a critical point, and Orodan felt as though his Mana Manipulation wouldn’t be enough to maintain control.\par
So he threw it into the air.\par
And a quarter of the training chamber was awash with flame.\par
\textbf{[New Skill → Flare 7]}\par
Seven levels in a single cast.\par
A common rarity spell that was meant to send signals, was now a projectile with power equivalent to a magical artillery shot.\par
Draconic Mana Channeling… was an incredibly powerful amplifier.\par
Who knew how far his skills that used mana could go with this skill amplifying them?\par
“Now that’s an explosion worthy of a dragon!”\par
Orodan tuned Rosvedir out.\par
\par
“The dragons tell me you’ve learned their arts. Is that cocky look upon your face the belief that you can now beat me? Bullying your elders isn’t very nice.”\par
“How else will I better myself if I don’t push my limits?” Orodan asked. “Beating up senile old men just happens to be the next benchmark I need to reach.”\par
“Alright then, show this senile old man what you’re capable of with this new skill of yours.”\par
And Orodan obliged.\par
Arvayne’s eyes took on a serious look as eight Flares the size of a building shot towards him. Quadrupled thanks to the Action Increase.\par
Even with just a level 7 Flare, he could now do what was done to him so long ago in Eversong Plaza. Overwhelming and suppressive magical bombardment.\par
The distance immediately closed as Arvayne refused to allow him the luxury of spamming spells. Which was to Orodan’s liking as he disliked fighting from range anyways.\par
Their usual deadly exchange of melee occurred, and Arvayne found that Orodan’s Weapon Aura was incredibly powerful now.\par
It wasn’t his usual shield, that one had been destroyed long ago when fighting the Dweller Worm. But even with Weapon Aura, these new shields of Elite-level craftsmanship would normally be destroyed by Arvayne’s greatsword.\par
But this time, the old man’s sword found no purchase as a titanic amount of mana was pouring into the skill. Draconic Mana Channeling was an amplifier on all skills that used mana.\par
His shield held strong. It rung and eardrum bursting booms echoed with each blocked blow. But the material held true and Arvayne reconsidered slamming his blade against it.\par
Next came Orodan’s return of quadrupled All-Strikes.\par
The legendary rarity active combat skill used mana, soul energy and vitality as fuel. It was an All-Strike in every sense of the term as every energy pool was used.\par
Now, the mana portion of the skill was greatly empowered, and it received an almost half-again increase in power.\par
Unless using Endless Blitz with All-Strikes, something that would nearly kill him. Orodan was always at a disadvantage in every exchange of blows he had with the old man.\par
But for once, his All-Strikes which were empowered by Draconic Mana Channeling, were now forcing the old man to almost stalemate.\par
So he decided to try combining his newly empowered All-Strikes, with Endless Blitz.\par
Everything turned white as his soul energy flared wildly and his body nearly broke down.\par
But in the split second of hundreds of All-Strikes being delivered via Endless Blitz, Arvayne…\par
…was actually losing!\par
And then the fun ended as the old man’s eyes took on a subtle glow.\par
Orodan found himself reforming from the near-puddle of flesh he was turned into shortly after.\par
“Not bad,” Arvayne Firesword spoke as he drank a healing potion to repair from the serious damage he incurred hitting Orodan. “I’ll be taking the frustration of this moment out on you for the rest of your time with me… but not bad at all.”\par
“I actually forced you to tap into the lowest level of your Avatar state!” Orodan excitedly shouted.\par
“Bah! I could still kill you without it… but admittedly, you now have a non-trivial chance of killing me,” the old man retorted. “I only called upon Agathor to put a swift end to your nonsense and to temper your ego.”\par
Arvayne spent the rest of the session brutally reminding Orodan that he didn’t need Agathor’s help to demolish him.\par
But the fights were far more even now. Even if he lost out against the old man’s skills and experience. It was as Arvayne said.\par
Orodan actually had a small chance of winning now if he truly committed to it.\par
With Draconic Mana Channeling at just level 3, Orodan was getting closer and closer to the level of a mortal triple-Grandmaster.\par
A week had now passed during which he acquired Draconic Mana Channeling.\par
Another three weeks now remained before the excavation of the energy well he’d discovered would begin.\par
A team of the Republic’s Grandmasters would descend the hole, and Orodan would naturally accompany Arvayne.\par
He was looking forward to seeing what lay within.\par
Treasure or horror.\par


\section*{Chapter 24 - Skill Combinations \u0026 A Standoff At The Well}
\addcontentsline{toc}{section}{\protect\numberline{}Chapter 24 - Skill Combinations \u0026 A Standoff At The Well}%
\par
Skill combination was quite difficult.\par
As a rule, skill combination always lead to two skills of lower rarity producing one of higher rarity. Not every skill could be combined; and just because two skills sounded similar didn’t mean a combination was possible.\par
Experimentation and coming to an insight which saw the two skills fused together was also key. Simply using them concurrently wasn’t enough. One had to understand both skills thoroughly, grasp what were the essential parts of each, and try to create a new whole that blended together well.\par
The process was meant to be difficult, with the class offered at Bluefire being meant for fourth year students to begin with. And even then, it was a competitive class that required a separate application process to be considered for.\par
Of course, Orodan was working on skill combinations with Arvayne as his mentor.\par
And Orodan’s talent in warrior-related skills was far from average.\par
He had also been working on this combination for a week now.\par
He was sitting in the center of the training chamber, unmoving, as Arvayne sliced, stabbed and tore him apart with deft blade work.\par
In truth, since he wasn’t defending himself, the old man was free to methodically target everywhere he could. Without periodic uses of an enchanted cleaning amulet which drew all the gore within it, the chamber would look ridiculous by now.\par
Pain Resistance was now high enough that Orodan didn’t register the pain of the old man’s blade unless he wanted. So he simply sat in quiet meditation as his body was hacked apart.\par
His goal?\par
To merge Slashing Resistance, Piercing Resistance and Impact Resistance into one.\par
Combining two skills was difficult enough for most, and while there were records of triple skill combinations… it was still rare. Orodan was self-aware about his own monstrous talent in the martial arts by now.\par
It would be a disservice if his first attempt wasn’t at least a triple skill combination.\par
As usual, the old man was chugging an excessive amount of healing potions as he butchered Orodan, the backlash from Warrior’s Reciprocity being strong. However he decided to forgo the glass flasks entirely and now chugged the concoctions directly from a spatial ring. He prepared this ahead of time for the training session.\par
As the blood flowed from his savaged body, Orodan Regenerated, and he meditated.\par
Sometimes his head would be destroyed, but his Unyielding Vitality was now strong enough that he could think without his physical brain. At least for a decent amount of time. It was as though his consciousness existed in his vitality, which was spread throughout his whole being.\par
Orodan’s ruminations continued, uninterrupted by the damage he suffered.\par
Piercing stabs, slashing cuts, and crushing impacts. These weren’t elemental in nature, but they were… physical.\par
What he needed then was a skill which synergized all three.\par
Piercing Resistance involved mentally commanding his skin and flesh to harden.\par
During his repeated deaths against the undead Demonic Berserker, Orodan realized that mentally structuring his skin and flesh to turn stabbing blows aside was the best method of diverting them.\par
As it had savaged him, Orodan realized that cutting attacks were best resisted through focusing on making his skin harder and almost slippery, causing the blows to not cut as deep.\par
As he was battered by the explosions of the mages in Eversong Plaza, he realized that Impacts were best resisted by counteracting the force by going with it. By making himself heavier and his flesh almost absorptive of impact.\par
But, to combine all that?\par
He would need to structure the body to resist penetrating attacks, harden it against slashing, while also resisting impacts through rolling with the force and absorbing them.\par
His skills, were essentially a form of Damage Mitigation… and that skill was the key piece.\par
A body which could resist all physical damage, while also mitigating whatever got through.\par
The three resistance skills began showing an unnatural synergy together… and the warrior within who was returning Arvayne’s attacks all this time, whispered insights to him.\par
Orodan and the warrior worked together, and soon an equilibrium was reached.\par
The warrior posed a finished product to Orodan, it would be the combination of the three skills that he was targeting. Piercing Resistance, Slashing Resistance and Impact Resistance. It would be an Exquisite rarity skill.\par
But Orodan refused!\par
He argued with the inner spirit within, and decided to venture further.\par
The warrior remained silent, almost irritated that Orodan had spurned it. But it looked on eagerly.\par
But truthfully, Orodan didn’t need its help, as it was missing the key piece to wrap it all together.\par
Damage Mitigation.\par
The warrior was satisfied with what it saw. With what Orodan came up with after the week of constant training.\par
\textbf{[Skill Combination - Piercing Resistance 59 + Slashing Resistance 60 + Impact Resistance 66 + Damage Mitigation 78 → Bulwark Physical Resistance 65 (Legendary)]}\par
The difference was immediately apparent.\par
The old man still took the same amount of damage from delivering his brutal blows upon Orodan. But now the damage received was reduced by almost two thirds!\par
“What the… did you succeed?” Arvayne asked.\par
“Yes. In fact I might have exceeded expectations in the attempt,” Orodan replied.\par
“As if you don’t do enough of that already… stupid prodigies,” the old man muttered. “So given that you combined three skills into one, the rarity should be exquisite.”\par
“Actually, I combined four skills into one… the rarity is legendary.”\par
To his credit, the old man simply paused for a half second before speaking.\par
“Of course you did. Why am I even surprised?” the man remarked. “You kill a spider dragon, you claim the top ranking in the trial of abundance against dragons… and now you combine four skills into one on your first attempt. What next? Shall we put a crown upon your head and declare you the king of the world?”\par
“That sounds exhausting and better suited to a grumpy old worrywart like you,” Orodan quipped. “Being king would require too much thinking and politics for my taste.”\par
“Heh… now you know why Grandmasters don’t officially announce their existence or bother taking important political positions,” the old man spoke. “Still… it’s as though you’re some kind of anomaly. The more time I spend training you, the more it becomes clear that you exceed all known bounds of common sense. What do you really intend to do once this is all over Orodan?”\par
His mentor’s tone was dead serious for the first time.\par
“I don’t know what that question is supposed to mean. Right now, the insurmountable wall that is the Eldritch Avatar stands before me. I’m not even a match for a single Chosen Avatar just yet, and I’m given a Quest to defeat one that is an Avatar for three separate Eldritch Gods?” Orodan asked. “I don’t even have the time to think so far in the future. I do not know what I’ll do.”\par
“What I’m trying to say is… perhaps you should take things a bit slower. Your potential is incredible and your growth could very well be limitless,” the old man carefully spoke, and his face grew a little worried. “Perhaps even attaining Godhood isn’t out of the question for you, so when it comes to receiving a Blessing near the end of this loop you sh-”\par
The old man’s eyes took on a subtle glow as his words were interrupted.\par
It was the Inuanan God of War who spoke next.\par
\textbf{“What my loyal and diligent Chosen One means to say, Orodan Wainwright… is that you should continue on your current course. You are a true warrior, and the glory you may claim in the future is limitless.”}\par
That was quite strange.\par
Orodan could be said to be stupid.\par
But being illiterate and stubborn wasn’t mutually exclusive to being street smart.\par
And that sounded very much like the old man had just been silenced.\par
Maybe it was best to hold off on receiving a Blessing from Agathor until he knew more about what it might entail?\par
\textbf{“From now on, I shall handle your training. I believe you have advanced quite incredibly within the span of almost two months. Such prodigious talent would be best suited by my own guidance.”}\par
“I see… and what would this guidance involve?” Orodan asked.\par
\textbf{“Training in various martial arts and perhaps even learning to call upon my power yourself… if you wish it.”}\par
“And if I say I don’t want to become host to an Avatar?”\par
\textbf{“I would lament your short-sightedness and lose some respect for you. Understandable, as not every warrior can dare to reach for true eternal glory. But you can do as you wish.”}\par
That sounded nice to Orodan. A little too nice.\par
The training session ended soon after.\par
Agathor claimed he had some business to deal with, and the God of War left while still in possession of the old man’s body. Although Agathor did say that Arvayne was expecting him in Jerestir two weeks from now.\par
Orodan never once let up the Fate Disconnect skill from that point onwards. Not since he knew that Gods couldn't grant Blessings while it was active.\par
There were two weeks left till the descent into the energy well, and Orodan would train by himself if needed.\par
Something told him he wouldn’t get the chance to speak to the old man again till then.\par
\par
The old man never sought him out again during that time.\par
Orodan was slightly worried about whether the God of War had harmed his mentor. But then let the concern go upon calculating that powerful Chosen were difficult to come across.\par
Arvayne Firesword wasn’t the only Chosen One of Agathor in the world. The Inuanan God of War had other Chosen in Novarria and the Eastern Kingdoms. But they weren’t so numerous that he could afford to kill them without weakening his influence and losing powerful assets.\par
And Arvayne Firesword was Agathor's most powerful Chosen in the Republic.\par
So Orodan focused, and he trained.\par
He worked by himself over the course of the two weeks in-between attending classes.\par
While Arvayne wasn’t available to be his sparring partner any longer, he learned a nifty trick.\par
His action increase selves could hit him. Even if they lasted for a single second, he could continuously re-trigger them. This could create the effect of constant battle against his own ‘clones’.\par
Admittedly, it was a strange and somewhat janky method where he wasn’t able to have any meaningful melee exchanges. Each action increase clone lasted for only a second.\par
But this was compensated by the fact that he could spawn upto three of them and have them blitz him at the same time. And when he could launch hundreds of attacks a second. One second could fit a surprising amount of self-combat.\par
But, it was still an inferior method compared to having a training partner stronger than him.\par
So the next skill combination he achieved took more time. A triple combination borne from two weeks of effort.\par
Evading attacks that came his way, parrying ones that did in a manner that caused the attacker to become imbalanced. And being able to withstand incredible pressure and frequency of attacks. He was basically, unassailable within the same level.\par
\textbf{[Skill Combination - Evasiveness 65 + Perfect Parry 71 + Impregnable Bladewall 72 → Unassailable Fortress 69 (Legendary)]}\par
It was a fantastic defensive skill which allowed him to condense the effects of the skills he used in its creation.\par
As Orodan had come to learn, skill combinations removed the skills used in the combination from his Status altogether.\par
The thing was getting rather clunky and unsightly nowadays. So the more skill combinations, the better.\par
The level of the resulting skill would always be the average of the combining skills. And the rarity would be a step higher than the highest rarity skill used. In other words, skill combinations were only a benefit.\par
From the two results of skill combination, he would say the efficacy of the resulting skill was an almost half-again boost over simply using the combinatory skills in tandem.\par
But now, two weeks had passed, and it was time to make way for Jerestir, where the newly excavated energy well was waiting to be delved. A team of the Republic’s Grandmasters would be descending the shaft.\par
Orodan left the training chamber, and made his way to the landing zone of Bluefire where he would have a griffin waiting for him. Courtesy of Burgher Ignatius Firesword.\par
He made way and arrived, to find a familiar face.\par
“How come I always find you at the landing zone?” Orodan asked. “I feel this is a typical meeting point for us.”\par
“I could say the same for you Orodan! You’re always gallivanting about like some big shot, flying in and out on griffins,” the excitable girl exclaimed and then had a frown on her face. “Maybe this is all some conspiracy of yours to follow me around!”\par
Well… she was the first one here.\par
“I never asked why you’re here so early all the time,” Orodan remarked. “I saw Altaj here early as well. Some sort of morning flight to warm up?”\par
“Yes, that too… but mainly because my companion and his brother often travel back to their clan during this time to socialize and receive guidance from their elders,” Mahari spoke. “Just like we train, so do pegasi. Their elders provide mentorship and lessons to the promising younger ones among them. Frankly, I got lucky bonding with my companion… he has a Master-level pegasus as his teacher. They say he’ll grow up to be quite fierce.”\par
It explained why she had no pegasi around her currently.\par
“Interesting, so he’s some sort of prodigy then?” Orodan asked.\par
“Quite! He’s very fast and has some pretty high rarity skills for a pegasus of his age,” Mahari explained. “But if you want to see a real prodigy, my brother’s pegasus Ostronor is something else. He’s one of the main reasons we’re here and not at Rubywater back home.”\par
“Now that sounds like a story to tell.”\par
“Oh, it’s quite the tale back home. Altaj doesn’t like being the center of attention much though, he’s always been shy of such things,” Mahari elaborated. “Ostronor is one of the greatest pegasi born in many generations. He’s at the late Elite-level but could likely fight a Grandmaster evenly… and he decided to bond with my brother Altaj when he was a child, instead of the heir from the main line of our house.”The narrative has been illicitly obtained; should you discover it on Amazon, report the violation.\par
Orodan didn’t miss how Mahari’s face changed when she spoke about the main line. And for once he decided to ask.\par
“From the times I’ve heard you talk about it, you don’t sound very happy about the main line of your house,” Orodan remarked. “If I recall, you said they’re treated like the golden children?”\par
“I… don’t usually like talking about it. Altaj even less so. But, we’re friends and you’ve been far less nosy than the other students,” she added. “It’s not as conspiratorial of a tale as you’d think.”\par
“You don’t have to talk about it if you don’t want to. I have enough things of my own that people are always trying to badger me about,” Orodan assuaged. “I wasn’t aware that you get badgered by students about it though.”\par
“Well, of course. House Vedharna might be a border house, but our ancestor is probably one of the strongest people in the world,” Mahari spoke. “His shield has no equal. And he’s friends with the benevolent Sarastuga, the glorious lion that guards our people.”\par
A shield wielding man? Friends with that lion?\par
Orodan vaguely recalled seeing such a figure struggle valiantly against the Eldritch Avatar. He was one of the few to make it to the very end when most others had fallen. He was likely even more impressive than Mahari’s words could do justice. Especially if he was one of the final four remaining who fought the Eldritch Avatar.\par
“Hmm… I bet he’s quite the powerhouse,” Orodan muttered to himself, but gestured Mahari to continue.\par
“Anyways, long story short. House Vedharna’s main line are a bunch of arrogant jerks who’re still angry that Ostronor chose my brother as a companion rather than the noble and prophesied Akelrim Ilo Vedharna, the ‘golden heir’,” she explained. “To avoid the risk of any foul play against my brother and the risk of subsequently offending the pegasi clans, the house sent us to Bluefire, away from home.”\par
“I’m sorry… that does sound annoying. Why not grow strong and then return to crush their heads beneath your heels?” Orodan asked.\par
“What do you think I’m here for!? To knit dresses and cook meals?”\par
Orodan admitted he couldn’t see Mahari sitting still long enough to ever do either of those things. That she was dabbling in Alchemy was wondrous enough.\par
“Alright, alright… I get it,” Orodan said, raising his arms in surrender. “I assume this Akelrim isn’t a nice character?”\par
“It’s not that he’s an abrasive bully, but that he just has no time for the likes of us,” Mahari explained. “I almost wish it was easier to hate him… but Akelrim didn’t even care when Ostronor picked my brother. He’s more focused on his own path to personal strength. He’s strong enough to give a newly advanced Grandmaster a run for their money, and only at the Elite-level too. He’s without a doubt Rubywater’s strongest student and a monster in his generation like you are.”\par
Sounded like a fun fight to Orodan.\par
“But, I presume your house uses him as the point of contention to send you here? How does that make sense when the man himself bears no ill will?” Orodan asked. “Unless he has some sycophantic followers who would do desperate things to curry favor from him?”\par
Mahari resentfully nodded.\par
“Precisely so… thus we’re stuck in Bluefire,” Mahari spoke bitterly. “Not to say this isn’t a nice place and we haven’t met pleasant people such as you. But it isn’t home.”\par
“I think I understand. I quite miss my old hovel in Ogdenborough,” Orodan related. “Sleeping in all these new guest manors and lodgings the Burgher and the academy provide me just doesn’t feel right.”\par
Mahari looked at him…\par
…and she laughed.\par
“Oh my! Here I am complaining about my homesick woes while you were struggling in one of the poorest areas in the Republic,” Mahari remarked. “I apologize Orodan. I’m not laughing at you, rather at the absurdity of my own situation. You’ve really helped put things into perspective for me with your words… for a straightforward blunt man as yourself, you’re surprisingly keen and wise when you want to be.”\par
“Huh?”\par
“Oh, you need not play stupid. Accept the praise!”\par
Orodan didn’t know what she was talking about! He really had tried to make her feel a bit better by relating about his experience with all these overly gaudy lodgings he was provided.\par
Was it something profound to say he missed his old hovel?\par
It had been so long since he cleaned the place.\par
It was his!\par
\par
Energy wells were coveted national treasures. They had rare resources that could only be acquired within. World energy practically flooded from energy wells, and even if it was invisible to the eye it still suffused the environment for many miles.\par
Jerestir’s existing magical trees and plant reserves were likely due to the previously undiscovered well.\par
The only other known energy well in the Republic was at the center of Anthus. A city which had defenses comparable to Karilsgard itself.\par
So it stood to reason, that the discovery of a new one in the border town of Jerestir would cause much upheaval.\par
It went without saying that the excavation was as prompt as could be. But the real reason it had taken almost two entire months to excavate the path all the way to the opening, was that new path was reinforced beyond measure.\par
Shockwaves from fighting collapsing the tunnels leading out would no longer be an issue. The walls could take the blows of a Grandmaster and there were additional reinforcing columns and pillars every few feet.\par
Orodan suspected that attacks which destroyed the entire surface town of Jerestir would still leave these new tunnels untouched.\par
But energy wells were not only coveted by the mortal races, but by monsters as well.\par
He stood alongside Burgher Ignatius Firesword as he received the report from the Republic’s survey team.\par
In truth the Burgher, a mere Elite, was woefully unqualified to be present for such a report. But his position as the nominal head of House Firesword meant that he was in charge of a lot of background support.\par
Additionally, the excavated path to the energy well ran through his mines. And a decent portion of the town of Jerestir was under his control. The only other competitor of note being House Simarji who were quite friendly with House Firesword.\par
So while the man was rather underpowered in battle, he still featured prominently in the administrative side of things.\par
“Mister Wainwright! Burgher Ignatius!” the frantic scout greeted, his eyes particularly widening at the sight of Orodan. “Sirs, the survey team and scouts report that the situation is stable for now, but it could deteriorate at any moment.”\par
“What do you mean it could deteriorate?” Orodan asked. “I was under the impression that even during excavation there was a rather heavily armed force present here at all times? Unless… something from below might crawl upwards now that we’ve fully excavated the opening?”\par
“Precisely so sir!” the scout dutifully replied. “The war party we have on standby consists of multiple Masters and decent magical artillery support, but that’s mainly to deter the Novarrians from being opportunistic.”\par
That was another dimension of the situation at Jerestir.\par
The discovery of the energy well spread quickly, within the Republic and without.\par
For the Empire of Novarria that bordered the Republic, a newly discovered energy well in the border town of Jerestir could provoke opportunism.\par
The Republic’s military presence on the surface was thus quite heavy. Both to defend against the constant monster attacks from minor critters during excavation, and to dissuade the covetous Novarrians.\par
The ancient war machine under Mount Castarian, while a unique opportunity to open a permanent passage to the hells, wasn’t as valuable as the proven wealth that an energy well could generate for a nation.\par
Thus, the war party consisted of many Master-level individuals. Even the High-Burgher, the nominal head of the Republic’s council, was present. It was a far cry and a massive step up in force deployment from what he’d seen in regards to Eversong Plaza where no Republican Masters had shown up in response.\par
The Republic considered energy wells a big deal, and were willing to deploy force to defend them.\par
“Have the Novarrians tried anything?” Orodan asked.\par
“No sir, thankfully they’ve just increased their scouting parties and have a decent force on their side of the border like we do,” the man replied. “Admittedly, their beast tamers have tried sending familiars to spy on us from the sky or by hiding among the foliage, but our psionics sniffed them out.”\par
“Good. And the energy well itself? What’s the situation down there?” the Burgher interjected.\par
“Sir… the situation must have changed from when Mister Wainwright delved downwards. There are some new creatures that our earth mages and sensory specialists can detect,” the man spoke with a bit of fear. “A colony of ants attempted to charge upwards from the lower levels of the well, but they looked like they were running from something. We captured them and they told us that they were the last survivors of their colony. They were running from… a Death Roach.”\par
A Death Roach? Would he finally get the chance to face one down?\par
Orodan’s blood boiled in excitement.\par
In contrast the Burgher’s face paled and the man had a look of genuine fear on his face.\par
“Surely they aren’t as bad as the stories make them out to be,” Orodan remarked.\par
“My young friend… your prodigious talent and heroic disposition are qualities not shared by everyone else,” the man muttered. “Death Roaches are responsible for entire war parties of Masters going missing. I know you’re someone whose power approaches that of the ancestor… but I still bid you be cautious.”\par
“I make no promises… but I have things to live for yet, so I’ll do my best,” Orodan weakly reassured. “Anyhow, do we have some kind of tracking of its current whereabouts?”\par
“Yes sir, the Cathedral’s diviners have caught sight of it in the tapestry of fate and are attempting to monitor it as we speak. Although it's flitting in and out of the depth where they lose sight due to the world energy interference,” the man spoke and Orodan bade him to lead the way to them.\par
They walked towards a somewhat opulent tent, in typical Cathedral fashion. Two guards dressed in ornate armor guarded the entrance, although they parted upon seeing Orodan.\par
Inside were almost a dozen diviners using a variety of instruments. It looked like some sort of field command center for the diviners who were furiously working. Assistants waltzed about and artificers were monitoring the devices they were using.\par
Orodan had never seen diviners work together or what their work spaces looked like, so to him it was somewhat eye opening.\par
On a raised platform above, stood Lady Lakshiya, the High-Oracle of the Cathedral of Karilsgard. A famous Favored, and host to the Avatar of Ilyatana for many loops where the Goddess plagued Orodan.\par
He could probably kill her if she was in her Avatar state now, even if it would still be an uphill battle. Although Alcianne Rockwood and the two other Grandmasters standing next to her would complicate the matter.\par
And below, were diviners working on various orbs, assisting the High-Oracle as her eyes glowed. One of these diviners… was Katareya Eldragon.\par
Who had stopped working for a moment to look right at Orodan.\par
How awkward. Had Novus perhaps spoken to her about their interaction?\par
To her credit, the woman’s face betrayed no emotions and she kept a strictly business persona moving forward.\par
Speaking to her would put the woman in an uncomfortable position, and Orodan was more interested in getting the details directly from the High-Oracle.\par
He marched up to the platform and Alcianne Rockwood gave him a wave.\par
“Orodan Wainwright, I would have ordered you dragged here myself if you hadn’t showed up,” the old brawny woman spoke. “I hear you caused a ruckus with the Time Wind, good job. Those dragons could use a little humility.”\par
“I suppose I did, they challenged me at a specialty of mine,” Orodan replied. “I don’t suppose you’ve seen or heard of Arvayne Firesword in the last two weeks have you?”\par
“No? That old uptight fool has a habit of disappearing for months on end… ever since he started kissing Agathor’s arse many years ago,” Alcianne replied. “Did your mentor abandon you? My offer still stands you know? I’ve been looking into you more, and Halor is very impressed. He’d offer you training and assistance without any strings attached. I know Arvayne’s gotten his hands on you… but just make an informed decision before committing to Agathor.”\par
“You speak about Agathor as though I should be wary of him, why? The Cathedral and the books don’t say anything of concern,” Orodan remarked.\par
“Look… you’re Arvayne’s student, so I can’t go around trying to poach you too directly, but you should know that there’s a reason you see so many priests of Agathor and Ilyatana going around. The Cathedral won’t say this as they don’t like to promote distrust of the Gods or strife between followers of the Prime Five but-”\par
The tent flap opened, and an old man walked in.\par
His mentor who had bailed on him for two weeks had returned.\par
“Old man!” Orodan exclaimed. “Where have you been?”\par
“Boy… I’ve been busy. Nothing else to it,” the old man replied.\par
Orodan looked at him expectantly, and waited.\par
When no further answer came, Orodan said nothing himself.\par
There was definitely some sort of divine strong-arming going on.\par
Agathor was looking less trustworthy by the second. And his mentor Arvayne Firesword might be compromised.\par
“Revered ancients and young hero, I am honored to have you here,” Lady Lakshiya spoke. “Allow me to give you an update on the Death Roach and its trajectory.”\par
“Spare us the pleasantries, spit it out,” spoke Alcianne.\par
The High-Oracle couldn’t get offended even if she wanted to. Her senior, the Chosen of Ilyatana, would be beaten to a pulp if the man tried fighting Alcianne Rockwood. She had no backing to take offense from the blunt manners of the Chosen of Halor.\par
“As you wish my lady…” she muttered. “The Death Roach… is suspected to be at least a dual-Grandmaster. It is currently roaming about the lower portions of the energy well, not trending upwards. We lose sight of it at times when it ventures too deep.”\par
“Dual-Grandmaster? For a Death Roach to be that strong… if it dared approach the surface the world might even issue a Quest,” Arvayne Firesword muttered. “Perhaps we should bait it into rising upwards, young Orodan here might be able to receive a great reward from its defeat.”\par
Even Orodan wouldn’t have thought of that. It sounded like a great idea!\par
But coming from Arvayne Firesword, it sounded unnatural.\par
Orodan frowned at his mentor. He knew something was wrong with the man, but this as good as confirmed it. The old man, the very soul of caution… would never suggest something so reckless.\par
“Oh! So now you want to suddenly be a little daring Arvayne?” Alcianne derisively spat with a sharp look of her own. “Is this your attempt at making up for your past sins? Or have you gone farther than simply kissing Agathor’s ass cheeks?”\par
The banter might have sounded humorous, but it was the farthest from it.\par
Arvayne’s eyes spoke deadly violence, and even Alcianne looked as though she wanted to fight.\par
The standoff between the two continued for a while longer until the fizzle of a space portal opening up was heard. And a man stepped through.\par
Blue robes, long white beard and eyes that spoke of an immense wisdom.\par
The man had also somehow bypassed the anti-teleportation wards that should have been in effect around Jerestir.\par
“Destartes… since when have you been capable of doing that?” Arvayne sharply demanded. “How did you bypass the wards?”\par
“A simple affair once I have enough mana to brute force a needle sized portal directly to the ward’s power source. An emplaced mana siphoning device to drain the wards following that is rather trivial,” the old wizard explained. “Worry not, I’ve rebuilt the wards… with a slight entryway for myself of course.”\par
“You and your experiments… why not just punch things?” Alcianne asked with a grin.\par
“Now that just sounds dreadfully exhausting,” the old wizard Destartes spoke. “But is this Arvayne Firesword’s new protégé I see? I thought I had a tremendous mana pool for besting a Master-level dragon in that trial… but you really went ahead and just beat the whole thing?”\par
“It wasn’t too hard given that I had a Mythical skill meant for such contests,” Orodan replied.\par
“Of course you have a Mythical skill. It’d explain why the old zealot here has you as his student,” Destartes replied. “Has he told you about-”\par
“Enough! Destartes, stop meddling!” Arvayne roared.\par
Both Alcianne and Destartes now looked at the furious Arvayne with suspicion in their eyes. As did Orodan.\par
Before anything further could come of it however, the clarinets outside rang.\par
All parties agreed to shelve the conversation for later as they stepped outside.\par
A messenger spoke.\par
“My lords and ladies! Novarrians approach the town, they seek a meeting!”\par
\par
The Grandmasters of the Republic were gathered on one side, the Novarrian party on the other.\par
Despite them being nominal enemies, open war wasn’t the current diplomatic state of affairs. Furthermore, many of the Grandmasters knew each other from before the Liberation War.\par
To Grandmasters, what did a mere Liberation War a hundred and twenty years ago mean to friendships that were centuries long?\par
Orodan felt that nearly a dozen people on the Novarrian side were Grandmaster-level individuals. Matching the roughly dozen or so Grandmasters of their own. He instinctively felt that at least three of them in particular were quite deadly as they were giving him a dangerous feeling.\par
Two of them were old and decrepit looking. But the last one… was an almost middle aged, but still youthful looking man.\par
Alcianne Rockwood kept a wary gaze on this man.\par
“Alcianne, you’re looking quite healthy and unburdened,” the younger man spoke, taking the lead among the Novarrians. “We simply came by to pay our respects to the fortunate Republic who uncovered yet another energy well in their bountiful territory. Truly… such good fortune.”\par
“What do you want Demosthenos,” Alcianne spat. “Unless you’ve come looking for a fight, we don’t have much to say to one another.”\par
“A fight? That’d be unfair considering I sent you running the last time you tried causing trouble in my city,” the man known as Demosthenos spoke. “How did you lift the curse anyways? Ilogaji isn’t yet good enough to concoct a potion of curse-dispelling that works on one of mine. Unless of course… those far-fetched rumors I’ve been hearing are actually true?”\par
The man spoke with an exaggerated flourish and gasp.\par
“Fuck off! You should’ve stayed dead when you died the first time,” the burly woman said in a moment of heat. “We have enough military power here to send you packing, and you’ll take heavy casualties too. The Time Wind and Eastern Kingdoms are also ready to respond quickly… so reconsider if you've come here seeking trouble.”\par
“Now why would I be so rude as to rush into your quaint little border town and trash the place?” the Novarrian asked. “Why, after someone tried rushing into Novar’s Peak and rampaging during the Liberation War, I put a stop to them myself.”\par
Alcianne’s fist clenched as the man kept goading her.\par
The Liberation War? Could he be…?\par
“Enough, what do you want?”\par
“Nothing but the pleasure of a friendly visit and a reminder that the resources you find within the energy well should still be open to fair trade and bidding from us, as per the Treaty of Oxraan,” Demosthenos spoke. “Of course, I hope you’ll honor this treaty… unlike the Grandmaster non-interference pact which I’m certain was broken when a number of our Masters were killed underneath Mount Castarian.”\par
“Demosthenos, we’ve been through enough mutual truth-verifying sessions with skills and Blessings involved,” Destartes spoke. “I think we both know that we didn’t send any Grandmaster to interfere in the conflict between our Masters and yours.”\par
“I want to believe you… but the wounds on Duke Arestos suggest he was overwhelmed with raw power. For someone who was to advance to the Grandmaster-level in a century, he was quite talented,” Demosthenos spoke. “How else would a Master of his caliber be overpowered besides by a Grandmaster? Your High-Burgher wasn’t nearby, and no known opponents of his caliber were around.”\par
“And how is that our problem?” Alcianne sharply asked. “If he died to someone we don’t know about that can only be his problem.”\par
“Correct, hence I’ve begun to believe the crazy rumors going around and have an insane theory in my mind… that there’s this monstrous young prodigy who sprung up all of a sudden,” the Novarrian began. “And it’s this incredible young man who slew our Duke Arestos and then disabled the ancient machine. I also hear that this man slew a dweller worm, killed a spider dragon and is responsible for lifting your curse Alcianne. Considering you have only one young man standing up here with you amidst a gathering of old fogeys, I even daresay that this is him. Isn’t that right, Orodan Wainwright?”\par
Orodan suddenly felt very seen.\par
The Novarrian’s eyes were on him.\par
Orodan stared back and met Demosthenos’s gaze.\par
“You know my name, but I don’t think you gave me yours,” Orodan spoke.\par
“Well… much like yourself there are rumors surrounding me. Mostly nonsensical of course!” the man began. “Some say I’m a reincarnator, others say I’m the greatest curse master in history. I say that they’re correct on both those counts. Some knew me as the shadow emperor eleven-thousand years ago… others call me that now. I am Demosthenos Albathrax, advisor to the Emperor. And you greatly interest me my young friend.”\par
A bit long-winded, Orodan thought.\par
“Well, I have no interest in you… except perhaps fighting one day,” Orodan said with an excited grin.\par
“Ask that brutish woman how it went for her a hundred and twenty years ago,” the reincarnator remarked. “I see in your eyes that you’re a bit of a lunatic though… odd to see that in one so young. Quite powerful too from the feeling I get. Are you perhaps reborn like myself? What barbarian warlord were you in your past life?”\par
“None. I’m not a reincarnator,” Orodan replied.\par
“Hmm… interesting. If true, it’d make you a talent the likes of which even I haven’t seen,” Demosthenos spoke. “Why waste your time with the weaklings in this little pretend-Republic? If you joined Novarria, the Empire could properly guide a powerful young man such as yourself. You would have access to every possible luxury, treasure and rare item to help you along your path to power that you can think of.”\par
Orodan actually considered it for a moment.\par
Maybe not in this loop.\par
But down the line, it didn’t sound like a bad idea.\par
But for now, his lot was with the Republic.\par
“I’m afraid not. I have business here that needs to be wrapped up,” Orodan spoke. “The Republic is my home, so I also wouldn’t be too keen on fighting against it.”\par
If Orodan were to ever try throwing in with the Novarrians down the line, it would be in a non-military role. Or at least one that didn’t involve waging war against House Firesword or Simarji.\par
Killing was one thing. But harming people who'd done him good turns was another.\par
“Fair enough, I tried,” the man spoke. “That will be all on my end, I simply came by to leave you fair old coots of the Republic with the reminder about the Treaty. Getting to meet you was the icing on the cake Orodan Wainwright. For your sake, I hope we don’t meet in battle next time.”\par
The man said and turned away.\par
Orodan acutely felt the dangerous aura the reincarnator gave off…\par
…and it only made his blood sing for battle!\par
That man sent the Avatar of Halor running… just how strong was this reincarnator Demosthenos Albathrax? Orodan hoped to one day test that.\par
But for now, other matters awaited.\par
Descending the energy well, dealing with a dual-Grandmaster Death Roach and navigating his relationship with his altered mentor came first.\par
The first two sounded fun.\par
Orodan wasn’t too sure about how he’d deal with the third.\par


\end{document}
